### 2018-11-10 paper/main.tex
piling up some text

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

\input{packages}
\input{macros}

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PL'18]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2018}{New York, NY, USA}
\acmYear{2018}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from traditional SIGPLAN
%% proceedings format to PACMPL format must update the
%% '\documentclass' and topmatter commands above; see
%% 'acmart-pacmpl-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% Title information
\title{The Impact of Critical Slicing in SFL\Comment{tatistical Fault Localization}}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}                    %% \country is recommended
}
\email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{First2 Last2}
\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}                   %% \country is recommended
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}

%% PROBLEM MOTIVATION
Statistical Fault Localization (\sfl{})~\cite{7390282} is a popular
technique for automated software debugging.  It computes
suspiciousness values associated with program entities (e.g., basic
blocks) using coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in
decreasing order of suspiciousness.  \sfl{} received tremendous
attention over the years, but its applicability to support debugging
remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been shown
useful in supporting downstream analyses, such as Automated Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for likely fixes to
likely buggy statements.  Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

%Recent \apr{} techniques use \sfl{} to guide
%the search for repairs .

%% \Fix{Revise this $\rightarrow$} Mao and Wang
%% \cite{lei-mao-dai-wang-2012} had promising results compared to \sfl{}
%% state of the art techniques, such as Tarantula [cite] and Ochiai
%% [cite], concerning the relative percentage of the code above the
%% fault. Prior work used the same measurement approach
%% \cite{santelices-jones-yu-harrold-2009,wang-cheung-chan-zhang-2009,jones-2005}.
%% However, the problem with this approach lies in the effort to find the
%% defect, as shown on Parnin and Orso's study \cite{parnin-orso-2011},
%% in which a percentage rank does not scale with the size of a
%% codebase. For example, if a fault statement is ranked on the 83rd
%% position as a result of a \sfl{} technique, the percentage rank using
%% a codebase of 8300 LOC is only 1\%, with the amount of absolute lines
%% of code to be examined not being considered.  This can result in
%% millions of lines of code to be analysed, proving that a percentage
%% rank is not a practical evaluation metric
%% \cite{ang-perez-van-deursen-rui-2017}.  \Fix{end here}

\Fix{...too big of a jump...}

Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
technique for automated debugging \Fix{is it popular? I would rather say that
it is what best models developers thinking.}. It takes as input a failing test
and produces on output a set of statements (the slice) that influences
the evaluation of the fault-revealing assertion (the slice criterion).
This paper reports the results of an empirical study to evaluate the
impact of Dynamic Slicing (\ds{}) to improve \sfl{}.The intuition for
the \comb{} combination is that several highly ranked statements,
albeit covered by failing executions, may be unrelated to the
fault. Prior work reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012}.
For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
rankings when using dynamic slicing in combination with \sfl{} versus
plain \sfl{}. We found surprising that, despite these findings,
reported nearly 5 years ago, no tool or client analysis use this
combination today. One hypothesis to explain that observation is that
results reported in prior work are not as good as it seems. Prior
research evaluated \sfl{} using relative metrics, based on the
position of the first faulty statements found in the ranking relative
to the total number of ranking statements, which is often a very high
number. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact encouraging developers to adopt precise metrics
such as top@n
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. The
goal of this paper is to reassess whether the \comb{} combination is
worthwhile under the light of this metric. Developers of techniques
such as \acrAbrev{} would benefit from these results~---~either to
improve their results or to be aware they should not invest on this
integration.

%% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}

\Fix{Mention the research questions at some point, plus contributions.}

\section{Dynamic Slicing}
\label{sec:slicing}

Program slicing is a program understanding method to identify the
relevant parts of the program with respect to given points of
interest.  This paper focuses on dynamic slicing~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~for its
application in automated software
debugging~\cite{Binkley:2014:OLP:2635868.2635893}.  To select a slicer
implementation to run our experiments, we considered two criteria:
robustness as to support non-trivial programs and efficiency as to
support execution of our experiments in reasonable time.
Unfortunately, we failed to find public implementations satisfying
these criteria.

For those reasons, we decided to implement a critical slicer for Java,
which is the language of the subjects in our dataset, \dfj{}. We
focused on Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310} for
its simplicity.\Comment{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\Comment{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices\footnote{In the original implementation, critical
  slicing was not guaranteed to be executable.  Above we refer to the
  basic strategy of deleting statement and checking outcomes.}.
Critical Slicing slices the program by deleting statements such that
the sliced program preserves critical observations (\eg{}, assertion
violations).  The output we used to determine equivalence of the
original failing execution and the sliced failing execution was the
stack trace produced by the assertion violation.  It is important to
note that Binkley \etal{} recently proposed the critical slicer
ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
efficiency (important to run our experiments) for generality. Some of
the slicing jobs we ran on ORBS took hours to run. For example,
\Fix{...elaborate...}

The principle of Critical Slicing is rather simple, consisting of
mutating the program and observing the output. Despite that,
optimizations are important to make a Critical Slicing implementation
efficient. We describe the optimizations we used in the following.

%% \vspace{1ex}\noindent\textbf{Blackbox slicing.} Removing statements
%% from the program is necessary to discover whether it is essential
%% to the execution or not. For that reason, we compare the test stack
%% trace to look for changes in the output. Considering one execution,
%% if one line of the stack trace changes and that change is not
%% related to random values (\eg{}, hashcode), we discard that
%% specific slice. However, not every test case produces a stack trace
%% (\ie{}, passing tests), and thus, we guarantee that the test has
%% executing code by not instrumenting test classes and test methods.

\vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
major cost associated with critical
slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
  of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
program schemata where every statement in function bodies is guarded
by a branch predicate to control its activation. The slicer
re-executes the program with different guard configurations, recording
the smallest slice found. It uses a local search to find the smallest
slice for a given time budget. A slice is encoded as a list of flags,
each indicating whether or not a given guard is active. The initial
configuration of a slicing job has the flags set for all statements
covered by a given test.

%% \vspace{1ex}\noindent\textbf{Structure Awareness.}
%% ORBS is language-agnostic; it removes text from files but it does not
%% parse code. Each removal can lead to malformed
%% code. \Mar{$\leftarrow$how do we deal with this in the bytecode
%%   instrumentation?  explain...} We collect constraints of the form
%% $b\rightarrow{}a$ during code instrumentation to indicate that guard
%% $b$ is used in the region guarded by $a$, reflecting the nested
%% structure of the code. The slicer uses these constraints to prune the
%% search space of guard configurations, encoding the slice. For example,
%% it does not make sense to include statement $b$ in the slice and not
%% including statement $a$.

\vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
given test is necessary in Critical Slicing. However, test
re-execution may introduce flakiness due to side-effects in data
reachable from static fields. One alternative to address this problem
is to run each test in a separate JVM. Unfortunately, that alternative
is prohibitively slow. For that, we ran the slicing job in a single
JVM, using a test runner that is able to clean the static area of the
JVM as follows. At every re-execution of the critical slicer, the test
runner creates a new instance of a custom class loader, child of the
original JVM class loader.  Before loading a class, the custom class
loader checks in a cache whether or not the bytecodes were already
loaded. If not, the class file is loaded from disk and the bytecodes
are stored in the cache for future access. If the bytecodes were
previously loaded, the slicer avoids disk access by reading the data
directly from the cache.  To sum, the use of a new class loader
enables the slicer to ``reset'' the state prior to a new execution of
the same test~---~the objects accessible from the static area become
unreachable when the class loader is disposed at the end of an
execution.

\vspace{1ex}
Our implementation is publicly available under the following link (not
anonymized): \oururl{}.

\section{\sfl}
\label{sec:sfl}

\Mar{borrowed from our ICST17 paper. needs to }

Spectrum-based fault localization is an approach to pinpointing bugs
in software programs~\cite{FLSurvey2016, DBLP:conf/kbse/JonesH05,
  DBLP:journals/smr/LuciaLJTB14, DBLP:journals/jss/AbreuZGG09}.  In
spectrum-based fault localization, the following is given: a finite
set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.
The pair $(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}, and is depicted in~\cite{fig:spectrum-example}.
Several types of spectra exist.
The most commonly used is called hit-spectrum, where the coverage matrix is encoded in terms of
binary \emph{hit} (1) and \emph{not hit} (0) flags, i.e.,
$\A{ij} = 1$ if $c_j$ is involved in $t_i$ and $\A{ij} = 0$
otherwise.

\begin{figure}[h!]
    \centering
    \begin{tabular}{c|cccc|c}
      $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
      $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
      $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
      \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
      $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
    \end{tabular}
    \caption{An example spectrum.}
    \label{fig:spectrum-example}
\end{figure}

The pair $(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique consists of determining what columns
of the matrix $A$ resemble the error vector $e$ the most.
For that, an intermediate component frequency aggregator is computed:
%
\begin{equation}\label{eq:occurrence}
 n_{pq}(j) = |\{i\mid \A{ij}=p \wedge e_i=q\}|
\end{equation}
%
\noindent where $n_{pq}(j)$ is the number of runs in which the
component $j$ has been active during execution ($p = 1$) or not
($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
For instance, $n_{11}(j)$ counts the number of times component $j$ has
been involved ($p = 1$) in failing executions ($q = 1$), whereas
$n_{10}(j)$ counts the number of times component $j$ has been involved
in passing executions.

We then calculate similarity to the error vector by means of applying \emph{fault predictors} to
each component to produce a score quantifying how likely it is to be faulty.
Components are then ranked according to such likelihood scores and reported to the user.

\section{Dynamic Slicing + \sfl{}}
\label{sec:combination}

The methodology we used to combine dynamic slicing with \sfl{}
consists of the following steps: (1) Compute the execution spectra as
discussed in Section~\ref{sec:sfl}, (2) Compute slices associated with
tests, (3) Adjust the spectra computed in Step 1 with results obtained
in Step 2, and (4) Compute suspiciousness
scores. Figure~\ref{fig:illustration} illustrates the process of
updating the spectra and suspiciousness ranking as result of slicing
the program against the failing test $t_2$.  The faulty statement in
this example is the component $c_2$.

%% \begin{enumerate}
%% \item\label{step-spectra} Compute the execution spectra.
%% \item\label{step-slice} Compute slices associated with tests.
%% \item Adjust the spectra computed in Step~\ref{step-spectra} with
%%   results obtained in Step~\ref{step-slice}.
%% \item Compute suspiciousness scores.
%% %\item {[optional]} Filter statements covered by selected failing tests.
%% \end{enumerate}

\begin{figure}[h!]
  \centering
{\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
   \begin{tabular}{c|ccccc|c}
     $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
     $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
     $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
     $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
     $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
     $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
     \hline
   \end{tabular}
   \quad
   $\Rightarrow$
   \quad
   \begin{tabular}{c|ccccc|c}
     $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
     $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
     $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
     $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
     $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
     $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
     \hline
   \end{tabular}

   \vspace{3ex}

   \begin{tabular}{cccccc}
     & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$  \\
     & 0.32 & 0.35 & 0.55 & 0.59 & 0.32 \\
   \end{tabular}
   \quad
   $\Rightarrow$
   \quad
   \begin{tabular}{cccccc}
     & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$  \\
     & 0.32 & 0.35 & {\cellcolor{Gray}0.29} & {\cellcolor{Gray}0.32} & 0.32 \\
   \end{tabular}

 }
\caption{Illustration of spectra and ranking update.}
\label{fig:illustration}
\end{figure}

The slice obtained from $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
enables identification of cells in the matrix (/spectra) whose values
can be set to zero. In general, updates in the matrix results in an
increase of suspiciousness for a given component when the target test
is passing or a reduction of suspiciousness when the target test is
failing. Consider the Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06}

\[
\frac{\N{11}}{\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}}}
\vspace{1ex}\], where $n_{pq}(j)$ is the number of runs in which the
component $j$ has been active during execution ($p = 1$) or not
($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
Slicing of a failing test reduces the value of $\N{11}$ and increases
the value of $\N{01}$ for those statements $j$ which are not part of
the slice. Therefore, suspiciosness of those statements decrease. In
this example, components $c_3$ and $c_4$, which are not in the slice
of $t_2$, have their suspiciousness reduced, enabling the faulty
component $c_2$ to rise from the third to the first position in the
ranking.

\Fix{I suggest to add an algorithm section and perhaps a discussion on
time/space complexity.}

\section{Evaluation}
\label{sec:eval}

This section reports results of our study to assess the impact of the
\comb{} combination.

\subsection{Objects of Analysis}

Following other recent studies, we used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and 395 faults.
\lang{} is a library
that provides a set of helper utilities for the {\small\texttt{java.lang}}
API. \cmath{} is a lightweight library of self-contained
mathematics and statistics components. The \closure{} is a toolset for
turning JavaScript files into smaller scripts for faster
download and execution in the browser. \chart{} is a library with a
full-featured charts user interface for Java. \jtime{} is a
lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
a mocking testing framework.\Comment{ that enables the developer to simulate
the behavior of classes that cannot be used in unit testing.}

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Defects \Comment{& Failing Test Cases &}  \\
      \midrule
      \lang{}            & -  & - & 65          \Comment{& 124   &  -}\\
      \cmath{}           & -  & - & 106          \Comment{& 177   &  -}\\
      \closure{}         & -  & - & 133         \Comment{& 350   &  -}\\
      \chart{}           & -  & - & 26         \Comment{& 92    &  -}\\
      \jtime{}           & -  & - & 27          \Comment{& 76    &  -}\\
      \mockito{}         & -  & - & 38          \Comment{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}
\end{table}
\normalsize

%% old text related to single faults...
%%%%%%%%%%%%
%% It is important to note that the construction of the \dfj{} dataset is
%% not suited to evaluate the rate of single faults, but prior research
%% did that.  Perez~\etal{}~\cite{7927959} recently showed that single
%% faults are prevalent in open-source project. They conducted a
%% comprehensive empirical study involving 279 open-source Java projects
%% where they found that single faults were observed in 82\% of the cases
%% of regression.

\subsection{Results of Dynamic Slicing}

We describe the results of dynamic slicing alone in the following.

\subsubsection{How much reduction in one execution trace
  can one get with Dynamic Slicing?}

Table~\ref{fig:ds-reduction} shows the average reduction obtained with
slicing considering our implementation. The first column shows the \dfj{} project name.
Column ``Stmts. Covered'' shows the number of statements covered in
the execution of one failing test, column ``Slice Size'' shows the
number of statements appearing in the slice size, and column ``\%
Reduction'' shows the percentage reduction obtained. Numbers reported
are averaged across all executions. We only considered cases where we
knew a priori the slice contained the faulty statements
(Section~\ref{sec:ds-limitations}). Overall, it is noticeable that
both absolute reduction (as per column ``Slice Size'') and relatitve
reduction (as per column ``\% Reduction'') obtained are
significant.

\begin{table}[h]
  \centering
  %  \resizebox{\columnwidth}{!}{%
  \setlength{\tabcolsep}{3pt}
    \begin{tabular}{lrrrr}
      \toprule
      Project             & Stmts. & Slice &
      \multicolumn{2}{c}{Reduction} \\
      \cline{4-5}
                          &  Covered &  Size  & \multicolumn{1}{c}{Avg.} & \multicolumn{1}{c}{$\sigma$}\\
      \midrule
      \lang{}             & 4,221             & 94            &  97.77\%  & -       \\
      \cmath{}            & 743,587           & 175           &  90.16\%  & 14.98\% \\
      \closure{}          & -                 & -             &  -        & -       \\
      \chart{}            & 13,474            & 155           &  90.26\%  & 16.52\% \\
      \jtime{}            & 23,360            & 912           &  95.99\%  & 01.25\% \\
      \mockito{}          & 3,064             & 340           &  82.48\%  & 12.02\% \\
      \bottomrule
  \end{tabular}
%}
\caption {\label{fig:ds-reduction}Average reduction in slice sizes. We
  rounded averages to the closest integer in columns
  ``Stmts. Covered'' and ``Slice Size''.\Mar{Para a coluna
    avg. reduction, o correto IMO eh tirar a media das reducoes e nao a
    reducao media.  Mais precisamente, considerando lang, ao inves de
    calcular 100*(4221-94)/4221 (como acima), deveriamos tirar a media
das reducoes considerando cada caso de lang.}\Mar{Nao costumo ver
    desvio padrao como percentagem}}
\end{table}
\normalsize

\subsubsection{What are the limitations of Dynamic Slicing?}
\label{sec:ds-limitations}

%% Omission errors, implicit dependencies, and multiple regression faults
%% can result in bug misses.  Omission errors occur when existing code
%% requires no modification but new code is needed to fix a
%% bug. Consequently, the slice of a failing test that manifests an
%% omission error misses the faulty statements as they are yet to be
%% added in code.  Figure~\Fix{ref} shows an example of omission
%% error.\Mar{add example}\Mar{consider removing omission errors as
%%   \sfl{} cannot handle this case anyway.  check what we did on ICST'17
%%   paper.}

%% \begin{figure}[h!]
%%   \begin{lstlisting}[frame=single]  % Start your code-block
%%     int myMethod(int myParam) {
%%       var result: Int = 0
%%       //result = myParam //This line is missing
%%       if (myParam <= 10) {
%%         result = result / 10
%%       }
%%       return result
%%     }
%%   \end{lstlisting}
%%   \caption{\Luis{Exemplo de falha de omissao do tipo \textbf{New Code}}}
%%   \label{example-new-code}
%% \end{figure}

The pie chart in Figure~\ref{pie-chart} highlights the sources of
problems associated with slicing.  We classify the slicing task as
problematic when it misses the faulty statement. A number of reasons
can explain a miss:

\begin{itemize}
\item \textbf{Missing code:} this case happens when the
bug is due to missing code. Any fault localization method, including
Slicing and \sfl{}, are innefective in this case. This is the main
source of problem we found in our dataset. Note that, although this
problem is not specific to slicing, executable slices could be used to
help the developer identify missing statements with
inspection.

\item \textbf{Non-observable effect:} This case happens when the
buggy code does not produce effect on the output. Consider, for
example, the scenario where there is a bug in a branch predicate that
results in execution not taking the branch guarded by a
conditional. In that case, the \CS{} is able to produce a slice that
does not contain the faulty if statement, still reproducing the
original output. This problem is specific to \CS{}. Note from the
piechart that this is the second most prevalent source of problem but
much less significant compared to missing
code.

\item \textbf{Non-deterministic output:} This case happens when the
  output of the program changes in every execution, such as random
  output sizes. Although, we handled specific cases such as that of a
  hashcode printed on the stack trace, which we are able to detect
  with re-execution, in general, \CS{} cannot pinpoint those cases.
  Consider, for example, the case of a stack overflow where the trace
  can vary from one execution to another.

%% There are supported cases, such as small changes in the output (i.e.,
%% hashcode of an object printed in the stack trace). Although,
%% StackOverflowException is not one of those cases, which the size of
%% lines printed is not the same.

\end{itemize}

\begin{figure}[ht]
  \centering
  \begin {tikzpicture}
    \pie[
      text=pin,
      radius=1.5,
      color={
        white!22.1,
        white!14.7,
        white!1.6,
        white!61.6
      }
    ]{
      61.6/{Missing Code (117)},
      14.7/{Non-Observable Effect (28)},
      1.6/{Non-deterministic Output (3)},
      22.1/{REMOVEME (42)}
    }
  \end {tikzpicture}
  \caption{\label{pie-chart}Source of problems in \Fix{XX} of the
    \Fix{YY} cases where Dynamic Slicing misses the faulty statement.}
\end{figure}

\Fix{I was left wondering: so what? What is the message and the actionable points?}
\Fix{The goal of this paper is debugging, so we should answer the question: does
dynamic slicing alone help in debugging?}

\subsection{Results of the \comb{} combination}

This section describes the results of the \comb{} combination. The
independent variables we used in the following experiments are (i) the
selection of tests to slice (see Section~\ref{sec:combination}) and
(ii) whether ot not the statements covered by selected tests are
filtered from the ranking.  Considering the first variable, the
illustration above shows the effect of slicing code using a single
failing test. However, we also analyzed the combination where we
compute slices of all failing tests. Intuitively, in those cases, more
lines in the matrix would be affected. The rationale for varying the
selection of tests to slice is to assess the impact that the amount of
slicing code has on performance of \sfl{}.  Considering the second
variable, the illustration above shows the scenario where all
components are reported in the ranking. However, we also analyzed the
scenario where only the components covered by our selection of tests
appear in the ranking. For the case above, only $c_2$ and $c_5$ would
be listed.  The dependent variable we used was the performance of
\sfl{} measured with
Top@N~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which indicates, for a given value N, the percentage of faults ranked
at position no lower than N. As recently discussed by Ang
\etal~\cite{ang-perez-van-deursen-rui-2017}, \sfl{} researchers
started using absolute metrics, such as Top@N, after Parnin and
Orso~\cite{parnin-orso-2011} highlighed the bias in metrics based on
the position of the faulty statement in the ranking relative to the
total size of the ranking, which is often very high. It is worth
mentioning that we used the GZoltar~\cite{gzoltar} toolset to run our
experiments.

\Fix{discutir Tabela~\ref{tab:summary}...}

\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrrr}
      \toprule
      Project            & (1,N) & (1,F) & (A,N) & (A,F)  \\
      \midrule
      \lang{}            & -  & - & -  & - \\
      \cmath{}           & -  & - & -  & - \\
      \closure{}         & -  & - & -  & - \\
      \chart{}           & -  & - & -  & - \\
      \jtime{}           & -  & - & -  & - \\
      \mockito{}         & -  & - & -  & - \\
      \bottomrule
  \end{tabular}
\caption {\label{tab:summary}Summary of results considering Top@N, for
  N=50, which is the midpoint value of N for the range we selected
  1-100.}
\end{table}
\normalsize

\subsubsection{What is the impact of slicing one failing test?}
This scenario reflects the case where the developer selects one given
test to focus debugging efforts. Figure \ref{fig:one-failing-test}
compares the results of \sfl{} and \comb{} when slicing code
associated with a single failing test. The top section of the figure
shows results without filtering covered statements whereas the lower
section shows the results with filtering. Each table shows the results of \sfl{} and \comb{}
for increasing values of N.  The top section of each table shows the
results for \sfl{} whereas the lower section shows results of
\comb{}. A plot for each subject appears under the tables to
illustrate how techniques compare. The x-axis denote the value of N
and the y-axis denotes the value of Top@N. Informally, a quick
increase is good~--~it means a high percentage of faults was detected
for small values of N.\Mar{@Rui, ainda nao esta claro qual a mensagem
  que vamos transmitir. Considerando resultados atuais, existe
  reducao, mas parece ser pouca para N<20. Existe algum valor de N
  considerado referencia para que a gente possa dar mais substancia ao
  resultado?}

\subsubsection{What is the impact of slicing all failing tests?}
Table~\ref{fig:all-failing-tests} \Fix{...............}

\begin{figure*}[!ht]
  \centering
    \begin{tabular}{cl|rrrrrrrrrr}
      \toprule
      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
      \midrule

      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
      \midrule
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
      & \lang{}       & 24.72 & 25.84 & 28.09 & 32.58 & 35.96 & 46.07 & 79.78 & 79.78 & 83.15 & 84.27 \\
      & \chart{}      & 18.97 & 24.14 & 31.03 & 31.03 & 32.76 & 72.41 & 72.41 & 75.86 & 79.31 & 79.31 \\
      & \jtime{}      & 34.78 & 58.7  & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 71.74 & 71.74 \\
      & \mockito{}    & 44.32 & 47.73 & 57.95 & 61.36 & 61.36 & 63.64 & 65.91 & 70.45 & 76.14 & 77.27 \\
      \hline
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
      & \lang{}       & 31.46 & 37.08 & 51.69 & 57.3  & 65.17 & 77.53 & 80.9  & 82.02 & 87.64 & 91.01 \\
      & \chart{}      & 43.1  & 46.55 & 60.34 & 81.03 & 94.83 & 96.55 & 96.55 & 96.55 & 96.55 & 98.28 \\
      & \jtime{}      & 50.0  & 63.04 & 63.04 & 63.04 & 63.04 & 67.39 & 71.74 & 71.74 & 71.74 & 71.74 \\
      & \mockito{}    & 45.45 & 47.73 & 60.23 & 60.23 & 61.36 & 62.5  & 67.05 & 76.14 & 79.55 & 80.68 \\
      \midrule

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest.pdf}}\\

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}\\

      \midrule

      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
      \midrule
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
      & \lang{}     & 33.71 & 41.57 & 49.44 & 52.81 & 60.67 & 84.27 & 94.38 & 95.51 & 96.63 & 98.88 \\
      & \chart{}    & 25.86& 36.21& 36.21& 36.21& 60.34& 75.86& 75.86 & 79.31& 79.31& 79.31 \\
      & \jtime{}       & 43.48 & 63.04 & 65.22 & 69.57 & 71.74 & 71.74 &73.91 & 73.91 & 73.91 & 73.91 \\
      & \mockito{} & 72.09 & 74.42 & 77.91 & 80.23 & 83.72 & 83.72 & 84.88 & 84.88 & 86.05 & 86.05 \\
      \midrule
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
      & \lang{}     & 46.07 & 58.43 & 66.29 & 67.42 & 74.16 & 93.26 & 97.75 & 98.88 & 100.0 & 100.0 \\
      & \chart{} & 51.72& 63.79& 65.52& 86.21& 98.28& 98.28& 98.28& 98.28& 98.28& 98.28 \\
      & \jtime{} & 65.22 & 69.57 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 \\
      & \mockito{} & 73.26 & 77.91 & 82.56 & 87.21 & 87.21 & 88.37 &91.86 & 94.19 & 95.35 & 95.35 \\
      \midrule

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest-filtering.pdf}}\\

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}\\

      \bottomrule

    \end{tabular}
    \caption{\label{fig:one-failing-test}Top@N, considering one failing test.}
\end{figure*}

\begin{figure*}[!ht]
  \centering
    \begin{tabular}{cl|rrrrrrrrrr}
      \toprule
      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
      \midrule

      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
      \midrule
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\sfl}}}
      &Apache commons-lang     & 25.0  & 27.27 & 29.55 & 38.64 & 43.18
      & 56.82 & 63.64 & 63.64 & 68.18 & 70.45 \\
      &\chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 87.5  & 93.75 & 93.75 \\
      &Joda-Time       & 23.08 & 38.46 & 46.15 & 46.15 & 46.15 & 46.15
      & 46.15 & 46.15 & 46.15 & 46.15 \\
      &Mockito & 16.67 & 29.17 & 33.33 & 37.5  & 37.5  & 41.67 & 45.83
      & 54.17 & 58.33 & 62.5 \\
      \hline
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\comb}}}
      &Apache commons-lang     & 36.36 & 50.0  & 56.82 & 59.09 & 63.64
      & 65.91 & 65.91 & 68.18 & 75.0  & 81.82 \\
      & \chart{}       & 68.75 & 81.25 & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
      &Joda-Time       & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15
      & 46.15 & 46.15 & 46.15 & 46.15 \\
      &Mockito & 20.83 & 29.17 & 41.67 & 41.67 & 41.67 & 45.83 & 58.33
      & 66.67 & 70.83 & 75.0 \\
      \midrule

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest.pdf}}\\

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}\\
      \midrule

      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
      \midrule
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
      & \lang{}     & 36.36 & 45.45 & 59.09 & 63.64 & 70.45  & 79.55 & 88.64 & 90.91 & 93.18 & 97.73 \\
      & \chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 93.75 & 93.75 & 93.75 \\
      & \jtime{}        & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15  & 53.85 & 53.85 & 53.85 & 53.85 \\
      & \mockito{} & 50.0  & 54.17 & 62.5  & 66.67 & 70.83 & 75.0  & 79.17 & 79.17 & 79.17 & 79.17 \\
      \hline
      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
      & \lang{}     & 56.82 & 81.82 & 93.18 & 93.18 & 95.45  & 95.45 &95.45 & 97.73 & 100.0 & 100.0 \\
      & \chart{}       & 68.75 & 87.5  & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
      & \jtime{}        & 53.85 & 53.85 & 53.85 & 53.85 & 53.85 & 53.85  & 53.85 & 53.85 & 53.85 & 53.85 \\
      & \mockito{} & 54.17 & 70.83 & 79.17 & 83.33 & 83.33 & 87.5  & 87.5 & 87.5  & 91.67 & 91.67 \\
      \midrule

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest-filtering.pdf}}\\

      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
      &
      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}\\
      \bottomrule

    \end{tabular}
    \caption{\label{fig:all-failing-test}Top@N, considering all failing test.}
\end{figure*}

%
%We pose the following research questions:

%\textit{RQ1: How frequent are dynamic slices without the bug produced? }
%~\Davino{ XX\% of the results show omission cases, i.e., cases where the fault of the program wasn't present on the generated slice. }

%\textit{RQ2: Are SFL techniques effective on minimizing the effort to manual/automated fault localization?}
%~\Davino{ With the results, we show that it surely isn't. Rank of
%suspiciousness commonly puts the fault at the top 50+ lines of code,
%which isn't practical using manual or automated fault localization, or
%even automated program repair.}

%\textit{RQ3: Can Critical Slicing improve Statistical Fault Localization of real faults in a program?}
%~\Davino{ The results are based on REAL faults (instead of artificial
%ones, which are the basis case of evaluations of techniques involving
%slicing and SFL) presented in Defect4J's data set and show small
%improvements when comparing SFL and DS+SFL.}

\section{Related Work}

\Mar{beware, this is >>NOT<< revised! .........................................................................}

\textbf{Program Slicing}: Most recently related tool is ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}. \Fix{...}

Program Slicing~\cite{Weiser:1981:PS:800078.802557} is a technique to
identify program entities (the slice)\Comment{that influence the
  computation of} computationally related to a user-provided point of
interest (the slice criterion).

Similarly, dynamic slicing lacks successful cases of downstream
analyses. The WhyLine debugging assistant~\cite{whyline-website} is an
isolated case of success.

There are some approaches that utilize dynamic slicing and
spectrum-based fault localization (SFL) as fault localization methods.

Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
technique involving dynamic slicing and SFL applied to MATLAB/Simulink
models.The technique consists of iteratively
generating tests that cause an error using satisfiability modulo
theories (SMT) so that the slices generated are distinct from each
other.  For slicing, their technique uses a program dependence graph
(PDG) that express both data and control dependencies between blocks,
so that the slice is built only on blocks that affect a specific line
in the model - \textit{effective blocks}.  Their goal with the slicing
was (1) to keep suspiciousness of a fault maximum if a target model
has only one fault, and (2), to reduce the number of fault candidates
obtained by the slicer.  For this, they utilize only failed test cases
generated with SMT solvers ~\cite{peleska-vorobev-lapschies-2011} to
calculate suspiciousness, as passed test cases might lower the
suspiciousness of a fault.  The calculated suspiciousness is the
number of times that a block belongs to the \textit{effective blocks}
group by the number of total failed test cases.  Although their
experiments and results showed promise with small models, the accuracy
of the technique decreases when applied to models with multiple faults
instead of one, as does the efficiency when exposed to large models,
number of generated tests, sizes of sliced models and so on.

\Fix{...}

\subsection{Automatic Program Repair}
Automated repair techiniques have received considerable attention on
the last decade and consists of three basic steps: fault localization, patch
generation, and patch validation.  Regarding the fault localization
step, Automated Program Repair (APR) tools can be guided by statistical
fault localization techiniques to modify code which most likely
contains the fault. On this section, we will briefly describe some of
these tools.
\Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }

GenProg\Fix{cite} is a state of the art tool based on genetic
programming to repair defects in off-the-shelf C programs. GenProg's
strategy to fault localization consists of instrumenting the program
so that all lines visited when executing failing test cases are
recorded and used on the genetic search algorithm. The algorithm
involves serching for other parts of the program, considering that a
program that contains an error in one area likely implements the
correct behaviour elsewhere. The tool proved to be effective in
reparing 16 programs involving 1.25 millions LOC, and efficient as the
algorithm search space takes advantage of test case coverage
information, reusing  existing program statements.

Debroy and Wong\Fix{cite} presented a techinique for automatically
fixing faults in a program combining both mutation and statistical
fault localization. Using the Tarantula fault localizer\Fix{cite}, the
techinique focus the top ranked statements in terms of suspiciousness
for the mutation operations. The percentage of statements examined in
search for the fault is based on the total number of statements of the
program, with the 10 percent being a reasonable number on the subject
programs studied.

JAFF\Fix{cite} is a Java automatic repair tool based on evolutionary principles that uses fault localization for ranking the statements in the code in terms of suspiciousness level.
Before searching for the fix, the Java program is translated into a syntax tree composed of nodes related to the top ranked statements being used on the search process.
The tool uses a specific formula to get the number of nodes that will be used on the search based on the number of statements with the same rank of suspiciousness,
with the range between 1 to 20 nodes being used on the cases studied.

SemFix is based on symbolic execution, constraint solving and program synthesis applied to software automatic repair. The tool uses statistical fault localization (SFL) with Tarantula to
obtain the rank of suspiciousness and iteratively takes the most suspicious statement that has not been tried out to be used on the search for a fix. Compared to GenProg, the presented tool
took consideredably less time to find a fix for programs utilizing the same test suites. However, the authors mention that the choice of the SFL techinique could potentially affect the
effectiviness of the tool, particularly with large programs.

SPR\Fix{cite} \Davino{ Fan Long } is based on staged
program repair with condition synthesis. SPR uses fault localization
to identify target statements that will be transformed in search for a
fix on the program. The search space is built with a list of
statements ranked by suspiciousness level, where only the first 200
ranked statements are considered. The authors observed that increasing
the search space to the top 2000 statements would bring additional
repairs, but with a obvious cost of searching a large space.
\Davino { Another tool presented by the same authors is Prophet, which uses the same search space, top 200. }

MintHint \Fix{cite} uses statistical analysis with SFL to rank
statements by their likelihood of being faulty. Given the ranked list,
the tool analysis the top \textit{k} statements, where \textit{k} is a
threshold set by the user, and proceeds with the repair algorithm
assuming the fault can be repaired by changing a single statement.

\Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }

\subsection{Dynamic Slicing and Statistical Fault Localization}

Previous works studied the impact of bringing together both dynamic
slicing and statistical fault localization applied to software
debugging.

Lei et al. proposed the use of program slices built with a
dynamic backward slicing approach to defined statistical variables
which can capture the influence of a statement execution on the output
using SFL quantification of suspiciousness to each statement\cite{lei-mao-dai-wang-2012}.

Ishii and Kutsuna proposed a fault localization method with dynamic slicing that iteratively generates failing test cases using Satisfiability Modulo Theories (SMT) solvers to get distinct slices
for each test case. The proposed method was evaluated using MATLAB/Simulink models\cite{ishii-kutsuna-2016}.

Acknowledging the dependencies problem to locate a fault in the probram, Wen\cite{wen-2012} combines the concept of critical slicing, i.e., deleting statements with no contributions to faults,
with statistical fault localization proposing a program slicing spectrum-based software fault localization model.

He et al. proposed a new method to automated fault localization with
CPSS (coverage and program structure slicing)\cite{he-zhang-liu-gao-201}.  Based on program
execution path struture data dependency analysis, the idea is to
extract execution paths streamlined into a complete program dependence
path, reverse data dependence analysis and calculate the defect rate
with state of the art SFL techiniques (i.e., Tarantula).

\subsection{Other}

\Mar{moved to here...revise when possible...}

For example,
dependency tracking alternatives such as
JSlice~\cite{Wang:2004:UCB:998675.999455} and
JavaSlicer~\cite{hammacher-bachthesis-2008} instrument the analyzed
code~\cite{hammacher-bachthesis-2008} or modify
interpreters~\cite{Wang:2004:UCB:998675.999455} to build compact
execution traces.  Then, they process the traces to reconstruct
program states; this step recovers the dependency chains rooted in
points of interest.

ORBS~\cite{Binkley:2014:OLP:2635868.2635893} is a observation-based
slicing method independent of programming language. ORBS deletes
statements in the files of interest and checks whether the test output is
the same as the original
test~\cite{Binkley:2014:OLP:2635868.2635893}.

\Fix{revise? merge?}
Observation-Based Slicing technique, similar to Critical Slicing, is
based on deleting statements that are not relevant to the test case
failure. Although, with this technique is possible to remain the rest
of the system untouched.

%% Acknowledgments
\begin{acks}                            %% acks environment is optional

  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

%% Bibliography
\bibliography{tmp}

%% Appendix
%% \appendix
%% \section{Appendix}
%% Text of appendix \ldots

\end{document}

### 2018-11-10 paper/R/stacked-density.r

@@ -1,0 +1,34 @@
+library("ggplot2")
+
+names <- c("commons-lang", "jfreechart", "jodatime", "mockito")
+
+suffixes <- c("-onefailingtest-filtering", "-allfailingtest-filtering", "-allfailingtest", "-onefailingtest")
+
+for (name in names) {
+    for (suffix in suffixes) {
+        # loading file
+        filename <- paste(name, suffix, sep="")
+        mydata <- read.table(paste(filename, ".dat", sep=""), header=TRUE)
+            
+        # rendering plot
+        p <- ggplot(mydata, aes(n, topn, group=slicing))+
+        geom_step()+
+        geom_point(aes(colour=slicing))+
+        annotate("text",x=min(mydata$n)+30,y=min(mydata$topn)+2,hjust=.2,label=name)+
+        scale_x_continuous(breaks = seq(min(mydata$n), max(mydata$n), 20), limits = c(min(mydata$n), max(mydata$n))) +
+        # scale_y_continuous(breaks = seq(0, 100, 20), limits = c(0, 100)) +
+        theme(legend.position=c(.9,.15)) +
+        theme(axis.text.x = element_text(size=9))  +
+        theme(axis.text.y = element_text(size=9))  
+        
+        
+        p <- p + geom_vline(xintercept=10, color="red")
+
+        # saving plot to file
+        update_geom_defaults("point", list(size=1))
+        theme_set(theme_grey(base_size=6))
+        pdf(paste(filename, ".pdf", sep=""), width=3, height=2)
+        print(p)
+        graphics.off()
+    }
+}

### 2018-11-10 paper/main.tex
quick pass on intro

@@
 %% PROBLEM MOTIVATION
-Statistical Fault Localization (\sfl{})~\cite{7390282} is a popular
-technique for automated software debugging.  It computes
+Automated debugging is very important.\Fix{...elaborate...}
+
+Statistical Fault Localization (\sfl{}) and Dynamic Slicing are
+popular complementary approaches proposed to automate debugging.
+\sfl{}~\cite{7390282} computes
 suspiciousness values associated with program entities (e.g., basic
@@
 and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
-likely fixes.
+likely fixes. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
+technique for automated debugging. It takes as input a failing test
+and produces on output a set of statements--the slice--that influence
+the evaluation of the fault-revealing assertion.
 
@@
 
-\Fix{...too big of a jump...}
-
-Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
-technique for automated debugging \Fix{is it popular? I would rather say that
-it is what best models developers thinking.}. It takes as input a failing test
-and produces on output a set of statements (the slice) that influences
-the evaluation of the fault-revealing assertion (the slice criterion).
 This paper reports the results of an empirical study to evaluate the
-impact of Dynamic Slicing (\ds{}) to improve \sfl{}.The intuition for
+impact of Dynamic Slicing (\ds{}) to improve \sfl{}. The intuition for
 the \comb{} combination is that several highly ranked statements,
@@
 plain \sfl{}. We found surprising that, despite these findings,
-reported nearly 5 years ago, no tool or client analysis use this
+reported nearly 5 years ago, no tool or client analyses use this
 combination today. One hypothesis to explain that observation is that

### 2018-11-10 paper/main.tex
describing lithium and its complexity

@@
 
-Statistical Fault Localization (\sfl{}) and Dynamic Slicing are
+Spectrum-Based Fault Localization (\sfl{}) and Dynamic Slicing are
 popular complementary approaches proposed to automate debugging.
-\sfl{}~\cite{7390282} computes
+\sfl{}~\cite{7390282} is a statistical debugging method that computes
 suspiciousness values associated with program entities (e.g., basic
@@
 
-\section{Dynamic Slicing}
+\section{Background}
+\label{sec:background}
+
+This section presents important background material for the rest of the paper.
+
+\subsection{Critical Slicing}
 \label{sec:slicing}
+
+%% To select a slicer implementation to run our experiments, we
+%% considered two criteria: robustness as to support non-trivial programs
+%% and efficiency as to support execution of our experiments in
+%% reasonable time.  Unfortunately, we failed to find public
+%% implementations satisfying these criteria.
+%% For those reasons, we decided to implement a critical slicer for Java,
+%% which is the language of the subjects in our dataset, \dfj{}.
 
@@
 relevant parts of the program with respect to given points of
-interest.  This paper focuses on dynamic slicing~--~as opposed to
-static slicing~\cite{Weiser:1981:PS:800078.802557}~--~for its
-application in automated software
-debugging~\cite{Binkley:2014:OLP:2635868.2635893}.  To select a slicer
-implementation to run our experiments, we considered two criteria:
-robustness as to support non-trivial programs and efficiency as to
-support execution of our experiments in reasonable time.
-Unfortunately, we failed to find public implementations satisfying
-these criteria.
-
-For those reasons, we decided to implement a critical slicer for Java,
-which is the language of the subjects in our dataset, \dfj{}. We
-focused on Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310} for
-its simplicity.\Comment{ In constrast with alternative slicing
+interest.  This paper focuses on dynamic slicing\Comment{~--~as
+  opposed to static slicing~\cite{Weiser:1981:PS:800078.802557}~--~}
+for its application in automated software
+debugging~\cite{Binkley:2014:OLP:2635868.2635893} where failing tests
+exist. We focused on Critical
+Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
+simplicity/generality.\Comment{ In constrast with alternative slicing
   implementations based on dependency
@@
 prescribes a black-box language-semantics-agnostic recipe to computing
-executable slices\footnote{In the original implementation, critical
-  slicing was not guaranteed to be executable.  Above we refer to the
-  basic strategy of deleting statement and checking outcomes.}.
-Critical Slicing slices the program by deleting statements such that
-the sliced program preserves critical observations (\eg{}, assertion
-violations).  The output we used to determine equivalence of the
-original failing execution and the sliced failing execution was the
-stack trace produced by the assertion violation.  It is important to
-note that Binkley \etal{} recently proposed the critical slicer
-ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
-efficiency (important to run our experiments) for generality. Some of
-the slicing jobs we ran on ORBS took hours to run. For example,
-\Fix{...elaborate...}
-
-The principle of Critical Slicing is rather simple, consisting of
-mutating the program and observing the output. Despite that,
-optimizations are important to make a Critical Slicing implementation
-efficient. We describe the optimizations we used in the following.
+executable slices.  Critical Slicing minimizes the program by deleting
+statements such that the sliced program preserves critical
+observations (\eg{}, assertion violations). The simplification
+mechanism used in Critical Slicing is rather simple, consisting of
+mutating the program and observing the output.
+
+We used the Mozilla Lithium tool~\cite{lithium} as the implementation
+for Critical Slicing. Lithium is conceptually similar to the DD-min
+Delta Debugging algorithm~\cite{zeller-hildebrandt-tse2002}, but
+operates on code instead of test inputs. It takes as input a file and
+produces as output a simplified version of that file that satisfies a
+user-defined oracle. For dynamic slicing, the oracle is defined such
+that the test produces the same failure manifestation. The Lithium
+minimization process starts by determining the initial size of
+chunks---in number of lines---to delete from the input file. For that,
+it chooses the highest power of two number smaller than the file
+size. For example, if the file has 1,000 lines, Lithium sets the
+initial chunk size to 512 lines. Then, the tool starts a local search
+looking for chunks to remove from the file that satisfy the
+oracle. When no more chunks of that given size can be removed, Lithium
+divides the chunk size by two and repeats the search. This iterative
+process continues until no more line can be removed.  If $n$ is the
+size of the input file and $m$ is the size of the 1-minimal file found
+by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
+iterations. Proofs can be found elsewhere~\cite{lithium-complexity}.
+
+%% Despite that, optimizations are important to
+%% make a Critical Slicing implementation efficient. We describe the
+%% optimizations we used in the following.
+
+%% The output we used to determine equivalence of the original failing
+%% execution and the sliced failing execution was the stack trace
+%% produced by the assertion violation.  It is important to note that
+%% Binkley \etal{} recently proposed the critical slicer
+%% ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
+%% efficiency (important to run our experiments) for generality. Some of
+%% the slicing jobs we ran on ORBS took hours to run. For example,
+%% \Fix{...elaborate...}
 
@@
 
-\vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
-major cost associated with critical
-slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
-  of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
-program schemata where every statement in function bodies is guarded
-by a branch predicate to control its activation. The slicer
-re-executes the program with different guard configurations, recording
-the smallest slice found. It uses a local search to find the smallest
-slice for a given time budget. A slice is encoded as a list of flags,
-each indicating whether or not a given guard is active. The initial
-configuration of a slicing job has the flags set for all statements
-covered by a given test.
+%% \vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
+%% major cost associated with critical
+%% slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
+%%   of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
+%% program schemata where every statement in function bodies is guarded
+%% by a branch predicate to control its activation. The slicer
+%% re-executes the program with different guard configurations, recording
+%% the smallest slice found. It uses a local search to find the smallest
+%% slice for a given time budget. A slice is encoded as a list of flags,
+%% each indicating whether or not a given guard is active. The initial
+%% configuration of a slicing job has the flags set for all statements
+%% covered by a given test.
 
@@
 
-\vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
-given test is necessary in Critical Slicing. However, test
-re-execution may introduce flakiness due to side-effects in data
-reachable from static fields. One alternative to address this problem
-is to run each test in a separate JVM. Unfortunately, that alternative
-is prohibitively slow. For that, we ran the slicing job in a single
-JVM, using a test runner that is able to clean the static area of the
-JVM as follows. At every re-execution of the critical slicer, the test
-runner creates a new instance of a custom class loader, child of the
-original JVM class loader.  Before loading a class, the custom class
-loader checks in a cache whether or not the bytecodes were already
-loaded. If not, the class file is loaded from disk and the bytecodes
-are stored in the cache for future access. If the bytecodes were
-previously loaded, the slicer avoids disk access by reading the data
-directly from the cache.  To sum, the use of a new class loader
-enables the slicer to ``reset'' the state prior to a new execution of
-the same test~---~the objects accessible from the static area become
-unreachable when the class loader is disposed at the end of an
-execution.
-
-\vspace{1ex}
-Our implementation is publicly available under the following link (not
-anonymized): \oururl{}.
-
-\section{\sfl}
+%% \vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
+%% given test is necessary in Critical Slicing. However, test
+%% re-execution may introduce flakiness due to side-effects in data
+%% reachable from static fields. One alternative to address this problem
+%% is to run each test in a separate JVM. Unfortunately, that alternative
+%% is prohibitively slow. For that, we ran the slicing job in a single
+%% JVM, using a test runner that is able to clean the static area of the
+%% JVM as follows. At every re-execution of the critical slicer, the test
+%% runner creates a new instance of a custom class loader, child of the
+%% original JVM class loader.  Before loading a class, the custom class
+%% loader checks in a cache whether or not the bytecodes were already
+%% loaded. If not, the class file is loaded from disk and the bytecodes
+%% are stored in the cache for future access. If the bytecodes were
+%% previously loaded, the slicer avoids disk access by reading the data
+%% directly from the cache.  To sum, the use of a new class loader
+%% enables the slicer to ``reset'' the state prior to a new execution of
+%% the same test~---~the objects accessible from the static area become
+%% unreachable when the class loader is disposed at the end of an
+%% execution.
+
+\subsection{Spectrum-based Fault Localization}
 \label{sec:sfl}
-
-\Mar{borrowed from our ICST17 paper. needs to }
 

### 2018-11-10 paper/main.tex
another pass

@@
 
-Spectrum-based fault localization is an approach to pinpointing bugs
-in software programs~\cite{FLSurvey2016, DBLP:conf/kbse/JonesH05,
-  DBLP:journals/smr/LuciaLJTB14, DBLP:journals/jss/AbreuZGG09}.  In
-spectrum-based fault localization, the following is given: a finite
-set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
+Spectrum-based fault localization (\sfl) is a statistical fault
+localization technique that takes as input a test suite including at
+least one failing test and reports on output a ranked list of
+components likely to be in fault~\cite{FLSurvey2016,
+  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
+  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
+finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
 \emph{components}\footnote{A component can be any source code artifact
@@
 transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
-M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
-coverage of component $c_j$ in transaction $t_i$.
-The pair $(\mathcal{A},e)$ is commonly referred to as
-spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}, and is depicted in~\cite{fig:spectrum-example}.
-Several types of spectra exist.
-The most commonly used is called hit-spectrum, where the coverage matrix is encoded in terms of
-binary \emph{hit} (1) and \emph{not hit} (0) flags, i.e.,
-$\A{ij} = 1$ if $c_j$ is involved in $t_i$ and $\A{ij} = 0$
-otherwise.
-
-\begin{figure}[h!]
+M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
+of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
+is commonly referred to as
+spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
+shows an example spectrum.
+\begin{wrapfigure}[8]{r}{0.29\textwidth}
+  \vspace{-2ex}
+  \hspace{-3ex}
   \centering
+  \small
   \begin{tabular}{c|cccc|c}
@@
   \label{fig:spectrum-example}
-\end{figure}
-
-The pair $(\mathcal{A},e)$ serves as input to the fault localization technique.
-With this input, the next step in this coverage-based technique consists of determining what columns
-of the matrix $A$ resemble the error vector $e$ the most.
-For that, an intermediate component frequency aggregator is computed:
+\end{wrapfigure}
+Several types of spectra exist.  The most commonly used is called
+hit-spectrum, where the coverage matrix is encoded in terms of binary
+\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
+$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
+$(\mathcal{A},e)$ serves as input to the fault localization technique.
+With this input, the next step in this coverage-based technique
+consists of determining what columns of the matrix $A$ resemble the
+error vector $e$ the most.  For that, an intermediate component
+frequency aggregator $n_{pq}(j)$ is computed:
 %
@@
 %
-\noindent where $n_{pq}(j)$ is the number of runs in which the
+%\noindent
+$n_{pq}(j)$ denotes the number of runs in which the
 component $j$ has been active during execution ($p = 1$) or not
@@
 $n_{10}(j)$ counts the number of times component $j$ has been involved
-in passing executions.
-
-We then calculate similarity to the error vector by means of applying \emph{fault predictors} to
-each component to produce a score quantifying how likely it is to be faulty.
-Components are then ranked according to such likelihood scores and reported to the user.
+in passing executions. We then calculate similarity to the error
+vector by means of applying \emph{fault predictors} to each component
+to produce a score quantifying how likely it is to be faulty.
+Components are then ranked according to such likelihood scores and
+reported to the user. \Fix{show ochiai here...}
+
+\Mar{----------------------- estou aqui}
 

### 2018-11-10 paper/main.tex
pass on section 3

@@
 error vector $e$ the most.  For that, an intermediate component
-frequency aggregator $n_{pq}(j)$ is computed:
-%
-\begin{equation}\label{eq:occurrence}
- n_{pq}(j) = |\{i\mid \A{ij}=p \wedge e_i=q\}|
-\end{equation}
-%
-%\noindent
-$n_{pq}(j)$ denotes the number of runs in which the
-component $j$ has been active during execution ($p = 1$) or not
-($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
-For instance, $n_{11}(j)$ counts the number of times component $j$ has
-been involved ($p = 1$) in failing executions ($q = 1$), whereas
-$n_{10}(j)$ counts the number of times component $j$ has been involved
-in passing executions. We then calculate similarity to the error
-vector by means of applying \emph{fault predictors} to each component
-to produce a score quantifying how likely it is to be faulty.
-Components are then ranked according to such likelihood scores and
-reported to the user. \Fix{show ochiai here...}
-
-\Mar{----------------------- estou aqui}
-
-\section{Dynamic Slicing + \sfl{}}
+frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
+\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
+which the component $j$ has been active during execution ($p = 1$) or
+not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
+0$).  For instance, $n_{11}(j)$ counts the number of times component
+$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
+whereas $n_{10}(j)$ counts the number of times component $j$ has been
+involved in passing executions. We then calculate similarity to the
+error vector by means of applying \emph{fault predictors} to each
+component to produce a score quantifying how likely it is to be
+faulty.  Components are then ranked according to such likelihood
+scores and reported to the user. Ochiai is one of those fault
+predictors that has shown to perform well~\Fix{cite}. The Ochiai
+formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
+$\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10})}$.
+
+\section{Critical Slicing + \sfl{}}
 \label{sec:combination}
 
-The methodology we used to combine dynamic slicing with \sfl{}
-consists of the following steps: (1) Compute the execution spectra as
-discussed in Section~\ref{sec:sfl}, (2) Compute slices associated with
+The combinination of critical slicing and \sfl{} consists of the
+following steps: (1) Compute the execution spectra as discussed in
+Section~\ref{sec:sfl}, (2) Compute slices associated with failing
 tests, (3) Adjust the spectra computed in Step 1 with results obtained
 in Step 2, and (4) Compute suspiciousness
-scores. Figure~\ref{fig:illustration} illustrates the process of
-updating the spectra and suspiciousness ranking as result of slicing
-the program against the failing test $t_2$.  The faulty statement in
-this example is the component $c_2$.
+scores. Figure~\ref{fig:illustration} illustrates the update of the
+spectra and suspiciousness rankings as result of slicing the program
+against the failing test $t_2$. The faulty statement in this example
+is the component $c_2$.  The slice obtained from $t_2$ is $\{c_2,
+c_5\}$.  Intuitively, slicing enables identification of cells in the
+matrix (/spectra) whose values can be set to zero.
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
   \centering
+  \begin{subfigure}{0.5\textwidth}  
     {\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
@@
       \end{tabular}
-
-   \vspace{3ex}
-
+    }
+    \caption{Spectra update.}
+  \end{subfigure}
+
+  \vspace{2ex}
+
+  \begin{subfigure}{0.5\textwidth}
+    \centering
     \begin{tabular}{cccccc}
-     & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$  \\
-     & 0.32 & 0.35 & 0.55 & 0.59 & 0.32 \\
+      1 & $c_4$ (0.59) & & 1 & $c_2$ (0.35) \\
+      2 & $c_3$ (0.55) & & 2.5 & $c_1$ (0.32)\\
+      3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
+      4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
+      4.5 & $c_5$ (0.32) & & 5 & $c_3$ (0.24)\\
     \end{tabular}
-   \quad
-   $\Rightarrow$
-   \quad
-   \begin{tabular}{cccccc}
-     & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$  \\
-     & 0.32 & 0.35 & {\cellcolor{Gray}0.29} & {\cellcolor{Gray}0.32} & 0.32 \\
-   \end{tabular}
-
- }
-\caption{Illustration of spectra and ranking update.}
+    \caption{Ranking update.}
+  \end{subfigure}
+
+  \caption{Modifications on spectra and ranking as result of slicing code against test $t_2$.}
   \label{fig:illustration}
@@
 
-The slice obtained from $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
-enables identification of cells in the matrix (/spectra) whose values
-can be set to zero. In general, updates in the matrix results in an
-increase of suspiciousness for a given component when the target test
-is passing or a reduction of suspiciousness when the target test is
-failing. Consider the Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06}
-
-\[
-\frac{\N{11}}{\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}}}
-\vspace{1ex}\], where $n_{pq}(j)$ is the number of runs in which the
-component $j$ has been active during execution ($p = 1$) or not
-($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
-Slicing of a failing test reduces the value of $\N{11}$ and increases
-the value of $\N{01}$ for those statements $j$ which are not part of
-the slice. Therefore, suspiciosness of those statements decrease. In
-this example, components $c_3$ and $c_4$, which are not in the slice
-of $t_2$, have their suspiciousness reduced, enabling the faulty
-component $c_2$ to rise from the third to the first position in the
-ranking.
-
-\Fix{I suggest to add an algorithm section and perhaps a discussion on
-time/space complexity.}
+%% In general, updates in the matrix results in an increase of
+%% suspiciousness for a given component when the target test is passing
+%% or a reduction of suspiciousness when the target test is failing.
+
+\begin{theorem}
+  The rank of faulty statements cannot decrease if the slice includes
+  the faulty statements.
+\end{theorem}
+
+For those statements $j$ which are not part of the slice of a failing
+test, the combination reduces the value of $\N{11}$ and increases the
+value of $\N{01}$. Therefore, suspiciosness of those statements
+decrease. In this example, components $c_3$ and $c_4$, which are not
+in the slice of $t_2$, have their suspiciousness reduced, enabling the
+faulty component $c_2$ to rise from the third to the first position in
+the ranking. \Mar{what about other formula?}
+
+\Mar{think of another theorem...}
 
@@
 \label{sec:eval}
+
+\Mar{-------------------- estou aqui}
 

### 2018-11-11 app/run-lithium-parallel.sh
run in parallel

@@ -1,15 +1,15 @@
 #!/bin/sh
 
-if $1 == '0'; then
-    for BUG in $(seq 1 $1); do 
-        bash runner.sh $2 $i &
-    done
-elif $1 == '1'; then
-    IFS=',' read -ra ADDR <<< "$3"
-    for i in "${ADDR[@]}"; do
-        bash runner.sh $2 $i &
-    done
-fi
+PROJECT=$1
+BUGS=$2
+
+IFS="," read -ra ADDR <<< "$BUGS"
+
+if [[ ${#ADDR[@]} > 1 ]]; then BUGS_LIST="${ADDR[@]}"; else BUGS_LIST=$(seq 1 $BUGS); fi
+
+for BUG in $BUGS_LIST; do
+	bash runner.sh $PROJECT $BUG &
+done
 
 wait
 echo all processes complete

### 2018-11-11 app/generate_inputs.py
No such file or directory error solved

@@ -30,7 +30,9 @@ def get_source_path(project_name):
         "Chart": "source",
         "Closure": "src",
         "Lang": "src/java",
+        "Lang2": "src/main/java",
         "Math": "src/main/java",
+        "Math2": "src/java",
         "Mockito": "src",
         "Time": "src/main/java"
     }
@@ -50,8 +52,13 @@ def generate_seed(project, bugnumber, output):
         print("FAILED") # should print to stop the main script
         raise Exception("Project {} directory not found".format(project_path))
     
-    source_path = get_source_path(project)
-    
+    if project == 'Lang' and int(bugnumber) < 36:
+        source_path = get_source_path(project+'2')
+    elif project == 'Math' and int(bugnumber) > 84:
+        source_path = get_source_path(project+'2')
+    else:
+        source_path = get_source_path(project)
+
     # get only bugs choosen by user
     bugnumber = bugnumber.split(",")
     
@@ -65,7 +72,7 @@ def generate_seed(project, bugnumber, output):
         bugnumbers = os.listdir(project_path)
     else:
         bugnumbers = [doc for doc in os.listdir(project_path) if doc in bugnumbers]
-
+    
     with open(output, "w") as seed_file:
         for bug in bugnumbers:
             data = json_to_dict(os.path.join(project_path, bug))

### 2018-11-11 app/run_lithium.py

@@ -120,7 +120,7 @@ def minimize_file(filepath):
         copy(java_file, minimized_path)
 
         # update 
-        output_lithium["class"] = get_relative_path(project, java_file)
+        output_lithium["class"] = get_relative_path(project, java_file, args.bug_number[0])
         output_lithium["loc"] = get_locs(origin_path, minimized_path) if not remove_comments else get_locs(uncomment_path, minimized_path)
 
         est_time = int((time.time() - start_lithium)/60.0)

### 2018-11-11 app/utils.py

@@ -19,21 +19,27 @@ def checkout_project(project, bug_number, project_dir):
     call(cmd, stderr=STDOUT)
 
 
-def get_relative_path(project, class_name):
+def get_relative_path(project, class_name, bug_number):
     """ get the path inside the project directory """
     paths = {
         "Chart": "source",
         "Closure": "src",
         "Lang": "src/java",
+        "Lang2": "src/main/java",
         "Math": "src/main/java",
+        "Math2": "src/java",
         "Mockito": "src",
         "Time": "src/main/java"
     }
 
-    project_path = paths[project]
+    if project == 'Lang' and int(bug_number) < 36:
+        project_path = paths[project+'2']
+    elif project == 'Math' and int(bug_number) > 84:
+        project_path = paths[project+'2']
+    else:
+        project_path = paths[project]
     path = "{}/".format(project_path)
     index = class_name.index(path) + len(path)
-    
     class_name = class_name[index:]
 
     return class_name
@@ -129,7 +135,6 @@ def check_obj_comparison(expected_msg, output_msg):
     if search_expected and search_output:
         expected = search_expected.group(1).split('@')[0], search_expected.group(2).split('@')[0]
         output = search_output.group(1).split('@')[0], search_output.group(2).split('@')[0]
-        print('UTILS.PY check_obj_comparison EXPECTED[0]', expected[0], 'OUTPUT[0]', output[0], 'EXPECTED[1]', expected[1], 'OUTPUT[1]', output[1])
         return (expected[0] == output[0]) and (expected[1] == output[1])  
     return False
 

### 2018-11-12 paper/main.tex
adding (empty) implementation section
pass on intro

@@
 %% Title information
-\title{The Impact of Critical Slicing in SFL\Comment{tatistical Fault Localization}}         %% [Short Title] is optional;
+\title{Reassessing the Impact of Dynamic Slicing in SFL}         %% [Short Title] is optional;
                                         %% when present, will be used in
@@
 %% PROBLEM MOTIVATION
-Automated debugging is very important.\Fix{...elaborate...}
-
-Spectrum-Based Fault Localization (\sfl{}) and Dynamic Slicing are
-popular complementary approaches proposed to automate debugging.
-\sfl{}~\cite{7390282} is a statistical debugging method that computes
-suspiciousness values associated with program entities (e.g., basic
-blocks) using coverage information of passing and failing test
-cases. \sfl{} produces a list of program entities ranked in
-decreasing order of suspiciousness.  \sfl{} received tremendous
-attention over the years, but its applicability to support debugging
-remains
+Software debugging is difficult. The task of locating the faulty code
+(\ie{}, fault localization) is particularly challenging. For that
+reason, countless automated techniques have been proposed in the past
+to reduce cost of fault localization. Among those are Dynamic Slicing
+(\ds{}) and Spectrum-Based Fault Localization (\sfl{}). Dynamic
+Slicing~\cite{Agrawal:1990:DPS:93542.93576} takes as input a failing
+test and produces on output a set of statements that influence the
+evaluation of the fault-revealing assertion.  Although the technique
+has been intensively explored, few slicing applications became
+popular---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
+exception.  \sfl{}~\cite{7390282} is another popular automated
+debugging technique. It is a statistical fault localization method
+that computes suspiciousness values associated with program entities
+(e.g., basic blocks) using coverage information of passing and failing
+test cases. \sfl{} produces a list of program entities ranked in
+decreasing order of suspiciousness.  Likewise dynamic slicing, \sfl{}
+received tremendous attention over the years, but its applicability to
+support debugging remains
 questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
-Despite the skepticism of the research community, \sfl{} has been shown
-useful in supporting downstream analyses, such as Automated Program Repair
+Despite the skepticism of the research community, \sfl{} has been
+shown useful in supporting downstream analyses, such as Automated
+Program Repair
 (\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
@@
 and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
-likely fixes. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
-technique for automated debugging. It takes as input a failing test
-and produces on output a set of statements--the slice--that influence
-the evaluation of the fault-revealing assertion.
+likely fixes.
 
@@
 
-This paper reports the results of an empirical study to evaluate the
-impact of Dynamic Slicing (\ds{}) to improve \sfl{}. The intuition for
-the \comb{} combination is that several highly ranked statements,
-albeit covered by failing executions, may be unrelated to the
-fault. Prior work reported promising results in this combination
+\ds{} and \sfl{} are complementary. Conceptually, \ds{} identifies
+irrelevant parts of the code whereas \sfl{} ranks relevant parts of
+the code.  This paper reports the results of an empirical study to
+evaluate the impact of \ds{} to improve \sfl{}. The intuition for the
+\comb{} combination is that several highly ranked statements, albeit
+covered by failing executions, may be unrelated to the fault. Prior
+work reported promising results in this combination
 \cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012}.
@@
 goal of this paper is to reassess whether the \comb{} combination is
-worthwhile under the light of this metric. Developers of techniques
-such as \acrAbrev{} would benefit from these results~---~either to
-improve their results or to be aware they should not invest on this
-integration.
+worthwhile under the light of this metric and using a larger
+dataset. Developers of \acrAbrev{} techniques would directly benefit
+from these results~---~either to improve their results or to be aware
+they should not invest on this integration.
 
@@
 
+\subsection{Implementation}
+
+\Mar{...elaborate...}
+
 \section{Evaluation}

### 2018-11-12 paper/main.tex
pass on Section 3

@@
 
-%% In general, updates in the matrix results in an increase of
-%% suspiciousness for a given component when the target test is passing
-%% or a reduction of suspiciousness when the target test is failing.
+\begin{theorem}
+  The faulty statement may not be included in the critical slice of
+  failing test cases.
+\end{theorem}
+
+It is possible that a slice that discards the faulty statement still
+produces the expected message checked by the oracle. This can happen,
+for example, if the oracle is too general.\qed
+
+\Mar{Sofia, please add a short (3-4 lines at most) example based on
+  one of our subjects} Section~\ref{sec:impl} explains the heuristics
+we used to infer oracles for critical slicing that mitigates this
+issue and Section~\ref{sec:eval} shows how often critical slicing
+misses faulty statements.
 
@@
 
-For those statements $j$ which are not part of the slice of a failing
-test, the combination reduces the value of $\N{11}$ and increases the
-value of $\N{01}$. Therefore, suspiciosness of those statements
-decrease. In this example, components $c_3$ and $c_4$, which are not
-in the slice of $t_2$, have their suspiciousness reduced, enabling the
-faulty component $c_2$ to rise from the third to the first position in
-the ranking. \Mar{what about other formula?}
-
-\Mar{think of another theorem...}
+Considering the Ochiai formula, for those statements $j$ which are not
+part of the slice of a failing test, the combination reduces the value
+of $\N{11}$ and increases the value of $\N{01}$. Therefore,
+suspiciosness of those statements decrease. Similar argument applies
+to other fault predictors.\qed{}
+
+In the example from Figure~\ref{fig:illustration}, components $c_3$
+and $c_4$, which are not in the slice of $t_2$, have their
+suspiciousness reduced, enabling the faulty component $c_2$ to rise
+from the third to the first position in the ranking.
 
 \subsection{Implementation}
+\label{sec:impl}
 
 \Mar{...elaborate...}
+
+\Mar{...explain how we built our oracles/checkers...}
 

### 2018-11-15 paper/main.tex
intro+comments, background reviewed, implementation+ifunc+limitations

@@
 \begin{abstract}
-Text of abstract \ldots.
+\Sof{@todo} 
 \end{abstract}
@@
 %% comma separated list
-\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission
+\keywords{Slicing, Testing, Debugging}  %% \keywords are mandatory in final camera-ready submission
 
@@
 
+\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}
+
 %% PROBLEM MOTIVATION
@@
 reason, countless automated techniques have been proposed in the past
-to reduce cost of fault localization. Among those are Dynamic Slicing
+to reduce the cost of fault localization. Among those are Dynamic Slicing
 (\ds{}) and Spectrum-Based Fault Localization (\sfl{}). Dynamic
@@
 and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
-likely fixes.
+likely fixes. \Sof{likely appears too many times on the last 3 lines.}
 
@@
 \ds{} and \sfl{} are complementary. Conceptually, \ds{} identifies
-irrelevant parts of the code whereas \sfl{} ranks relevant parts of
+irrelevant parts of the code whereas \sfl{} ranks the relevant parts of
 the code.  This paper reports the results of an empirical study to
@@
 pointed to that fact encouraging developers to adopt precise metrics
-such as top@n
-\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. The
-goal of this paper is to reassess whether the \comb{} combination is
+such as top-k
+\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. \Sof{Elaborate k}The goal of this paper is to reassess whether the \comb{} combination is
 worthwhile under the light of this metric and using a larger
-dataset. Developers of \acrAbrev{} techniques would directly benefit
+dataset.
+The test suite used for the empirical evaluation is the defect4j dataset which is about twice larger than the biggest test suite used in previous studies.
+Developers of \acrAbrev{} techniques may directly benefit
 from these results~---~either to improve their results or to be aware
 they should not invest on this integration. 
-
 %% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
 
-\Fix{Mention the research questions at some point, plus contributions.}
+This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):
+
+\begin{itemize}[leftmargin=*]
+	\item[] \textbf{\RQ{}1} \textit{Does the critical slice include the faulty statements?}
+	\item[] \textbf{\RQ{}2} \textit{How many test cases have the faulty statements in the top-5 of classes with the highest suspiciousness ranks?}
+	\item[] \textbf{\RQ{}3} \textit{How effective is the \sfl{}+\ds{} combination for bug localization?} 
+\end{itemize}
+
+A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
+\morpho{} retrieves as an output the input for \lithium{}.
+\lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization.
+\morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}.
+
+The most significant contributions of this research for the testing community are the following ones:
+\begin{itemize}
+	\item The presentation of a more extensive evaluation on the efficiency of combining \sfl{} and \ds{} for bug localization in \emph{Java} faulty programs.
+	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
+	\item Both tools are open-source (\morpho{} and \lithium{}), so other researchers can replicate or extent the current research. Benchmarks and experimental results are also publicly available.
+\end{itemize}
+
+\Sof{@TODO: sections organization paragraph}
+
+This paper is organized as follows: ....
 
@@
 relevant parts of the program with respect to given points of
-interest.  This paper focuses on dynamic slicing\Comment{~--~as
+interest.  This paper focuses on dynamic slicing\comments{~--~as
   opposed to static slicing~\cite{Weiser:1981:PS:800078.802557}~--~}
@@
 Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
-simplicity/generality.\Comment{ In constrast with alternative slicing
+simplicity/generality.\comments{ In constrast with alternative slicing
   implementations based on dependency
-  chains~\cite{Tip:1994:SPS:869354}\Comment{(\eg{},
+  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
     JSlice~\cite{Wang:2004:UCB:998675.999455} and
@@
 scores and reported to the user. Ochiai is one of those fault
-predictors that has shown to perform well~\Fix{cite}. The Ochiai
+predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}. \Sof{@Rui, please check if the papers are correct} The Ochiai
 formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
-$\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10})}$.
+\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10})}\]
 
@@
 
-\Mar{Sofia, please add a short (3-4 lines at most) example based on
-  one of our subjects} Section~\ref{sec:impl} explains the heuristics
+\Sof{@todo: Add a short 3-4 lines at most example based on one of our subjects} Section~\ref{sec:impl} explains the heuristics
 we used to infer oracles for critical slicing that mitigates this
@@
 
-\Mar{...elaborate...}
-
-\Mar{...explain how we built our oracles/checkers...}
+Two different tools were developed to support this research: \morpho{} and \lithium{}.
+\morpho{} was designed to calculate the suspiciousness of all statements of a project before, and after the top-k minimization performed by \lithium{} whereas \lithium{} is responsible for reducing the search domain of each \texttt{Java} class of the project for the after-\sfl{} analysis.
+\morpho{} uses the spectrum matrix (Figure \ref{fig:spectrum-example}), and the pair \emph{name\#location} for each statement to calculate the respective ranking.
+All rankings are ordered from highest to lowest ranked.
+This information is retrieved along with each test case stack trace in a \texttt{.json} file which serves as an output to \lithium{}.
+\lithium{} starts by generating the inputs (Algorithm \ref{alg:ls}, line $2$) for the top-k classes of each failing test based, mainly, on the output of \emph{morpho} ~---~ ranked list of statements and the test cases stacktraces.
+Then, the tool iterates each class from the top-k classes ($c$) of each test $t$.
+In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{http://javaparser.org/} library.
+This step was added to \lithium{} because it turns \texttt{MozillaLithium}\footnote{https://github.com/MozillaSecurity/lithium} faster since the empty lines are ignored.
+Then, \texttt{MozillaLithium} performs the class minimization using a function of interest (Algorithm \ref{alg:finc}) which compares the output of the test with the expected one which is given as an input.
+Finally, the location of all relevant statements (Algorithm \ref{alg:ls}, line 9) is saved in a \texttt{.json} which is used for the before-\sfl{} analysis.
+\morpho{} uses the output from \lithium{} to create a copy of the older spectrum matrix and updates it according to the explanation provided on Figure \ref{fig:ds-reduction} where the statements that are not in the slice of the test suffer a suspiciouness reduction.
+In the end, \morpho{} performs the \sfl{} analysis for both matrixes and calculates the probability of the first line being faulty, the probability of the last line being faulty, and the mean and median of the position of the faulty line in the ranking.
+These are the metrics used to evaluate how considerable is the improvement obtained when combining \ds{} with \sfl{}.
+
+\begin{algorithm}[h]
+	\caption{Class Minimization Algorithm}
+	\label{alg:ls}
+	\begin{flushleft}
+		\textbf{Input:} $proj$ - project name \\
+		\hspace{2.75em} $bug$ - bug number\\
+		\hspace{2.75em} $k$ - number of top ranked classes\\
+		\hspace{2.75em} $stk$ - expected stacktrace\\
+	 \textbf{Output:} Top-k classes minimization for each test \\
+	\end{flushleft}
+	\begin{algorithmic}[1]
+		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
+			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
+			\ForAll {$t \in testsInfo$}
+				\State $classes \leftarrow$ getClasses($proj$, $bug$)
+				\ForAll {$c \in classes$}
+					\State $unc \leftarrow$ removeComments($c$)
+					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
+				\EndFor
+				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
+			\EndFor
+			\State \Return $slicer$
+		\EndProcedure
+	\end{algorithmic}
+
+\end{algorithm}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=1.0\textwidth]{lithium.pdf}
+	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
+\end{figure*}
+
+\subsection{Function of Interest }
+\label{sec:funcofint}
+
+\begin{algorithm}[h]
+	\caption{Function of interest (iFunc)}
+	\label{alg:finc}
+	\begin{flushleft}
+		\textbf{Input:} $c$ - class to be minimized\\
+		\hspace{2.75em} $t$ - testcase name\\
+		\hspace{2.75em} $expStk$ -  expected stacktrace\\
+		\textbf{Output:} $interest$ - $True$ if it is interesting, $False$ if not \\
+	\end{flushleft}
+	\begin{algorithmic}[1]
+		\Function{iFunc}{$c$, $t$, $expStk$}
+		\State $testStk \leftarrow$ runTest($t$)
+		\State $testOracle \leftarrow$ getOracleToCompare($testStk$)
+		\State $expOracle \leftarrow$ getOracleToCompare($expStk$)
+		\State \Return $testOracle$ == $expOracle$
+		\EndFunction
+
+	\end{algorithmic}
+
+\end{algorithm}
+
+The \texttt{MozillaLithium} tool takes as input a function of interest that can be designed according to the problem to be solved.
+The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not.
+In this study, interesting means that the test execution path is equal to the expected one.
+This information can be deducted from \texttt{Java} stack traces which show the stack of functions called until the thrown of an exception.
+The authors assume that it is only necessary to compare both stack traces until the call where the test fails.
+For each chunk selected by \texttt{MozillaLithium}, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2).
+Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails.
+These operations are performed by line 3 and 4 from Algorithm 2.
+The result is an oracle such as the one provided in the box below:
+
+\vspace{3mm}
+\begin{myframe} \label{box:1}
+java.lang.IndexOutOfBoundsException: Index: -1, Size: 1, 
+java.util.ArrayList.rangeCheckForAdd(ArrayList.java:643), 
+java.util.ArrayList.add(ArrayList.java:455), 
+org.jfree.data.xy.XYSeries.addOrUpdate(XYSeries.java:564), 
+org.jfree.data.xy.XYSeries.addOrUpdate(XYSeries.java:527), 
+\textbf{org.jfree.data.xy.junit.XYSeriesTests.}\\
+\textbf{testBug1955483(XYSeriesTests.java:479)},\\
+... 
+\end{myframe}
+
+The oracle includes an exception error message (\emph{java.lang.\\IndexOutOfBoundsException: Index: -1, Size: 1}) and the program execution path until the class test where it fails (\emph{XYSeriesTests.java:479}).
+The regular expression \verb/Test(.*).java/ retrieves the test class position in the stack trace.
+If the test class is not found, the entire stack trace is compared.
+There is, however, an exception.
+When the failure is a \emph{StackOverflowError}, there is no test class mentioned in the stack trace because the exception is a runtime error.
+This exception is triggered when the JVM encounters a situation where there is no space for a new stack frame to be created which is, normally, the outcome of infinite recursion.
+Consequently, the stack trace contains many times the failed call.
+So, when the failure message contains a \emph{StackOverflowError}, the oracle is only considered until the call is repeated for the fifth time.
+
+\vspace{3mm}
+\begin{myframe}
+	java.lang.StackOverflowError,  
+	sun.reflect.generics.reflectiveObjects.\linebreak
+			TypeVariableImpl.hashCode(TypeVariableImpl.java:198), 
+	java.util.HashMap.hash(HashMap.java:362), 
+	java.util.HashMap.getEntry(HashMap.java:462), 
+	java.util.HashMap.get(HashMap.java:417),  org.mockito.internal.util.reflection.GenericMetadataSupport.
+		getActualTypeArgumentFor(GenericMetadataSupport.java:182), \linebreak
+	org.mockito.internal.util.reflection.GenericMetadataSupport.
+	getActualTypeArgumentFor(GenericMetadataSupport.java:185),
+	org.mockito.internal.util.reflection.GenericMetadataSupport.
+	getActualTypeArgumentFor(GenericMetadataSupport.java:185),
+	...
+\end{myframe}
+
+Some of the error messages can be different even if the test is executed with the same inputs and in the same environment.
+One example is the one provided in the box below, where the memory positions (\emph{class@<memory-position>}) may differ from the ones in the expected message.
+In order to solve this, it was designed a mechanism to check this kind of exception patterns.
+However, the current version of the interesting function only considers this pattern.
+Other patterns will be added soon into the next version of \lithium{}.
+
+\vspace{3mm}
+\begin{myframe}
+	junit.framework.AssertionFailedError: \\
+	expected:<org.jfree.chart.util.ShapeList@\textbf{d0e55451}> but \\ was:<org.jfree.chart.util.ShapeList@\textbf{d951b68f}>
+	...
+\end{myframe}
 
@@
 {\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
-a mocking testing framework.\Comment{ that enables the developer to simulate
+a mocking testing framework.\comments{ that enables the developer to simulate
 the behavior of classes that cannot be used in unit testing.}
@@
       \toprule
-      Project            & Size (kLOC) & \# Tests & \# Defects \Comment{& Failing Test Cases &}  \\
+      Project            & Size (kLOC) & \# Tests & \# Defects \\ %\comments{& Failing Test Cases &}  
       \midrule
-      \lang{}            & -  & - & 65          \Comment{& 124   &  -}\\
-      \cmath{}           & -  & - & 106          \Comment{& 177   &  -}\\
-      \closure{}         & -  & - & 133         \Comment{& 350   &  -}\\
-      \chart{}           & -  & - & 26         \Comment{& 92    &  -}\\
-      \jtime{}           & -  & - & 27          \Comment{& 76    &  -}\\
-      \mockito{}         & -  & - & 38          \Comment{& 118   &  -}\\
+      \lang{}            & -  & - & 65       \\   %\commentst{& 124   &  -}\\
+      \cmath{}           & -  & - & 106     \\   %\comments{& 177   &  -}\\
+      \closure{}         & -  & - & 133     \\   %\comments{& 350   &  -}\\
+      \chart{}           & -  & - & 26      \\  %\comments{& 92    &  -}\\
+      \jtime{}           & -  & - & 27       \\   %\comments{& 76    &  -}\\
+      \mockito{}         & -  & - & 38    \\     %\comments{& 118   &  -}\\
       \bottomrule
@@
 
-\begin{figure*}[!ht]
-  \centering
-    \begin{tabular}{cl|rrrrrrrrrr}
-      \toprule
-      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
-      \midrule
-
-      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
-      \midrule
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
-      & \lang{}       & 24.72 & 25.84 & 28.09 & 32.58 & 35.96 & 46.07 & 79.78 & 79.78 & 83.15 & 84.27 \\
-      & \chart{}      & 18.97 & 24.14 & 31.03 & 31.03 & 32.76 & 72.41 & 72.41 & 75.86 & 79.31 & 79.31 \\
-      & \jtime{}      & 34.78 & 58.7  & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 71.74 & 71.74 \\
-      & \mockito{}    & 44.32 & 47.73 & 57.95 & 61.36 & 61.36 & 63.64 & 65.91 & 70.45 & 76.14 & 77.27 \\
-      \hline
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
-      & \lang{}       & 31.46 & 37.08 & 51.69 & 57.3  & 65.17 & 77.53 & 80.9  & 82.02 & 87.64 & 91.01 \\
-      & \chart{}      & 43.1  & 46.55 & 60.34 & 81.03 & 94.83 & 96.55 & 96.55 & 96.55 & 96.55 & 98.28 \\
-      & \jtime{}      & 50.0  & 63.04 & 63.04 & 63.04 & 63.04 & 67.39 & 71.74 & 71.74 & 71.74 & 71.74 \\
-      & \mockito{}    & 45.45 & 47.73 & 60.23 & 60.23 & 61.36 & 62.5  & 67.05 & 76.14 & 79.55 & 80.68 \\
-      \midrule
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest.pdf}}\\
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}\\
-
-      \midrule
-
-      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
-      \midrule
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
-      & \lang{}     & 33.71 & 41.57 & 49.44 & 52.81 & 60.67 & 84.27 & 94.38 & 95.51 & 96.63 & 98.88 \\
-      & \chart{}    & 25.86& 36.21& 36.21& 36.21& 60.34& 75.86& 75.86 & 79.31& 79.31& 79.31 \\
-      & \jtime{}       & 43.48 & 63.04 & 65.22 & 69.57 & 71.74 & 71.74 &73.91 & 73.91 & 73.91 & 73.91 \\
-      & \mockito{} & 72.09 & 74.42 & 77.91 & 80.23 & 83.72 & 83.72 & 84.88 & 84.88 & 86.05 & 86.05 \\
-      \midrule
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
-      & \lang{}     & 46.07 & 58.43 & 66.29 & 67.42 & 74.16 & 93.26 & 97.75 & 98.88 & 100.0 & 100.0 \\
-      & \chart{} & 51.72& 63.79& 65.52& 86.21& 98.28& 98.28& 98.28& 98.28& 98.28& 98.28 \\
-      & \jtime{} & 65.22 & 69.57 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 \\
-      & \mockito{} & 73.26 & 77.91 & 82.56 & 87.21 & 87.21 & 88.37 &91.86 & 94.19 & 95.35 & 95.35 \\
-      \midrule
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest-filtering.pdf}}\\
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}\\
-
-      \bottomrule
-
-    \end{tabular}
-    \caption{\label{fig:one-failing-test}Top@N, considering one failing test.}
-\end{figure*}
-
-\begin{figure*}[!ht]
-  \centering
-    \begin{tabular}{cl|rrrrrrrrrr}
-      \toprule
-      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
-      \midrule
-
-      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
-      \midrule
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\sfl}}}
-      &Apache commons-lang     & 25.0  & 27.27 & 29.55 & 38.64 & 43.18
-      & 56.82 & 63.64 & 63.64 & 68.18 & 70.45 \\
-      &\chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 87.5  & 93.75 & 93.75 \\
-      &Joda-Time       & 23.08 & 38.46 & 46.15 & 46.15 & 46.15 & 46.15
-      & 46.15 & 46.15 & 46.15 & 46.15 \\
-      &Mockito & 16.67 & 29.17 & 33.33 & 37.5  & 37.5  & 41.67 & 45.83
-      & 54.17 & 58.33 & 62.5 \\
-      \hline
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\comb}}}
-      &Apache commons-lang     & 36.36 & 50.0  & 56.82 & 59.09 & 63.64
-      & 65.91 & 65.91 & 68.18 & 75.0  & 81.82 \\
-      & \chart{}       & 68.75 & 81.25 & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
-      &Joda-Time       & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15
-      & 46.15 & 46.15 & 46.15 & 46.15 \\
-      &Mockito & 20.83 & 29.17 & 41.67 & 41.67 & 41.67 & 45.83 & 58.33
-      & 66.67 & 70.83 & 75.0 \\
-      \midrule
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest.pdf}}\\
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}\\
-      \midrule
-
-      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
-      \midrule
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
-      & \lang{}     & 36.36 & 45.45 & 59.09 & 63.64 & 70.45  & 79.55 & 88.64 & 90.91 & 93.18 & 97.73 \\
-      & \chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 93.75 & 93.75 & 93.75 \\
-      & \jtime{}        & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15  & 53.85 & 53.85 & 53.85 & 53.85 \\
-      & \mockito{} & 50.0  & 54.17 & 62.5  & 66.67 & 70.83 & 75.0  & 79.17 & 79.17 & 79.17 & 79.17 \\
-      \hline
-      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
-      & \lang{}     & 56.82 & 81.82 & 93.18 & 93.18 & 95.45  & 95.45 &95.45 & 97.73 & 100.0 & 100.0 \\
-      & \chart{}       & 68.75 & 87.5  & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
-      & \jtime{}        & 53.85 & 53.85 & 53.85 & 53.85 & 53.85 & 53.85  & 53.85 & 53.85 & 53.85 & 53.85 \\
-      & \mockito{} & 54.17 & 70.83 & 79.17 & 83.33 & 83.33 & 87.5  & 87.5 & 87.5  & 91.67 & 91.67 \\
-      \midrule
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest-filtering.pdf}}\\
-
-      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
-      &
-      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}\\
-      \bottomrule
-
-    \end{tabular}
-    \caption{\label{fig:all-failing-test}Top@N, considering all failing test.}
-\end{figure*}
+%
+%\begin{figure*}[!ht]
+%  \centering
+%    \begin{tabular}{cl|rrrrrrrrrr}
+%      \toprule
+%      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
+%      \midrule
+%
+%      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
+%      \midrule
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
+%      & \lang{}       & 24.72 & 25.84 & 28.09 & 32.58 & 35.96 & 46.07 & 79.78 & 79.78 & 83.15 & 84.27 \\
+%      & \chart{}      & 18.97 & 24.14 & 31.03 & 31.03 & 32.76 & 72.41 & 72.41 & 75.86 & 79.31 & 79.31 \\
+%      & \jtime{}      & 34.78 & 58.7  & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 71.74 & 71.74 \\
+%      & \mockito{}    & 44.32 & 47.73 & 57.95 & 61.36 & 61.36 & 63.64 & 65.91 & 70.45 & 76.14 & 77.27 \\
+%      \hline
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
+%      & \lang{}       & 31.46 & 37.08 & 51.69 & 57.3  & 65.17 & 77.53 & 80.9  & 82.02 & 87.64 & 91.01 \\
+%      & \chart{}      & 43.1  & 46.55 & 60.34 & 81.03 & 94.83 & 96.55 & 96.55 & 96.55 & 96.55 & 98.28 \\
+%      & \jtime{}      & 50.0  & 63.04 & 63.04 & 63.04 & 63.04 & 67.39 & 71.74 & 71.74 & 71.74 & 71.74 \\
+%      & \mockito{}    & 45.45 & 47.73 & 60.23 & 60.23 & 61.36 & 62.5  & 67.05 & 76.14 & 79.55 & 80.68 \\
+%      \midrule
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest.pdf}}\\
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}\\
+%
+%      \midrule
+%
+%      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
+%      \midrule
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
+%      & \lang{}     & 33.71 & 41.57 & 49.44 & 52.81 & 60.67 & 84.27 & 94.38 & 95.51 & 96.63 & 98.88 \\
+%      & \chart{}    & 25.86& 36.21& 36.21& 36.21& 60.34& 75.86& 75.86 & 79.31& 79.31& 79.31 \\
+%      & \jtime{}       & 43.48 & 63.04 & 65.22 & 69.57 & 71.74 & 71.74 &73.91 & 73.91 & 73.91 & 73.91 \\
+%      & \mockito{} & 72.09 & 74.42 & 77.91 & 80.23 & 83.72 & 83.72 & 84.88 & 84.88 & 86.05 & 86.05 \\
+%      \midrule
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
+%      & \lang{}     & 46.07 & 58.43 & 66.29 & 67.42 & 74.16 & 93.26 & 97.75 & 98.88 & 100.0 & 100.0 \\
+%      & \chart{} & 51.72& 63.79& 65.52& 86.21& 98.28& 98.28& 98.28& 98.28& 98.28& 98.28 \\
+%      & \jtime{} & 65.22 & 69.57 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 \\
+%      & \mockito{} & 73.26 & 77.91 & 82.56 & 87.21 & 87.21 & 88.37 &91.86 & 94.19 & 95.35 & 95.35 \\
+%      \midrule
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest-filtering.pdf}}\\
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}\\
+%
+%      \bottomrule
+%
+%    \end{tabular}
+%    \caption{\label{fig:one-failing-test}Top@N, considering one failing test.}
+%\end{figure*}
+%
+%\begin{figure*}[!ht]
+%  \centering
+%    \begin{tabular}{cl|rrrrrrrrrr}
+%      \toprule
+%      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
+%      \midrule
+%
+%      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
+%      \midrule
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\sfl}}}
+%      &Apache commons-lang     & 25.0  & 27.27 & 29.55 & 38.64 & 43.18
+%      & 56.82 & 63.64 & 63.64 & 68.18 & 70.45 \\
+%      &\chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 87.5  & 93.75 & 93.75 \\
+%      &Joda-Time       & 23.08 & 38.46 & 46.15 & 46.15 & 46.15 & 46.15
+%      & 46.15 & 46.15 & 46.15 & 46.15 \\
+%      &Mockito & 16.67 & 29.17 & 33.33 & 37.5  & 37.5  & 41.67 & 45.83
+%      & 54.17 & 58.33 & 62.5 \\
+%      \hline
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\comb}}}
+%      &Apache commons-lang     & 36.36 & 50.0  & 56.82 & 59.09 & 63.64
+%      & 65.91 & 65.91 & 68.18 & 75.0  & 81.82 \\
+%      & \chart{}       & 68.75 & 81.25 & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
+%      &Joda-Time       & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15
+%      & 46.15 & 46.15 & 46.15 & 46.15 \\
+%      &Mockito & 20.83 & 29.17 & 41.67 & 41.67 & 41.67 & 45.83 & 58.33
+%      & 66.67 & 70.83 & 75.0 \\
+%      \midrule
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest.pdf}}\\
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}\\
+%      \midrule
+%
+%      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
+%      \midrule
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
+%      & \lang{}     & 36.36 & 45.45 & 59.09 & 63.64 & 70.45  & 79.55 & 88.64 & 90.91 & 93.18 & 97.73 \\
+%      & \chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 93.75 & 93.75 & 93.75 \\
+%      & \jtime{}        & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15  & 53.85 & 53.85 & 53.85 & 53.85 \\
+%      & \mockito{} & 50.0  & 54.17 & 62.5  & 66.67 & 70.83 & 75.0  & 79.17 & 79.17 & 79.17 & 79.17 \\
+%      \hline
+%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
+%      & \lang{}     & 56.82 & 81.82 & 93.18 & 93.18 & 95.45  & 95.45 &95.45 & 97.73 & 100.0 & 100.0 \\
+%      & \chart{}       & 68.75 & 87.5  & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
+%      & \jtime{}        & 53.85 & 53.85 & 53.85 & 53.85 & 53.85 & 53.85  & 53.85 & 53.85 & 53.85 & 53.85 \\
+%      & \mockito{} & 54.17 & 70.83 & 79.17 & 83.33 & 83.33 & 87.5  & 87.5 & 87.5  & 91.67 & 91.67 \\
+%      \midrule
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest-filtering.pdf}}\\
+%
+%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
+%      &
+%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}\\
+%      \bottomrule
+%
+%    \end{tabular}
+%    \caption{\label{fig:all-failing-test}Top@N, considering all failing test.}
+%\end{figure*}
 
@@
 Program Slicing~\cite{Weiser:1981:PS:800078.802557} is a technique to
-identify program entities (the slice)\Comment{that influence the
+identify program entities (the slice)\comments{that influence the
   computation of} computationally related to a user-provided point of

### 2018-11-16 paper/main.tex
object of analysis done + evaluation structure

@@
       \midrule
-      \lang{}            & -  & - & 65       \\   %\commentst{& 124   &  -}\\
-      \cmath{}           & -  & - & 106     \\   %\comments{& 177   &  -}\\
-      \closure{}         & -  & - & 133     \\   %\comments{& 350   &  -}\\
-      \chart{}           & -  & - & 26      \\  %\comments{& 92    &  -}\\
-      \jtime{}           & -  & - & 27       \\   %\comments{& 76    &  -}\\
-      \mockito{}         & -  & - & 38    \\     %\comments{& 118   &  -}\\
+      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
+      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
+      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
+      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
+      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
+      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
       \bottomrule
@@
 
-\subsubsection{How much reduction in one execution trace
-  can one get with Dynamic Slicing?}
-
-Table~\ref{fig:ds-reduction} shows the average reduction obtained with
-slicing considering our implementation. The first column shows the \dfj{} project name.
-Column ``Stmts. Covered'' shows the number of statements covered in
-the execution of one failing test, column ``Slice Size'' shows the
-number of statements appearing in the slice size, and column ``\%
-Reduction'' shows the percentage reduction obtained. Numbers reported
-are averaged across all executions. We only considered cases where we
-knew a priori the slice contained the faulty statements
-(Section~\ref{sec:ds-limitations}). Overall, it is noticeable that
-both absolute reduction (as per column ``Slice Size'') and relatitve
-reduction (as per column ``\% Reduction'') obtained are
-significant.
-
-\begin{table}[h]
-  \centering
-  %  \resizebox{\columnwidth}{!}{%
-  \setlength{\tabcolsep}{3pt}
-    \begin{tabular}{lrrrr}
-      \toprule
-      Project             & Stmts. & Slice &
-      \multicolumn{2}{c}{Reduction} \\
-      \cline{4-5}
-                          &  Covered &  Size  & \multicolumn{1}{c}{Avg.} & \multicolumn{1}{c}{$\sigma$}\\
-      \midrule
-      \lang{}             & 4,221             & 94            &  97.77\%  & -       \\
-      \cmath{}            & 743,587           & 175           &  90.16\%  & 14.98\% \\
-      \closure{}          & -                 & -             &  -        & -       \\
-      \chart{}            & 13,474            & 155           &  90.26\%  & 16.52\% \\
-      \jtime{}            & 23,360            & 912           &  95.99\%  & 01.25\% \\
-      \mockito{}          & 3,064             & 340           &  82.48\%  & 12.02\% \\
-      \bottomrule
-  \end{tabular}
-%}
-\caption {\label{fig:ds-reduction}Average reduction in slice sizes. We
-  rounded averages to the closest integer in columns
-  ``Stmts. Covered'' and ``Slice Size''.\Mar{Para a coluna
-    avg. reduction, o correto IMO eh tirar a media das reducoes e nao a
-    reducao media.  Mais precisamente, considerando lang, ao inves de
-    calcular 100*(4221-94)/4221 (como acima), deveriamos tirar a media
-das reducoes considerando cada caso de lang.}\Mar{Nao costumo ver
-    desvio padrao como percentagem}}
-\end{table}
-\normalsize
-
-\subsubsection{What are the limitations of Dynamic Slicing?}
-\label{sec:ds-limitations}
-
-%% Omission errors, implicit dependencies, and multiple regression faults
-%% can result in bug misses.  Omission errors occur when existing code
-%% requires no modification but new code is needed to fix a
-%% bug. Consequently, the slice of a failing test that manifests an
-%% omission error misses the faulty statements as they are yet to be
-%% added in code.  Figure~\Fix{ref} shows an example of omission
-%% error.\Mar{add example}\Mar{consider removing omission errors as
-%%   \sfl{} cannot handle this case anyway.  check what we did on ICST'17
-%%   paper.}
-
-%% \begin{figure}[h!]
-%%   \begin{lstlisting}[frame=single]  % Start your code-block
-%%     int myMethod(int myParam) {
-%%       var result: Int = 0
-%%       //result = myParam //This line is missing
-%%       if (myParam <= 10) {
-%%         result = result / 10
-%%       }
-%%       return result
-%%     }
-%%   \end{lstlisting}
-%%   \caption{\Luis{Exemplo de falha de omissao do tipo \textbf{New Code}}}
-%%   \label{example-new-code}
-%% \end{figure}
-
-The pie chart in Figure~\ref{pie-chart} highlights the sources of
-problems associated with slicing.  We classify the slicing task as
-problematic when it misses the faulty statement. A number of reasons
-can explain a miss:
-
-\begin{itemize}
-\item \textbf{Missing code:} this case happens when the
-bug is due to missing code. Any fault localization method, including
-Slicing and \sfl{}, are innefective in this case. This is the main
-source of problem we found in our dataset. Note that, although this
-problem is not specific to slicing, executable slices could be used to
-help the developer identify missing statements with
-inspection.
-
-\item \textbf{Non-observable effect:} This case happens when the
-buggy code does not produce effect on the output. Consider, for
-example, the scenario where there is a bug in a branch predicate that
-results in execution not taking the branch guarded by a
-conditional. In that case, the \CS{} is able to produce a slice that
-does not contain the faulty if statement, still reproducing the
-original output. This problem is specific to \CS{}. Note from the
-piechart that this is the second most prevalent source of problem but
-much less significant compared to missing
-code.
-
-\item \textbf{Non-deterministic output:} This case happens when the
-  output of the program changes in every execution, such as random
-  output sizes. Although, we handled specific cases such as that of a
-  hashcode printed on the stack trace, which we are able to detect
-  with re-execution, in general, \CS{} cannot pinpoint those cases.
-  Consider, for example, the case of a stack overflow where the trace
-  can vary from one execution to another.
-
-%% There are supported cases, such as small changes in the output (i.e.,
-%% hashcode of an object printed in the stack trace). Although,
-%% StackOverflowException is not one of those cases, which the size of
-%% lines printed is not the same.
-
-\end{itemize}
-
-\begin{figure}[ht]
-  \centering
-  \begin {tikzpicture}
-    \pie[
-      text=pin,
-      radius=1.5,
-      color={
-        white!22.1,
-        white!14.7,
-        white!1.6,
-        white!61.6
-      }
-    ]{
-      61.6/{Missing Code (117)},
-      14.7/{Non-Observable Effect (28)},
-      1.6/{Non-deterministic Output (3)},
-      22.1/{REMOVEME (42)}
-    }
-  \end {tikzpicture}
-  \caption{\label{pie-chart}Source of problems in \Fix{XX} of the
-    \Fix{YY} cases where Dynamic Slicing misses the faulty statement.}
-\end{figure}
-
-\Fix{I was left wondering: so what? What is the message and the actionable points?}
-\Fix{The goal of this paper is debugging, so we should answer the question: does
-dynamic slicing alone help in debugging?}
-
-\subsection{Results of the \comb{} combination}
-
-This section describes the results of the \comb{} combination. The
-independent variables we used in the following experiments are (i) the
-selection of tests to slice (see Section~\ref{sec:combination}) and
-(ii) whether ot not the statements covered by selected tests are
-filtered from the ranking.  Considering the first variable, the
-illustration above shows the effect of slicing code using a single
-failing test. However, we also analyzed the combination where we
-compute slices of all failing tests. Intuitively, in those cases, more
-lines in the matrix would be affected. The rationale for varying the
-selection of tests to slice is to assess the impact that the amount of
-slicing code has on performance of \sfl{}.  Considering the second
-variable, the illustration above shows the scenario where all
-components are reported in the ranking. However, we also analyzed the
-scenario where only the components covered by our selection of tests
-appear in the ranking. For the case above, only $c_2$ and $c_5$ would
-be listed.  The dependent variable we used was the performance of
-\sfl{} measured with
-Top@N~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
-which indicates, for a given value N, the percentage of faults ranked
-at position no lower than N. As recently discussed by Ang
-\etal~\cite{ang-perez-van-deursen-rui-2017}, \sfl{} researchers
-started using absolute metrics, such as Top@N, after Parnin and
-Orso~\cite{parnin-orso-2011} highlighed the bias in metrics based on
-the position of the faulty statement in the ranking relative to the
-total size of the ranking, which is often very high. It is worth
-mentioning that we used the GZoltar~\cite{gzoltar} toolset to run our
-experiments.
-
-\Fix{discutir Tabela~\ref{tab:summary}...}
-
-\begin{table}[h]
-  \centering
-  \setlength{\tabcolsep}{4pt}
-    \begin{tabular}{lrrrr}
-      \toprule
-      Project            & (1,N) & (1,F) & (A,N) & (A,F)  \\
-      \midrule
-      \lang{}            & -  & - & -  & - \\
-      \cmath{}           & -  & - & -  & - \\
-      \closure{}         & -  & - & -  & - \\
-      \chart{}           & -  & - & -  & - \\
-      \jtime{}           & -  & - & -  & - \\
-      \mockito{}         & -  & - & -  & - \\
-      \bottomrule
-  \end{tabular}
-\caption {\label{tab:summary}Summary of results considering Top@N, for
-  N=50, which is the midpoint value of N for the range we selected
-  1-100.}
-\end{table}
-\normalsize
-
-\subsubsection{What is the impact of slicing one failing test?}
-This scenario reflects the case where the developer selects one given
-test to focus debugging efforts. Figure \ref{fig:one-failing-test}
-compares the results of \sfl{} and \comb{} when slicing code
-associated with a single failing test. The top section of the figure
-shows results without filtering covered statements whereas the lower
-section shows the results with filtering. Each table shows the results of \sfl{} and \comb{}
-for increasing values of N.  The top section of each table shows the
-results for \sfl{} whereas the lower section shows results of
-\comb{}. A plot for each subject appears under the tables to
-illustrate how techniques compare. The x-axis denote the value of N
-and the y-axis denotes the value of Top@N. Informally, a quick
-increase is good~--~it means a high percentage of faults was detected
-for small values of N.\Mar{@Rui, ainda nao esta claro qual a mensagem
-  que vamos transmitir. Considerando resultados atuais, existe
-  reducao, mas parece ser pouca para N<20. Existe algum valor de N
-  considerado referencia para que a gente possa dar mais substancia ao
-  resultado?}
-
-\subsubsection{What is the impact of slicing all failing tests?}
-Table~\ref{fig:all-failing-tests} \Fix{...............}
+\Sof{@todo: after answering rqs add a subsection to discuss the performance of \ds{}}
+
+\subsubsection{\textit{Does the critical slice include the faulty statements?}}
+
+\subsubsection{\textit{How many test cases have the faulty statements in the top-5 of classes with the highest suspiciousness ranks?}}
+
+\subsection{Results of \sfl{}+\ds{} Combination}
+
+\subsubsection{\textit{How effective is the \sfl{}+\ds{} combination for bug localization?}}
+
+\subsection{Threats to validity}
+
+\pagebreak
+
+%
+%
+%\subsubsection{How much reduction in one execution trace
+%  can one get with Dynamic Slicing?}
+%
+%Table~\ref{fig:ds-reduction} shows the average reduction obtained with
+%slicing considering our implementation. The first column shows the \dfj{} project name.
+%Column ``Stmts. Covered'' shows the number of statements covered in
+%the execution of one failing test, column ``Slice Size'' shows the
+%number of statements appearing in the slice size, and column ``\%
+%Reduction'' shows the percentage reduction obtained. Numbers reported
+%are averaged across all executions. We only considered cases where we
+%knew a priori the slice contained the faulty statements
+%(Section~\ref{sec:ds-limitations}). Overall, it is noticeable that
+%both absolute reduction (as per column ``Slice Size'') and relatitve
+%reduction (as per column ``\% Reduction'') obtained are
+%significant.
+%
+%\begin{table}[h]
+%  \centering
+%  %  \resizebox{\columnwidth}{!}{%
+%  \setlength{\tabcolsep}{3pt}
+%    \begin{tabular}{lrrrr}
+%      \toprule
+%      Project             & Stmts. & Slice &
+%      \multicolumn{2}{c}{Reduction} \\
+%      \cline{4-5}
+%                          &  Covered &  Size  & \multicolumn{1}{c}{Avg.} & \multicolumn{1}{c}{$\sigma$}\\
+%      \midrule
+%      \lang{}             & 4,221             & 94            &  97.77\%  & -       \\
+%      \cmath{}            & 743,587           & 175           &  90.16\%  & 14.98\% \\
+%      \closure{}          & -                 & -             &  -        & -       \\
+%      \chart{}            & 13,474            & 155           &  90.26\%  & 16.52\% \\
+%      \jtime{}            & 23,360            & 912           &  95.99\%  & 01.25\% \\
+%      \mockito{}          & 3,064             & 340           &  82.48\%  & 12.02\% \\
+%      \bottomrule
+%  \end{tabular}
+%%}
+%\caption {\label{fig:ds-reduction}Average reduction in slice sizes. We
+%  rounded averages to the closest integer in columns
+%  ``Stmts. Covered'' and ``Slice Size''.\Mar{Para a coluna
+%    avg. reduction, o correto IMO eh tirar a media das reducoes e nao a
+%    reducao media.  Mais precisamente, considerando lang, ao inves de
+%    calcular 100*(4221-94)/4221 (como acima), deveriamos tirar a media
+%das reducoes considerando cada caso de lang.}\Mar{Nao costumo ver
+%    desvio padrao como percentagem}}
+%\end{table}
+%\normalsize
+%
+%\subsubsection{What are the limitations of Dynamic Slicing?}
+%\label{sec:ds-limitations}
+%
+%%% Omission errors, implicit dependencies, and multiple regression faults
+%%% can result in bug misses.  Omission errors occur when existing code
+%%% requires no modification but new code is needed to fix a
+%%% bug. Consequently, the slice of a failing test that manifests an
+%%% omission error misses the faulty statements as they are yet to be
+%%% added in code.  Figure~\Fix{ref} shows an example of omission
+%%% error.\Mar{add example}\Mar{consider removing omission errors as
+%%%   \sfl{} cannot handle this case anyway.  check what we did on ICST'17
+%%%   paper.}
+%
+%%% \begin{figure}[h!]
+%%%   \begin{lstlisting}[frame=single]  % Start your code-block
+%%%     int myMethod(int myParam) {
+%%%       var result: Int = 0
+%%%       //result = myParam //This line is missing
+%%%       if (myParam <= 10) {
+%%%         result = result / 10
+%%%       }
+%%%       return result
+%%%     }
+%%%   \end{lstlisting}
+%%%   \caption{\Luis{Exemplo de falha de omissao do tipo \textbf{New Code}}}
+%%%   \label{example-new-code}
+%%% \end{figure}
+%
+%The pie chart in Figure~\ref{pie-chart} highlights the sources of
+%problems associated with slicing.  We classify the slicing task as
+%problematic when it misses the faulty statement. A number of reasons
+%can explain a miss:
+%
+%\begin{itemize}
+%\item \textbf{Missing code:} this case happens when the
+%bug is due to missing code. Any fault localization method, including
+%Slicing and \sfl{}, are innefective in this case. This is the main
+%source of problem we found in our dataset. Note that, although this
+%problem is not specific to slicing, executable slices could be used to
+%help the developer identify missing statements with
+%inspection.
+%
+%\item \textbf{Non-observable effect:} This case happens when the
+%buggy code does not produce effect on the output. Consider, for
+%example, the scenario where there is a bug in a branch predicate that
+%results in execution not taking the branch guarded by a
+%conditional. In that case, the \CS{} is able to produce a slice that
+%does not contain the faulty if statement, still reproducing the
+%original output. This problem is specific to \CS{}. Note from the
+%piechart that this is the second most prevalent source of problem but
+%much less significant compared to missing
+%code.
+%
+%\item \textbf{Non-deterministic output:} This case happens when the
+%  output of the program changes in every execution, such as random
+%  output sizes. Although, we handled specific cases such as that of a
+%  hashcode printed on the stack trace, which we are able to detect
+%  with re-execution, in general, \CS{} cannot pinpoint those cases.
+%  Consider, for example, the case of a stack overflow where the trace
+%  can vary from one execution to another.
+%
+%%% There are supported cases, such as small changes in the output (i.e.,
+%%% hashcode of an object printed in the stack trace). Although,
+%%% StackOverflowException is not one of those cases, which the size of
+%%% lines printed is not the same.
+%
+%\end{itemize}
+%
+%
+%\begin{figure}[ht]
+%  \centering
+%  \begin {tikzpicture}
+%    \pie[
+%      text=pin,
+%      radius=1.5,
+%      color={
+%        white!22.1,
+%        white!14.7,
+%        white!1.6,
+%        white!61.6
+%      }
+%    ]{
+%      61.6/{Missing Code (117)},
+%      14.7/{Non-Observable Effect (28)},
+%      1.6/{Non-deterministic Output (3)},
+%      22.1/{REMOVEME (42)}
+%    }
+%  \end {tikzpicture}
+%  \caption{\label{pie-chart}Source of problems in \Fix{XX} of the
+%    \Fix{YY} cases where Dynamic Slicing misses the faulty statement.}
+%\end{figure}
+%
+%\Fix{I was left wondering: so what? What is the message and the actionable points?}
+%\Fix{The goal of this paper is debugging, so we should answer the question: does
+%dynamic slicing alone help in debugging?}
+%
+%\subsection{Results of the \comb{} combination}
+%
+%This section describes the results of the \comb{} combination. The
+%independent variables we used in the following experiments are (i) the
+%selection of tests to slice (see Section~\ref{sec:combination}) and
+%(ii) whether ot not the statements covered by selected tests are
+%filtered from the ranking.  Considering the first variable, the
+%illustration above shows the effect of slicing code using a single
+%failing test. However, we also analyzed the combination where we
+%compute slices of all failing tests. Intuitively, in those cases, more
+%lines in the matrix would be affected. The rationale for varying the
+%selection of tests to slice is to assess the impact that the amount of
+%slicing code has on performance of \sfl{}.  Considering the second
+%variable, the illustration above shows the scenario where all
+%components are reported in the ranking. However, we also analyzed the
+%scenario where only the components covered by our selection of tests
+%appear in the ranking. For the case above, only $c_2$ and $c_5$ would
+%be listed.  The dependent variable we used was the performance of
+%\sfl{} measured with
+%Top@N~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
+%which indicates, for a given value N, the percentage of faults ranked
+%at position no lower than N. As recently discussed by Ang
+%\etal~\cite{ang-perez-van-deursen-rui-2017}, \sfl{} researchers
+%started using absolute metrics, such as Top@N, after Parnin and
+%Orso~\cite{parnin-orso-2011} highlighed the bias in metrics based on
+%the position of the faulty statement in the ranking relative to the
+%total size of the ranking, which is often very high. It is worth
+%mentioning that we used the GZoltar~\cite{gzoltar} toolset to run our
+%experiments.
+%
+%\Fix{discutir Tabela~\ref{tab:summary}...}
+%
+%
+%\begin{table}[h]
+%  \centering
+%  \setlength{\tabcolsep}{4pt}
+%    \begin{tabular}{lrrrr}
+%      \toprule
+%      Project            & (1,N) & (1,F) & (A,N) & (A,F)  \\
+%      \midrule
+%      \lang{}            & -  & - & -  & - \\
+%      \cmath{}           & -  & - & -  & - \\
+%      \closure{}         & -  & - & -  & - \\
+%      \chart{}           & -  & - & -  & - \\
+%      \jtime{}           & -  & - & -  & - \\
+%      \mockito{}         & -  & - & -  & - \\
+%      \bottomrule
+%  \end{tabular}
+%\caption {\label{tab:summary}Summary of results considering Top@N, for
+%  N=50, which is the midpoint value of N for the range we selected
+%  1-100.}
+%\end{table}
+%\normalsize
+%
+%\subsubsection{What is the impact of slicing one failing test?}
+%This scenario reflects the case where the developer selects one given
+%test to focus debugging efforts. Figure \ref{fig:one-failing-test}
+%compares the results of \sfl{} and \comb{} when slicing code
+%associated with a single failing test. The top section of the figure
+%shows results without filtering covered statements whereas the lower
+%section shows the results with filtering. Each table shows the results of \sfl{} and \comb{}
+%for increasing values of N.  The top section of each table shows the
+%results for \sfl{} whereas the lower section shows results of
+%\comb{}. A plot for each subject appears under the tables to
+%illustrate how techniques compare. The x-axis denote the value of N
+%and the y-axis denotes the value of Top@N. Informally, a quick
+%increase is good~--~it means a high percentage of faults was detected
+%for small values of N.\Mar{@Rui, ainda nao esta claro qual a mensagem
+%  que vamos transmitir. Considerando resultados atuais, existe
+%  reducao, mas parece ser pouca para N<20. Existe algum valor de N
+%  considerado referencia para que a gente possa dar mais substancia ao
+%  resultado?}
+%
+%\subsubsection{What is the impact of slicing all failing tests?}
+%Table~\ref{fig:all-failing-tests} \Fix{...............}
 
@@
 
-\Mar{beware, this is >>NOT<< revised! .........................................................................}
+\Mar{beware, this is >>NOT<< revised! ................}\\
+\Sof{@todo: review this}
 
@@
 
+\section{Conclusions and Future Work}\label{sec:conc}
+
 %% Acknowledgments

### 2018-11-16 paper/main.tex
issue solved

@@
 \end{wrapfigure}
+
 Several types of spectra exist.  The most commonly used is called
@@
 \begin{figure}[t!]
+
   \centering
@@
     \caption{Spectra update.}
+    \label{fig:ds-reduction}
   \end{subfigure}
@@
 He et al. proposed a new method to automated fault localization with
-CPSS (coverage and program structure slicing)\cite{he-zhang-liu-gao-201}.  Based on program
+CPSS (coverage and program structure slicing)\cite{he-zhang-liu-gao-2014}.  Based on program
 execution path struture data dependency analysis, the idea is to

### 2018-11-16 paper/main.tex
pass on intro

--- 2018-11-16 paper/main.tex
@@
 
-\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}
+%\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}
 
@@
 reason, countless automated techniques have been proposed in the past
-to reduce the cost of fault localization. Among those are Dynamic Slicing
-(\ds{}) and Spectrum-Based Fault Localization (\sfl{}). Dynamic
-Slicing~\cite{Agrawal:1990:DPS:93542.93576} takes as input a failing
-test and produces on output a set of statements that influence the
-evaluation of the fault-revealing assertion. Although the technique
-has been intensively explored, few slicing applications became
-popular---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
-exception.  \sfl{}~\cite{7390282} is another popular automated
-debugging technique. It is a statistical fault localization method
-that computes suspiciousness values associated with program entities
-(e.g., basic blocks) using coverage information of passing and failing
-test cases. \sfl{} produces a list of program entities ranked in
-decreasing order of suspiciousness. Likewise dynamic slicing, \sfl{}
-received tremendous attention over the years, but its applicability to
-support debugging remains
+to reduce the cost of fault localization.
+
+Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
+are two very popular techniques that use different principles to
+automate debugging. Dynamic
+Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
+in code that influence the evaluation of the fault-revealing
+assertion. Although the technique has been intensively investigated in
+research, few use cases gained
+notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
+exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
+recover the influence region of faulty statements. It is a black-box
+statistical fault localization method that computes suspiciousness
+values associated with program entities (e.g., basic blocks). For
+that, it uses coverage information of passing and failing test
+cases. \sfl{} produces a list of program entities ranked in decreasing
+order of suspiciousness. Similarly to \ds{}, \sfl{} received
+tremendous attention over the years, but its applicability to support
+debugging remains
 questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
@@
 (\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
-an increasingly popular technique that looks for likely fixes to
-likely buggy statements. Tools like JAFF \cite{arcuri-2011}, Prophet
+an increasingly popular technique that looks for fixes to buggy
+statements. Tools like JAFF \cite{arcuri-2011}, Prophet
 \cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
 and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
-likely fixes. \Sof{likely appears too many times on the last 3 lines.}
+likely fixes.
 
@@
 
-\ds{} and \sfl{} are complementary. Conceptually, \ds{} identifies
-irrelevant parts of the code whereas \sfl{} ranks the relevant parts of
-the code.  This paper reports the results of an empirical study to
-evaluate the impact of \ds{} to improve \sfl{}. The intuition for the
-\comb{} combination is that several highly ranked statements, albeit
-covered by failing executions, may be unrelated to the fault. Prior
-work reported promising results in this combination
-\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012}.
-For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
-reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
-rankings when using dynamic slicing in combination with \sfl{} versus
-plain \sfl{}. We found surprising that, despite these findings,
-reported nearly 5 years ago, no tool or client analyses use this
-combination today. One hypothesis to explain that observation is that
-results reported in prior work are not as good as it seems. Prior
-research evaluated \sfl{} using relative metrics, based on the
+%% For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
+%% reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
+%% rankings when using dynamic slicing in combination with \sfl{} versus
+%% plain \sfl{}.
+
+\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
+irrelevant parts of the code whereas \sfl{} ranks the relevant parts
+of the code.  This paper reports the results of a comprehensive study
+to evaluate the impact of \ds{} to improve \sfl{}. The study involves
+\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
+dataset~\cite{just-defects4j-issta2014}, which is frequently used to
+evaluated fault localization research. The intuition for the \comb{}
+combination is that several highly ranked statements, albeit covered
+by failing executions, may be unrelated to the fault. Prior work
+reported promising results in this combination
+\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
+We found surprising that, despite these findings, reported nearly 5
+years ago, no tool or client analyses use this combination
+today. Several reasons could justify that observation. One hypothesis
+to explain that observation is that results reported in prior work are
+over-optimistic. For example, most prior work evaluated improvements
+of \sfl{} techniques using relative metrics, which are based on the
 position of the first faulty statements found in the ranking relative
-to the total number of ranking statements, which is often a very high
-number. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
-pointed to that fact encouraging developers to adopt precise metrics
-such as top-k
-\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. \Sof{Elaborate k}The goal of this paper is to reassess whether the \comb{} combination is
-worthwhile under the light of this metric and using a larger
-dataset.
-The test suite used for the empirical evaluation is the defect4j dataset which is about twice larger than the biggest test suite used in previous studies.
-Developers of \acrAbrev{} techniques may directly benefit
-from these results~---~either to improve their results or to be aware
-they should not invest on this integration. 
+to the total number of ranking statements, which is often a large
+number. As such, it inflates actual improvements and deceives paper
+reviewers. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
+pointed to that fact encouraging researchers to adopt precise metrics,
+such as \topatn{}
+\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. This
+metric reports the percentage of faults captured by a technique when
+the rank is trimmed to the first N components.
+
+The goal of this paper is to reassess whether the \comb{} combination
+is worthwhile under the light of a more accurate metric and a larger
+dataset. The D4J dataset is about twice as large than the biggest test
+suite used in previous studies. It is worth noting that \acrAbrev{}
+techniques should directly benefit from these results---either to
+improve their results or to be aware they should not invest on this
+integration. This study covers the following research questions:
+
 %% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
-
-This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):
+%% This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):
 
 \begin{itemize}[leftmargin=*]
-	\item[] \textbf{\RQ{}1} \textit{Does the critical slice include the faulty statements?}
-	\item[] \textbf{\RQ{}2} \textit{How many test cases have the faulty statements in the top-5 of classes with the highest suspiciousness ranks?}
-	\item[] \textbf{\RQ{}3} \textit{How effective is the \sfl{}+\ds{} combination for bug localization?} 
+%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}  
+\item[]{\footnotesize[soundness]}~\textit{How often DS misses faulty statements?}
+\item[]{\footnotesize[effectiveness]}~\textit{How much reduction in file size can DS obtain?}  
+\item[]{\footnotesize[effectiveness]}~\textit{How effective is the \comb{} combination?} 
 \end{itemize}
 
-A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
-\morpho{} retrieves as an output the input for \lithium{}.
-\lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization.
-\morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}.
-
-The most significant contributions of this research for the testing community are the following ones:
+To sum, our results show that \Fix{write a paragraph about this...}
+
+The contributions of this work are as follows:
 \begin{itemize}
-	\item The presentation of a more extensive evaluation on the efficiency of combining \sfl{} and \ds{} for bug localization in \emph{Java} faulty programs.
-	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
-	\item Both tools are open-source (\morpho{} and \lithium{}), so other researchers can replicate or extent the current research. Benchmarks and experimental results are also publicly available.
+	\item A comprehensive study on the combination of \sfl{} and \ds{}
+     for bug localization of \emph{Java} faulty programs.
+%	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
+	\item The tools used to run the study. Benchmarks and experimental results are also publicly available.
 \end{itemize}
-
-\Sof{@TODO: sections organization paragraph}
-
-This paper is organized as follows: ....
 
@@
 formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
-\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10})}\]
+\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}})\]
 
@@
 
+\Mar{Sofia, I think this was way too low-level for intro and decided
+  to move here. please check how to fit.}
+\Fix{
+A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
+\morpho{} retrieves as an output the input for \lithium{}.
+\lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization.
+\morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}.
+}
+
 Two different tools were developed to support this research: \morpho{} and \lithium{}.
@@
 experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
-includes six subjects and 395 faults.
+includes six subjects and \numFaults{} faults.
 \lang{} is a library

### 2018-11-16 paper/main.tex
remove comment
another pass on intro

@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
+% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
 \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
@@
 %% use defaults for review submission.
-\acmConference[PL'18]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2018}{New York, NY, USA}
-\acmYear{2018}
+\acmConference[PLDI'19]{ ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 24--26, 2019}{Phoenix, AZ, USA}
+\acmYear{2019}
 \acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
@@
 years ago, no tool or client analyses use this combination
-today. Several reasons could justify that observation. One hypothesis
-to explain that observation is that results reported in prior work are
+today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
 over-optimistic. For example, most prior work evaluated improvements
@@
 position of the first faulty statements found in the ranking relative
-to the total number of ranking statements, which is often a large
-number. As such, it inflates actual improvements and deceives paper
-reviewers. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
-pointed to that fact encouraging researchers to adopt precise metrics,
-such as \topatn{}
-\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. This
+to the total number of ranked statements, which is often a large
+number. As such, it inflates actual improvements and deceives
+potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
+pointed to that fact and encouraged researchers to adopt more precise metrics,
+such as \topk{}
+\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
+which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
 metric reports the percentage of faults captured by a technique when
-the rank is trimmed to the first N components.
+the rank is trimmed to the first $k$ components.
 
@@
 %% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
-%% This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):
+%% This research aims to address the doubts surrounding the efficiency
+%% of \sfl{}+\ds{} combination through the answer to the following
+%% research questions (\RQ{}):
+
+\newcommand{\rqone}{How often does DS miss faulty statements?}
+%\newcommand{\rqtwo}{How much reduction in file size can DS obtain?}
+\newcommand{\rqthree}{How effective is the \comb{} combination?}
+
+%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}
 
 \begin{itemize}[leftmargin=*]
-%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}  
-\item[]{\footnotesize[soundness]}~\textit{How often DS misses faulty statements?}
-\item[]{\footnotesize[effectiveness]}~\textit{How much reduction in file size can DS obtain?}  
-\item[]{\footnotesize[effectiveness]}~\textit{How effective is the \comb{} combination?} 
+\item[]{\footnotesize[(un)soundness]}~\textit{\rqone{}}
+\item[]{\footnotesize[effectiveness]}~\textit{\rqthree{}}  
 \end{itemize}
 
-To sum, our results show that \Fix{write a paragraph about this...}
+The first question addresses an important problem associated with
+dynamic slicing techniques---that of missing faulty
+statements. Naturally, the consequence of that problem for debugging
+is that developers would never be able to locate faults. Different
+slicers can miss faulty statements for different reasons. In this
+paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
+which, in principle, could miss statements because of imprecise
+oracles that guide the slicing process. We evaluated how often that
+important problem happens in our experiments. The second research
+questions effectively evaluates the impact of the combination. To sum,
+our results show that \Fix{write a paragraph about this...}
 
@@
 
+\newpage
+
 \section{Background}
@@
 %% implementations satisfying these criteria.
-%% For those reasons, we decided to implement a critical slicer for Java,
+%% For those reasons, we ded to implement a critical slicer for Java,
 %% which is the language of the subjects in our dataset, \dfj{}.

### 2018-11-16 paper/main.tex
merge
quick pass on related work

@@
 by failing executions, may be unrelated to the fault. Prior work
-reported promising results in this combination
-\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
+reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
 We found surprising that, despite these findings, reported nearly 5
@@
 \newcommand{\rqthree}{How effective is the \comb{} combination?}
-
-%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}
 
@@
 scores and reported to the user. Ochiai is one of those fault
-predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}. \Sof{@Rui, please check if the papers are correct} The Ochiai
-formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
+predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}.
+The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
 \[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}})\]
@@
 
-\Mar{beware, this is >>NOT<< revised! ................}\\
-\Sof{@todo: review this}
-
-\textbf{Program Slicing}: Most recently related tool is ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}. \Fix{...}
-
-Program Slicing~\cite{Weiser:1981:PS:800078.802557} is a technique to
-identify program entities (the slice)\comments{that influence the
-  computation of} computationally related to a user-provided point of
-interest (the slice criterion).
-
-Similarly, dynamic slicing lacks successful cases of downstream
-analyses. The WhyLine debugging assistant~\cite{whyline-website} is an
-isolated case of success.
-
-There are some approaches that utilize dynamic slicing and
-spectrum-based fault localization (SFL) as fault localization methods.
+\subsection{Program Slicing}
+
+Program Slicing is an old technique with several applications in PL
+and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
+implemented in different ways. Dynamic Slicing has found its main
+application in fault
+localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
+context, failing tests exist. Research in this area has mainly focused
+on slicing code
+efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
+and avoiding data and control omission
+errors~\cite{Zhang:2007:TLE:1250734.1250782,
+  Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
+cases where tests fail because some part of the code was not executed
+when it should. Dynamic fault localization techniques cannot hope to
+soundly report bugs in those cases. The issue is that incorporating
+static information to capture those cases can result in unacceptably
+large slices, which defeats the purpose of reducing the fault search
+space. It is worth noting that, conceptually, the \comb{} combination
+can be used with any form of dynamic slicing. We chose an
+implementation of Critical
+Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.
+
+%% ORBS~\cite{Binkley:2014:OLP:2635868.2635893,DBLP:conf/iwpc/IslamB16}
+%% is a recently-proposed slicing technique that is similar to Critical
+%% Slicing. It is worth noting that
+
+\subsection{SFL}
+
+\Mar{...Rui, please elaborate...}
+
+\subsection{\comb{}}
+
+Prior work has investigated the combination of dynamic slicing and
+spectrum-based fault
+localization~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
+the methodology used in these papers vary, the overall message is that
+the combination is valuable. Note that slicing alone does not provide
+the guarantee of improvement to \sfl{} as statements discarded with
+slicing could have been ranked lower compared to faulty
+statements. This paper differs from prior work in that it uses a much
+larger dataset of programs and faults and a more rigorous experimental
+methodology.
+
+\subsubsection{Applications}
+
+\Mar{...Rui, can you revise this? I guess Luis/Davino wrote it.}
 
@@
 
-\Fix{...}
-
-\subsection{Automatic Program Repair}
+\subsubsection{Automatic Program Repair}
 Automated repair techiniques have received considerable attention on
@@
 \Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }
-
-\subsection{Dynamic Slicing and Statistical Fault Localization}
-
-Previous works studied the impact of bringing together both dynamic
-slicing and statistical fault localization applied to software
-debugging.
-
-Lei et al. proposed the use of program slices built with a
-dynamic backward slicing approach to defined statistical variables
-which can capture the influence of a statement execution on the output
-using SFL quantification of suspiciousness to each statement\cite{lei-mao-dai-wang-2012}.
-
-Ishii and Kutsuna proposed a fault localization method with dynamic slicing that iteratively generates failing test cases using Satisfiability Modulo Theories (SMT) solvers to get distinct slices
-for each test case. The proposed method was evaluated using MATLAB/Simulink models\cite{ishii-kutsuna-2016}.
-
-Acknowledging the dependencies problem to locate a fault in the probram, Wen\cite{wen-2012} combines the concept of critical slicing, i.e., deleting statements with no contributions to faults,
-with statistical fault localization proposing a program slicing spectrum-based software fault localization model.
-
-He et al. proposed a new method to automated fault localization with
-CPSS (coverage and program structure slicing)\cite{he-zhang-liu-gao-2014}.  Based on program
-execution path struture data dependency analysis, the idea is to
-extract execution paths streamlined into a complete program dependence
-path, reverse data dependence analysis and calculate the defect rate
-with state of the art SFL techiniques (i.e., Tarantula).
-
-\subsection{Other}
-
-\Mar{moved to here...revise when possible...}
-
-For example,
-dependency tracking alternatives such as
-JSlice~\cite{Wang:2004:UCB:998675.999455} and
-JavaSlicer~\cite{hammacher-bachthesis-2008} instrument the analyzed
-code~\cite{hammacher-bachthesis-2008} or modify
-interpreters~\cite{Wang:2004:UCB:998675.999455} to build compact
-execution traces.  Then, they process the traces to reconstruct
-program states; this step recovers the dependency chains rooted in
-points of interest.
-
-ORBS~\cite{Binkley:2014:OLP:2635868.2635893} is a observation-based
-slicing method independent of programming language. ORBS deletes
-statements in the files of interest and checks whether the test output is
-the same as the original
-test~\cite{Binkley:2014:OLP:2635868.2635893}.
-
-\Fix{revise? merge?}
-Observation-Based Slicing technique, similar to Critical Slicing, is
-based on deleting statements that are not relevant to the test case
-failure. Although, with this technique is possible to remain the rest
-of the system untouched.
 

### 2018-11-16 paper/main.tex
related work on sfl

@@
 
-\Mar{...Rui, please elaborate...}
+Statistics-based techniques (e.g.,~\cite{Pearson:2017:EIF:3097368.3097441}) are
+popular automated fault localization techniques within the Software Engineering
+community. They correlate information about program fragments that have been
+exercised in multiple program execution traces (also called \textit{program
+spectra}) with information about successful and failing executions. By doing
+that, statistics-based approaches yield a list of suspect program fragments
+sorted by their likelihood to be at fault. Since this technique is efficient in
+practice, it is attractive for large modern software systems~\cite{ecbs07}.
+
+Spectrum-based fault localization (\sfl) is amongst the most common statistical
+fault localization technique that takes as input a test suite including at least
+one failing test and reports on output a ranked list of components likely to be
+in fault~\cite{FLSurvey2016, DBLP:conf/kbse/JonesH05,
+DBLP:journals/smr/LuciaLJTB14, DBLP:journals/jss/AbreuZGG09}.
 
@@
 
-\Mar{...Rui, can you revise this? I guess Luis/Davino wrote it.}
-
 Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
 technique involving dynamic slicing and SFL applied to MATLAB/Simulink
-models.The technique consists of iteratively
+models. The technique consists of iteratively
 generating tests that cause an error using satisfiability modulo

### 2018-11-19 paper/main.tex
results

--- 2018-11-16 paper/main.tex
@@
-% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
+%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
 \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
@@
 %% use defaults for review submission.
-\acmConference[PLDI'19]{ ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 24--26, 2019}{Phoenix, AZ, USA}
-\acmYear{2019}
+\acmConference[PL'18]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2018}{New York, NY, USA}
+\acmYear{2018}
 \acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
@@
 years ago, no tool or client analyses use this combination
-today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
+today. Several reasons could justify that observation. One hypothesis
+to explain that observation is that results reported in prior work are
 over-optimistic. For example, most prior work evaluated improvements
@@
 position of the first faulty statements found in the ranking relative
-to the total number of ranked statements, which is often a large
-number. As such, it inflates actual improvements and deceives
-potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
-pointed to that fact and encouraged researchers to adopt more precise metrics,
-such as \topk{}
-\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
-which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
+to the total number of ranking statements, which is often a large
+number. As such, it inflates actual improvements and deceives paper
+reviewers. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
+pointed to that fact encouraging researchers to adopt precise metrics,
+such as \topatn{}
+\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. This
 metric reports the percentage of faults captured by a technique when
-the rank is trimmed to the first $k$ components.
+the rank is trimmed to the first N components.
 
@@
 %% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
-%% This research aims to address the doubts surrounding the efficiency
-%% of \sfl{}+\ds{} combination through the answer to the following
-%% research questions (\RQ{}):
-
-\newcommand{\rqone}{How often does DS miss faulty statements?}
-%\newcommand{\rqtwo}{How much reduction in file size can DS obtain?}
-\newcommand{\rqthree}{How effective is the \comb{} combination?}
-
+%% This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):
+
+\begin{itemize}[leftmargin=*]
 %\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}  
-
-\begin{itemize}[leftmargin=*]
-\item[]{\footnotesize[(un)soundness]}~\textit{\rqone{}}
-\item[]{\footnotesize[effectiveness]}~\textit{\rqthree{}}  
+\item[]{\footnotesize[soundness]}~\textit{How often DS misses faulty statements?}
+\item[]{\footnotesize[effectiveness]}~\textit{How much reduction in file size can DS obtain?}  
+\item[]{\footnotesize[effectiveness]}~\textit{How effective is the \comb{} combination?} 
 \end{itemize}
 
-The first question addresses an important problem associated with
-dynamic slicing techniques---that of missing faulty
-statements. Naturally, the consequence of that problem for debugging
-is that developers would never be able to locate faults. Different
-slicers can miss faulty statements for different reasons. In this
-paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
-which, in principle, could miss statements because of imprecise
-oracles that guide the slicing process. We evaluated how often that
-important problem happens in our experiments. The second research
-questions effectively evaluates the impact of the combination. To sum,
-our results show that \Fix{write a paragraph about this...}
+To sum, our results show that \Fix{write a paragraph about this...}
 
@@
 
-\newpage
-
 \section{Background}
@@
 %% implementations satisfying these criteria.
-%% For those reasons, we ded to implement a critical slicer for Java,
+%% For those reasons, we decided to implement a critical slicer for Java,
 %% which is the language of the subjects in our dataset, \dfj{}.
@@
 
-We describe the results of dynamic slicing alone in the following.
-
-\Sof{@todo: after answering rqs add a subsection to discuss the performance of \ds{}}
-
-\subsubsection{\textit{Does the critical slice include the faulty statements?}}
-
-\subsubsection{\textit{How many test cases have the faulty statements in the top-5 of classes with the highest suspiciousness ranks?}}
-
-\subsection{Results of \sfl{}+\ds{} Combination}
+We describe the results of dynamic slicing alone in the following
+
+\subsubsection{\textit{How often DS misses faulty statements?}}
+
+From the t
+
+\begin{table*}[h]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrrrrrrr}
+		\toprule
+		Project             & \#FS  & \# T & \# Ev & \#Bugs & \%  $\overline{in}$ &  \% top-k & \% in  \\ 
+		\midrule
+		\chart{} 	& 40 &  57  &  136 & 21 & 13.2\% & 0\% & 86.8\%   \\
+		\closure{} 	& 56 &  10  &  81 & 6 & 0\% & 3.7\% & 96.3\%   \\
+		\lang{} 	& 204 &  90  &  447 & 59 & 0\% & 0\% & 100\%   \\
+		\cmath{} 	& 299 &  112  &  438 & 86 & 8\% & 2.1\% & 89.9\%   \\
+		\mockito{} 	& 94 &  93  &  397 & 25 & 3.3\% & 3.5\% & 93.2\%   \\
+		\jtime{} 	& 63 &  49  &  171 & 16 & 1.2\% & 0\% & 98.8\%   \\
+				\midrule
+				Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
+		%		\lang{}             & 100\% &  90  &  59  \\
+		%		\cmath{}           & 96.4\% & 111   & 86  \\   
+		%		\closure{}         & 100 \%  & 10  & 6   \\   
+		%		\chart{}            &  86.8\% &  57  &  21 \\ 
+		%		\jtime{}           &  &     &    \\   
+		%		\mockito{}     & 100\% & 25  & 38  \\    
+	\end{tabular}
+	\caption {\ds{} performance evaluation}
+\end{table*}
+\normalsize
 
@@
 
+\begin{table*}[h]
+	\centering
+	\setlength{\tabcolsep}{2pt}
+	\begin{tabular}{lrrrrrrrr}
+		\toprule
+
+		Project             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}
+		\midrule
+
+			\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
+		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
+		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
+			\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
+		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
+		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
+	\end{tabular}
+	\caption {\sfl{}+\ds{} performance evaluation}
+\end{table*}
+\normalsize
+
 \subsection{Threats to validity}
-
-\pagebreak
 

### 2018-11-19 paper/main.tex
lithium illustration added to figures folder
results metrics meaning

@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{lithium.pdf}
+	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
 	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
@@
 
+\subsection{Experiments}
+
+These experiments only consider 213 of 395 bugs of the \dfj. 
+Each bug has one or more failing tests associated.
+For each test, it is verified if all the faulty statements of the bug are in the slicer.
+\#Ev is the total number of verifications performed by bug.
+For each bug ($i$) of the project, this experiment checks if all the faulty statements of the bug ($FS_i$) are in the slicer retrieved by each test ($T_i$).
+$n$ is the total number of bugs considered for each project.
+
+$$\#Ev = \sum_{i=1}^{n} T_i * FS_i$$
+
+\Sof{It does not make much sense to report \#Bugs here. If we end up not using the all dataset I think it would be better to report this in another section.}
+To evaluate the performance of \ds{} alone, the following metrics were taken into consideration: the total number of faulty statements ($\#FS$) in each project; the total number of tests ($\#T$) in each project; the number of times that each $FS$ may be in the slicer of each $T$, $\#Ev$; the number of bugs considered per project to the experiments, $\#Bugs$; the percentage of $FS$ that are not in the slicers of $T$, \% $\overline{in}$; the percentage of $FS$ that are not found in the top-5 of the classes with the highest ranks of suspiciousness; and, the percentage of $FS$ that are in the slicers of $T$.
+Regarding the \sfl{}+\ds{} combination, performance is evaluated based on four different metrics: the probability of the first line being the faulty one, $\% imp(f)$; the probability of the last line being the faulty one, $\% imp(l)$; and, finally the mean, $\% imp(\overline{m})$, and median $\% imp (median)$ of the position of the faulty line in the ranking.
+This combination is evaluated considering all the classes of the project (all) and only the classes of the project involved in the failing tests execution (loaded).
+
 \subsection{Results of Dynamic Slicing}
 
-We describe the results of dynamic slicing alone in the following
+We describe the results of dynamic slicing alone in the following sections.
 
 \subsubsection{\textit{How often DS misses faulty statements?}}
-
-From the t
 
@@
 	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lrrrrrrr}
+	\begin{tabular}{lccccccc}
 		\toprule
@@
 		\jtime{} 	& 63 &  49  &  171 & 16 & 1.2\% & 0\% & 98.8\%   \\
-				\midrule
+		\bottomrule
 				Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
-		%		\lang{}             & 100\% &  90  &  59  \\
-		%		\cmath{}           & 96.4\% & 111   & 86  \\   
-		%		\closure{}         & 100 \%  & 10  & 6   \\   
-		%		\chart{}            &  86.8\% &  57  &  21 \\ 
-		%		\jtime{}           &  &     &    \\   
-		%		\mockito{}     & 100\% & 25  & 38  \\    
 	\end{tabular}
-	\caption {\ds{} performance evaluation}
+	\caption {Report of the capability of \ds{} on missing faulty statements}
 \end{table*}
@@
 	\setlength{\tabcolsep}{2pt}
-	\begin{tabular}{lrrrrrrrr}
+	\begin{tabular}{lcccccccc}
 		\toprule
 
-		Project             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}
+			    \multirow{2}{*}{Project}   & \multicolumn{4}{c}{all} & \multicolumn{4}{c}{loaded}  \\
+
+		             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
 		\midrule
@@
 		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
+		\bottomrule
 	\end{tabular}

### 2018-11-22 paper/ijcai/figures/comparison_intro.tex
ijcai template

\small
\lstset{
  numbers=left,
  stepnumber=1,    
  firstnumber=1,
  numberfirstline=true,
  frame=none
}
\begin{figure}[t]
    \centering
\resizebox{0.9\columnwidth}{!}{%
    \begin{tabular}{l}
        \hline
        E \  C \  O\\ 
        \hline
        \lstinputlisting[
        language=C,
        basicstyle=\ttfamily,
        tabsize=1,
        ]{figures/example1.java} \\
        \hline
    \end{tabular}
    }
\caption{\label{caption:code-snippet-intro}
Code excerpt from the original Critical Slicing
    paper~\cite{DeMillo:1996:CSS:229000.226310}. E: Executed, C:
    (Original) Critical Slicing, O: \orbs{}~\cite{Binkley:2014:OLP:2635868.2635893}.  Symbol ``|''
    indicates that a statement is in the slice.}
\end{figure}
\normalsize

### 2018-11-22 paper/ijcai/paper.tex
ijcai template

--- 2018-11-19 paper/main.tex
@@
-% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
-%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-%\documentclass[sigplan]{acmart}\settopmatter{}
+\documentclass{article}
+\pdfpagewidth=8.5in
+\pdfpageheight=11in
+\usepackage{ijcai18}
+% The file ijcai18.sty is the style file for IJCAI-18 (same as ijcai08.sty).
 
@@
 
-%% Conference information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmConference[PLDI'19]{ ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 24--26, 2019}{Phoenix, AZ, USA}
-\acmYear{2019}
-\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\copyrightyear{2018}           %% If different from \acmYear
-
-%% Bibliography style
-\bibliographystyle{ACM-Reference-Format}
-%% Citation style
-%\citestyle{acmauthoryear}  %% For author/year citations
-%\citestyle{acmnumeric}     %% For numeric citations
-%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
-                            %% sorting of references within a single citation;
-                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
-                            %% rendered as [14,5,2] rather than [2,5,14].
-%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
-                            %% compression of sequential references within a
-                            %% single citation;
-                            %% e.g., \cite{Baker12,Baker14,Baker16}
-                            %% rendered as [2,3,4] rather than [2-4].
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Note: Authors migrating a paper from traditional SIGPLAN
-%% proceedings format to PACMPL format must update the
-%% '\documentclass' and topmatter commands above; see
-%% 'acmart-pacmpl-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% the following package is optional:
+\usepackage{latexsym}
+
+% Following comment is from ijcai97-submit.tex:
+% The preparation of these files was supported by Schlumberger Palo Alto
+% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
+% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
+% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
+% preparation.
+
+% These instructions can be modified and used in other conferences as long
+% as credit to the authors and supporting agencies is retained, this notice
+% is not changed, and further modification or reuse is not restricted.
+% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
+% contacts for providing assistance without their prior permission.
+
+% To use for other conferences, change references to files and the
+% conference appropriate and use other authors, contacts, publishers, and
+% organizations.
+% Also change the deadline and address for returning papers and the length and
+% page charge instructions.
+% Put where the files are available in the appropriate places.
+
+\title{Reassessing the Impact of Dynamic Slicing in SFL}
+
+% Single author syntax
+%\author{Jérôme Lang\\ 
+%Laboratoire d'Analyse et Modélisation des Systèmes pour l'Aide à la Décision (LAMSADE)  \\
+%pcchair@ijcai-18.org}
+
+% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
+
+\author{
+First Author$^1$,
+Second Author$^2$,
+Third Author$^3$
+\\ 
+$^1$ First Affiliation\\
+$^2$ Second Affiliation\\
+$^3$ Third Affiliation\\
+%
+first@email.address,
+second@email.address,
+third@email.address
+}
+
+% If your authors do not fit in the default space, you can increase it 
+% by uncommenting the following (adjust the "2.5in" size to make it fit
+% properly)
+% \setlength\titlebox{2.5in}
 
@@
 
-%% Title information
-\title{Reassessing the Impact of Dynamic Slicing in SFL}         %% [Short Title] is optional;
-                                        %% when present, will be used in
-                                        %% header instead of Full Title.
-%\titlenote{with title note}             %% \titlenote is optional;
-                                        %% can be repeated if necessary;
-                                        %% contents suppressed with 'anonymous'
-%\subtitle{Subtitle}                     %% \subtitle is optional
-%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-                                        %% can be repeated if necessary;
-                                        %% contents suppressed with 'anonymous'
-
-%% Author information
-%% Contents and number of authors suppressed with 'anonymous'.
-%% Each author should be introduced by \author, followed by
-%% \authornote (optional), \orcid (optional), \affiliation, and
-%% \email.
-%% An author may have multiple affiliations and/or emails; repeat the
-%% appropriate command.
-%% Many elements are not rendered, but should be provided for metadata
-%% extraction tools.
-
-%% Author with single affiliation.
-\author{First1 Last1}
-\authornote{with author1 note}          %% \authornote is optional;
-                                        %% can be repeated if necessary
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-  \position{Position1}
-  \department{Department1}              %% \department is recommended
-  \institution{Institution1}            %% \institution is required
-  \streetaddress{Street1 Address1}
-  \city{City1}
-  \state{State1}
-  \postcode{Post-Code1}
-  \country{Country1}                    %% \country is recommended
-}
-\email{first1.last1@inst1.edu}          %% \email is recommended
-
-%% Author with two affiliations and emails.
-\author{First2 Last2}
-\authornote{with author2 note}          %% \authornote is optional;
-                                        %% can be repeated if necessary
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-  \position{Position2a}
-  \department{Department2a}             %% \department is recommended
-  \institution{Institution2a}           %% \institution is required
-  \streetaddress{Street2a Address2a}
-  \city{City2a}
-  \state{State2a}
-  \postcode{Post-Code2a}
-  \country{Country2a}                   %% \country is recommended
-}
-\email{first2.last2@inst2a.com}         %% \email is recommended
-\affiliation{
-  \position{Position2b}
-  \department{Department2b}             %% \department is recommended
-  \institution{Institution2b}           %% \institution is required
-  \streetaddress{Street3b Address2b}
-  \city{City2b}
-  \state{State2b}
-  \postcode{Post-Code2b}
-  \country{Country2b}                   %% \country is recommended
-}
-\email{first2.last2@inst2b.org}         %% \email is recommended
-
-%% Abstract
-%% Note: \begin{abstract}...\end{abstract} environment must come
-%% before \maketitle command
+\maketitle
+
 \begin{abstract}
@@
 \end{abstract}
-
-%% 2012 ACM Computing Classification System (CSS) concepts
-%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011006.10011008</concept_id>
-<concept_desc>Software and its engineering~General programming languages</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10003456.10003457.10003521.10003525</concept_id>
-<concept_desc>Social and professional topics~History of programming languages</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~General programming languages}
-\ccsdesc[300]{Social and professional topics~History of programming languages}
-%% End of generated code
-
-%% Keywords
-%% comma separated list
-\keywords{Slicing, Testing, Debugging}  %% \keywords are mandatory in final camera-ready submission
-
-%% \maketitle
-%% Note: \maketitle command must come after title commands, author
-%% commands, abstract environment, Computing Classification System
-%% environment and commands, and keywords command.
-\maketitle
 
@@
 are two very popular techniques that use different principles to
-automate debugging. Dynamic
-Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
+automate debugging. Dynamic Slicing ~\citeauthor{Agrawal:1990:DPS:93542.93576} looks for the statements
 in code that influence the evaluation of the fault-revealing
 assertion. Although the technique has been intensively investigated in
-research, few use cases gained
-notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
+research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
 exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
@@
 
-%% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
-%% This research aims to address the doubts surrounding the efficiency
-%% of \sfl{}+\ds{} combination through the answer to the following
-%% research questions (\RQ{}):
-
 \newcommand{\rqone}{How often does DS miss faulty statements?}
-%\newcommand{\rqtwo}{How much reduction in file size can DS obtain?}
 \newcommand{\rqthree}{How effective is the \comb{} combination?}
@@
 \end{itemize}
-
-\newpage
 
@@
 
-We used the Mozilla Lithium tool~\cite{lithium} as the implementation
+We used the Mozilla Lithium tool~\footnote{ Lithium is available at \url{https://github.com/MozillaSecurity/lithium} (accessed November 2018).} as the implementation
 for Critical Slicing. Lithium is conceptually similar to the DD-min
@@
 by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
-iterations. Proofs can be found elsewhere~\cite{lithium-complexity}.
+iterations.
+Proofs can be found elsewhere\footnote{ Algorithm complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (accessed November 2018).}.
 
@@
 least one failing test and reports on output a ranked list of
-components likely to be in fault~\cite{FLSurvey2016,
-  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
-  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
+components likely to be in fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
 finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
@@
 produces the expected message checked by the oracle. This can happen,
-for example, if the oracle is too general.\qed
+for example, if the oracle is too general.
 
@@
 suspiciosness of those statements decrease. Similar argument applies
-to other fault predictors.\qed{}
+to other fault predictors.
 
@@
 Then, the tool iterates each class from the top-k classes ($c$) of each test $t$.
-In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{http://javaparser.org/} library.
-This step was added to \lithium{} because it turns \texttt{MozillaLithium}\footnote{https://github.com/MozillaSecurity/lithium} faster since the empty lines are ignored.
+In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{JavaParser is available at http://javaparser.org/ (accessed November 2018).} library.
+This step was added to \lithium{} because it turns \texttt{MozillaLithium} faster since the empty lines are ignored.
 Then, \texttt{MozillaLithium} performs the class minimization using a function of interest (Algorithm \ref{alg:finc}) which compares the output of the test with the expected one which is given as an input.
@@
 		\toprule
-		Project             & \#FS  & \# T & \# Ev & \#Bugs & \%  $\overline{in}$ &  \% top-k & \% in  \\ 
+		Project            &  \% top-5 & \%  $\overline{in}$  & \% in  \\ % & \#FS  & \# T & \# Ev & \#Bugs
 		\midrule
-		\chart{} 	& 40 &  57  &  136 & 21 & 13.2\% & 0\% & 86.8\%   \\
-		\closure{} 	& 56 &  10  &  81 & 6 & 0\% & 3.7\% & 96.3\%   \\
-		\lang{} 	& 204 &  90  &  447 & 59 & 0\% & 0\% & 100\%   \\
-		\cmath{} 	& 299 &  112  &  438 & 86 & 8\% & 2.1\% & 89.9\%   \\
-		\mockito{} 	& 94 &  93  &  397 & 25 & 3.3\% & 3.5\% & 93.2\%   \\
-		\jtime{} 	& 63 &  49  &  171 & 16 & 1.2\% & 0\% & 98.8\%   \\
+		\chart{} 	& 0\% & 13.2\% & 86.8\%   \\ %& 40 &  57  &  136 & 21 
+		\closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
+		\lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
+		\cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
+		\mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
+		\jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
 		\bottomrule
-				Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
+				%Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
 	\end{tabular}
@@
 and avoiding data and control omission
-errors~\cite{Zhang:2007:TLE:1250734.1250782,
-  Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
+errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
 cases where tests fail because some part of the code was not executed
@@
 
-Statistics-based techniques (e.g.,~\cite{Pearson:2017:EIF:3097368.3097441}) are
+Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
 popular automated fault localization techniques within the Software Engineering
@@
 sorted by their likelihood to be at fault. Since this technique is efficient in
-practice, it is attractive for large modern software systems~\cite{ecbs07}.
+practice, it is attractive for large modern software systems. \Sof{solve citation latex error}%%\cite{ecbs07}.
 
@@
 one failing test and reports on output a ranked list of components likely to be
-in fault~\cite{FLSurvey2016, DBLP:conf/kbse/JonesH05,
-DBLP:journals/smr/LuciaLJTB14, DBLP:journals/jss/AbreuZGG09}.
+in fault ~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
 
@@
 spectrum-based fault
-localization~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
+localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
 the methodology used in these papers vary, the overall message is that
@@
 \section{Conclusions and Future Work}\label{sec:conc}
-
-%% Acknowledgments
-\begin{acks}                            %% acks environment is optional
-
-  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
-  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
-  %% acknowledge financial support and will be used by metadata
-  %% extraction tools.
-  This material is based upon work supported by the
-  \grantsponsor{GS100000001}{National Science
-    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
-  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
-  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
-  conclusions or recommendations expressed in this material are those
-  of the author and do not necessarily reflect the views of the
-  National Science Foundation.
-\end{acks}
-
-%% Bibliography
-\bibliography{tmp}
-
-%% Appendix
-%% \appendix
-%% \section{Appendix}
-%% Text of appendix \ldots
+\section*{Acknowledgments}
+
+%% The file named.bst is a bibliography style file for BibTeX 0.99c
+{
+  \small
+  \balance
+  \bibliographystyle{named}
+  \bibliography{paper}
+}
 

### 2018-11-22 paper/pldi/figures/example1.java

@@ -1,0 +1,12 @@
+|   | input a;  /* input for a is 7 */
+|   | x = 0;
+| | | j = 5;
+| |   a = a - 10; /* should a = a + 10; */
+| |   if (a > j) {
+        x = x + 1;
+      }
+|     else {
+|       z = 0;
+|     }
+| | | x = x + j;
+| | | print x;   /* x is 5, but should be 6 */

### 2019-01-04 paper/ijcai/paper.tex
reference fix
ochiai formula fixed
diagnosis stats

@@
 The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
-\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}})\]
+\[\frac{\N{11}}{\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}}\]
 
@@
 
+\begin{table}[h]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	  \begin{tabular}{lrrr}
+		\toprule
+		Project            & top-5 & top-10 & imp   \\ %\comments{& Failing Test Cases &}
+		\midrule
+		\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
+		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
+		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
+		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
+		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
+		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
+		\bottomrule
+	\end{tabular}
+  \caption {Diagnosis Capability without Slicing}
+  \end{table}
+  \normalsize
+
 \subsection{Threats to validity}
@@
 sorted by their likelihood to be at fault. Since this technique is efficient in
-practice, it is attractive for large modern software systems. \Sof{solve citation latex error}%%\cite{ecbs07}.
+practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
 

### 2019-01-06 paper/ijcai/paper.tex
stats added

@@
 
+To evaluate the performance of the \comb{} combination
+suggested to improve \sfl{}
+
 This section reports results of our study to assess the impact of the
@@
       \toprule
-      Project            & Size (kLOC) & \# Tests & \# Defects \\ %\comments{& Failing Test Cases &}
+      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
       \midrule
@@
 
-\subsection{Experiments}
-
-These experiments only consider 213 of 395 bugs of the \dfj. 
-Each bug has one or more failing tests associated.
-For each test, it is verified if all the faulty statements of the bug are in the slicer.
-\#Ev is the total number of verifications performed by bug.
-For each bug ($i$) of the project, this experiment checks if all the faulty statements of the bug ($FS_i$) are in the slicer retrieved by each test ($T_i$).
-$n$ is the total number of bugs considered for each project.
-
-$$\#Ev = \sum_{i=1}^{n} T_i * FS_i$$
-
-\Sof{It does not make much sense to report \#Bugs here. If we end up not using the all dataset I think it would be better to report this in another section.}
-To evaluate the performance of \ds{} alone, the following metrics were taken into consideration: the total number of faulty statements ($\#FS$) in each project; the total number of tests ($\#T$) in each project; the number of times that each $FS$ may be in the slicer of each $T$, $\#Ev$; the number of bugs considered per project to the experiments, $\#Bugs$; the percentage of $FS$ that are not in the slicers of $T$, \% $\overline{in}$; the percentage of $FS$ that are not found in the top-5 of the classes with the highest ranks of suspiciousness; and, the percentage of $FS$ that are in the slicers of $T$.
-Regarding the \sfl{}+\ds{} combination, performance is evaluated based on four different metrics: the probability of the first line being the faulty one, $\% imp(f)$; the probability of the last line being the faulty one, $\% imp(l)$; and, finally the mean, $\% imp(\overline{m})$, and median $\% imp (median)$ of the position of the faulty line in the ranking.
-This combination is evaluated considering all the classes of the project (all) and only the classes of the project involved in the failing tests execution (loaded).
+\subsection{Methodology}
+
+Aiming the evaluation of the \comb{} performance, three main 
+experiements were performed: only using \sfl{} top calculate the statements
+rank, . First, for each version
 
@@
 	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lccccccc}
+	\begin{tabular}{llllll}
 		\toprule
-		Project            &  \% top-5 & \%  $\overline{in}$  & \% in  \\ % & \#FS  & \# T & \# Ev & \#Bugs
+		Project             &  \# MFS-5  & \% MFS-5 & \# MFS-10 & \% MFS-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
 		\midrule
-		\chart{} 	& 0\% & 13.2\% & 86.8\%   \\ %& 40 &  57  &  136 & 21 
-		\closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
-		\lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
-		\cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
-		\mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
-		\jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
+		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\ %& 40 &  57  &  136 & 21 
+		% \closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
+		% \lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
+		% \cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
+		% \mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
+		% \jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
 		\bottomrule
@@
 
-\subsubsection{\textit{How effective is the \sfl{}+\ds{} combination for bug localization?}}
-
+\subsubsection{\textit{How effective is the \comb{} combination for bug localization?}}
+
+The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
+project. Figure \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
+applying two main techiniques (\sfl{} and \comb{})
+
+% \begin{table*}[h]
+% 	\centering
+% 	\setlength{\tabcolsep}{2pt}
+% 	\begin{tabular}{lcccccccc}
+% 		\toprule
+
+% 			    \multirow{2}{*}{Project}   & \multicolumn{4}{c}{all} & \multicolumn{4}{c}{loaded}  \\
+
+% 		             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
+% 		\midrule
+
+% 		\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
+% 		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
+% 		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
+% 		\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
+% 		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
+% 		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
+% 		\bottomrule
+% 	\end{tabular}
+% 	\caption {\sfl{}+\ds{} performance evaluation}
+% \end{table*}
+% \normalsize
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
 \begin{table*}[h]
-	\centering
-	\setlength{\tabcolsep}{2pt}
-	\begin{tabular}{lcccccccc}
+	\setlength{\tabcolsep}{3pt}
+	\begin{tabular}{llllllllllllll}
 		\toprule
-
-			    \multirow{2}{*}{Project}   & \multicolumn{4}{c}{all} & \multicolumn{4}{c}{loaded}  \\
-
-		             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
-		\midrule
-
-		\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
-		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
-		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
-		\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
-		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
-		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
+		   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
+	red-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
+	red-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
+		   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
+	red-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
+	red-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
 		\bottomrule
 	\end{tabular}
-	\caption {\sfl{}+\ds{} performance evaluation}
+	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
+	\label{table:reduction}
+\end{table*}
+
+\begin{table*}[h]
+	\setlength{\tabcolsep}{3pt}
+	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.6cm}p{1.3cm}p{0.8cm}p{1.2cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1.5cm}p{1cm}p{0.8cm}p{1.3cm}p{0.8cm}@{}}
+	\toprule
+		   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
+	SFL    & 36   & 265.5625    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
+	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
+	\comb{}-10  & 35.5 & 406.375     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
+	\cellcolor[HTML]{FFFFC7}IMP-5  & 20.5 & -450.9375   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
+	\cellcolor[HTML]{FFFFC7}IMP-10 & 0.5  & -140.8125   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
+	\cellcolor[HTML]{9AFF99}IMP    & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
+		   & 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
+	SFL    & 15.5 & 2471.1667 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.2143  & 6818.5 & 3  & 3516    & 140  \\
+	\comb{}-5   & 15.5 & 2254.1667 & 9.1667 & 2   & 7.6667 & 2.5 & 6  & 21   & 105.4286  & 6818.5 & 3  & 6046.5  & 717  \\
+	\comb{}-10  & 15.5 & 2264.8333 & 10.8333 & 2   & 7.6667 & 2.5 & 6  & 29.5 & 105.4286  & 6818.5 & 3  & 6063.5  & 140  \\
+	\cellcolor[HTML]{FFFFC7}IMP-5  & 0    & 217         & 4.3333 & 0   & 1.8333 & 1   & 0  & 18   & -48.2143 & 0      & 0  & -2530.5 & -577 \\
+	\cellcolor[HTML]{FFFFC7}IMP-10 & 0    & 206.3333 & 2.6667 & 0   & 1.8333 & 1   & 0  & 9.5  & -48.2143 & 0      & 0  & -2547.5 & 0    \\
+	\cellcolor[HTML]{9AFF99}IMP    & 0    & {\success217} & {\success4.3333} & 0   & {\success1.8333} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
+	\bottomrule
+	\end{tabular}
+	\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 (IMP-5) and top-10 (IMP-10) of the faulty classes}
+	\label{table:performance}
 \end{table*}
@@
 		\toprule
-		Project            & top-5 & top-10 & imp   \\ %\comments{& Failing Test Cases &}
+		Project            & \# (k = 5) & \# (k = 10) &  \% imp   \\ %\comments{& Failing Test Cases &}
 		\midrule
@@
 	\end{tabular}
-  \caption {Diagnosis Capability without Slicing}
+  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
+  \label{table:fs}
   \end{table}
@@
 \subsection{Threats to validity}
+
+\Sof{@todo}
 
@@
 
-\subsubsection{Applications}
-
-Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
-technique involving dynamic slicing and SFL applied to MATLAB/Simulink
-models. The technique consists of iteratively
-generating tests that cause an error using satisfiability modulo
-theories (SMT) so that the slices generated are distinct from each
-other.  For slicing, their technique uses a program dependence graph
-(PDG) that express both data and control dependencies between blocks,
-so that the slice is built only on blocks that affect a specific line
-in the model - \textit{effective blocks}.  Their goal with the slicing
-was (1) to keep suspiciousness of a fault maximum if a target model
-has only one fault, and (2), to reduce the number of fault candidates
-obtained by the slicer.  For this, they utilize only failed test cases
-generated with SMT solvers ~\cite{peleska-vorobev-lapschies-2011} to
-calculate suspiciousness, as passed test cases might lower the
-suspiciousness of a fault.  The calculated suspiciousness is the
-number of times that a block belongs to the \textit{effective blocks}
-group by the number of total failed test cases.  Although their
-experiments and results showed promise with small models, the accuracy
-of the technique decreases when applied to models with multiple faults
-instead of one, as does the efficiency when exposed to large models,
-number of generated tests, sizes of sliced models and so on.
-
-\subsubsection{Automatic Program Repair}
-Automated repair techiniques have received considerable attention on
-the last decade and consists of three basic steps: fault localization, patch
-generation, and patch validation.  Regarding the fault localization
-step, Automated Program Repair (APR) tools can be guided by statistical
-fault localization techiniques to modify code which most likely
-contains the fault. On this section, we will briefly describe some of
-these tools.
-\Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }
-
-GenProg\Fix{cite} is a state of the art tool based on genetic
-programming to repair defects in off-the-shelf C programs. GenProg's
-strategy to fault localization consists of instrumenting the program
-so that all lines visited when executing failing test cases are
-recorded and used on the genetic search algorithm. The algorithm
-involves serching for other parts of the program, considering that a
-program that contains an error in one area likely implements the
-correct behaviour elsewhere. The tool proved to be effective in
-reparing 16 programs involving 1.25 millions LOC, and efficient as the
-algorithm search space takes advantage of test case coverage
-information, reusing  existing program statements.
-
-Debroy and Wong\Fix{cite} presented a techinique for automatically
-fixing faults in a program combining both mutation and statistical
-fault localization. Using the Tarantula fault localizer\Fix{cite}, the
-techinique focus the top ranked statements in terms of suspiciousness
-for the mutation operations. The percentage of statements examined in
-search for the fault is based on the total number of statements of the
-program, with the 10 percent being a reasonable number on the subject
-programs studied.
-
-JAFF\Fix{cite} is a Java automatic repair tool based on evolutionary principles that uses fault localization for ranking the statements in the code in terms of suspiciousness level.
-Before searching for the fix, the Java program is translated into a syntax tree composed of nodes related to the top ranked statements being used on the search process.
-The tool uses a specific formula to get the number of nodes that will be used on the search based on the number of statements with the same rank of suspiciousness,
-with the range between 1 to 20 nodes being used on the cases studied.
-
-SemFix is based on symbolic execution, constraint solving and program synthesis applied to software automatic repair. The tool uses statistical fault localization (SFL) with Tarantula to
-obtain the rank of suspiciousness and iteratively takes the most suspicious statement that has not been tried out to be used on the search for a fix. Compared to GenProg, the presented tool
-took consideredably less time to find a fix for programs utilizing the same test suites. However, the authors mention that the choice of the SFL techinique could potentially affect the
-effectiviness of the tool, particularly with large programs.
-
-SPR\Fix{cite} \Davino{ Fan Long } is based on staged
-program repair with condition synthesis. SPR uses fault localization
-to identify target statements that will be transformed in search for a
-fix on the program. The search space is built with a list of
-statements ranked by suspiciousness level, where only the first 200
-ranked statements are considered. The authors observed that increasing
-the search space to the top 2000 statements would bring additional
-repairs, but with a obvious cost of searching a large space.
-\Davino { Another tool presented by the same authors is Prophet, which uses the same search space, top 200. }
-
-MintHint \Fix{cite} uses statistical analysis with SFL to rank
-statements by their likelihood of being faulty. Given the ranked list,
-the tool analysis the top \textit{k} statements, where \textit{k} is a
-threshold set by the user, and proceeds with the repair algorithm
-assuming the fault can be repaired by changing a single statement.
-
-\Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }
+% \subsubsection{Applications}
+
+% Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
+% technique involving dynamic slicing and SFL applied to MATLAB/Simulink
+% models. The technique consists of iteratively
+% generating tests that cause an error using satisfiability modulo
+% theories (SMT) so that the slices generated are distinct from each
+% other.  For slicing, their technique uses a program dependence graph
+% (PDG) that express both data and control dependencies between blocks,
+% so that the slice is built only on blocks that affect a specific line
+% in the model - \textit{effective blocks}.  Their goal with the slicing
+% was (1) to keep suspiciousness of a fault maximum if a target model
+% has only one fault, and (2), to reduce the number of fault candidates
+% obtained by the slicer.  For this, they utilize only failed test cases
+% generated with SMT solvers ~\cite{peleska-vorobev-lapschies-2011} to
+% calculate suspiciousness, as passed test cases might lower the
+% suspiciousness of a fault.  The calculated suspiciousness is the
+% number of times that a block belongs to the \textit{effective blocks}
+% group by the number of total failed test cases.  Although their
+% experiments and results showed promise with small models, the accuracy
+% of the technique decreases when applied to models with multiple faults
+% instead of one, as does the efficiency when exposed to large models,
+% number of generated tests, sizes of sliced models and so on.
+
+% \subsubsection{Automatic Program Repair}
+% Automated repair techiniques have received considerable attention on
+% the last decade and consists of three basic steps: fault localization, patch
+% generation, and patch validation.  Regarding the fault localization
+% step, Automated Program Repair (APR) tools can be guided by statistical
+% fault localization techiniques to modify code which most likely
+% contains the fault. On this section, we will briefly describe some of
+% these tools.
+% \Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }
+
+% GenProg\Fix{cite} is a state of the art tool based on genetic
+% programming to repair defects in off-the-shelf C programs. GenProg's
+% strategy to fault localization consists of instrumenting the program
+% so that all lines visited when executing failing test cases are
+% recorded and used on the genetic search algorithm. The algorithm
+% involves serching for other parts of the program, considering that a
+% program that contains an error in one area likely implements the
+% correct behaviour elsewhere. The tool proved to be effective in
+% reparing 16 programs involving 1.25 millions LOC, and efficient as the
+% algorithm search space takes advantage of test case coverage
+% information, reusing  existing program statements.
+
+% Debroy and Wong\Fix{cite} presented a techinique for automatically
+% fixing faults in a program combining both mutation and statistical
+% fault localization. Using the Tarantula fault localizer\Fix{cite}, the
+% techinique focus the top ranked statements in terms of suspiciousness
+% for the mutation operations. The percentage of statements examined in
+% search for the fault is based on the total number of statements of the
+% program, with the 10 percent being a reasonable number on the subject
+% programs studied.
+
+% JAFF\Fix{cite} is a Java automatic repair tool based on evolutionary principles that uses fault localization for ranking the statements in the code in terms of suspiciousness level.
+% Before searching for the fix, the Java program is translated into a syntax tree composed of nodes related to the top ranked statements being used on the search process.
+% The tool uses a specific formula to get the number of nodes that will be used on the search based on the number of statements with the same rank of suspiciousness,
+% with the range between 1 to 20 nodes being used on the cases studied.
+
+% SemFix is based on symbolic execution, constraint solving and program synthesis applied to software automatic repair. The tool uses statistical fault localization (SFL) with Tarantula to
+% obtain the rank of suspiciousness and iteratively takes the most suspicious statement that has not been tried out to be used on the search for a fix. Compared to GenProg, the presented tool
+% took consideredably less time to find a fix for programs utilizing the same test suites. However, the authors mention that the choice of the SFL techinique could potentially affect the
+% effectiviness of the tool, particularly with large programs.
+
+% SPR\Fix{cite} \Davino{ Fan Long } is based on staged
+% program repair with condition synthesis. SPR uses fault localization
+% to identify target statements that will be transformed in search for a
+% fix on the program. The search space is built with a list of
+% statements ranked by suspiciousness level, where only the first 200
+% ranked statements are considered. The authors observed that increasing
+% the search space to the top 2000 statements would bring additional
+% repairs, but with a obvious cost of searching a large space.
+% \Davino { Another tool presented by the same authors is Prophet, which uses the same search space, top 200. }
+
+% MintHint \Fix{cite} uses statistical analysis with SFL to rank
+% statements by their likelihood of being faulty. Given the ranked list,
+% the tool analysis the top \textit{k} statements, where \textit{k} is a
+% threshold set by the user, and proceeds with the repair algorithm
+% assuming the fault can be repaired by changing a single statement.
+
+% \Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }
 
 \section{Conclusions and Future Work}\label{sec:conc}
+
+\Sof{@todo}
+
 \section*{Acknowledgments}
+
+\Sof{...}
 
@@
 
+\begin{appendices}
+	\section{Other data that might be interesting to report}
+	This section has the only purpose of presenting and discussing other data that 
+	are not intended yet to be used in the paper. If you find something interesting 
+	in this block of information, please report.
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{figures/Chart_abs.pdf}
+		\caption{Comparing the rank of all faulty statetments for each project version obtained by \sfl{} and \comb{} considering the top-5 and top-10 of classes}
+		\begin{tabular}{r@{: }l}
+			SFL & Rank of all faulty statements only using \sfl{}\\
+			LS-$5$& Rank of all faulty statements after slicing the top-5 classes \\
+			LS-$10$& Rank of all faulty statements after slicing the top-10 classes 
+		\end{tabular}
+		\label{fig:ranking}
+	\end{figure*}
+
+	\begin{figure*}
+		\centering
+		\includegraphics[width=\textwidth]{figures/Chart_abs_imp.pdf}
+		\caption{\sfl{} rank improvement by applying \ds{} to the top-5 and top-10 classes of each project version}
+		\begin{tabular}{r@{: }l}
+			IMP-$5$& \sfl{} rank improvement by applying \ds{} to the top-5 classes \\
+			IMP-$10$& \sfl{} rank improvement by applying \ds{} to the top-10 classes
+		\end{tabular}
+		\label{fig:performance}
+	\end{figure*}
+
+\end{appendices}
+
 \end{document}

### 2019-01-07 paper/ijcai/paper.tex
new paper version, small changes

@@
 
-Aiming the evaluation of the \comb{} performance, three main 
-experiements were performed: only using \sfl{} top calculate the statements
-rank, . First, for each version
+Aiming the evaluation of the \comb{} performance, two different experiment
 
@@
 	\end{tabular}
-	\caption {Report of the capability of \ds{} on missing faulty statements}
+	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
 \end{table*}
@@
 		   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
-	red-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
-	red-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
+	top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
+	top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
 		   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
-	red-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
-	red-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
+	top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
+	top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
 		\bottomrule
@@
 	\setlength{\tabcolsep}{3pt}
-	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.6cm}p{1.3cm}p{0.8cm}p{1.2cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1.5cm}p{1cm}p{0.8cm}p{1.3cm}p{0.8cm}@{}}
+	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.3cm}p{1cm}p{0.8cm}p{1cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1cm}p{1cm}p{0.8cm}p{1.1cm}p{0.8cm}@{}}
 	\toprule
 		   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
-	SFL    & 36   & 265.5625    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
+	SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
 	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
-	\comb{}-10  & 35.5 & 406.375     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
-	\cellcolor[HTML]{FFFFC7}IMP-5  & 20.5 & -450.9375   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
-	\cellcolor[HTML]{FFFFC7}IMP-10 & 0.5  & -140.8125   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
-	\cellcolor[HTML]{9AFF99}IMP    & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
+	\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
+	\cellcolor[HTML]{FFFFC7}$\Delta-5$  & 20.5 & -450.94   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
+	\cellcolor[HTML]{FFFFC7}$\Delta-10$ & 0.5  & -140.81   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
+	\cellcolor[HTML]{9AFF99}$\Delta$   & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
 		   & 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
-	SFL    & 15.5 & 2471.1667 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.2143  & 6818.5 & 3  & 3516    & 140  \\
-	\comb{}-5   & 15.5 & 2254.1667 & 9.1667 & 2   & 7.6667 & 2.5 & 6  & 21   & 105.4286  & 6818.5 & 3  & 6046.5  & 717  \\
-	\comb{}-10  & 15.5 & 2264.8333 & 10.8333 & 2   & 7.6667 & 2.5 & 6  & 29.5 & 105.4286  & 6818.5 & 3  & 6063.5  & 140  \\
-	\cellcolor[HTML]{FFFFC7}IMP-5  & 0    & 217         & 4.3333 & 0   & 1.8333 & 1   & 0  & 18   & -48.2143 & 0      & 0  & -2530.5 & -577 \\
-	\cellcolor[HTML]{FFFFC7}IMP-10 & 0    & 206.3333 & 2.6667 & 0   & 1.8333 & 1   & 0  & 9.5  & -48.2143 & 0      & 0  & -2547.5 & 0    \\
-	\cellcolor[HTML]{9AFF99}IMP    & 0    & {\success217} & {\success4.3333} & 0   & {\success1.8333} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
+	SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
+	\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
+	\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
+	\cellcolor[HTML]{FFFFC7}$\Delta-5$  & 0    & 217         & 4.33 & 0   & 1.83 & 1   & 0  & 18   & -48.21 & 0      & 0  & -2530.5 & -577 \\
+	\cellcolor[HTML]{FFFFC7}$\Delta-10$ & 0    & 206.33 & 2.67 & 0   & 1.83 & 1   & 0  & 9.5  & -48.21 & 0      & 0  & -2547.5 & 0    \\
+	\cellcolor[HTML]{9AFF99}$\Delta$    & 0    & {\success217} & {\success4.33} & 0   & {\success1.83} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
 	\bottomrule
@@
 		\toprule
-		Project            & \# (k = 5) & \# (k = 10) &  \% imp   \\ %\comments{& Failing Test Cases &}
+		Project            & \# (k = 5) & \# (k = 10) &  \% $\Delta$   \\ %\comments{& Failing Test Cases &}
 		\midrule

### 2019-01-12 paper/ijcai/paper.tex
some improvements in the paper

@@
 		\toprule
-		Project             &  \# MFS-5  & \% MFS-5 & \# MFS-10 & \% MFS-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
+		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
 		\midrule
@@
 \begin{table*}[h]
+	\small
 	\setlength{\tabcolsep}{3pt}
-	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.3cm}p{1cm}p{0.8cm}p{1cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1cm}p{1cm}p{0.8cm}p{1.1cm}p{0.8cm}@{}}
+	\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
 	\toprule
@@
 	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
+	$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
 	\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
-	\cellcolor[HTML]{FFFFC7}$\Delta-5$  & 20.5 & -450.94   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
-	\cellcolor[HTML]{FFFFC7}$\Delta-10$ & 0.5  & -140.81   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
-	\cellcolor[HTML]{9AFF99}$\Delta$   & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
+	$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
 	& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
@@
 	\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
+	$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
 	\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
-	\cellcolor[HTML]{FFFFC7}$\Delta-5$  & 0    & 217         & 4.33 & 0   & 1.83 & 1   & 0  & 18   & -48.21 & 0      & 0  & -2530.5 & -577 \\
-	\cellcolor[HTML]{FFFFC7}$\Delta-10$ & 0    & 206.33 & 2.67 & 0   & 1.83 & 1   & 0  & 9.5  & -48.21 & 0      & 0  & -2547.5 & 0    \\
-	\cellcolor[HTML]{9AFF99}$\Delta$    & 0    & {\success217} & {\success4.33} & 0   & {\success1.83} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
+	$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
 	\bottomrule
@@
 		\toprule
-		Project            & \# (k = 5) & \# (k = 10) &  \% $\Delta$   \\ %\comments{& Failing Test Cases &}
+		Project            & \# top-5 & \# top-10 &  \% $\Delta$   \\ %\comments{& Failing Test Cases &}
 		\midrule

### 2019-01-12 app/compare_messages.py
python interpreter added

@@ -1,3 +1,4 @@
+#! /usr/bin/python3
 import sys, os, logging
 from utils import check_obj_comparison, is_object_comparison, get_testname_expected_msg, get_to_compare
 import re

### 2019-01-12 app/generate_expected_msg.py

@@ -1,7 +1,6 @@
+#! /usr/bin/python3
 import argparse, os
 from utils import json_to_dict, get_testname_expected_msg, call_cmd
-
-
 
 main = argparse.ArgumentParser()
 main.add_argument("--project", type=str, nargs=1, help="Project name")

### 2019-01-12 app/generate_inputs.py

@@ -1,7 +1,6 @@
+#! /usr/bin/python3
 import argparse, os
 from utils import json_to_dict, get_testname_expected_msg, call_cmd
-
-
 
 main = argparse.ArgumentParser()
 main.add_argument("--output", type=str, nargs=1, help="The output path to save the seed file")

### 2019-01-12 app/interesting.py

@@ -1,3 +1,4 @@
+#! /usr/bin/python3
 import os, signal, time, logging
 from shutil import copy
 

### 2019-01-12 app/run_lithium.py

@@ -1,3 +1,4 @@
+#! /usr/bin/python3
 import os, logging, time, argparse, tempfile
 from shutil import copy, rmtree
 import subprocess

### 2019-01-12 app/utils.py

@@ -1,3 +1,4 @@
+#! /usr/bin/python3
 import json, re, shlex, difflib, os
 from subprocess import STDOUT, CalledProcessError, check_output, Popen, PIPE, call
 from timeout_decorator import timeout, TimeoutError

### 2019-01-18 paper/ijcai/paper.tex
paper with statistical tests

@@
 
-% Following comment is from ijcai97-submit.tex:
-% The preparation of these files was supported by Schlumberger Palo Alto
-% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
-% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
-% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
-% preparation.
-
-% These instructions can be modified and used in other conferences as long
-% as credit to the authors and supporting agencies is retained, this notice
-% is not changed, and further modification or reuse is not restricted.
-% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
-% contacts for providing assistance without their prior permission.
-
-% To use for other conferences, change references to files and the
-% conference appropriate and use other authors, contacts, publishers, and
-% organizations.
-% Also change the deadline and address for returning papers and the length and
-% page charge instructions.
-% Put where the files are available in the appropriate places.
-
 \title{Reassessing the Impact of Dynamic Slicing in SFL}
-
-% Single author syntax
-%\author{Jérôme Lang\\ 
-%Laboratoire d'Analyse et Modélisation des Systèmes pour l'Aide à la Décision (LAMSADE)  \\
-%pcchair@ijcai-18.org}
-
-% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
 
@@
 \begin{abstract}
-  \Sof{@todo}
+\Sof{@TODO}Lorem Ipsum is simply dummy text of the printing and typesetting industry.
+Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.
+It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.
+It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
+It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
 \end{abstract}
@@
 
-%\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}
-
-%% PROBLEM MOTIVATION
 Software debugging is difficult. The task of locating the faulty code
@@
 exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
-recover the influence region of faulty statements. It is a black-box
+recover the influence region of faulty statements. It is a black-box~
 statistical fault localization method that computes suspiciousness
@@
 likely fixes.
-
-%Recent \apr{} techniques use \sfl{} to guide
-%the search for repairs .
-
-%% \Fix{Revise this $\rightarrow$} Mao and Wang
-%% \cite{lei-mao-dai-wang-2012} had promising results compared to \sfl{}
-%% state of the art techniques, such as Tarantula [cite] and Ochiai
-%% [cite], concerning the relative percentage of the code above the
-%% fault. Prior work used the same measurement approach
-%% \cite{santelices-jones-yu-harrold-2009,wang-cheung-chan-zhang-2009,jones-2005}.
-%% However, the problem with this approach lies in the effort to find the
-%% defect, as shown on Parnin and Orso's study \cite{parnin-orso-2011},
-%% in which a percentage rank does not scale with the size of a
-%% codebase. For example, if a fault statement is ranked on the 83rd
-%% position as a result of a \sfl{} technique, the percentage rank using
-%% a codebase of 8300 LOC is only 1\%, with the amount of absolute lines
-%% of code to be examined not being considered.  This can result in
-%% millions of lines of code to be analysed, proving that a percentage
-%% rank is not a practical evaluation metric
-%% \cite{ang-perez-van-deursen-rui-2017}.  \Fix{end here}
-
-%% For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
-%% reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
-%% rankings when using dynamic slicing in combination with \sfl{} versus
-%% plain \sfl{}.
 
@@
      for bug localization of \emph{Java} faulty programs.
-%	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
-	\item The tools used to run the study. Benchmarks and experimental results are also publicly available.
+	\item Empirical evidence that the \comb{} combination improves 
 \end{itemize}
@@
 \label{sec:slicing}
-
-%% To select a slicer implementation to run our experiments, we
-%% considered two criteria: robustness as to support non-trivial programs
-%% and efficiency as to support execution of our experiments in
-%% reasonable time.  Unfortunately, we failed to find public
-%% implementations satisfying these criteria.
-%% For those reasons, we ded to implement a critical slicer for Java,
-%% which is the language of the subjects in our dataset, \dfj{}.
 
@@
 
-We used the Mozilla Lithium tool~\footnote{ Lithium is available at \url{https://github.com/MozillaSecurity/lithium} (accessed November 2018).} as the implementation
+We used the Mozilla Lithium tool~\footnote{Lithium is available at \url{https://github.com/MozillaSecurity/lithium} (accessed November 2018).} as the implementation
 for Critical Slicing. Lithium is conceptually similar to the DD-min
@@
 iterations.
-Proofs can be found elsewhere\footnote{ Algorithm complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (accessed November 2018).}.
-
-%% Despite that, optimizations are important to
-%% make a Critical Slicing implementation efficient. We describe the
-%% optimizations we used in the following.
-
-%% The output we used to determine equivalence of the original failing
-%% execution and the sliced failing execution was the stack trace
-%% produced by the assertion violation.  It is important to note that
-%% Binkley \etal{} recently proposed the critical slicer
-%% ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
-%% efficiency (important to run our experiments) for generality. Some of
-%% the slicing jobs we ran on ORBS took hours to run. For example,
-%% \Fix{...elaborate...}
-
-%% \vspace{1ex}\noindent\textbf{Blackbox slicing.} Removing statements
-%% from the program is necessary to discover whether it is essential
-%% to the execution or not. For that reason, we compare the test stack
-%% trace to look for changes in the output. Considering one execution,
-%% if one line of the stack trace changes and that change is not
-%% related to random values (\eg{}, hashcode), we discard that
-%% specific slice. However, not every test case produces a stack trace
-%% (\ie{}, passing tests), and thus, we guarantee that the test has
-%% executing code by not instrumenting test classes and test methods.
-
-%% \vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
-%% major cost associated with critical
-%% slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
-%%   of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
-%% program schemata where every statement in function bodies is guarded
-%% by a branch predicate to control its activation. The slicer
-%% re-executes the program with different guard configurations, recording
-%% the smallest slice found. It uses a local search to find the smallest
-%% slice for a given time budget. A slice is encoded as a list of flags,
-%% each indicating whether or not a given guard is active. The initial
-%% configuration of a slicing job has the flags set for all statements
-%% covered by a given test.
-
-%% \vspace{1ex}\noindent\textbf{Structure Awareness.}
-%% ORBS is language-agnostic; it removes text from files but it does not
-%% parse code. Each removal can lead to malformed
-%% code. \Mar{$\leftarrow$how do we deal with this in the bytecode
-%%   instrumentation?  explain...} We collect constraints of the form
-%% $b\rightarrow{}a$ during code instrumentation to indicate that guard
-%% $b$ is used in the region guarded by $a$, reflecting the nested
-%% structure of the code. The slicer uses these constraints to prune the
-%% search space of guard configurations, encoding the slice. For example,
-%% it does not make sense to include statement $b$ in the slice and not
-%% including statement $a$.
-
-%% \vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
-%% given test is necessary in Critical Slicing. However, test
-%% re-execution may introduce flakiness due to side-effects in data
-%% reachable from static fields. One alternative to address this problem
-%% is to run each test in a separate JVM. Unfortunately, that alternative
-%% is prohibitively slow. For that, we ran the slicing job in a single
-%% JVM, using a test runner that is able to clean the static area of the
-%% JVM as follows. At every re-execution of the critical slicer, the test
-%% runner creates a new instance of a custom class loader, child of the
-%% original JVM class loader.  Before loading a class, the custom class
-%% loader checks in a cache whether or not the bytecodes were already
-%% loaded. If not, the class file is loaded from disk and the bytecodes
-%% are stored in the cache for future access. If the bytecodes were
-%% previously loaded, the slicer avoids disk access by reading the data
-%% directly from the cache.  To sum, the use of a new class loader
-%% enables the slicer to ``reset'' the state prior to a new execution of
-%% the same test~---~the objects accessible from the static area become
-%% unreachable when the class loader is disposed at the end of an
-%% execution.
+Proofs can be found elsewhere\footnote{Algorithm complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (accessed November 2018).}.
 
@@
 The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
-\[\frac{\N{11}}{\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}}\]
-
-\section{Critical Slicing + \sfl{}}
+\[ochiai = \frac{\N{11}}{\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}}\]
+
+\section{\sfl{} + Critical Slicing}
 \label{sec:combination}
 
-The combinination of critical slicing and \sfl{} consists of the
+\Sof{Maybe discuss the limitations of \sfl{} based on the capabilibility of \ds{}}The combinination of critical slicing and \sfl{} consists of the
 following steps: (1) Compute the execution spectra as discussed in
@@
 c_5\}$.  Intuitively, slicing enables identification of cells in the
-matrix (/spectra) whose values can be set to zero.
-
-%% \begin{enumerate}
-%% \item\label{step-spectra} Compute the execution spectra.
-%% \item\label{step-slice} Compute slices associated with tests.
-%% \item Adjust the spectra computed in Step~\ref{step-spectra} with
-%%   results obtained in Step~\ref{step-slice}.
-%% \item Compute suspiciousness scores.
-%% %\item {[optional]} Filter statements covered by selected failing tests.
-%% \end{enumerate}
+spectra whose values can be set to zero.
 
@@
 
-\Sof{@todo: Add a short 3-4 lines at most example based on one of our subjects} Section~\ref{sec:impl} explains the heuristics
-we used to infer oracles for critical slicing that mitigates this
-issue and Section~\ref{sec:eval} shows how often critical slicing
-misses faulty statements.
+\vspace{3mm}
+\begin{myframe} \label{box:1}
+\textbf{java.lang.NullPointerException}, \\
+at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
+testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
+...
+\end{myframe}
 
@@
 
-\subsection{Implementation}
-\label{sec:impl}
-
-\Mar{Sofia, I think this was way too low-level for intro and decided
-  to move here. please check how to fit.}
-\Fix{
-A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
+Section~\ref{sec:oracleheuristics} explains the heuristics
+we used to infer oracles for critical slicing that mitigates this
+issue.
+
+\subsection{Oracle Heuristics}
+\label{sec:oracleheuristics}
+
+% \subsection{Implementation}
+% \label{sec:impl}
+
+% \Mar{Sofia, I think this was way too low-level for intro and decided
+%   to move here. please check how to fit.}
+% \Fix{
+% A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
 \morpho{} retrieves as an output the input for \lithium{}.
@@
 
-Two different tools were developed to support this research: \morpho{} and \lithium{}.
+% Two different tools were developed to support this research: \morpho{} and \lithium{}.
 \morpho{} was designed to calculate the suspiciousness of all statements of a project before, and after the top-k minimization performed by \lithium{} whereas \lithium{} is responsible for reducing the search domain of each \texttt{Java} class of the project for the after-\sfl{} analysis.
@@
 
-\begin{algorithm}[h]
-	\caption{Class Minimization Algorithm}
-	\label{alg:ls}
-	\begin{flushleft}
-		\textbf{Input:} $proj$ - project name \\
-		\hspace{2.75em} $bug$ - bug number\\
-		\hspace{2.75em} $k$ - number of top ranked classes\\
-		\hspace{2.75em} $stk$ - expected stacktrace\\
-	 \textbf{Output:} Top-k classes minimization for each test \\
-	\end{flushleft}
-	\begin{algorithmic}[1]
-		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
-			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
-			\ForAll {$t \in testsInfo$}
-				\State $classes \leftarrow$ getClasses($proj$, $bug$)
-				\ForAll {$c \in classes$}
-					\State $unc \leftarrow$ removeComments($c$)
-					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
-				\EndFor
-				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
-			\EndFor
-			\State \Return $slicer$
-		\EndProcedure
-	\end{algorithmic}
-
-\end{algorithm}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
-	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
-\end{figure*}
-
-\subsection{Function of Interest }
-\label{sec:funcofint}
+% \begin{algorithm}[h]
+% 	\caption{Class Minimization Algorithm}
+% 	\label{alg:ls}
+% 	\begin{flushleft}
+% 		\textbf{Input:} $proj$ - project name \\
+% 		\hspace{2.75em} $bug$ - bug number\\
+% 		\hspace{2.75em} $k$ - number of top ranked classes\\
+% 		\hspace{2.75em} $stk$ - expected stacktrace\\
+% 	 \textbf{Output:} Top-k classes minimization for each test \\
+% 	\end{flushleft}
+% 	\begin{algorithmic}[1]
+% 		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
+% 			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
+% 			\ForAll {$t \in testsInfo$}
+% 				\State $classes \leftarrow$ getClasses($proj$, $bug$)
+% 				\ForAll {$c \in classes$}
+% 					\State $unc \leftarrow$ removeComments($c$)
+% 					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
+% 				\EndFor
+% 				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
+% 			\EndFor
+% 			\State \Return $slicer$
+% 		\EndProcedure
+% 	\end{algorithmic}
+%
+% \end{algorithm}
+%
+% \begin{figure*}[t]
+% 	\centering
+% 	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
+% 	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
+% \end{figure*}
+%
+% \subsection{Function of Interest }
+% \label{sec:funcofint}
+%
+%
+
+\Sof{@TODO: Melhorar terminologia e algoritmo} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved.
+The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not.
+In this study, interesting means that the test execution path is equal to the expected one.
+This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception.
+The authors assume that it is only necessary to compare both stack traces until the call where the test fails.
+For each chunk under evaluation, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2).
+Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails.
+These operations are performed by line 3 and 4 from Algorithm 2.
+Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
 
@@
 
-The \texttt{MozillaLithium} tool takes as input a function of interest that can be designed according to the problem to be solved.
-The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not.
-In this study, interesting means that the test execution path is equal to the expected one.
-This information can be deducted from \texttt{Java} stack traces which show the stack of functions called until the thrown of an exception.
-The authors assume that it is only necessary to compare both stack traces until the call where the test fails.
-For each chunk selected by \texttt{MozillaLithium}, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2).
-Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails.
-These operations are performed by line 3 and 4 from Algorithm 2.
-The result is an oracle such as the one provided in the box below:
-
-\vspace{3mm}
-\begin{myframe} \label{box:1}
-java.lang.IndexOutOfBoundsException: Index: -1, Size: 1,
-java.util.ArrayList.rangeCheckForAdd(ArrayList.java:643),
-java.util.ArrayList.add(ArrayList.java:455),
-org.jfree.data.xy.XYSeries.addOrUpdate(XYSeries.java:564),
-org.jfree.data.xy.XYSeries.addOrUpdate(XYSeries.java:527),
-\textbf{org.jfree.data.xy.junit.XYSeriesTests.}\\
-\textbf{testBug1955483(XYSeriesTests.java:479)},\\
-...
-\end{myframe}
-
-The oracle includes an exception error message (\emph{java.lang.\\IndexOutOfBoundsException: Index: -1, Size: 1}) and the program execution path until the class test where it fails (\emph{XYSeriesTests.java:479}).
-The regular expression \verb/Test(.*).java/ retrieves the test class position in the stack trace.
-If the test class is not found, the entire stack trace is compared.
-There is, however, an exception.
-When the failure is a \emph{StackOverflowError}, there is no test class mentioned in the stack trace because the exception is a runtime error.
-This exception is triggered when the JVM encounters a situation where there is no space for a new stack frame to be created which is, normally, the outcome of infinite recursion.
-Consequently, the stack trace contains many times the failed call.
-So, when the failure message contains a \emph{StackOverflowError}, the oracle is only considered until the call is repeated for the fifth time.
-
-\vspace{3mm}
-\begin{myframe}
-	java.lang.StackOverflowError,
-	sun.reflect.generics.reflectiveObjects.\linebreak
-			TypeVariableImpl.hashCode(TypeVariableImpl.java:198),
-	java.util.HashMap.hash(HashMap.java:362),
-	java.util.HashMap.getEntry(HashMap.java:462),
-	java.util.HashMap.get(HashMap.java:417),  org.mockito.internal.util.reflection.GenericMetadataSupport.
-		getActualTypeArgumentFor(GenericMetadataSupport.java:182), \linebreak
-	org.mockito.internal.util.reflection.GenericMetadataSupport.
-	getActualTypeArgumentFor(GenericMetadataSupport.java:185),
-	org.mockito.internal.util.reflection.GenericMetadataSupport.
-	getActualTypeArgumentFor(GenericMetadataSupport.java:185),
-	...
-\end{myframe}
-
-Some of the error messages can be different even if the test is executed with the same inputs and in the same environment.
-One example is the one provided in the box below, where the memory positions (\emph{class@<memory-position>}) may differ from the ones in the expected message.
-In order to solve this, it was designed a mechanism to check this kind of exception patterns.
-However, the current version of the interesting function only considers this pattern.
-Other patterns will be added soon into the next version of \lithium{}.
-
-\vspace{3mm}
-\begin{myframe}
-	junit.framework.AssertionFailedError: \\
-	expected:<org.jfree.chart.util.ShapeList@\textbf{d0e55451}> but \\ was:<org.jfree.chart.util.ShapeList@\textbf{d951b68f}>
-	...
-\end{myframe}
-
 \section{Evaluation}
@@
 
-\Mar{-------------------- estou aqui}
-
-To evaluate the performance of the \comb{} combination
-suggested to improve \sfl{}
-
-This section reports results of our study to assess the impact of the
-\comb{} combination.
+To evaluate the impact of the \comb{} combination, the authors rcompare the cost of diagnosing faulty software programs using SFL against using \comb{} for top-5 and top-10 of classes.
 
@@
 experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
-includes six subjects and \numFaults{} faults.
+includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
 \lang{} is a library
@@
   \setlength{\tabcolsep}{4pt}
-    \begin{tabular}{lrrr}
+    \begin{tabular}{lccc}
       \toprule
@@
 \caption {Characterization of \dfj{} subjects.}
+\label{tab:df4j}
 \end{table}
@@
 
-%% old text related to single faults...
-%%%%%%%%%%%%
-%% It is important to note that the construction of the \dfj{} dataset is
-%% not suited to evaluate the rate of single faults, but prior research
-%% did that.  Perez~\etal{}~\cite{7927959} recently showed that single
-%% faults are prevalent in open-source project. They conducted a
-%% comprehensive empirical study involving 279 open-source Java projects
-%% where they found that single faults were observed in 82\% of the cases
-%% of regression.
-
 \subsection{Methodology}
 
-Aiming the evaluation of the \comb{} performance, two different experiment
-
-\subsection{Results of Dynamic Slicing}
-
-We describe the results of dynamic slicing alone in the following sections.
-
-\subsubsection{\textit{How often DS misses faulty statements?}}
-
-\begin{table*}[h]
+To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components.
+This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
+two approaches. A variety in diagnostic effort is measured
+using
+
+\begin{equation}
+    \Delta{}C = C(\textrm{SFL}) - C(\textrm{SFL+DS-k})
+\end{equation}
+
+where C is the cost of diagnosis. \Sof{Need to explain this better}
+A positive $\Delta$C means that the faulty component has risen in
+the ranking reported by SFL techniques when DS is used,
+yielding a lowered cost of diagnosing.
+
+\subsection{Results}
+
+The following section aims to answer the research questions presented previously.
+
+\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
+
+In \textbf{RQ1}, we pretend to evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
+
+Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}.
+The gain from considering the top-10 of classes instead of top-5 is small or null.
+
+Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project.
+The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes.
+Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.
+
+\begin{table}[h]
 	\centering
 	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{llllll}
+	  \begin{tabular}{lccc}
 		\toprule
-		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
-		\midrule
-		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\ %& 40 &  57  &  136 & 21 
-		% \closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
-		% \lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
-		% \cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
-		% \mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
-		% \jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
-		\bottomrule
-				%Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
-	\end{tabular}
-	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
-\end{table*}
-\normalsize
-
-\subsubsection{\textit{How effective is the \comb{} combination for bug localization?}}
-
-The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
-project. Figure \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
-applying two main techiniques (\sfl{} and \comb{})
-
-% \begin{table*}[h]
-% 	\centering
-% 	\setlength{\tabcolsep}{2pt}
-% 	\begin{tabular}{lcccccccc}
-% 		\toprule
-
-% 			    \multirow{2}{*}{Project}   & \multicolumn{4}{c}{all} & \multicolumn{4}{c}{loaded}  \\
-
-% 		             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
-% 		\midrule
-
-% 		\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
-% 		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
-% 		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
-% 		\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
-% 		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
-% 		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
-% 		\bottomrule
-% 	\end{tabular}
-% 	\caption {\sfl{}+\ds{} performance evaluation}
-% \end{table*}
-% \normalsize
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table*}[h]
-	\setlength{\tabcolsep}{3pt}
-	\begin{tabular}{llllllllllllll}
-		\toprule
-		   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
-	top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
-	top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
-		   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
-	top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
-	top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
-		\bottomrule
-	\end{tabular}
-	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
-	\label{table:reduction}
-\end{table*}
-
-\begin{table*}[h]
-	\small
-	\setlength{\tabcolsep}{3pt}
-	\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
-	\toprule
-		   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
-	SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
-	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
-	$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
-	\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
-	$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
-	& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
-	SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
-	\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
-	$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
-	\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
-	$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
-	\bottomrule
-	\end{tabular}
-	\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 (IMP-5) and top-10 (IMP-10) of the faulty classes}
-	\label{table:performance}
-\end{table*}
-\normalsize
-
-\begin{table}[h]
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	  \begin{tabular}{lrrr}
-		\toprule
-		Project            & \# top-5 & \# top-10 &  \% $\Delta$   \\ %\comments{& Failing Test Cases &}
+		Project            & \# top-5 & \# top-10  & \% $\Delta$  \\ 
 		\midrule
@@
   \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
-  \label{table:fs}
+  \label{table:fsws}
+\end{table}
+
+\begin{table*}[h]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{llllll}
+		\toprule
+		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\ 
+		\midrule
+		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\
+		\jtime{}  &  &  &  &   & \\
+		\bottomrule
+	\end{tabular}
+	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
+	\label{tab:fs}
+\end{table*}
+\normalsize
+
+\Sof{@todo: Answer the question}
+
+\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}
+
+In \textbf{RQ2}, we pretend to evaluate the impact of combining \ds{} to improve \ds{}.
+
+The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
+project. Figure \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
+applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.
+
+Table \ref{tab:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
+$\Delta<0$ means that the faulty statement may be removed.
+$\Delta=0$ means that the faulty statement remained in the same position.
+$\Delta>0$ means that \ds{} improved diagnosability.
+For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%.
+However, top-5 has less classes to minimize than top-10.
+
+Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant.
+Shapiro-Wilk \Fix{cite} test is performed to test for normality in the three techniques.
+With 99 \% of confidence, the results tell us that the distributions are not normal.
+Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman \Fix{cite}.
+The null-hypothesis is that all distributions are the same.
+With 99 \% of confidence, the results show that the distributions are not all the same.
+In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis \Fix{cite}.
+Figure \ref{fig:performance} report the results of that analysis for all the distributions.
+With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.
+
+\begin{table}[h]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{ccc}
+		\toprule
+		$\Delta$             &  \comb{}-5  & \comb{}-10 \\ 
+		\midrule
+		$<0$  & 5 & 4 \\ 
+		$=0$  & 6 & 7 \\ 
+		$>0$  & 15 & 15 \\
+
+		\bottomrule
+	\end{tabular}
+	\caption {\Sof{This can be a barchart} Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+	\label{tab:diagnosis}
 \end{table}
@@
 
+\begin{table*}[h]
+	\centering
+	\begin{tabular}{@{}llll@{}}
+\toprule
+  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
+Mean & 531.04     & 745.71   & 715.62    \\ \midrule
+Median & 17.5                   & 15.25                & 15.25                 \\ \midrule
+Variance & 1520.09      & 1794.86   & 1803.11    \\ \midrule
+Shapiro-Wilk & \makecell{W = 0.40 \\ p-value = 2.95 x $10^{-9}$} & \makecell{W = 0.48 \\ p-value = 1.54 x $10^{-8}$} & \makecell{W = 0.46 \\ p-value = 9.11 x $10^{-9}$}  \\ \midrule
+Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 10.46 \\ p-value = 2.95 x $10^{-9}$}} \\ 
+\bottomrule
+\end{tabular}
+  \caption {Statistical tests \Sof{Only for \chart{} yet}}
+  \label{table:st}
+\end{table*}
+
+\begin{figure}[h]
+		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
+		\caption{Nemenyi post-hoc analysis results \Sof{Only for \chart{} yet}}
+		\label{fig:performance}
+\end{figure}
+
+\subsection{Reduction Performance of \ds{}}
+
+\begin{table}[h]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{cccc}
+		\toprule
+		Project             &  top-5  & top-10 & $\Delta$ \%\\ 
+		\midrule
+		\chart{}  & 59.30\% & 53.64\% & 5.66 \%\\ 		
+		\bottomrule
+	\end{tabular}
+	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
+	\label{tab:red}
+\end{table}
+\normalsize
+
+Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.
+The reduction percentage decreases 5.66\% if the top-10 is considered instead of the top-5.
+
 \subsection{Threats to validity}
 
-\Sof{@todo}
-
-%
-%
-%\subsubsection{How much reduction in one execution trace
-%  can one get with Dynamic Slicing?}
-%
-%Table~\ref{fig:ds-reduction} shows the average reduction obtained with
-%slicing considering our implementation. The first column shows the \dfj{} project name.
-%Column ``Stmts. Covered'' shows the number of statements covered in
-%the execution of one failing test, column ``Slice Size'' shows the
-%number of statements appearing in the slice size, and column ``\%
-%Reduction'' shows the percentage reduction obtained. Numbers reported
-%are averaged across all executions. We only considered cases where we
-%knew a priori the slice contained the faulty statements
-%(Section~\ref{sec:ds-limitations}). Overall, it is noticeable that
-%both absolute reduction (as per column ``Slice Size'') and relatitve
-%reduction (as per column ``\% Reduction'') obtained are
-%significant.
-%
-%\begin{table}[h]
-%  \centering
-%  %  \resizebox{\columnwidth}{!}{%
-%  \setlength{\tabcolsep}{3pt}
-%    \begin{tabular}{lrrrr}
-%      \toprule
-%      Project             & Stmts. & Slice &
-%      \multicolumn{2}{c}{Reduction} \\
-%      \cline{4-5}
-%                          &  Covered &  Size  & \multicolumn{1}{c}{Avg.} & \multicolumn{1}{c}{$\sigma$}\\
-%      \midrule
-%      \lang{}             & 4,221             & 94            &  97.77\%  & -       \\
-%      \cmath{}            & 743,587           & 175           &  90.16\%  & 14.98\% \\
-%      \closure{}          & -                 & -             &  -        & -       \\
-%      \chart{}            & 13,474            & 155           &  90.26\%  & 16.52\% \\
-%      \jtime{}            & 23,360            & 912           &  95.99\%  & 01.25\% \\
-%      \mockito{}          & 3,064             & 340           &  82.48\%  & 12.02\% \\
-%      \bottomrule
-%  \end{tabular}
-%%}
-%\caption {\label{fig:ds-reduction}Average reduction in slice sizes. We
-%  rounded averages to the closest integer in columns
-%  ``Stmts. Covered'' and ``Slice Size''.\Mar{Para a coluna
-%    avg. reduction, o correto IMO eh tirar a media das reducoes e nao a
-%    reducao media.  Mais precisamente, considerando lang, ao inves de
-%    calcular 100*(4221-94)/4221 (como acima), deveriamos tirar a media
-%das reducoes considerando cada caso de lang.}\Mar{Nao costumo ver
-%    desvio padrao como percentagem}}
-%\end{table}
-%\normalsize
-%
-%\subsubsection{What are the limitations of Dynamic Slicing?}
-%\label{sec:ds-limitations}
-%
-%%% Omission errors, implicit dependencies, and multiple regression faults
-%%% can result in bug misses.  Omission errors occur when existing code
-%%% requires no modification but new code is needed to fix a
-%%% bug. Consequently, the slice of a failing test that manifests an
-%%% omission error misses the faulty statements as they are yet to be
-%%% added in code.  Figure~\Fix{ref} shows an example of omission
-%%% error.\Mar{add example}\Mar{consider removing omission errors as
-%%%   \sfl{} cannot handle this case anyway.  check what we did on ICST'17
-%%%   paper.}
-%
-%%% \begin{figure}[h!]
-%%%   \begin{lstlisting}[frame=single]  % Start your code-block
-%%%     int myMethod(int myParam) {
-%%%       var result: Int = 0
-%%%       //result = myParam //This line is missing
-%%%       if (myParam <= 10) {
-%%%         result = result / 10
-%%%       }
-%%%       return result
-%%%     }
-%%%   \end{lstlisting}
-%%%   \caption{\Luis{Exemplo de falha de omissao do tipo \textbf{New Code}}}
-%%%   \label{example-new-code}
-%%% \end{figure}
-%
-%The pie chart in Figure~\ref{pie-chart} highlights the sources of
-%problems associated with slicing.  We classify the slicing task as
-%problematic when it misses the faulty statement. A number of reasons
-%can explain a miss:
-%
-%\begin{itemize}
-%\item \textbf{Missing code:} this case happens when the
-%bug is due to missing code. Any fault localization method, including
-%Slicing and \sfl{}, are innefective in this case. This is the main
-%source of problem we found in our dataset. Note that, although this
-%problem is not specific to slicing, executable slices could be used to
-%help the developer identify missing statements with
-%inspection.
-%
-%\item \textbf{Non-observable effect:} This case happens when the
-%buggy code does not produce effect on the output. Consider, for
-%example, the scenario where there is a bug in a branch predicate that
-%results in execution not taking the branch guarded by a
-%conditional. In that case, the \CS{} is able to produce a slice that
-%does not contain the faulty if statement, still reproducing the
-%original output. This problem is specific to \CS{}. Note from the
-%piechart that this is the second most prevalent source of problem but
-%much less significant compared to missing
-%code.
-%
-%\item \textbf{Non-deterministic output:} This case happens when the
-%  output of the program changes in every execution, such as random
-%  output sizes. Although, we handled specific cases such as that of a
-%  hashcode printed on the stack trace, which we are able to detect
-%  with re-execution, in general, \CS{} cannot pinpoint those cases.
-%  Consider, for example, the case of a stack overflow where the trace
-%  can vary from one execution to another.
-%
-%%% There are supported cases, such as small changes in the output (i.e.,
-%%% hashcode of an object printed in the stack trace). Although,
-%%% StackOverflowException is not one of those cases, which the size of
-%%% lines printed is not the same.
-%
-%\end{itemize}
-%
-%
-%\begin{figure}[ht]
-%  \centering
-%  \begin {tikzpicture}
-%    \pie[
-%      text=pin,
-%      radius=1.5,
-%      color={
-%        white!22.1,
-%        white!14.7,
-%        white!1.6,
-%        white!61.6
-%      }
-%    ]{
-%      61.6/{Missing Code (117)},
-%      14.7/{Non-Observable Effect (28)},
-%      1.6/{Non-deterministic Output (3)},
-%      22.1/{REMOVEME (42)}
-%    }
-%  \end {tikzpicture}
-%  \caption{\label{pie-chart}Source of problems in \Fix{XX} of the
-%    \Fix{YY} cases where Dynamic Slicing misses the faulty statement.}
-%\end{figure}
-%
-%\Fix{I was left wondering: so what? What is the message and the actionable points?}
-%\Fix{The goal of this paper is debugging, so we should answer the question: does
-%dynamic slicing alone help in debugging?}
-%
-%\subsection{Results of the \comb{} combination}
-%
-%This section describes the results of the \comb{} combination. The
-%independent variables we used in the following experiments are (i) the
-%selection of tests to slice (see Section~\ref{sec:combination}) and
-%(ii) whether ot not the statements covered by selected tests are
-%filtered from the ranking.  Considering the first variable, the
-%illustration above shows the effect of slicing code using a single
-%failing test. However, we also analyzed the combination where we
-%compute slices of all failing tests. Intuitively, in those cases, more
-%lines in the matrix would be affected. The rationale for varying the
-%selection of tests to slice is to assess the impact that the amount of
-%slicing code has on performance of \sfl{}.  Considering the second
-%variable, the illustration above shows the scenario where all
-%components are reported in the ranking. However, we also analyzed the
-%scenario where only the components covered by our selection of tests
-%appear in the ranking. For the case above, only $c_2$ and $c_5$ would
-%be listed.  The dependent variable we used was the performance of
-%\sfl{} measured with
-%Top@N~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
-%which indicates, for a given value N, the percentage of faults ranked
-%at position no lower than N. As recently discussed by Ang
-%\etal~\cite{ang-perez-van-deursen-rui-2017}, \sfl{} researchers
-%started using absolute metrics, such as Top@N, after Parnin and
-%Orso~\cite{parnin-orso-2011} highlighed the bias in metrics based on
-%the position of the faulty statement in the ranking relative to the
-%total size of the ranking, which is often very high. It is worth
-%mentioning that we used the GZoltar~\cite{gzoltar} toolset to run our
-%experiments.
-%
-%\Fix{discutir Tabela~\ref{tab:summary}...}
-%
-%
-%\begin{table}[h]
-%  \centering
-%  \setlength{\tabcolsep}{4pt}
-%    \begin{tabular}{lrrrr}
-%      \toprule
-%      Project            & (1,N) & (1,F) & (A,N) & (A,F)  \\
-%      \midrule
-%      \lang{}            & -  & - & -  & - \\
-%      \cmath{}           & -  & - & -  & - \\
-%      \closure{}         & -  & - & -  & - \\
-%      \chart{}           & -  & - & -  & - \\
-%      \jtime{}           & -  & - & -  & - \\
-%      \mockito{}         & -  & - & -  & - \\
-%      \bottomrule
-%  \end{tabular}
-%\caption {\label{tab:summary}Summary of results considering Top@N, for
-%  N=50, which is the midpoint value of N for the range we selected
-%  1-100.}
-%\end{table}
-%\normalsize
-%
-%\subsubsection{What is the impact of slicing one failing test?}
-%This scenario reflects the case where the developer selects one given
-%test to focus debugging efforts. Figure \ref{fig:one-failing-test}
-%compares the results of \sfl{} and \comb{} when slicing code
-%associated with a single failing test. The top section of the figure
-%shows results without filtering covered statements whereas the lower
-%section shows the results with filtering. Each table shows the results of \sfl{} and \comb{}
-%for increasing values of N.  The top section of each table shows the
-%results for \sfl{} whereas the lower section shows results of
-%\comb{}. A plot for each subject appears under the tables to
-%illustrate how techniques compare. The x-axis denote the value of N
-%and the y-axis denotes the value of Top@N. Informally, a quick
-%increase is good~--~it means a high percentage of faults was detected
-%for small values of N.\Mar{@Rui, ainda nao esta claro qual a mensagem
-%  que vamos transmitir. Considerando resultados atuais, existe
-%  reducao, mas parece ser pouca para N<20. Existe algum valor de N
-%  considerado referencia para que a gente possa dar mais substancia ao
-%  resultado?}
-%
-%\subsubsection{What is the impact of slicing all failing tests?}
-%Table~\ref{fig:all-failing-tests} \Fix{...............}
-
-%
-%\begin{figure*}[!ht]
-%  \centering
-%    \begin{tabular}{cl|rrrrrrrrrr}
-%      \toprule
-%      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
-%      \midrule
-%
-%      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
-%      \midrule
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
-%      & \lang{}       & 24.72 & 25.84 & 28.09 & 32.58 & 35.96 & 46.07 & 79.78 & 79.78 & 83.15 & 84.27 \\
-%      & \chart{}      & 18.97 & 24.14 & 31.03 & 31.03 & 32.76 & 72.41 & 72.41 & 75.86 & 79.31 & 79.31 \\
-%      & \jtime{}      & 34.78 & 58.7  & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 63.04 & 71.74 & 71.74 \\
-%      & \mockito{}    & 44.32 & 47.73 & 57.95 & 61.36 & 61.36 & 63.64 & 65.91 & 70.45 & 76.14 & 77.27 \\
-%      \hline
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
-%      & \lang{}       & 31.46 & 37.08 & 51.69 & 57.3  & 65.17 & 77.53 & 80.9  & 82.02 & 87.64 & 91.01 \\
-%      & \chart{}      & 43.1  & 46.55 & 60.34 & 81.03 & 94.83 & 96.55 & 96.55 & 96.55 & 96.55 & 98.28 \\
-%      & \jtime{}      & 50.0  & 63.04 & 63.04 & 63.04 & 63.04 & 67.39 & 71.74 & 71.74 & 71.74 & 71.74 \\
-%      & \mockito{}    & 45.45 & 47.73 & 60.23 & 60.23 & 61.36 & 62.5  & 67.05 & 76.14 & 79.55 & 80.68 \\
-%      \midrule
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest.pdf}}\\
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest.pdf}}\\
-%
-%      \midrule
-%
-%      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
-%      \midrule
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
-%      & \lang{}     & 33.71 & 41.57 & 49.44 & 52.81 & 60.67 & 84.27 & 94.38 & 95.51 & 96.63 & 98.88 \\
-%      & \chart{}    & 25.86& 36.21& 36.21& 36.21& 60.34& 75.86& 75.86 & 79.31& 79.31& 79.31 \\
-%      & \jtime{}       & 43.48 & 63.04 & 65.22 & 69.57 & 71.74 & 71.74 &73.91 & 73.91 & 73.91 & 73.91 \\
-%      & \mockito{} & 72.09 & 74.42 & 77.91 & 80.23 & 83.72 & 83.72 & 84.88 & 84.88 & 86.05 & 86.05 \\
-%      \midrule
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
-%      & \lang{}     & 46.07 & 58.43 & 66.29 & 67.42 & 74.16 & 93.26 & 97.75 & 98.88 & 100.0 & 100.0 \\
-%      & \chart{} & 51.72& 63.79& 65.52& 86.21& 98.28& 98.28& 98.28& 98.28& 98.28& 98.28 \\
-%      & \jtime{} & 65.22 & 69.57 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 & 73.91 \\
-%      & \mockito{} & 73.26 & 77.91 & 82.56 & 87.21 & 87.21 & 88.37 &91.86 & 94.19 & 95.35 & 95.35 \\
-%      \midrule
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-onefailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-onefailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-onefailingtest-filtering.pdf}}\\
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-onefailingtest-filtering.pdf}}\\
-%
-%      \bottomrule
-%
-%    \end{tabular}
-%    \caption{\label{fig:one-failing-test}Top@N, considering one failing test.}
-%\end{figure*}
-%
-%\begin{figure*}[!ht]
-%  \centering
-%    \begin{tabular}{cl|rrrrrrrrrr}
-%      \toprule
-%      & \multicolumn{1}{c|}{Project~\textbackslash{}~LOC}             & 10  & 20  & 30  &  40  & 50  & 60 & 70 &  80 &  90& 100 \\
-%      \midrule
-%
-%      \multicolumn{12}{c}{\emph{\textbf{Not} Filtering statements covered by test(s).}}\\
-%      \midrule
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\sfl}}}
-%      &Apache commons-lang     & 25.0  & 27.27 & 29.55 & 38.64 & 43.18
-%      & 56.82 & 63.64 & 63.64 & 68.18 & 70.45 \\
-%      &\chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 87.5  & 93.75 & 93.75 \\
-%      &Joda-Time       & 23.08 & 38.46 & 46.15 & 46.15 & 46.15 & 46.15
-%      & 46.15 & 46.15 & 46.15 & 46.15 \\
-%      &Mockito & 16.67 & 29.17 & 33.33 & 37.5  & 37.5  & 41.67 & 45.83
-%      & 54.17 & 58.33 & 62.5 \\
-%      \hline
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\comb}}}
-%      &Apache commons-lang     & 36.36 & 50.0  & 56.82 & 59.09 & 63.64
-%      & 65.91 & 65.91 & 68.18 & 75.0  & 81.82 \\
-%      & \chart{}       & 68.75 & 81.25 & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
-%      &Joda-Time       & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15
-%      & 46.15 & 46.15 & 46.15 & 46.15 \\
-%      &Mockito & 20.83 & 29.17 & 41.67 & 41.67 & 41.67 & 45.83 & 58.33
-%      & 66.67 & 70.83 & 75.0 \\
-%      \midrule
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest.pdf}}\\
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest.pdf}}\\
-%      \midrule
-%
-%      \multicolumn{12}{c}{\emph{Filtering statements covered by test(s).}}\\
-%      \midrule
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\sfl}}}}
-%      & \lang{}     & 36.36 & 45.45 & 59.09 & 63.64 & 70.45  & 79.55 & 88.64 & 90.91 & 93.18 & 97.73 \\
-%      & \chart{}       & 50.0  & 68.75 & 75.0  & 75.0  & 75.0  & 87.5  & 87.5  & 93.75 & 93.75 & 93.75 \\
-%      & \jtime{}        & 30.77 & 46.15 & 46.15 & 46.15 & 46.15 & 46.15  & 53.85 & 53.85 & 53.85 & 53.85 \\
-%      & \mockito{} & 50.0  & 54.17 & 62.5  & 66.67 & 70.83 & 75.0  & 79.17 & 79.17 & 79.17 & 79.17 \\
-%      \hline
-%      \parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{\footnotesize{\comb}}}}
-%      & \lang{}     & 56.82 & 81.82 & 93.18 & 93.18 & 95.45  & 95.45 &95.45 & 97.73 & 100.0 & 100.0 \\
-%      & \chart{}       & 68.75 & 87.5  & 93.75 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 \\
-%      & \jtime{}        & 53.85 & 53.85 & 53.85 & 53.85 & 53.85 & 53.85  & 53.85 & 53.85 & 53.85 & 53.85 \\
-%      & \mockito{} & 54.17 & 70.83 & 79.17 & 83.33 & 83.33 & 87.5  & 87.5 & 87.5  & 91.67 & 91.67 \\
-%      \midrule
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/commons-lang-allfailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jfreechart-allfailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/jodatime-allfailingtest-filtering.pdf}}\\
-%
-%      \multicolumn{2}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}
-%      &
-%      \multicolumn{5}{c}{\includegraphics[width=0.25\textwidth]{R/mockito-allfailingtest-filtering.pdf}}\\
-%      \bottomrule
-%
-%    \end{tabular}
-%    \caption{\label{fig:all-failing-test}Top@N, considering all failing test.}
-%\end{figure*}
-
-%
-%We pose the following research questions:
-
-%\textit{RQ1: How frequent are dynamic slices without the bug produced? }
-%~\Davino{ XX\% of the results show omission cases, i.e., cases where the fault of the program wasn't present on the generated slice. }
-
-%\textit{RQ2: Are SFL techniques effective on minimizing the effort to manual/automated fault localization?}
-%~\Davino{ With the results, we show that it surely isn't. Rank of
-%suspiciousness commonly puts the fault at the top 50+ lines of code,
-%which isn't practical using manual or automated fault localization, or
-%even automated program repair.}
-
-%\textit{RQ3: Can Critical Slicing improve Statistical Fault Localization of real faults in a program?}
-%~\Davino{ The results are based on REAL faults (instead of artificial
-%ones, which are the basis case of evaluations of techniques involving
-%slicing and SFL) presented in Defect4J's data set and show small
-%improvements when comparing SFL and DS+SFL.}
+\Sof{@todo} Lorem Ipsum is simply dummy text of the printing and typesetting industry.
+Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.
+It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.
+It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
+It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
 
@@
 
-%% ORBS~\cite{Binkley:2014:OLP:2635868.2635893,DBLP:conf/iwpc/IslamB16}
-%% is a recently-proposed slicing technique that is similar to Critical
-%% Slicing. It is worth noting that
-
 \subsection{SFL}
@@
 
-% \subsubsection{Applications}
-
-% Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
-% technique involving dynamic slicing and SFL applied to MATLAB/Simulink
-% models. The technique consists of iteratively
-% generating tests that cause an error using satisfiability modulo
-% theories (SMT) so that the slices generated are distinct from each
-% other.  For slicing, their technique uses a program dependence graph
-% (PDG) that express both data and control dependencies between blocks,
-% so that the slice is built only on blocks that affect a specific line
-% in the model - \textit{effective blocks}.  Their goal with the slicing
-% was (1) to keep suspiciousness of a fault maximum if a target model
-% has only one fault, and (2), to reduce the number of fault candidates
-% obtained by the slicer.  For this, they utilize only failed test cases
-% generated with SMT solvers ~\cite{peleska-vorobev-lapschies-2011} to
-% calculate suspiciousness, as passed test cases might lower the
-% suspiciousness of a fault.  The calculated suspiciousness is the
-% number of times that a block belongs to the \textit{effective blocks}
-% group by the number of total failed test cases.  Although their
-% experiments and results showed promise with small models, the accuracy
-% of the technique decreases when applied to models with multiple faults
-% instead of one, as does the efficiency when exposed to large models,
-% number of generated tests, sizes of sliced models and so on.
-
-% \subsubsection{Automatic Program Repair}
-% Automated repair techiniques have received considerable attention on
-% the last decade and consists of three basic steps: fault localization, patch
-% generation, and patch validation.  Regarding the fault localization
-% step, Automated Program Repair (APR) tools can be guided by statistical
-% fault localization techiniques to modify code which most likely
-% contains the fault. On this section, we will briefly describe some of
-% these tools.
-% \Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }
-
-% GenProg\Fix{cite} is a state of the art tool based on genetic
-% programming to repair defects in off-the-shelf C programs. GenProg's
-% strategy to fault localization consists of instrumenting the program
-% so that all lines visited when executing failing test cases are
-% recorded and used on the genetic search algorithm. The algorithm
-% involves serching for other parts of the program, considering that a
-% program that contains an error in one area likely implements the
-% correct behaviour elsewhere. The tool proved to be effective in
-% reparing 16 programs involving 1.25 millions LOC, and efficient as the
-% algorithm search space takes advantage of test case coverage
-% information, reusing  existing program statements.
-
-% Debroy and Wong\Fix{cite} presented a techinique for automatically
-% fixing faults in a program combining both mutation and statistical
-% fault localization. Using the Tarantula fault localizer\Fix{cite}, the
-% techinique focus the top ranked statements in terms of suspiciousness
-% for the mutation operations. The percentage of statements examined in
-% search for the fault is based on the total number of statements of the
-% program, with the 10 percent being a reasonable number on the subject
-% programs studied.
-
-% JAFF\Fix{cite} is a Java automatic repair tool based on evolutionary principles that uses fault localization for ranking the statements in the code in terms of suspiciousness level.
-% Before searching for the fix, the Java program is translated into a syntax tree composed of nodes related to the top ranked statements being used on the search process.
-% The tool uses a specific formula to get the number of nodes that will be used on the search based on the number of statements with the same rank of suspiciousness,
-% with the range between 1 to 20 nodes being used on the cases studied.
-
-% SemFix is based on symbolic execution, constraint solving and program synthesis applied to software automatic repair. The tool uses statistical fault localization (SFL) with Tarantula to
-% obtain the rank of suspiciousness and iteratively takes the most suspicious statement that has not been tried out to be used on the search for a fix. Compared to GenProg, the presented tool
-% took consideredably less time to find a fix for programs utilizing the same test suites. However, the authors mention that the choice of the SFL techinique could potentially affect the
-% effectiviness of the tool, particularly with large programs.
-
-% SPR\Fix{cite} \Davino{ Fan Long } is based on staged
-% program repair with condition synthesis. SPR uses fault localization
-% to identify target statements that will be transformed in search for a
-% fix on the program. The search space is built with a list of
-% statements ranked by suspiciousness level, where only the first 200
-% ranked statements are considered. The authors observed that increasing
-% the search space to the top 2000 statements would bring additional
-% repairs, but with a obvious cost of searching a large space.
-% \Davino { Another tool presented by the same authors is Prophet, which uses the same search space, top 200. }
-
-% MintHint \Fix{cite} uses statistical analysis with SFL to rank
-% statements by their likelihood of being faulty. Given the ranked list,
-% the tool analysis the top \textit{k} statements, where \textit{k} is a
-% threshold set by the user, and proceeds with the repair algorithm
-% assuming the fault can be repaired by changing a single statement.
-
-% \Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }
-
 \section{Conclusions and Future Work}\label{sec:conc}
 
-\Sof{@todo}
+\Sof{@todo} Lorem Ipsum is simply dummy text of the printing and typesetting industry.
+Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.
+It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.
+It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
+It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
 
@@
 
-\Sof{...}
-
-%% The file named.bst is a bibliography style file for BibTeX 0.99c
+\Sof{maybe} Lorem Ipsum is simply dummy text of the printing and typesetting industry.Lorem Ipsum is simply dummy text of the printing and typesetting industry.
+
 {
@@
 
+	\begin{table*}[h]
+		\setlength{\tabcolsep}{3pt}
+		\begin{tabular}{llllllllllllll}
+			\toprule
+			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
+		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
+		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
+			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
+		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
+		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
+			\bottomrule
+		\end{tabular}
+		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
+		\label{table:reduction}
+	\end{table*}
+
+	\begin{table*}[h]
+		\small
+		\setlength{\tabcolsep}{3pt}
+		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
+		\toprule
+			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
+		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
+		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
+		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
+		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
+		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
+		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
+		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
+		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
+		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
+		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
+		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
+		\bottomrule
+		\end{tabular}
+		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
+		\label{table:performance}
+	\end{table*}
+	\normalsize
+
 	\begin{figure*}

### 2019-01-18 paper/ijcai/paper.tex
fixed some citations

@@
 Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant.
-Shapiro-Wilk \Fix{cite} test is performed to test for normality in the three techniques.
+Shapiro-Wilk ~\cite{10.2307/2333709} tests the null hypothesis that results are drawn from a normal distribution.
+The test is perfomed for the three techniques under evaluation (\sfl{}, \comb{}-5, \comb{}-10).
 With 99 \% of confidence, the results tell us that the distributions are not normal.
-Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman \Fix{cite}.
+Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman ~\cite{10.2307/2279372}.
 The null-hypothesis is that all distributions are the same.

### 2019-01-18 paper/ijcai/paper.tex
pass

@@
 
-\author{
-First Author$^1$,
-Second Author$^2$,
-Third Author$^3$
-\\ 
-$^1$ First Affiliation\\
-$^2$ Second Affiliation\\
-$^3$ Third Affiliation\\
-%
-first@email.address,
-second@email.address,
-third@email.address
-}
+%% \author{
+%% First Author$^1$,
+%% Second Author$^2$,
+%% \\ 
+%% $^1$ First Affiliation\\
+%% $^2$ Second Affiliation\\
+%% %
+%% first@email.address,
+%% second@email.address,
+%% third@email.address
+%% }
 
@@
 \begin{abstract}
-\Sof{@TODO}Lorem Ipsum is simply dummy text of the printing and typesetting industry.
-Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.
-It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.
-It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
-It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
+  ...
 \end{abstract}
@@
 are two very popular techniques that use different principles to
-automate debugging. Dynamic Slicing ~\citeauthor{Agrawal:1990:DPS:93542.93576} looks for the statements
+automate debugging. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
 in code that influence the evaluation of the fault-revealing
@@
 research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
-exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
-recover the influence region of faulty statements. It is a black-box~
+exception. In contrast to \ds{}, \sfl{}~\cite{7390282} does not analyze
+code. It is a black-box~
 statistical fault localization method that computes suspiciousness
@@
 reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
-We found surprising that, despite these findings, reported nearly 5
-years ago, no tool or client analyses use this combination
-today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
+We found surprising that, despite these findings, no tool or client analyses use this combination
+today.\Mar{$\leftarrow$ revise. inconsistent. there is a recent paper
+  building on that idea...from 2018.} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
 over-optimistic. For example, most prior work evaluated improvements
@@
 least one failing test and reports on output a ranked list of
-components likely to be in fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
-finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
-\emph{components}\footnote{A component can be any source code artifact
-  of arbitrary granularity such as a class, a method, a statement, or
-  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
+components likely to be in
+fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
+following are given in \sfl{}: a finite set $\mathcal{C} =
+\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
+  component can be any source code artifact of arbitrary granularity
+  such as a class, a method, a statement, or a
+  branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
 $\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
@@
 the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
-transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
-M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
-of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
-is commonly referred to as
+transaction $t_i$ has failed and $e_i = 0$ otherwise; and an
+$N\times{}M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
+coverage of component $c_j$ in transaction $t_i$.  The pair
+$(\mathcal{A},e)$ is commonly referred to as
 spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
 shows an example spectrum.
-\begin{wrapfigure}[8]{r}{0.29\textwidth}
-  \vspace{-2ex}
-  \hspace{-3ex}
+\begin{wrapfigure}[8]{2}{0.3\textwidth}
+  \hspace{-2ex}
   \centering
-  \small
+  \scriptsize
   \begin{tabular}{c|cccc|c}
@@
 
-To evaluate the impact of the \comb{} combination, the authors rcompare the cost of diagnosing faulty software programs using SFL against using \comb{} for top-5 and top-10 of classes.
+%This section evaluates \comb{}.
 
@@
 
-Following other recent studies, we used the \dfj{} benchmark in our
-experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
+As in other recent related studies, we used the \dfj{} benchmark in
+our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
 includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
-\lang{} is a library
-that provides a set of helper utilities for the {\small\texttt{java.lang}}
-API. \cmath{} is a lightweight library of self-contained
-mathematics and statistics components. The \closure{} is a toolset for
-turning JavaScript files into smaller scripts for faster
-download and execution in the browser. \chart{} is a library with a
-full-featured charts user interface for Java. \jtime{} is a
-lightweight library that aims to replace the default Java
-{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
-a mocking testing framework.\comments{ that enables the developer to simulate
-the behavior of classes that cannot be used in unit testing.}
+\lang{} is a library that provides a set of helper utilities for the
+     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
+     of self-contained mathematics and statistics components. The
+     \closure{} is a toolset for turning JavaScript files into smaller
+     scripts for faster download and execution in the
+     browser. \chart{} is a Java library for creating charts. \jtime{}
+     is a lightweight library that aims to replace the default Java
+     {\small\texttt{java.util.Date}} classes providing simpler
+     APIs. \mockito{} is a mocking testing framework.\comments{ that
+       enables the developer to simulate the behavior of classes that
+       cannot be used in unit testing.}
 
@@
   \setlength{\tabcolsep}{4pt}
-    \begin{tabular}{lccc}
+    \begin{tabular}{lrrr}
       \toprule
@@
   \end{tabular}
-\caption {Characterization of \dfj{} subjects.}
+\caption {Characterization of \dfj{} subjects.\Mar{numbers seem too
+    big. is this really in
+    *k*LOC or just LOC? please, confirm.}}
 \label{tab:df4j}
@@
 
+The evaluation techniques are SFL and \comb{}-$k$, for
+$k\in\{5,10\}$. \Mar{Simplified and moved this par. from Section
+  4.0. I noticed you used this terminology (\comb{} with ``-k'')
+  below. Please, explain and provide rationale}.
+
 To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components.
@@
 two approaches. A variety in diagnostic effort is measured
-using
+using\Mar{$\leftarrow$Sofia, I found this par. confusing.}
 
@@
 
-In \textbf{RQ1}, we pretend to evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
+In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
 

### 2019-01-20 paper/ijcai/paper.tex
new update
small fixes discussed in the last meeting

@@
      for bug localization of \emph{Java} faulty programs.
-	\item Empirical evidence that the \comb{} combination improves 
+	%\item Empirical evidence that the \comb{} combination improves 
 \end{itemize}
@@
 
-\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
-
-In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
-
-Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}.
-The gain from considering the top-10 of classes instead of top-5 is small or null.
-
-Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project.
-The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes.
-Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.
+\subsubsection{RQ1: \textit{Diagnosis capability}}
 
@@
 		\midrule
-\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
-		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
-		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
-		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
-		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
-		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
+		\lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
+		\cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
+		\closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
+		\chart{}           & 84.61 \%  & 92.31 \% & 7.70 \%      \\  %\comments{& 92    &  -}\\
+		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
+		\mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
 		\bottomrule
@@
 \end{table}
+
+\subsubsection{RQ2: \textit{How often DS misses faulty statements?}}
+
+In \textbf{RQ2}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
+
+Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}.
+The gain from considering the top-10 of classes instead of top-5 is small or null.
+
+Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project.
+The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes.
+Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.
 
@@
 
-In \textbf{RQ2}, we pretend to evaluate the impact of combining \ds{} to improve \ds{}.
+In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.
 
@@
 	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{cccc}
+	\begin{tabular}{ccc}
 		\toprule
-		Project             &  top-5  & top-10 & $\Delta$ \%\\ 
+		Project             &  top-5  & top-10 \\ 
 		\midrule
-		\chart{}  & 59.30\% & 53.64\% & 5.66 \%\\ 		
+		\chart{}  & 59.30\% & 53.64\% \\ 		
 		\bottomrule

### 2019-01-21 app/generate_expected_msg.py
get exp fixed

@@ -1,5 +1,5 @@
 #! /usr/bin/python3
-import argparse, os
+import argparse, os, tempfile
 from utils import json_to_dict, get_testname_expected_msg, call_cmd
 
 main = argparse.ArgumentParser()
@@ -79,23 +79,22 @@ def generate_seed(project, bugnumber):
                 os.makedirs(expected_dir)
             
             expected_msg_path = expected_dir+bug_number
-            project_dir = '/tmp/'+project_name+'_'+bug_number+'b/'
-            output_filepath = project_dir+'failing_tests'
+            project_dir = tempfile.mkdtemp(prefix="lithium-slicer_")
+            output_filepath = project_dir+'/failing_tests'
+            print('output_filepath=', output_filepath)
             expected_msg = []
+            failing = ''
             
-            for test in data['failing']:
-                testcase = test['test']
-                runtest_script = "bash run_input_test.sh {PROJECTDIR} {TESTCASE} {PROJECT} {BUG}"
-                cmd_str = runtest_script.format(PROJECTDIR=project_dir, TESTCASE=testcase, PROJECT=project_name, BUG=bug_number+'b')
-                output = call_cmd(cmd_str) # call shell script
-                if os.path.isfile(output_filepath):
+            runtest_script = "bash run_input_test.sh {PROJECTDIR} {PROJECT} {BUG}"
+            cmd_str = runtest_script.format(PROJECTDIR=project_dir, PROJECT=project_name, BUG=bug_number+'b')
+            output = call_cmd(cmd_str) # call shell script
+            if os.path.isfile(output_filepath):
                     with open(output_filepath) as out_fail:
-                        failing = out_fail.readlines() 
-                        expected_msg+=failing
+                        failing = out_fail.readlines()
                 
             with open(expected_msg_path,"w+") as expected:
                 expected.write(
-                    "{}\n".format(''.join(expected_msg))
+                    "{}".format(''.join(failing))
                 )
 
 generate_seed(project_name, bugs)

### 2019-01-21 app/run_input_test.sh

@@ -8,13 +8,12 @@
 
 # PARAMS
 PROJECTDIR=$1 #e.g. /tmp/Lang_1b/
-TESTCASE=$2 #e.g. org.jfree......Tests::test9999
-PROJECT=$3 #e.g. Lang
-BUG=$4 #e.g. 1b
+PROJECT=$2 #e.g. Lang
+BUG=$3 #e.g. 1b
 
 ####################
 # run the test case
 ####################
 defects4j checkout -p $PROJECT -v $BUG -w ${PROJECTDIR}
 defects4j compile -w ${PROJECTDIR} 2>/dev/null
-defects4j test -t $TESTCASE -w ${PROJECTDIR} 2>/dev/null
+defects4j test -w ${PROJECTDIR} 2>/dev/null

### 2019-01-24 paper/ijcai/paper.tex
paper

@@
 
+\subsection{Dynamic Slicing}
+
+\begin{table}[h]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lcc}
+		\toprule
+		Project             &  top-5  & top-10 \\ 
+		\midrule
+
+        \lang{}            &  & \\ 	
+        \cmath{}           &  & \\
+        \closure{}          &  & \\	
+		\chart{}			& 59.30\% & 53.64\% \\ 	
+        \jtime{}            &  & \\	
+        \mockito{}          &  & \\
+
+		\bottomrule
+	\end{tabular}
+	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
+	\label{tab:red}
+\end{table}
+\normalsize
+
+Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.
+The reduction percentage decreases 5.66\% if the top-10 is considered instead of the top-5.
+
 \subsection{Results}
@@
 
-\begin{table}[h]
+\begin{table*}[h]
 	\centering
-	\setlength{\tabcolsep}{4pt}
-	  \begin{tabular}{lccc}
+	  \begin{tabular}{|l|ccc|cccc|c|}
 		\toprule
-		Project            & \# top-5 & \# top-10  & \% $\Delta$  \\ 
+		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{SFL+DS-$k$} & \multirow{2}{*}{\# Faults} \\
+
+		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
 		\midrule
-		\lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
-		\cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
-		\closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
-		\chart{}           & 84.61 \%  & 92.31 \% & 7.70 \%      \\  %\comments{& 92    &  -}\\
-		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
-		\mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
+		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
+		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
+		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
+		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
+		% \jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
+		% \mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
 		\bottomrule
@@
   \label{table:fsws}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table*}[h]
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{llllll}
-		\toprule
-		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\ 
-		\midrule
-		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\
-		\jtime{}  &  &  &  &   & \\
-		\bottomrule
-	\end{tabular}
-	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
-	\label{tab:fs}
-\end{table*}
-\normalsize
+% \begin{table*}[h]
+% 	\centering
+% 	\setlength{\tabcolsep}{4pt}
+% 	\begin{tabular}{llllll}
+% 		\toprule
+% 		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\
+% 		\midrule
+% 		\chart{}  & 20 & 76.92\% & 22 & 84.62\%  & 26\\
+% 		\jtime{}  &  &  &  &   & \\
+% 		\bottomrule
+% 	\end{tabular}
+% 	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
+% 	\label{tab:fs}
+% \end{table*}
+% \normalsize
 
@@
 
-\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}
+\subsubsection{RQ3: \textit{How effective is the \comb{} combination for bug localization?}}
 
@@
 		\toprule
-		$\Delta$             &  \comb{}-5  & \comb{}-10 \\ 
+		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
 		\midrule
-		$<0$  & 5 & 4 \\ 
-		$=0$  & 6 & 7 \\ 
-		$>0$  & 15 & 15 \\
+		$<0$  & 19.2\% & 15.4\% \\ 
+		$=0$  & 23.1\% & 26.9\% \\ 
+		$>0$  & 57.7\% & 57.7\% \\
 
@@
 \end{figure}
-
-\subsection{Reduction Performance of \ds{}}
-
-\begin{table}[h]
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{ccc}
-		\toprule
-		Project             &  top-5  & top-10 \\ 
-		\midrule
-		\chart{}  & 59.30\% & 53.64\% \\ 		
-		\bottomrule
-	\end{tabular}
-	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
-	\label{tab:red}
-\end{table}
-\normalsize
-
-Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.
-The reduction percentage decreases 5.66\% if the top-10 is considered instead of the top-5.
 

### 2019-01-25 paper/ijcai/paper.tex
results for time and mockito added

@@
 		\chart{}			& 59.30\% & 53.64\% \\ 	
-        \jtime{}            &  & \\	
-        \mockito{}          &  & \\
+        \jtime{}            & 17.27\% & 32.92\%\\	
+        \mockito{}          & 16.99\% & 21.67\%\\
 
@@
 
-\subsubsection{RQ1: \textit{Diagnosis capability}}
+\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
+
+In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
+
+Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}.
+The gain from considering the top-10 of classes instead of top-5 is small or null.
+
+Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project.
+The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes.
+Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.
 
@@
 		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
-		% \jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
-		% \mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
+		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%  & 22 & 81.48\% & 23 & 85.19\% & 27     \\   %\comments{& 76    &  -}\\
+		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.05\% & 30 & 78.95\% & 38 \\     %\comments{& 118   &  -}\\
 		\bottomrule
@@
 \end{table*}
-
-\subsubsection{RQ2: \textit{How often DS misses faulty statements?}}
-
-In \textbf{RQ2}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
-
-Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}.
-The gain from considering the top-10 of classes instead of top-5 is small or null.
-
-Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project.
-The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes.
-Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.
 
@@
 
-\subsubsection{RQ3: \textit{How effective is the \comb{} combination for bug localization?}}
+\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}
 
-In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.
+In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.
 
@@
 		\midrule
-		$<0$  & 19.2\% & 15.4\% \\ 
-		$=0$  & 23.1\% & 26.9\% \\ 
-		$>0$  & 57.7\% & 57.7\% \\
+		$<0$  & 31.87\% & 25.27\% \\ 
+		$=0$  & 26.37\% & 26.37\% \\ 
+		$>0$  & 41.76\% & 41.76\% \\
 
@@
 	\end{tabular}
-	\caption {\Sof{This can be a barchart} Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
 	\label{tab:diagnosis}
@@
   & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
-Mean & 531.04     & 745.71   & 715.62    \\ \midrule
-Median & 17.5                   & 15.25                & 15.25                 \\ \midrule
-Variance & 1520.09      & 1794.86   & 1803.11    \\ \midrule
-Shapiro-Wilk & \makecell{W = 0.40 \\ p-value = 2.95 x $10^{-9}$} & \makecell{W = 0.48 \\ p-value = 1.54 x $10^{-8}$} & \makecell{W = 0.46 \\ p-value = 9.11 x $10^{-9}$}  \\ \midrule
-Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 10.46 \\ p-value = 2.95 x $10^{-9}$}} \\ 
+Mean & 521.59     & 855.34   & 758.06    \\ \midrule
+Median & 57.21      & 260.33                & 109                \\ \midrule
+Variance & 1021.65      & 1307.70   & 1275.34    \\ \midrule
+Shapiro-Wilk & \makecell{W = 0.56 \\ p-value = 4.00 x $10^{-15}$} & \makecell{W = 0.69 \\ p-value = 1.81 x $10^{-12}$} & \makecell{W = 0.65 \\ p-value = 1.68 x $10^{-13}$}  \\ \midrule
+Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 7.22 \\ p-value = 0.027}} \\ 
 \bottomrule
 \end{tabular}
-  \caption {Statistical tests \Sof{Only for \chart{} yet}}
+  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
   \label{table:st}
@@
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
-		\caption{Nemenyi post-hoc analysis results \Sof{Only for \chart{} yet}}
+		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
 		\label{fig:performance}
@@
 
+	\begin{table}[h]
+		\centering
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ccc}
+			\toprule
+			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
+			\midrule
+			$<0$  & 19.2\% & 15.4\% \\ 
+			$=0$  & 23.1\% & 26.9\% \\ 
+			$>0$  & 57.7\% & 57.7\% \\
+
+			\bottomrule
+		\end{tabular}
+		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+		\label{tab:diagnosis}
+	\end{table}
+	\normalsize
+
+	\begin{table}[h]
+		\centering
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ccc}
+			\toprule
+			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
+			\midrule
+			$<0$  & 40.7\% & 33.3\% \\ 
+			$=0$  & 25.9\% & 18.5\% \\ 
+			$>0$  & 33.3\% & 48.1\% \\
+
+			\bottomrule
+		\end{tabular}
+		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+		\label{tab:diagnosis}
+	\end{table}
+	\normalsize
+
+	\begin{table}[h]
+		\centering
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ccc}
+			\toprule
+			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
+			\midrule
+			$<0$  & 36.8\% & 28.9\% \\ 
+			$=0$  & 26.3\% & 28.6\% \\ 
+			$>0$  & 36.8\% & 50.0\% \\
+
+			\bottomrule
+		\end{tabular}
+		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+		\label{tab:diagnosis}
+	\end{table}
+	\normalsize
+
 	\begin{table*}[h]
@@
 
-	\begin{figure*}
-		\centering
-		\includegraphics[width=\textwidth]{figures/Chart_abs.pdf}
-		\caption{Comparing the rank of all faulty statetments for each project version obtained by \sfl{} and \comb{} considering the top-5 and top-10 of classes}
-		\begin{tabular}{r@{: }l}
-			SFL & Rank of all faulty statements only using \sfl{}\\
-			LS-$5$& Rank of all faulty statements after slicing the top-5 classes \\
-			LS-$10$& Rank of all faulty statements after slicing the top-10 classes 
-		\end{tabular}
-		\label{fig:ranking}
-	\end{figure*}
-
-	\begin{figure*}
-		\centering
-		\includegraphics[width=\textwidth]{figures/Chart_abs_imp.pdf}
-		\caption{\sfl{} rank improvement by applying \ds{} to the top-5 and top-10 classes of each project version}
-		\begin{tabular}{r@{: }l}
-			IMP-$5$& \sfl{} rank improvement by applying \ds{} to the top-5 classes \\
-			IMP-$10$& \sfl{} rank improvement by applying \ds{} to the top-10 classes
-		\end{tabular}
-		\label{fig:performance}
-	\end{figure*}
-
 \end{appendices}

### 2019-01-25 paper/ijcai/paper.tex
caption fixed and table percentages

@@
 
-Table \ref{tab:fs} report the absolute and relative numbers of faulty statements not found  for each project.
-The number of missing faulty statements by \ds{} decreases if we consider a higher number of classes.
-Even after considering the top-10 of faulty statements, 15.4\% of the subjects still do not contain the faulty statements.
-
 \begin{table*}[h]
@@
 		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
-		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
-		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%  & 22 & 81.48\% & 23 & 85.19\% & 27     \\   %\comments{& 76    &  -}\\
-		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.05\% & 30 & 78.95\% & 38 \\     %\comments{& 118   &  -}\\
+		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
+		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
+		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
 		\bottomrule
 	\end{tabular}
-  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
+  \caption {Number of versions where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report}
   \label{table:fsws}

### 2019-01-25 paper/ijcai/paper.tex
text + todos

@@
 \begin{abstract}
-  ...
+  \Sof{@todo}
 \end{abstract}
@@
 We found surprising that, despite these findings, no tool or client analyses use this combination
-today.\Mar{$\leftarrow$ revise. inconsistent. there is a recent paper
-  building on that idea...from 2018.} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
+today.\Sof{@todo: Revise this and look to the paper from 2018} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
 over-optimistic. For example, most prior work evaluated improvements
@@
 questions effectively evaluates the impact of the combination. To sum,
-our results show that \Fix{write a paragraph about this...}
+our results show that \Sof{@todo: sum up the results}.
 
-The contributions of this work are as follows:
+The contributions of this work are as follows \Sof{Finish this}:
 \begin{itemize}
@@
 
-\Sof{@TODO: Melhorar terminologia e algoritmo} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved.
+\Sof{@todo: Definatelly not near of finished, revise it and possibly redo it} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved.
 The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not.
@@
     big. is this really in
-    *k*LOC or just LOC? please, confirm.}}
+    *k*LOC or just LOC? please, confirm.}\Sof{I think it is a mistake and the unit should be LOC. But I will check.}}
 \label{tab:df4j}
@@
 \normalsize
+
+\Sof{@todo: Add pie chart to show the distribution of foos}
 
@@
   4.0. I noticed you used this terminology (\comb{} with ``-k'')
-  below. Please, explain and provide rationale}.
+  below. Please, explain and provide rationale}.\Sof{Not sure if it is the right one, an alterantive is using only SFL+DS
+  and instead of top-5 and top-10 use K = 5 and K = 10... Which do you think is the best?}
 
@@
 two approaches. A variety in diagnostic effort is measured
-using\Mar{$\leftarrow$Sofia, I found this par. confusing.}
+using\Sof{@todo: revise it, it is confusing}
 
@@
 
-where C is the cost of diagnosis. \Sof{Need to explain this better}
+where C is the cost of diagnosis. \Sof{@todo: Need to explain this better}
 A positive $\Delta$C means that the faulty component has risen in
@@
 Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.
-The reduction percentage decreases 5.66\% if the top-10 is considered instead of the top-5.
 
@@
 
-In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
+In \textbf{RQ1}, we evaluate how often \ds{} misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
 
-Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}.
-The gain from considering the top-10 of classes instead of top-5 is small or null.
+Table \ref{table:fsws} presents the number of faults where at least one of the faulty statements appears in the final reports of both techniques, \sfl{} and \comb{}-k.
 
@@
 	\end{tabular}
-  \caption {Number of versions where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report}
+  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
   \label{table:fsws}
@@
 
-\Sof{@todo: Answer the question}
-
 \subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}
@@
 The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
-project. Figure \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
+project. Table \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
 applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.
@@
 Table \ref{tab:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
-$\Delta<0$ means that the faulty statement may be removed.
-$\Delta=0$ means that the faulty statement remained in the same position.
-$\Delta>0$ means that \ds{} improved diagnosability.
-For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%.
-However, top-5 has less classes to minimize than top-10.
+$\Delta C <0$ means that the faulty statement may be removed.
+$\Delta C=0$ means that the faulty statement remained in the same position.
+$\Delta C >0$ means that \ds{} improved diagnosability.
+
+%For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%. However, top-5 has less classes to minimize than top-10.
 
@@
 		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-		\label{tab:diagnosis}
+		\label{tab:diagchart}
 	\end{table}
@@
 		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-		\label{tab:diagnosis}
+		\label{tab:diagtime}
 	\end{table}
@@
 		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-		\label{tab:diagnosis}
+		\label{tab:diagmockito}
 	\end{table}

### 2019-02-01 paper/ijcai/paper.tex
pass on intro

@@
 
+%% Although the technique has been intensively investigated in
+%% research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
+%% exception.
+
 Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
 are two very popular techniques that use different principles to
-automate debugging. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
-in code that influence the evaluation of the fault-revealing
-assertion. Although the technique has been intensively investigated in
-research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
-exception. In contrast to \ds{}, \sfl{}~\cite{7390282} does not analyze
-code. It is a black-box~
-statistical fault localization method that computes suspiciousness
-values associated with program entities (e.g., basic blocks). For
-that, it uses coverage information of passing and failing test
-cases. \sfl{} produces a list of program entities ranked in decreasing
-order of suspiciousness. Similarly to \ds{}, \sfl{} received
-tremendous attention over the years, but its applicability to support
-debugging remains
-questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
-Despite the skepticism of the research community, \sfl{} has been
-shown useful in supporting downstream analyses, such as Automated
-Program Repair
-(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
-an increasingly popular technique that looks for fixes to buggy
-statements. Tools like JAFF \cite{arcuri-2011}, Prophet
-\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
-and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
-likely fixes.
+automate debugging. Dynamic
+Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
+in code that influence some point of interest, such as the evaluation
+of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
+does not analyze code. It is a black-box statistical fault
+localization method that computes suspiciousness values associated
+with program entities (e.g., basic blocks) based on coverage and the
+output of test cases. More precisely, \sfl{} uses coverage information
+of passing and failing test cases to identify likely faulty
+statements. It produces on output a list of program entities ranked in
+decreasing order of suspiciousness.
+\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
+irrelevant parts of the code whereas \sfl{} ranks the relevant parts
+of the code.
 
-\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
-irrelevant parts of the code whereas \sfl{} ranks the relevant parts
-of the code.  This paper reports the results of a comprehensive study
+%% Similarly to \ds{}, \sfl{} received
+%% tremendous attention in research over the years,
+%% but its applicability to support
+%% debugging remains
+%% questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
+%% Despite the skepticism of the research community, \sfl{} has been
+%% shown useful in supporting downstream analyses, such as Automated
+%% Program Repair
+%% (\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
+%% an increasingly popular technique that looks for fixes to buggy
+%% statements. Tools like JAFF \cite{arcuri-2011}, Prophet
+%% \cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
+%% and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
+%% likely fixes.
+
+%% We found surprising that, despite these findings, no tool or client analyses use this combination
+%% today.\Sof{@todo: Revise this and look to the paper from 2018} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
+%% over-optimistic. For example, most prior work evaluated improvements
+%% of \sfl{} techniques using relative metrics, which are based on the
+%% position of the first faulty statements found in the ranking relative
+%% to the total number of ranked statements, which is often a large
+%% number. As such, it inflates actual improvements and deceives
+%% potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
+%% pointed to that fact and encouraged researchers to adopt more precise metrics,
+%% such as \topk{}
+%% \cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
+%% which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
+%% metric reports the percentage of faults captured by a technique when
+%% the rank is trimmed to the first $k$ components.
+
+This paper reports the results of a comprehensive study
 to evaluate the impact of \ds{} to improve \sfl{}. The study involves
-\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
-dataset~\cite{just-defects4j-issta2014}, which is frequently used to
-evaluated fault localization research. The intuition for the \comb{}
-combination is that several highly ranked statements, albeit covered
-by failing executions, may be unrelated to the fault. Prior work
-reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
-We found surprising that, despite these findings, no tool or client analyses use this combination
-today.\Sof{@todo: Revise this and look to the paper from 2018} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
-over-optimistic. For example, most prior work evaluated improvements
-of \sfl{} techniques using relative metrics, which are based on the
-position of the first faulty statements found in the ranking relative
-to the total number of ranked statements, which is often a large
-number. As such, it inflates actual improvements and deceives
-potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
-pointed to that fact and encouraged researchers to adopt more precise metrics,
-such as \topk{}
-\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
-which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
-metric reports the percentage of faults captured by a technique when
-the rank is trimmed to the first $k$ components.
-
+\numFaults{} faults from \numPrograms{} programs from the Defects4J
+(D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
+used to evaluated fault localization research. The intuition for the
+\comb{} combination is that several highly ranked statements, albeit
+covered by failing executions, may be unrelated to the fault. Prior
+work reported promising results in this
+combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
+but they used non-representative set of subjects in their evaluation
+or used less rigorours methods to assess improvement of techniques compared to those used
+today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
 The goal of this paper is to reassess whether the \comb{} combination

### 2019-02-04 paper/ijcai/paper.tex
pass on sections 2 and 3

@@
 
-Program slicing is a program understanding method to identify the
+Program slicing is a program understanding technique to identify the
 relevant parts of the program with respect to given points of
-interest.  This paper focuses on dynamic slicing\comments{~--~as
-  opposed to static slicing~\cite{Weiser:1981:PS:800078.802557}~--~}
-for its application in automated software
-debugging~\cite{Binkley:2014:OLP:2635868.2635893} where failing tests
-exist. We focused on Critical
-Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
+interest.  Dynamic
+slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
+  static
+  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
+has been shown useful in automated software debugging where the region
+of interest is restricted to what can be reached from failing
+tests. Several dynamic slicing techniques exist. This paper uses
+Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
 simplicity/generality.\comments{ In constrast with alternative slicing
@@
 prescribes a black-box language-semantics-agnostic recipe to computing
-executable slices.  Critical Slicing minimizes the program by deleting
-statements such that the sliced program preserves critical
-observations (\eg{}, assertion violations). The simplification
-mechanism used in Critical Slicing is rather simple, consisting of
-mutating the program and observing the output.
+slices that are executable.  Critical Slicing simplifies the original
+program such that the resulting program preserves critical
+observations, such as assertion violations. More precisely, the
+simplification mechanism consists of deleting statements on the
+original program and checking if the output of the original and
+modified program are the same.
 
-We used the Mozilla Lithium tool~\footnote{Lithium is available at \url{https://github.com/MozillaSecurity/lithium} (accessed November 2018).} as the implementation
-for Critical Slicing. Lithium is conceptually similar to the DD-min
-Delta Debugging algorithm~\cite{zeller-hildebrandt-tse2002}, but
-operates on code instead of test inputs. It takes as input a file and
-produces as output a simplified version of that file that satisfies a
-user-defined oracle. For dynamic slicing, the oracle is defined such
-that the test produces the same failure manifestation. The Lithium
-minimization process starts by determining the initial size of
+Our implementation of Critical Slicing is based on the Mozilla Lithium
+tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
+algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
+and produces as output a simplified version of that file that
+satisfies a user-defined oracle. In our case, the oracle is defined
+such that the test produces the same failure manifestation. The
+Lithium minimization process starts by determining the initial size of
 chunks---in number of lines---to delete from the input file. For that,
@@
 divides the chunk size by two and repeats the search. This iterative
-process continues until no more line can be removed.  If $n$ is the
+process continues until no more lines can be removed.  If $n$ is the
 size of the input file and $m$ is the size of the 1-minimal file found
 by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
-iterations.
-Proofs can be found elsewhere\footnote{Algorithm complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (accessed November 2018).}.
+iterations. Proofs of the algorithm complexity can be found
+elsewhere~\cite{lithium-complexity}. Our implementation is publicly
+available.
 
@@
 fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
-following are given in \sfl{}: a finite set $\mathcal{C} =
-\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
-  component can be any source code artifact of arbitrary granularity
-  such as a class, a method, a statement, or a
-  branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
+following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
+  component can be any code artifact of arbitrary granularity
+  such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
 $\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
@@
 \emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
-$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
-$(\mathcal{A},e)$ serves as input to the fault localization technique.
-With this input, the next step in this coverage-based technique
-consists of determining what columns of the matrix $A$ resemble the
-error vector $e$ the most.  For that, an intermediate component
-frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
-\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
-which the component $j$ has been active during execution ($p = 1$) or
-not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
-0$).  For instance, $n_{11}(j)$ counts the number of times component
-$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
-whereas $n_{10}(j)$ counts the number of times component $j$ has been
-involved in passing executions. We then calculate similarity to the
-error vector by means of applying \emph{fault predictors} to each
+$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  \sfl{} takes as input
+the pair $(\mathcal{A},e)$ and produces on output a list of components
+ranked by their faulty suspiciousness. To that end, the first step of
+the technique consists of determining what columns of the matrix $A$
+resemble the error vector $e$ the most.  For that, an intermediate
+component frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) =
+|\{i\mid \A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of
+runs in which the component $j$ has been active during execution ($p =
+1$) or not ($p=0$), and in which the runs failed ($q = 1$) or passed
+($q = 0$).  For instance, $n_{11}(j)$ counts the number of times
+component $j$ has been involved ($p = 1$) in failing executions ($q =
+1$), whereas $n_{10}(j)$ counts the number of times component $j$ has
+been involved in passing executions. We then calculate similarity to
+the error vector by means of applying \emph{fault predictors} to each
 component to produce a score quantifying how likely it is to be
@@
 scores and reported to the user. Ochiai is one of those fault
-predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}.
-The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
-\[ochiai = \frac{\N{11}}{\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}}\]
+predictors that has shown to perform
+well~\cite{7390282,Pearson:2017:EIF:3097368.3097441}. The Ochiai
+formula is given by the following equation
+$\textit{ochiai}\,$=$\,\N{11}/\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}$.
+%The Ochiai formula is given by~\cite{DBLP:conf/prdc/AbreuZG06}
+%\[ochiai = \frac\]
 
-\section{\sfl{} + Critical Slicing}
+\section{The \sfl{}+Critical Slicing combination}
 \label{sec:combination}
 
-\Sof{Maybe discuss the limitations of \sfl{} based on the capabilibility of \ds{}}The combinination of critical slicing and \sfl{} consists of the
-following steps: (1) Compute the execution spectra as discussed in
-Section~\ref{sec:sfl}, (2) Compute slices associated with failing
-tests, (3) Adjust the spectra computed in Step 1 with results obtained
-in Step 2, and (4) Compute suspiciousness
-scores. Figure~\ref{fig:illustration} illustrates the update of the
-spectra and suspiciousness rankings as result of slicing the program
-against the failing test $t_2$. The faulty statement in this example
-is the component $c_2$.  The slice obtained from $t_2$ is $\{c_2,
-c_5\}$.  Intuitively, slicing enables identification of cells in the
-spectra whose values can be set to zero.
+To illustrate the \sfl{}+slicing combination, consider a debugging
+scenario with five components $c_{1..5}$ and five transactions
+$t_{1..5}$, two of which are failing. Consider additionally that the
+component $c_2$ is faulty.  Figure~\ref{fig:illustration} shows, at
+the left-hand side of the arrow ($\Rightarrow$), the spectra for this
+scenario and its corresponding ranking, produced with the Ochiai
+predictor. Each line in the ranking shows the ranking position, the
+label of the component, and the Ochiai score (in parentheses). The
+spectra and ranking appearing at the right-side of the arrow are
+obtained with the \sfl{}+slicing combination, assuming that the slice
+for the transaction $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
+enables identification of cells in the spectra whose values can be set
+to zero, \ie{}, the components marked with 0 are irrelevant to
+determine the test output. Let us now observe the impact of this
+change at the ranking. Analyzing the Ochiai formula, one can observe
+that, for the statements $j$ which are not part of the slice of a
+failing test, the combination reduces the value of $\N{11}$ and
+increases the value of $\N{01}$. Therefore, suspiciosness of those
+statements decrease. Similar argument applies to other fault
+predictors. In the example from Figure~\ref{fig:illustration},
+components $c_3$ and $c_4$, which are not in the slice of $t_2$, have
+their suspiciousness reduced, enabling the faulty component $c_2$ to
+rise from the third to the first position in the ranking.
 
@@
       4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
-      4.5 & $c_5$ (0.32) & & 5 & $c_3$ (0.24)\\
+      4.5 & $c_5$ (0.32) & & 5 & $c_4$ (0.00)\\
     \end{tabular}
@@
 
-  \caption{Modifications on spectra and ranking as result of slicing code against test $t_2$.}
+  \caption{Modifications on spectra and ranking as result of slicing
+    code against test $t_2$. Double arrow ($\Rightarrow$) indicates
+    before and after.}
   \label{fig:illustration}
 \end{figure}
+
+---- estou aqui -Marcelo
+
+\Sof{Maybe discuss the limitations of \sfl{} based on the capabilibility of \ds{}}The combinination of critical slicing and \sfl{} consists of the
+following steps: (1) Compute the execution spectra as discussed in
+Section~\ref{sec:sfl}, (2) Compute slices associated with failing
+tests, (3) Adjust the spectra computed in Step 1 with results obtained
+in Step 2, and (4) Compute suspiciousness
+scores.
 
@@
 \end{theorem}
-
-Considering the Ochiai formula, for those statements $j$ which are not
-part of the slice of a failing test, the combination reduces the value
-of $\N{11}$ and increases the value of $\N{01}$. Therefore,
-suspiciosness of those statements decrease. Similar argument applies
-to other fault predictors.
-
-In the example from Figure~\ref{fig:illustration}, components $c_3$
-and $c_4$, which are not in the slice of $t_2$, have their
-suspiciousness reduced, enabling the faulty component $c_2$ to rise
-from the third to the first position in the ranking.
 

### 2019-02-05 paper/ijcai/paper.tex
pass on section 3

@@
 tests. Several dynamic slicing techniques exist. This paper uses
-Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
+Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
 simplicity/generality.\comments{ In constrast with alternative slicing
@@
 prescribes a black-box language-semantics-agnostic recipe to computing
-slices that are executable.  Critical Slicing simplifies the original
+executable slices.  Critical Slicing simplifies the original
 program such that the resulting program preserves critical
@@
 satisfies a user-defined oracle. In our case, the oracle is defined
-such that the test produces the same failure manifestation. The
-Lithium minimization process starts by determining the initial size of
-chunks---in number of lines---to delete from the input file. For that,
+such that the test produces the same failure manifestation as the one
+observed with the test execution on the original program. The
+Lithium minimization process starts by determining the initial size---in number of lines---of
+chunks to delete from the input file. For that,
 it chooses the highest power of two number smaller than the file
@@
 
-To illustrate the \sfl{}+slicing combination, consider a debugging
+The \sfl{}+\cs{} combination consists of four steps:
+\begin{enumerate}
+  \itemsep0em 
+  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
+  \item Select top $k$ most suspicious source files, according to $R$;
+  \item\label{step:compute-slice} Compute slices for every $k$;
+  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
+    the results obtained in Step~\ref{step:compute-slice} and recompute ranking;
+\end{enumerate}
+
+\Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
+  falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
+  de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
+  loop aninhado ao loop ``for every k'' que o lithium-slicer
+  implementa (algo como ``for every k and every failing test'')?  Caso
+  vc. faca slice contra um teste particular, vc. garante (checa saida)
+  que os demais testes que originalmente falhavam continuam falhando
+  pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
+  de inicio.}
+
+To illustrate the \sfl{}+\cs{} combination, consider a debugging
 scenario with five components $c_{1..5}$ and five transactions
@@
 spectra and ranking appearing at the right-side of the arrow are
-obtained with the \sfl{}+slicing combination, assuming that the slice
+obtained with the \sfl{}+\cs{} combination, assuming that the slice
 for the transaction $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
@@
 change at the ranking. Analyzing the Ochiai formula, one can observe
-that, for the statements $j$ which are not part of the slice of a
+that, for the components $j$ which are not part of the slice of a
 failing test, the combination reduces the value of $\N{11}$ and
 increases the value of $\N{01}$. Therefore, suspiciosness of those
-statements decrease. Similar argument applies to other fault
+components decrease. Similar argument applies to other fault
 predictors. In the example from Figure~\ref{fig:illustration},
@@
   \label{fig:illustration}
+  \vspace{-2ex}
 \end{figure}
 
----- estou aqui -Marcelo
-
-\Sof{Maybe discuss the limitations of \sfl{} based on the capabilibility of \ds{}}The combinination of critical slicing and \sfl{} consists of the
-following steps: (1) Compute the execution spectra as discussed in
-Section~\ref{sec:sfl}, (2) Compute slices associated with failing
-tests, (3) Adjust the spectra computed in Step 1 with results obtained
-in Step 2, and (4) Compute suspiciousness
-scores.
+\Mar{.....parei aqui}
 

### 2019-02-05 paper/ijcai/paper.tex
answering question

@@
   \item Select top $k$ most suspicious source files, according to $R$;
-  \item\label{step:compute-slice} Compute slices for every $k$;
+  \item\label{step:compute-slice} Compute slices for every $k$ and every failing test;
   \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
@@
   de inicio.}
+
+\Sof{O lithium-slicer funciona por caso de teste. Cada execução da nossa
+ferramenta chama o lithium tantas vezes como o número de casos de teste 
+que falham para cada versão do projecto. Assumindo que o numero de casos de
+testes a falhar são 5, numa execução da nossa plataforma o lithium é executado
+5x para os 5 testes diferentes. No fim, pega no resultado do slicing de cada 
+teste e actualiza a matrix spectra para calcular o ranking. Eu confiro depois de 
+executar a nossa ferramenta para uma versão do projecto que os 
+testes que aparecem na pasta da versão do projecto são os mesmos quando corro 
+o test do defects4j de novo. Uma precaução que tivemos foi ter a certeza que o
+oracle que estava a ser usado não sofria com a mudança de máquinas. Portanto,
+antes de correr as experiências eu corri o defects4j para obter as mensagens
+esperadas de novo para serem usadas como o oracle esperado. Estas são as verificações
+que faço. Posso tentar substituir as classes minimizadas nos projectos e ver se
+realmente a mensagem de erro continua a ser a mesma - coisa que não fiz. Relativamente,
+ao pseudocode eu diria que é for every $k$ and every failing test.}
 

### 2019-02-06 paper/ijcai/paper.tex
pass on Section 3 (up to 3.1)

--- 2019-02-05 paper/ijcai/paper.tex
@@
 
-\subsection{Critical Slicing}
+\subsection{Critical Slicing (\cs{})}
 \label{sec:slicing}
@@
 
-\subsection{Spectrum-based Fault Localization}
+\subsection{Spectrum-based Fault Localization (\sfl)}
 \label{sec:sfl}
 
-Spectrum-based fault localization (\sfl) is a statistical fault
+Spectrum-based fault localization is a statistical fault
 localization technique that takes as input a test suite including at
@@
 
-\section{The \sfl{}+Critical Slicing combination}
+\section{The \sfl{}+\cs{} combination}
 \label{sec:combination}
 
-The \sfl{}+\cs{} combination consists of four steps:
-\begin{enumerate}
-  \itemsep0em 
-  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
-  \item Select top $k$ most suspicious source files, according to $R$;
-  \item\label{step:compute-slice} Compute slices for every $k$;
-  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
-    the results obtained in Step~\ref{step:compute-slice} and recompute ranking;
-\end{enumerate}
+%% \Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
+%%   falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
+%%   de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
+%%   loop aninhado ao loop ``for every k'' que o lithium-slicer
+%%   implementa (algo como ``for every k and every failing test'')?  Caso
+%%   vc. faca slice contra um teste particular, vc. garante (checa saida)
+%%   que os demais testes que originalmente falhavam continuam falhando
+%%   pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
+%%   de inicio.}
 
-\Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
-  falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
-  de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
-  loop aninhado ao loop ``for every k'' que o lithium-slicer
-  implementa (algo como ``for every k and every failing test'')?  Caso
-  vc. faca slice contra um teste particular, vc. garante (checa saida)
-  que os demais testes que originalmente falhavam continuam falhando
-  pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
-  de inicio.}
+%% \Sof{O lithium-slicer funciona por caso de teste. Cada execução da nossa
+%% ferramenta chama o lithium tantas vezes como o número de casos de teste 
+%% que falham para cada versão do projecto. Assumindo que o numero de casos de
+%% testes a falhar são 5, numa execução da nossa plataforma o lithium é executado
+%% 5x para os 5 testes diferentes. No fim, pega no resultado do slicing de cada 
+%% teste e actualiza a matrix spectra para calcular o ranking. Eu confiro depois de 
+%% executar a nossa ferramenta para uma versão do projecto que os 
+%% testes que aparecem na pasta da versão do projecto são os mesmos quando corro 
+%% o test do defects4j de novo. Uma precaução que tivemos foi ter a certeza que o
+%% oracle que estava a ser usado não sofria com a mudança de máquinas. Portanto,
+%% antes de correr as experiências eu corri o defects4j para obter as mensagens
+%% esperadas de novo para serem usadas como o oracle esperado. Estas são as verificações
+%% que faço. Posso tentar substituir as classes minimizadas nos projectos e ver se
+%% realmente a mensagem de erro continua a ser a mesma - coisa que não fiz. Relativamente,
+%% ao pseudocode eu diria que é for every $k$ and every failing test.}
 
-To illustrate the \sfl{}+\cs{} combination, consider a debugging
-scenario with five components $c_{1..5}$ and five transactions
-$t_{1..5}$, two of which are failing. Consider additionally that the
-component $c_2$ is faulty.  Figure~\ref{fig:illustration} shows, at
-the left-hand side of the arrow ($\Rightarrow$), the spectra for this
-scenario and its corresponding ranking, produced with the Ochiai
-predictor. Each line in the ranking shows the ranking position, the
-label of the component, and the Ochiai score (in parentheses). The
-spectra and ranking appearing at the right-side of the arrow are
-obtained with the \sfl{}+\cs{} combination, assuming that the slice
-for the transaction $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
-enables identification of cells in the spectra whose values can be set
-to zero, \ie{}, the components marked with 0 are irrelevant to
-determine the test output. Let us now observe the impact of this
-change at the ranking. Analyzing the Ochiai formula, one can observe
-that, for the components $j$ which are not part of the slice of a
-failing test, the combination reduces the value of $\N{11}$ and
-increases the value of $\N{01}$. Therefore, suspiciosness of those
-components decrease. Similar argument applies to other fault
-predictors. In the example from Figure~\ref{fig:illustration},
-components $c_3$ and $c_4$, which are not in the slice of $t_2$, have
-their suspiciousness reduced, enabling the faulty component $c_2$ to
-rise from the third to the first position in the ranking.
+To illustrate the idea behind the \sfl{}+\cs{} combination, consider a
+debugging scenario with five components $c_{1..5}$ and five
+transactions $t_{1..5}$, two of which are failing. Consider,
+additionally, that the component $c_2$ is faulty.
+Figure~\ref{fig:illustration} shows, at the left-hand side of the
+arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
+ranking, produced with the Ochiai predictor. Each line in the ranking
+shows, respectively, the rank/position, the component label, and the
+Ochiai score (in parentheses).
 
@@
 
-\Mar{.....parei aqui}
+In the following, we illustrate the workflow of the \sfl{}+\cs{}
+combination for this scenario. First, the combined technique picks
+components $c_4$ and $c_3$, which appear at the top of the ranking,
+for further analysis. (The cutoff point is user-defined.) Second, the
+technique picks a failing test $t_2$ to slice the code.  Let us assume
+that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
+\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
+ranking are updated. The right-side of Figure~\ref{fig:illustration}
+shows the modified spectra and ranking after slicing test $t_2$
+against $c_4$ and $c_3$. It is worth noting that the technique slices
+the code for every failing tests. More precisely, the \sfl{}+\cs{} combination consists of four steps:
+\begin{enumerate}
+  \itemsep0em 
+  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
+  \item\label{step:susp-files} Select top $k$ most suspicious source files, according to $R$;
+  \item\label{step:compute-slice} Compute slice for every suspicious
+    file, obtained in Step~\ref{step:susp-files}, and every failing test;
+  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
+    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
+\end{enumerate}
+
+Intuitively, slicing enables identification of cells in the spectra
+whose values can be set to zero, \ie{}, the components marked with 0
+are irrelevant to determine the test output. Let us now observe the
+effect of this spectra modification on the ranking. Analyzing the
+Ochiai formula, one can observe that, for the components $j$ which are
+not part of the slice of a failing test, the combination reduces the
+value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
+suspiciosness of those components decrease. Similar argument applies
+to other fault predictors. In the example from
+Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
+not in the slice of $t_2$, have their suspiciousness reduced, enabling
+the faulty component $c_2$ to rise from the third to the first
+position in the ranking.
 
@@
 
-It is possible that a slice that discards the faulty statement still
+It is possible that a slice that discards the faulty component still
 produces the expected message checked by the oracle. This can happen,
-for example, if the oracle is too general.
+for example, if the oracle is too
+general. Section~\ref{sec:oracleheuristics} elaborates the heuristics
+we used to mitigate this fundamental limitation of Critical Slicing.
 
-\vspace{3mm}
-\begin{myframe} \label{box:1}
-\textbf{java.lang.NullPointerException}, \\
-at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
-testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
-...
-\end{myframe}
+%% \vspace{3mm}
+%% \begin{myframe} \label{box:1}
+%% \textbf{java.lang.NullPointerException}, \\
+%% at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
+%% testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
+%% ...
+%% \end{myframe}
 
@@
 
-Section~\ref{sec:oracleheuristics} explains the heuristics
-we used to infer oracles for critical slicing that mitigates this
-issue.
+The proof is based on the argument aforementioned that irrelevant
+components $j$ have their ranks reduced as $\N{11}$ decreases and
+$\N{01}$ increases. If those irrelevant components appear at positions
+above the faulty component, it is possible that the faulty component
+becomes more suspicious relative to $j$, \ie{}, the ranking of the
+faulty component increases. If those components appear at positions
+below the faulty components, the ranking of the faulty components is
+unaffected.
+
+\Mar{parei aqui}
 

### 2019-02-08 paper/ijcai/paper.tex
pass sec 2 and sec 3 - small fixes

@@
 size. For example, if the file has 1,000 lines, Lithium sets the
-initial chunk size to 512 lines. Then, the tool starts a local search
-looking for chunks to remove from the file that satisfy the
-oracle. When no more chunks of that given size can be removed, Lithium
+initial chunk size to 512 lines. Then, the tool starts a local search looking 
+for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
+When no more chunks of that given size can be removed, Lithium
 divides the chunk size by two and repeats the search. This iterative
@@
 value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
-suspiciosness of those components decrease. Similar argument applies
+suspiciousness of those components decrease. Similar argument applies
 to other fault predictors. In the example from

### 2019-02-08 paper/ijcai/paper.tex
more fixes

@@
 against $c_4$ and $c_3$. It is worth noting that the technique slices
-the code for every failing tests. More precisely, the \sfl{}+\cs{} combination consists of four steps:
+the code for every failing tests. More precisely, the \sfl{}+\cs{} 
+combination consists of four steps:\Sof{Should we specify that these steps are
+performed for each version of the projects/defect?}
 \begin{enumerate}
   \itemsep0em 
-  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
-  \item\label{step:susp-files} Select top $k$ most suspicious source files, according to $R$;
-  \item\label{step:compute-slice} Compute slice for every suspicious
+  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for 
+  the input test suite;
+  \item\label{step:susp-files} Select top $k$ most suspicious source 
+  files, according to $R$;
+  \item\label{step:compute-slice} Compute slicer for every suspicious
     file, obtained in Step~\ref{step:susp-files}, and every failing test;
@@
 
-\Sof{@todo: Definatelly not near of finished, revise it and possibly redo it} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved.
-The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not.
+Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved.
+The function of interest determines if the test case output is interesting or not.
 In this study, interesting means that the test execution path is equal to the expected one.
@@
 Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
+
+ (Algorithm \ref{alg:finc})
 

### 2019-02-08 paper/ijcai/paper.tex
cleaning

@@
 
-Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved.
+Lithium takes as input a function of interest that can be designed according to the problem to be solved.
 The function of interest determines if the test case output is interesting or not.
@@
 
-\Sof{@todo} Lorem Ipsum is simply dummy text of the printing and typesetting industry.
-Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.
-It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.
-It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
-It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
-
 \section{Related Work}
@@
 
-\Sof{@todo} Lorem Ipsum is simply dummy text of the printing and typesetting industry.
-Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.
-It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.
-It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
-It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
-
 \section*{Acknowledgments}
-
-\Sof{maybe} Lorem Ipsum is simply dummy text of the printing and typesetting industry.Lorem Ipsum is simply dummy text of the printing and typesetting industry.
 

### 2019-02-08 paper/ijcai/paper.tex
remove appendix

@@
 
-\begin{appendices}
-	\section{Other data that might be interesting to report}
-	This section has the only purpose of presenting and discussing other data that 
-	are not intended yet to be used in the paper. If you find something interesting 
-	in this block of information, please report.
+% \begin{appendices}
+% 	\section{Other data that might be interesting to report}
+% 	This section has the only purpose of presenting and discussing other data that
+% 	are not intended yet to be used in the paper. If you find something interesting
+% 	in this block of information, please report.
+%
+% 	\begin{table}[h]
+% 		\centering
+% 		\setlength{\tabcolsep}{4pt}
+% 		\begin{tabular}{ccc}
+% 			\toprule
+% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
+% 			\midrule
+% 			$<0$  & 19.2\% & 15.4\% \\
+% 			$=0$  & 23.1\% & 26.9\% \\
+% 			$>0$  & 57.7\% & 57.7\% \\
+%
+% 			\bottomrule
+% 		\end{tabular}
+% 		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+% 		\label{tab:diagchart}
+% 	\end{table}
+% 	\normalsize
+%
+% 	\begin{table}[h]
+% 		\centering
+% 		\setlength{\tabcolsep}{4pt}
+% 		\begin{tabular}{ccc}
+% 			\toprule
+% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
+% 			\midrule
+% 			$<0$  & 40.7\% & 33.3\% \\
+% 			$=0$  & 25.9\% & 18.5\% \\
+% 			$>0$  & 33.3\% & 48.1\% \\
+%
+% 			\bottomrule
+% 		\end{tabular}
+% 		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+% 		\label{tab:diagtime}
+% 	\end{table}
+% 	\normalsize
+%
+%
+% 	\begin{table}[h]
+% 		\centering
+% 		\setlength{\tabcolsep}{4pt}
+% 		\begin{tabular}{ccc}
+% 			\toprule
+% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
+% 			\midrule
+% 			$<0$  & 36.8\% & 28.9\% \\
+% 			$=0$  & 26.3\% & 28.6\% \\
+% 			$>0$  & 36.8\% & 50.0\% \\
+%
+% 			\bottomrule
+% 		\end{tabular}
+% 		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
+% 		\label{tab:diagmockito}
+% 	\end{table}
+% 	\normalsize
+%
+% 	\begin{table*}[h]
+% 		\setlength{\tabcolsep}{3pt}
+% 		\begin{tabular}{llllllllllllll}
+% 			\toprule
+% 			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
+% 		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
+% 		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
+% 			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
+% 		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
+% 		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
+% 			\bottomrule
+% 		\end{tabular}
+% 		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
+% 		\label{table:reduction}
+% 	\end{table*}
+%
+% 	\begin{table*}[h]
+% 		\small
+% 		\setlength{\tabcolsep}{3pt}
+% 		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
+% 		\toprule
+% 			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
+% 		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
+% 		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
+% 		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
+% 		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
+% 		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
+% 		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
+% 		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
+% 		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
+% 		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
+% 		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
+% 		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
+% 		\bottomrule
+% 		\end{tabular}
+% 		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
+% 		\label{table:performance}
+% 	\end{table*}
+% 	\normalsize
 
-	\begin{table}[h]
-		\centering
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ccc}
-			\toprule
-			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
-			\midrule
-			$<0$  & 19.2\% & 15.4\% \\ 
-			$=0$  & 23.1\% & 26.9\% \\ 
-			$>0$  & 57.7\% & 57.7\% \\
-
-			\bottomrule
-		\end{tabular}
-		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-		\label{tab:diagchart}
-	\end{table}
-	\normalsize
-
-	\begin{table}[h]
-		\centering
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ccc}
-			\toprule
-			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
-			\midrule
-			$<0$  & 40.7\% & 33.3\% \\ 
-			$=0$  & 25.9\% & 18.5\% \\ 
-			$>0$  & 33.3\% & 48.1\% \\
-
-			\bottomrule
-		\end{tabular}
-		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-		\label{tab:diagtime}
-	\end{table}
-	\normalsize
-
-	\begin{table}[h]
-		\centering
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ccc}
-			\toprule
-			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
-			\midrule
-			$<0$  & 36.8\% & 28.9\% \\ 
-			$=0$  & 26.3\% & 28.6\% \\ 
-			$>0$  & 36.8\% & 50.0\% \\
-
-			\bottomrule
-		\end{tabular}
-		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-		\label{tab:diagmockito}
-	\end{table}
-	\normalsize
-
-	\begin{table*}[h]
-		\setlength{\tabcolsep}{3pt}
-		\begin{tabular}{llllllllllllll}
-			\toprule
-			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
-		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
-		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
-			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
-		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
-		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
-			\bottomrule
-		\end{tabular}
-		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
-		\label{table:reduction}
-	\end{table*}
-
-	\begin{table*}[h]
-		\small
-		\setlength{\tabcolsep}{3pt}
-		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
-		\toprule
-			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
-		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
-		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
-		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
-		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
-		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
-		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
-		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
-		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
-		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
-		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
-		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
-		\bottomrule
-		\end{tabular}
-		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
-		\label{table:performance}
-	\end{table*}
-	\normalsize
-
-\end{appendices}
+% \end{appendices}
 

### 2019-02-08 paper/ijcai/paper.tex
small fix

@@
 The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
-project. Table \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
+project. Table , reports the average rank of all faulty statements for each version of \chart{} project after
 applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.

### 2019-02-09 paper/ijcai/paper.tex
intro pass

@@
 
-%% \author{
-%% First Author$^1$,
-%% Second Author$^2$,
-%% \\ 
-%% $^1$ First Affiliation\\
-%% $^2$ Second Affiliation\\
-%% %
-%% first@email.address,
-%% second@email.address,
-%% third@email.address
-%% }
+% \author{
+% First Author$^1$,
+% Second Author$^2$,
+% \\
+% $^1$ First Affiliation\\
+% $^2$ Second Affiliation\\
+% %
+% first@email.address,
+% second@email.address,
+% third@email.address
+% }
 
@@
 
+\hypersetup{draft} 
 \begin{document}
@@
 Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
-in code that influence some point of interest, such as the evaluation
+in the code that influence some point of interest, such as the evaluation
 of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
@@
 of passing and failing test cases to identify likely faulty
-statements. It produces on output a list of program entities ranked in
+statements and produces on output a list of program entities ranked in
 decreasing order of suspiciousness.
@@
 to evaluate the impact of \ds{} to improve \sfl{}. The study involves
-\numFaults{} faults from \numPrograms{} programs from the Defects4J
-(D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
-used to evaluated fault localization research. The intuition for the
+\numFaults{} faults from \numPrograms{} different programs comprised in the 
+Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
+used to evaluate fault localization research. The intuition for the
 \comb{} combination is that several highly ranked statements, albeit
@@
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
-but they used non-representative set of subjects in their evaluation
-or used less rigorours methods to assess improvement of techniques compared to those used
+but they used a non-representative set of subjects in their evaluation
+or used less rigorous methods to assess improvement of techniques compared to those used
 today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
@@
 dataset. The D4J dataset is about twice as large than the biggest test
-suite used in previous studies. It is worth noting that \acrAbrev{}
-techniques should directly benefit from these results---either to
+suite used in previous studies. It is worth noting that Automated
+Program Repair techniques should directly benefit from these results---either to
 improve their results or to be aware they should not invest on this
@@
 performed for each version of the projects/defect?}
+
 \begin{enumerate}

### 2019-02-11 paper/ijcai/paper.tex
oracle heuristics + object of analysis + methodology pass

@@
 Our implementation of Critical Slicing is based on the Mozilla Lithium
-tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
+tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
 algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
@@
 iterations. Proofs of the algorithm complexity can be found
-elsewhere~\cite{lithium-complexity}. Our implementation is publicly
+elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
 available.
@@
 This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception.
-The authors assume that it is only necessary to compare both stack traces until the call where the test fails.
-For each chunk under evaluation, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2).
-Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails.
+The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails.
+For each chunk under evaluation, the test is executed after the chunk being deleted from the source code (Algorithm \ref{alg:finc}, line 2).
+Both test ($testStk$) and expected ($expStk$) stack traces are filtered.
+We only consider stack traces until the line where the main exception is launched.
 These operations are performed by line 3 and 4 from Algorithm 2.
 Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
-
- (Algorithm \ref{alg:finc})
 
@@
 
-%This section evaluates \comb{}.
+To evaluate our approach, we compare the cost of diagnosing
+a collection of faulty versions using \sfl{}
+against \comb{}.
 
-\subsection{Objects of Analysis}
+\subsection{Objects of Analysis}\label{sec:analysis}
 
@@
 our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
-includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
+includes six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
 \lang{} is a library that provides a set of helper utilities for the
@@
       \toprule
-      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
+      Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
       \midrule
@@
   \end{tabular}
-\caption {Characterization of \dfj{} subjects.\Mar{numbers seem too
-    big. is this really in
-    *k*LOC or just LOC? please, confirm.}\Sof{I think it is a mistake and the unit should be LOC. But I will check.}}
+\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
 \label{tab:df4j}
@@
 
-\subsection{Methodology}
+\subsection{Methodology}\label{sec:methodology}
 
-The evaluation techniques are SFL and \comb{}-$k$, for
-$k\in\{5,10\}$. \Mar{Simplified and moved this par. from Section
-  4.0. I noticed you used this terminology (\comb{} with ``-k'')
-  below. Please, explain and provide rationale}.\Sof{Not sure if it is the right one, an alterantive is using only SFL+DS
-  and instead of top-5 and top-10 use K = 5 and K = 10... Which do you think is the best?}
+The main goal of our evaluation is to understand what is the impact of \ds{} on 
+\sfl{} after minimizing the $k$ highest faulty source files which comprise the highest faulty statements. Firstly, we ran the dataset presented in Section~\ref{sec:analysis} with \sfl{} to 
+gather the coverage statements ordered from the highest faulty statement to the
+lowest faulty statement.
+This list is the input of the \comb{} technique.
+For each defect, the list is evaluated in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source files.
+Then, Lithium minimizes each source file for each testcase of the defect considering the top-$5$ (\comb{}-$5$) and top-$10$ (\comb{}-$10$) of source files separately.
+Some defects have more than one testcase.
+In the end, we update spectra $S$ based on the output of the minimization as presented in Figure~\ref{fig:ds-reduction} to obtain the faulty statements ranking after minimization.
+All scripts used to run these experiments and gather data are available at \url{TBA} and \url{TBA}, respectively.
 
-To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components.
-This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
-two approaches. A variety in diagnostic effort is measured
-using\Sof{@todo: revise it, it is confusing}
+We perform experiments for \comb{}-$5$ and \comb{}-$10$. These techniques results are analyzed against \sfl{}. The difference in the diagnostic effort is measured
+using
 
@@
 
-where C is the cost of diagnosis. \Sof{@todo: Need to explain this better}
-A positive $\Delta$C means that the faulty component has risen in
-the ranking reported by SFL techniques when DS is used,
-yielding a lowered cost of diagnosing.
+where C is the cost of diagnosis. \Sof{@todo: Explain this better in section 2 or 3}
+A positive $\Delta$C means that the faulty statement has risen in
+the ranking reported by \sfl{} techniques when \ds{} is used,
+producing a reduced cost of diagnosing.
 

### 2019-02-11 app/compare_messages.py
small fixes

@@ -18,13 +18,15 @@ if os.path.isfile(expected_msg_path):
         expected_to_cmp = ' '.join(expected_to_cmp)
     print('expected_to_cmp=', expected_to_cmp)
 
+output_to_cmp = None
+buggy_line = None
+
 if os.path.isfile(output_filepath):
-    output_to_cmp = None
-    buggy_line = None
     with open(output_filepath) as out_fail:
         failing = out_fail.readlines()
         failing_tests = get_testname_expected_msg(testname, failing)[1::]
         print('failing_tests=', failing_tests)
+        print('output_to_cmp=', output_to_cmp)
         if len(failing_tests) > 0:
             output_to_cmp, buggy_line = get_to_compare(failing_tests, testname)
             print('output_to_cmp=', output_to_cmp)
@@ -32,21 +34,22 @@ if os.path.isfile(output_filepath):
             print('output_to_cmp=', output_to_cmp)
             print('buggy_line=', buggy_line)
             
-
     try:
         # should print this line to check if there is the same buggy line
         print("[Buggy_START]{}[Buggy_END]".format(buggy_line))
     except:
         pass
-
-    # removes the "project_path/failing_tests" file
-    os.remove(output_filepath)
-
+    
     if debug:
         logger.debug("expected: {}\ngot: {}".format(expected_to_cmp, output_to_cmp))
-
-    if is_object_comparison(expected_to_cmp):
+    
+    # removes the "project_path/failing_tests" file
+    os.remove(output_filepath)
+    
+    if is_object_comparison(expected_to_cmp) and output_to_cmp != None:
         print("GOOD" if check_obj_comparison(expected_to_cmp, output_to_cmp) else "BAD")
     else:
         # should print GOOD or BAD in console
         print("GOOD" if (expected_to_cmp == output_to_cmp) else "BAD")
+    
+    

### 2019-02-11 app/interesting.py

@@ -27,7 +27,8 @@ def interesting(conditionArgs, prefix):
     testcase = conditionArgs[1]
     expected = conditionArgs[2]
     source_file = conditionArgs[3]
-
+    
+    print('Running test...')
     file_basename = os.path.basename(source_file).replace('.java', '')
     cmd_str = runtest_script.format(PROJECTDIR=project_dir, TESTCASE=testcase, EXPECTED=expected, SOURCE=file_basename)
     output = call_cmd(cmd_str) # call shell script
@@ -44,6 +45,8 @@ def interesting(conditionArgs, prefix):
         buggy_line = get_buggy_line(output)
     
     # double check comparison with buggy_line and expected/output message
+    if debug:
+        print('double_check outcome ', is_interesting and (buggy_line in output))
     return is_interesting and (buggy_line in output)
 
 def get_buggy_line(output):

### 2019-02-11 app/utils.py

@@ -134,19 +134,49 @@ def get_locs(origin_file, minimized_file):
 def check_obj_comparison(expected_msg, output_msg):
     """ returns True if the messages compare the same object """
     # expected:<...ClassName@MemoryAddress...> but was:<...ClassName@MemoryAddress...>
-    obj_comparison_pattern = r'.+(\<.+\@.+\>).+but was.+(\<.+\@.+\>)'
-    search_expected = re.search(obj_comparison_pattern, expected_msg)
-    search_output = re.search(obj_comparison_pattern, output_msg)
+    obj_comparison_pattern = (
+        r'junit.framework.AssertionFailedError: expected:(\<.+\@.+\>).+but was.+(\<.+\@.+\>)',
+        r'junit.framework.AssertionFailedError: expected:(\<.+ \[CL\]T\>) but was.+(\<.+ \[PS\]T\>)'
+        )
+    
+    needs_object_comp = False
+    i = 0
+    for p in obj_comparison_pattern:
+        needs_object_comp = True if re.search(p, expected_msg) else False
+        search_expected = re.search(p, expected_msg)
+        search_output = re.search(p, output_msg)
+        if needs_object_comp:
+            break   
+        i+=1 
+            
     if search_expected and search_output:
-        expected = search_expected.group(1).split('@')[0], search_expected.group(2).split('@')[0]
-        output = search_output.group(1).split('@')[0], search_output.group(2).split('@')[0]
+        if i == 0:
+            expected = search_expected.group(1).split('@')[0], search_expected.group(2).split('@')[0]
+            output = search_output.group(1).split('@')[0], search_output.group(2).split('@')[0]
+        elif i == 1:
+            expected = search_expected.group(1).split(' ')[1], search_expected.group(2).split(' ')[1]
+            print('expected=', expected)
+            output = search_output.group(1).split(' ')[1], search_output.group(2).split(' ')[1]
+            print('output=', output)
+            
+        print((expected[0] == output[0]) and (expected[1] == output[1]))
         return (expected[0] == output[0]) and (expected[1] == output[1])  
     return False
 
 def is_object_comparison(expected_msg):
     """ check if the message is an object comparison """
-    obj_comparison_pattern = r'.+(\<.+\@.+\>).+but was.+(\<.+\@.+\>)'
-    return re.search(obj_comparison_pattern, expected_msg) is not None
+    obj_comparison_pattern = (
[…]

### 2019-02-12 app/compare_messages.py
small changes

@@ -7,7 +7,7 @@ expected_msg_path = sys.argv[1] # "message expected" file path
 output_filepath = sys.argv[2] # "failing_test" file that contains the test output after run d4j-test
 testname = sys.argv[3] # test name
 
-debug = False # true to check expected and output messages in console (need to set debug=True in interesting.py as well)
+debug = True # true to check expected and output messages in console (need to set debug=True in interesting.py as well)
 logger = logging.getLogger(__name__)
 
 if os.path.isfile(expected_msg_path):

### 2019-02-12 app/interesting.py

@@ -16,7 +16,7 @@ test.
 runtest_script = "./runtest.sh {PROJECTDIR} {TESTCASE} {EXPECTED} {SOURCE}"
 timeout_seconds = 120
 buggy_line = None
-debug = False # True to check output in console
+debug = True # True to check output in console
 
 def interesting(conditionArgs, prefix):
     """ This function check if the file is interesting to reduce """

### 2019-02-12 app/utils.py

@@ -209,8 +209,15 @@ def get_to_compare(stacktrace, test):
                 ov_acm +=1
             if ov_acm > 5:
                 break
-        if re.search(r'Test(.*).java',stacktrace[i]) and test in stacktrace[i]: 
+        if test in stacktrace[i]: 
             break
+    if len(lines) == len(stacktrace):
+        lines=[];
+        for i in range(len(stacktrace)):
+            lines.append(stacktrace[i].strip())
+            buggy_line = stacktrace[i].strip()
+            if re.search(r'.*Test(.*).java',stacktrace[i]):
+                break 
     return lines, buggy_line
 
 @timeout(timeout_seconds) # 60s at most (compile and run test)

### 2019-02-12 paper/ijcai/paper.tex
guideline added
sketching abstract and polishing intro

@@
 
-\title{Reassessing the Impact of Dynamic Slicing in SFL}
+\title{Demystifying the Dynamic Slicing and SFL Combination}
 
@@
 \begin{abstract}
-  \Sof{@todo} 
+  The task of locating faulty code from failing testing is a very
+  important problem known as software fault localization. This paper
+  reports on a comprehensive study to reassess the impact of combining
+  two very popular techniques to that end--Dynamic Slicing and
+  Spectrum-based Fault Localization. Our results show that \Fix{...}
 \end{abstract}
@@
 
-This paper reports the results of a comprehensive study
-to evaluate the impact of \ds{} to improve \sfl{}. The study involves
-\numFaults{} faults from \numPrograms{} different programs comprised in the 
-Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
-used to evaluate fault localization research. The intuition for the
-\comb{} combination is that several highly ranked statements, albeit
-covered by failing executions, may be unrelated to the fault. Prior
-work reported promising results in this
-combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
+This paper reports the results of a comprehensive study evaluating the
+impact of combining \ds{} and \sfl{} to improve software fault
+localization. The intuition for the \comb{} combination is that
+several highly ranked statements, albeit covered by failing
+executions, may be unrelated to the fault. The study involves
+\numFaults{} faults from \numPrograms{} different programs comprised
+in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
+is frequently used to evaluate fault localization research. Prior work
+reported promising results in this
+combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
 but they used a non-representative set of subjects in their evaluation
-or used less rigorous methods to assess improvement of techniques compared to those used
-today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
+or used arcaic methods to evaluate technique
+improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
 The goal of this paper is to reassess whether the \comb{} combination
-is worthwhile under the light of a more accurate metric and a larger
-dataset. The D4J dataset is about twice as large than the biggest test
-suite used in previous studies. It is worth noting that Automated
-Program Repair techniques should directly benefit from these results---either to
-improve their results or to be aware they should not invest on this
-integration. This study covers the following research questions:
+is worthwhile under the light of a more rigorous experimental
+methodology and a larger dataset.\comments{ The D4J dataset is about
+  twice as large than the biggest test suite used in previous
+  studies.} This study covers the following research questions:
 
@@
 
-The first question addresses an important problem associated with
-dynamic slicing techniques---that of missing faulty
+The first question addresses the important problem of missing faulty
 statements. Naturally, the consequence of that problem for debugging
@@
 oracles that guide the slicing process. We evaluated how often that
-important problem happens in our experiments. The second research
-questions effectively evaluates the impact of the combination. To sum,
-our results show that \Sof{@todo: sum up the results}.
+issue manifests in our experiments. The second research questions
+effectively evaluates the impact of the combination. To sum, our
+results show that \Sof{@todo: sum up the results}.
 
@@
      for bug localization of \emph{Java} faulty programs.
+   \item A tool that implements \comb{}.
 	%\item Empirical evidence that the \comb{} combination improves 
@@
      {\small\texttt{java.util.Date}} classes providing simpler
-     APIs. \mockito{} is a mocking testing framework.\comments{ that
-       enables the developer to simulate the behavior of classes that
-       cannot be used in unit testing.}
+     APIs. \mockito{} is a mocking testing framework.
 
@@
 
+\Sof{Parei Aqui}
+
 \subsection{Dynamic Slicing}
@@
 
-        \lang{}            &  & \\ 	
+        \lang{}            & 0.77\% & 30.28\%\\ 	
         \cmath{}           &  & \\
@@
 		\midrule
-		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
+		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\   
 		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
@@
 		\midrule
-		$<0$  & 31.87\% & 25.27\% \\ 
-		$=0$  & 26.37\% & 26.37\% \\ 
-		$>0$  & 41.76\% & 41.76\% \\
+		$<0$  & 20.00\% & 17.42\% \\ 
+		$=0$  & 47.10\% & 37.42\% \\ 
+		$>0$  & 32.90\% & 45.16\% \\
 
@@
 	\end{tabular}
-	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
+	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
 	\label{tab:diagnosis}
@@
   & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
-Mean & 521.59     & 855.34   & 758.06    \\ \midrule
-Median & 57.21      & 260.33                & 109                \\ \midrule
-Variance & 1021.65      & 1307.70   & 1275.34    \\ \midrule
-Shapiro-Wilk & \makecell{W = 0.56 \\ p-value = 4.00 x $10^{-15}$} & \makecell{W = 0.69 \\ p-value = 1.81 x $10^{-12}$} & \makecell{W = 0.65 \\ p-value = 1.68 x $10^{-13}$}  \\ \midrule
-Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 7.22 \\ p-value = 0.027}} \\ 
+Mean & 387.46     & 576.74   & 522.35   \\ \midrule
+Median & 44.50      & 48.25               & 46.00                \\ \midrule
+Variance & 827.80      & 1075.90   & 1275.34    \\ \midrule
+Shapiro-Wilk & \makecell{W = 0.51 \\ p-value = 9.65 x $10^{-21}$} & \makecell{W = 0.59 \\ p-value = 5.29 x $10^{-19}$} & \makecell{W = 0.56 \\ p-value = 8.95 x $10^{-20}$}  \\ \midrule
+Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 16.87 \\ p-value = 2.2 x $10^{-4}$}} \\ 
 \bottomrule
 \end{tabular}
-  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
+  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
   \label{table:st}
@@
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
-		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
+		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
 		\label{fig:performance}
@@
 \section{Related Work}
+
+\Mar{moved from intro$\rightarrow$} It is worth noting that Automated
+Program Repair techniques should directly benefit from these
+results---either to improve their results or to be aware they should
+not invest on this integration.
 

### 2019-02-12 paper/ijcai/paper.tex
lang results

--- 2019-02-11 paper/ijcai/paper.tex
@@
 		\midrule
-		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
+		 \lang{}            & 84.1\%  & 84.1\&  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\   
 		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\

### 2019-02-12 paper/ijcai/paper.tex
small fix
pass on abstract

--- 2019-02-12 paper/ijcai/paper.tex
@@
 \begin{abstract}
-  The task of locating faulty code from failing testing is a very
-  important problem known as software fault localization. This paper
-  reports on a comprehensive study to reassess the impact of combining
-  two very popular techniques to that end--Dynamic Slicing and
-  Spectrum-based Fault Localization. Our results show that \Fix{...}
+  Software debugging is important and challenging. This paper reports
+  on a comprehensive study to reassess the impact of combining two
+  very popular automated techniques for software fault
+  localization--Dynamic Slicing and Spectrum-based Fault
+  Localization. Our results show that \Fix{...}
 \end{abstract}

### 2019-02-12 paper/ijcai/paper.tex
pass on section 3.0

@@
 
+\Mar{consider moving footnotes 1 and 2 to references.}
 Our implementation of Critical Slicing is based on the Mozilla Lithium
@@
 against $c_4$ and $c_3$. It is worth noting that the technique slices
-the code for every failing tests. More precisely, the \sfl{}+\cs{} 
-combination consists of four steps:\Sof{Should we specify that these steps are
-performed for each version of the projects/defect?}
+the code for every failing tests. More precisely, the workflow of the
+\sfl{}+\cs{} combination consists of four steps: \Sof{Should we
+  specify that these steps are performed for each version of the
+  projects/defect?}\Mar{Isn't this clear from the scenario in the
+  beginning of par?  Note that this is the definition of the workflow
+  for the technique, not the definition of the experiment (when it
+  makes sense to talk about versions/defects and D4J.)}
 
@@
 effect of this spectra modification on the ranking. Analyzing the
-Ochiai formula, one can observe that, for the components $j$ which are
+Ochiai formula, one observes that, for the components $j$ which are
 not part of the slice of a failing test, the combination reduces the
@@
 
-It is possible that a slice that discards the faulty component still
-produces the expected message checked by the oracle. This can happen,
-for example, if the oracle is too
-general. Section~\ref{sec:oracleheuristics} elaborates the heuristics
-we used to mitigate this fundamental limitation of Critical Slicing.
+Conceptually, if the oracles implemented in faulty tests are too
+general, the critical slicing algorithm could produce slices without
+the faulty code. For example, consider the scenario of an unexpected
+Null-Pointer Exception (NPE) thrown in the code. If the oracle checks
+for the presence of NPE regardless of where it occurs, it is possible,
+in principle, that the final slice does not include the faulty code
+but still raises NPE (in a different part of the code). The critical
+slicing algorithm would consider that as an acceptable simplification
+and would continue. Section~\ref{sec:oracleheuristics} shows how we
+mitigate this fundamental limitation of Critical Slicing and
+Section~\ref{sec:fault-misses} shows how problematic is that issue in
+practice.
 
@@
 \subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
+\label{sec:fault-misses}
 

### 2019-02-12 paper/ijcai/paper.tex
stop here. check if these metrics make sense.

@@
 
-\Mar{parei aqui}
-
 \subsection{Oracle Heuristics}
@@
 
+\Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
 Lithium takes as input a function of interest that can be designed according to the problem to be solved.
@@
 
-As in other recent related studies, we used the \dfj{} benchmark in
-our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
-includes six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
+We used the \dfj{} benchmark in our
+experiments~\cite{just-defects4j-issta2014}. This benchmark includes
+six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
 \lang{} is a library that provides a set of helper utilities for the
@@
       \midrule
-      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
-      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
-      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
-      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
-      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
-      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
+      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
+      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
+      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
+      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
+      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
+      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
       \bottomrule
@@
 
-\subsection{Methodology}\label{sec:methodology}
+\subsection{Experimental Methodology}\label{sec:methodology}
 
-The main goal of our evaluation is to understand what is the impact of \ds{} on 
-\sfl{} after minimizing the $k$ highest faulty source files which comprise the highest faulty statements. Firstly, we ran the dataset presented in Section~\ref{sec:analysis} with \sfl{} to 
-gather the coverage statements ordered from the highest faulty statement to the
-lowest faulty statement.
-This list is the input of the \comb{} technique.
-For each defect, the list is evaluated in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source files.
-Then, Lithium minimizes each source file for each testcase of the defect considering the top-$5$ (\comb{}-$5$) and top-$10$ (\comb{}-$10$) of source files separately.
-Some defects have more than one testcase.
-In the end, we update spectra $S$ based on the output of the minimization as presented in Figure~\ref{fig:ds-reduction} to obtain the faulty statements ranking after minimization.
-All scripts used to run these experiments and gather data are available at \url{TBA} and \url{TBA}, respectively.
+%% The main goal of our evaluation is to understand what is the impact of
+%% \ds{} on \sfl{} after minimizing the $k$ highest faulty source files
+%% which comprise the highest faulty statements.
 
-We perform experiments for \comb{}-$5$ and \comb{}-$10$. These techniques results are analyzed against \sfl{}. The difference in the diagnostic effort is measured
-using
+Recall from Section~\ref{sec:combination} that the \comb{} combination
+takes on input a value denoting the $k$ most suspicious distinct
+files. To evaluate the effectiveness of \comb{}, we compared its
+performance with \sfl{} for each defect on each subject program from
+the dataset, for $k\in\{5,10\}$. These files are obtained directly
+from the ranking. We refer to these variations as \combpar{k}. We
+compared \combpar{5} and \combpar{10} against \sfl{} using the
+following metrics.\Mar{Sofia, I don't see a reason for an equation to
+  only show the difference of cost. Please describe precisely the
+  metrics. In this case, I can't find what C stands for. Also,
+ you need to describe precisely what top@n (or someother name) means
+ in this context. Check if it makes sense for SFL.$\rightarrow$}
 
 \begin{equation}
-    \Delta{}C = C(\textrm{SFL}) - C(\textrm{SFL+DS-k})
+    \Delta{}C = C(\textrm{SFL}) - C(\textrm{\combpar{k}})
 \end{equation}
@@
 
-\Sof{Parei Aqui}
+%% Firstly, we ran the dataset presented in Section~\ref{sec:analysis}
+%% with \sfl{} to gather the coverage statements ordered from the highest
+%% faulty statement to the lowest faulty statement. This list is the
+%% input of the \comb{} technique. For each defect, the list is evaluated
+%% in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source
+%% files. Then, Lithium minimizes each source file for each testcase of
+%% the defect considering the top-$5$ (\comb{}-$5$) and top-$10$
+%% (\comb{}-$10$) of source files separately. Some defects have more than
+%% one testcase. In the end, we update spectra $S$ based on the output of
+%% the minimization as presented in Figure~\ref{fig:ds-reduction} to
+%% obtain the faulty statements ranking after minimization. All scripts
+%% used to run these experiments and gather data are available at
+%% \url{TBA} and \url{TBA}, respectively.
+
+%% \Sof{Parei Aqui}
 

### 2019-02-13 paper/ijcai/paper.tex
organizing and cleaning

@@
 
-\Mar{consider moving footnotes 1 and 2 to references.}
 Our implementation of Critical Slicing is based on the Mozilla Lithium
@@
 
-\section{The \sfl{}+\cs{} combination}
-\label{sec:combination}
+\section{Approach}
+\label{sec:approach}
 
@@
 %% ao pseudocode eu diria que é for every $k$ and every failing test.}
+
+\subsection{The \sfl{}+\cs{} combination}
+\label{sec:comb}
 
@@
 
-\begin{algorithm}[h]
-	\caption{Function of interest (iFunc)}
-	\label{alg:finc}
-	\begin{flushleft}
-		\textbf{Input:} $c$ - class to be minimized\\
-		\hspace{2.75em} $t$ - testcase name\\
-		\hspace{2.75em} $expStk$ -  expected stacktrace\\
-		\textbf{Output:} $interest$ - $True$ if it is interesting, $False$ if not \\
-	\end{flushleft}
-	\begin{algorithmic}[1]
-		\Function{iFunc}{$c$, $t$, $expStk$}
-		\State $testStk \leftarrow$ runTest($t$)
-		\State $testOracle \leftarrow$ getOracleToCompare($testStk$)
-		\State $expOracle \leftarrow$ getOracleToCompare($expStk$)
-		\State \Return $testOracle$ == $expOracle$
-		\EndFunction
-
-	\end{algorithmic}
-
-\end{algorithm}
+% \begin{algorithm}[h]
+% 	\caption{Function of interest (iFunc)}
+% 	\label{alg:finc}
+% 	\begin{flushleft}
+% 		\textbf{Input:} $c$ - class to be minimized\\
+% 		\hspace{2.75em} $t$ - testcase name\\
+% 		\hspace{2.75em} $expStk$ -  expected stacktrace\\
+% 		\textbf{Output:} $interest$ - $True$ if it is interesting, $False$ if not \\
+% 	\end{flushleft}
+% 	\begin{algorithmic}[1]
+% 		\Function{iFunc}{$c$, $t$, $expStk$}
+% 		\State $testStk \leftarrow$ runTest($t$)
+% 		\State $testOracle \leftarrow$ getOracleToCompare($testStk$)
+% 		\State $expOracle \leftarrow$ getOracleToCompare($expStk$)
+% 		\State \Return $testOracle$ == $expOracle$
+% 		\EndFunction
+%
+% 	\end{algorithmic}
+%
+% \end{algorithm}
 
@@
 
-Recall from Section~\ref{sec:combination} that the \comb{} combination
+Recall from Section~\ref{sec:approach} that the \comb{} combination
 takes on input a value denoting the $k$ most suspicious distinct

### 2019-02-13 paper/ijcai/paper.tex
pass over Intro; renaming approach to Tandem-FL

--- 2019-02-12 paper/ijcai/paper.tex
@@
 
-Software debugging is difficult. The task of locating the faulty code
-(\ie{}, fault localization) is particularly challenging. For that
-reason, countless automated techniques have been proposed in the past
-to reduce the cost of fault localization.
+Software debugging is difficult. In particular, the task of locating the faulty
+code (\ie{}, fault localization) is particularly challenging. For that reason,
+countless automated techniques have been proposed in the past to reduce the cost
+of fault localization. \Rui{cite my TSE survey paper.}
 
@@
 
-Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
-are two very popular techniques that use different principles to
-automate debugging. Dynamic
-Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
+Model-based software diagnosis (MBSD) and Spectrum-Based Fault Localization
+(\sfl{}) are two very popular techniques that leverage different principles
+to automate fault isolation. An example of a MBSD is Dynamic
+Slicing~\cite{Agrawal:1990:DPS:93542.93576}
+as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
+some works of Wotawa}, a technique that traces back statements
 in the code that influence some point of interest, such as the evaluation
 of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
-does not analyze code. It is a black-box statistical fault
+does not analyze code. Instead, it is a black-box, statistical fault
 localization method that computes suspiciousness values associated
-with program entities (e.g., basic blocks) based on coverage and the
+with program entities (e.g., methods) based on coverage information gathered
+during the execution of test cases as well as the
 output of test cases. More precisely, \sfl{} uses coverage information
@@
 decreasing order of suspiciousness.
-\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
-irrelevant parts of the code whereas \sfl{} ranks the relevant parts
-of the code.
+\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
+Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
+ranks the relevant parts of the code.
 
@@
 impact of combining \ds{} and \sfl{} to improve software fault
-localization. The intuition for the \comb{} combination is that
+localization, a technique we coin as \comb{}. The intuition for the combination is that
 several highly ranked statements, albeit covered by failing
-executions, may be unrelated to the fault. The study involves
+executions, may be unrelated to the fault. Our empirical study involves
 \numFaults{} faults from \numPrograms{} different programs comprised
@@
 but they used a non-representative set of subjects in their evaluation
-or used arcaic methods to evaluate technique
+or used archaic methods to evaluate technique
 improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
-The goal of this paper is to reassess whether the \comb{} combination
-is worthwhile under the light of a more rigorous experimental
-methodology and a larger dataset.\comments{ The D4J dataset is about
+
+The goal of this paper is to reassess whether the \comb{} approach
+yields promising results under a more rigorous experimental
+methodology and a larger dataset.\comments{The D4J dataset is about
   twice as large than the biggest test suite used in previous
@@
 \newcommand{\rqone}{How often does DS miss faulty statements?}
-\newcommand{\rqthree}{How effective is the \comb{} combination?}
+\newcommand{\rqthree}{How effective is the \comb{} approach?}
 

### 2019-02-13 paper/ijcai/paper.tex
another comment, intro

@@
 
-Model-based software diagnosis (MBSD) and Spectrum-Based Fault Localization
+Model-based software diagnosis (MBSD) \Rui{cite de kleer, reiter} and Spectrum-Based Fault Localization
 (\sfl{}) are two very popular techniques that leverage different principles

### 2019-02-13 paper/ijcai/paper.tex
update

--- 2019-02-13 paper/ijcai/paper.tex
@@
 
-Software debugging is difficult. In particular, the task of locating the faulty
-code (\ie{}, fault localization) is particularly challenging. For that reason,
-countless automated techniques have been proposed in the past to reduce the cost
-of fault localization. \Rui{cite my TSE survey paper.}
+Software debugging is difficult. The task of locating the faulty code
+(\ie{}, fault localization) is particularly challenging. For that
+reason, countless automated techniques have been proposed in the past
+to reduce the cost of fault localization.
 
@@
 
-Model-based software diagnosis (MBSD) and Spectrum-Based Fault Localization
-(\sfl{}) are two very popular techniques that leverage different principles
-to automate fault isolation. An example of a MBSD is Dynamic
-Slicing~\cite{Agrawal:1990:DPS:93542.93576}
-as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
-some works of Wotawa}, a technique that traces back statements
+Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
+are two very popular techniques that use different principles to
+automate debugging. Dynamic
+Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
 in the code that influence some point of interest, such as the evaluation
 of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
-does not analyze code. Instead, it is a black-box, statistical fault
+does not analyze code. It is a black-box statistical fault
 localization method that computes suspiciousness values associated
-with program entities (e.g., methods) based on coverage information gathered
-during the execution of test cases as well as the
+with program entities (e.g., basic blocks) based on coverage and the
 output of test cases. More precisely, \sfl{} uses coverage information
@@
 decreasing order of suspiciousness.
-\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
-Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
-ranks the relevant parts of the code.
+\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
+irrelevant parts of the code whereas \sfl{} ranks the relevant parts
+of the code.
 
@@
 impact of combining \ds{} and \sfl{} to improve software fault
-localization, a technique we coin as \comb{}. The intuition for the combination is that
+localization. The intuition for the \comb{} combination is that
 several highly ranked statements, albeit covered by failing
-executions, may be unrelated to the fault. Our empirical study involves
+executions, may be unrelated to the fault. The study involves
 \numFaults{} faults from \numPrograms{} different programs comprised
@@
 but they used a non-representative set of subjects in their evaluation
-or used archaic methods to evaluate technique
+or used arcaic methods to evaluate technique
 improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
-
-The goal of this paper is to reassess whether the \comb{} approach
-yields promising results under a more rigorous experimental
-methodology and a larger dataset.\comments{The D4J dataset is about
+The goal of this paper is to reassess whether the \comb{} combination
+is worthwhile under the light of a more rigorous experimental
+methodology and a larger dataset.\comments{ The D4J dataset is about
   twice as large than the biggest test suite used in previous
@@
 \newcommand{\rqone}{How often does DS miss faulty statements?}
-\newcommand{\rqthree}{How effective is the \comb{} approach?}
+\newcommand{\rqthree}{How effective is the \comb{} combination?}
 
@@
 \label{sec:approach}
+
+This section provides details on our \sfl{}+\ds{} combination approach
+and its heuristics.
 

### 2019-02-13 paper/ijcai/paper.tex
more changes; questions

--- 2019-02-13 paper/ijcai/paper.tex
@@
 
-This section presents important background material for the rest of the paper.
+This section discusses  important background material for the rest of the paper.
+\Rui{not very happy with this sentence.}
 
@@
 
+\Rui{intro needs to refer to Critical Slicing, somehow..}
+\Rui{Are we the first to use Critical Slicing in combination? Say so, if this
+is the case.}
 Program slicing is a program understanding technique to identify the
@@
 elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
-available.
+available at \Rui{site}.
 
@@
 
-\section{Approach}
+\section{The \comb{} Approach}
 \label{sec:approach}
 
-%% \Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
-%%   falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
-%%   de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
-%%   loop aninhado ao loop ``for every k'' que o lithium-slicer
-%%   implementa (algo como ``for every k and every failing test'')?  Caso
-%%   vc. faca slice contra um teste particular, vc. garante (checa saida)
-%%   que os demais testes que originalmente falhavam continuam falhando
-%%   pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
-%%   de inicio.}
+\Rui{add a sentence?}
 
-%% \Sof{O lithium-slicer funciona por caso de teste. Cada execução da nossa
-%% ferramenta chama o lithium tantas vezes como o número de casos de teste
-%% que falham para cada versão do projecto. Assumindo que o numero de casos de
-%% testes a falhar são 5, numa execução da nossa plataforma o lithium é executado
-%% 5x para os 5 testes diferentes. No fim, pega no resultado do slicing de cada
-%% teste e actualiza a matrix spectra para calcular o ranking. Eu confiro depois de
-%% executar a nossa ferramenta para uma versão do projecto que os
-%% testes que aparecem na pasta da versão do projecto são os mesmos quando corro
-%% o test do defects4j de novo. Uma precaução que tivemos foi ter a certeza que o
-%% oracle que estava a ser usado não sofria com a mudança de máquinas. Portanto,
-%% antes de correr as experiências eu corri o defects4j para obter as mensagens
-%% esperadas de novo para serem usadas como o oracle esperado. Estas são as verificações
-%% que faço. Posso tentar substituir as classes minimizadas nos projectos e ver se
-%% realmente a mensagem de erro continua a ser a mesma - coisa que não fiz. Relativamente,
-%% ao pseudocode eu diria que é for every $k$ and every failing test.}
-
-\subsection{The \sfl{}+\cs{} combination}
+\subsection{Combinging \sfl{} with \cs{}}
 \label{sec:comb}
 
-To illustrate the idea behind the \sfl{}+\cs{} combination, consider a
+To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
 debugging scenario with five components $c_{1..5}$ and five

### 2019-02-13 paper/ijcai/paper.tex
adding some of the citations

--- 2019-02-13 paper/ijcai/paper.tex
@@
 countless automated techniques have been proposed in the past to reduce the cost
-of fault localization. \Rui{cite my TSE survey paper.}
+of fault localization~\cite{7390282}.
 
@@
 
-Model-based software diagnosis (MBSD) \Rui{cite de kleer, reiter} and Spectrum-Based Fault Localization
+Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
 (\sfl{}) are two very popular techniques that leverage different principles
@@
 Slicing~\cite{Agrawal:1990:DPS:93542.93576}
-as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
+as wel as some work~\cite{Perez:2018:LQR:3304889.3304927}\Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
 some works of Wotawa}, a technique that traces back statements
@@
 decreasing order of suspiciousness.
-\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
+\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
 Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
@@
 The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails.
-For each chunk under evaluation, the test is executed after the chunk being deleted from the source code (Algorithm \ref{alg:finc}, line 2).
+For each chunk under evaluation, the test is executed after the chunk being deleted from the source code .
 Both test ($testStk$) and expected ($expStk$) stack traces are filtered.

### 2019-02-13 paper/ijcai/paper.tex

@@
 
-\section{Approach}
+\section{The \comb{} Approach}
 \label{sec:approach}
@@
 
-To illustrate the idea behind the \sfl{}+\cs{} combination, consider a
+To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
 debugging scenario with five components $c_{1..5}$ and five

### 2019-02-13 paper/ijcai/paper.tex
more changes

--- 2019-02-13 paper/ijcai/paper.tex
@@
 the code for every failing tests. More precisely, the workflow of the
-\sfl{}+\cs{} combination consists of four steps: \Sof{Should we
+\comb{} approach consists of four steps: \Sof{Should we
   specify that these steps are performed for each version of the
@@
   for the technique, not the definition of the experiment (when it
-  makes sense to talk about versions/defects and D4J.)}
+  makes sense to talk about versions/defects and D4J.)}\Rui{agree with Marcelo.}
+  \Rui{if space permits, a figure with the workflow might be good.}
 
@@
   \item\label{step:susp-files} Select top $k$ most suspicious source
-  files, according to $R$;
+  files\Rui{classes?}, according to $R$;
   \item\label{step:compute-slice} Compute slicer for every suspicious
     file, obtained in Step~\ref{step:susp-files}, and every failing test;
+    \Rui{union of slices of all points ?}
   \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
@@
 
-Intuitively, slicing enables identification of cells in the spectra
-whose values can be set to zero, \ie{}, the components marked with 0
+Intuitively, slicing enables identification of cells\Rui{cells?} in the spectra
+whose values can be set to zero, \ie{}, the components marked with $0$
 are irrelevant to determine the test output. Let us now observe the
@@
 not part of the slice of a failing test, the combination reduces the
-value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
+value of $\N{11}$ and increases the value of $\N{01}$ \Rui{lower case N?}. Therefore,
 suspiciousness of those components decrease. Similar argument applies
-to other fault predictors. In the example from
+to other fault predictors. In the running example,
 Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
@@
 
-The proof is based on the argument aforementioned that irrelevant
+The proof is based on the outlined argument that irrelevant
 components $j$ have their ranks reduced as $\N{11}$ decreases and
@@
 \Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
+\Rui{This is too rought. I would not talk about lithium right away.}
 Lithium takes as input a function of interest that can be designed according to the problem to be solved.

### 2019-02-13 paper/ijcai/paper.tex
continuing ...

@@
 To evaluate our approach, we compare the cost of diagnosing
-a collection of faulty versions using \sfl{}
-against \comb{}.
+a collection of faulty versions using \sfl{} versus \comb{}.
 
@@
 
-Recall from Section~\ref{sec:approach} that the \comb{} combination
-takes on input a value denoting the $k$ most suspicious distinct
-files. To evaluate the effectiveness of \comb{}, we compared its
+Recall from Section~\ref{sec:approach} that the \comb{}
+takes as input a value $k$ that denotes the $k$ most suspicious distinct
+classes to be considered. To evaluate the effectiveness of \comb{}, following
+related work, we compared its
 performance with \sfl{} for each defect on each subject program from
-the dataset, for $k\in\{5,10\}$. These files are obtained directly
+the dataset, for $k\in\{5,10\}$. These classes are obtained directly
 from the ranking. We refer to these variations as \combpar{k}. We
@@
  you need to describe precisely what top@n (or someother name) means
- in this context. Check if it makes sense for SFL.$\rightarrow$}
+ in this context. Check if it makes sense for SFL.$\rightarrow$}\Rui{It might
+ be good to keep it just to give it some emphasis... }
 
@@
 
-where C is the cost of diagnosis. \Sof{@todo: Explain this better in section 2 or 3}
-A positive $\Delta$C means that the faulty statement has risen in
-the ranking reported by \sfl{} techniques when \ds{} is used,
-producing a reduced cost of diagnosing.
-
-%% Firstly, we ran the dataset presented in Section~\ref{sec:analysis}
-%% with \sfl{} to gather the coverage statements ordered from the highest
-%% faulty statement to the lowest faulty statement. This list is the
-%% input of the \comb{} technique. For each defect, the list is evaluated
-%% in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source
-%% files. Then, Lithium minimizes each source file for each testcase of
-%% the defect considering the top-$5$ (\comb{}-$5$) and top-$10$
-%% (\comb{}-$10$) of source files separately. Some defects have more than
-%% one testcase. In the end, we update spectra $S$ based on the output of
-%% the minimization as presented in Figure~\ref{fig:ds-reduction} to
-%% obtain the faulty statements ranking after minimization. All scripts
-%% used to run these experiments and gather data are available at
-%% \url{TBA} and \url{TBA}, respectively.
-
-%% \Sof{Parei Aqui}
+\noindent
+where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
+the cost of diagnosis is: C is the number of statemetns (?) that need to be
+inspected before finding the fault, right? We also need to say that we assume a
+perfect bug understanding: that is, when the developer sees the bug in the
+ranking, he can say that it is the faulty one.}
+A positive $\Delta$C means that the position of the faulty statement has decreased
+in the ranking reported computed by \combpar{k}. Hence, reducing the cost to
+find the bug.
 

### 2019-02-13 paper/ijcai/paper.tex
another comment
consistency
more comments; polishing
t2v

@@
 \subsection{Dynamic Slicing}
+\Rui{ehmm.. what is this section all about? }
 
@@
 		\toprule
-		Project             &  top-5  & top-10 \\
+		Project             &  \combpar{k}  & \combpar{10} \\
 		\midrule
@@
 \subsection{Results}
+\Rui{Results \& Discussion?}
 
@@
 		\toprule
-		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{SFL+DS-$k$} & \multirow{2}{*}{\# Faults} \\
+		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
 
-		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\
+		            & \% $k = 5$ & \% $k = 10$  & $\Delta$ & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
 		\midrule
@@
 	\end{tabular}
-  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
+  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Sof{@todo: Add absolute numbers for SFL}\Rui{explain what $k$ is for SFL alone.}}
   \label{table:fsws}
@@
 		\toprule
-		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
+		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
 		\midrule
@@
 	\end{tabular}
-	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
+	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
 	\label{tab:diagnosis}
@@
 \subsection{Threats to validity}
+%
+A potential threat to external validity related to the set of programs used in
+our study. When choosing the projects for our study, our aim was to opt for
+projects that resemble a general and large-sized application. To reduce
+selection bias and facilitate the comparison of our results, we decided to
+choose a benchmark that is popular in the community \Rui{cite d4j}.
 
+A potential threat to construct validity relates to the choice of oracle generation
+for the Lithium toolset. However, we argue that our choice is able to capture whether
+a program is failing because of the same reason.
+
+The main threat to internal validity lies in the complexity of several of the tools
+used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
+and the implementation of \comb{}.
+%
 \section{Related Work}
+\Rui{needs work...}
 
@@
 \subsection{\comb{}}
+\Rui{\comb{} ??}
 
@@
 
-\section*{Acknowledgments}
+%\section*{Acknowledgments}
+%include only after review.
 

### 2019-02-13 paper/ijcai/paper.tex
polishing

@@
 \toprule
-  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
+  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
 Mean & 387.46     & 576.74   & 522.35   \\ \midrule

### 2019-02-13 paper/ijcai/paper.tex
fixes
saving

--- 2019-02-13 paper/ijcai/paper.tex
@@
 
-The contributions of this work are as follows \Sof{Finish this}:
+The contributions of this work are the following ones:
 \begin{itemize}
@@
    \item A tool that implements \comb{}.
-	%\item Empirical evidence that the \comb{} combination improves
 \end{itemize}
@@
 
-This section discusses  important background material for the rest of the paper.
-\Rui{not very happy with this sentence.}
+This section summarizes the ground concepts of our approach.
 
@@
 elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
-available at \Rui{site}.
+available at \textit{$<$anonymized for double-blind review$>$}.
 
@@
 \label{sec:sfl}
+
+\begin{wrapfigure}[8]{2}{0.3\textwidth}
+  \hspace{-2ex}
+  \centering
+  \scriptsize
+  \begin{tabular}{c|cccc|c}
+    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
+    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
+    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
+    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
+    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
+  \end{tabular}
+  \caption{An example spectrum.}
+  \label{fig:spectrum-example}
+\end{wrapfigure}
 
@@
 shows an example spectrum.
-\begin{wrapfigure}[8]{2}{0.3\textwidth}
-  \hspace{-2ex}
-  \centering
-  \scriptsize
-  \begin{tabular}{c|cccc|c}
-    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
-    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
-    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
-    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
-    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
-  \end{tabular}
-  \caption{An example spectrum.}
-  \label{fig:spectrum-example}
-\end{wrapfigure}
 
@@
 
-In the following, we illustrate the workflow of the \sfl{}+\cs{}
-combination for this scenario. First, the combined technique picks
+In the following, we illustrate the workflow of the \comb{}
+approach for this scenario. First, the combined technique picks
 components $c_4$ and $c_3$, which appear at the top of the ranking,
@@
 the code for every failing tests. More precisely, the workflow of the
-\comb{} approach consists of four steps: \Sof{Should we
-  specify that these steps are performed for each version of the
-  projects/defect?}\Mar{Isn't this clear from the scenario in the
-  beginning of par?  Note that this is the definition of the workflow
-  for the technique, not the definition of the experiment (when it
-  makes sense to talk about versions/defects and D4J.)}\Rui{agree with Marcelo.}
-  \Rui{if space permits, a figure with the workflow might be good.}
-
+\comb{} approach consists of four steps: 
 \begin{enumerate}
@@
 To evaluate our approach, we compare the cost of diagnosing
-a collection of faulty versions using \sfl{} versus \comb{}.
+a collection of faulty versions using \sfl{}
+against \comb{}.
 
@@
 
-Recall from Section~\ref{sec:approach} that the \comb{}
-takes as input a value $k$ that denotes the $k$ most suspicious distinct
-classes to be considered. To evaluate the effectiveness of \comb{}, following
-related work, we compared its
+Recall from Section~\ref{sec:approach} that the \comb{} combination
+takes on input a value denoting the $k$ most suspicious distinct
+files. To evaluate the effectiveness of \comb{}, we compared its
 performance with \sfl{} for each defect on each subject program from
-the dataset, for $k\in\{5,10\}$. These classes are obtained directly
+the dataset, for $k\in\{5,10\}$. These files are obtained directly
 from the ranking. We refer to these variations as \combpar{k}. We
@@
  you need to describe precisely what top@n (or someother name) means
- in this context. Check if it makes sense for SFL.$\rightarrow$}\Rui{It might
- be good to keep it just to give it some emphasis... }
+ in this context. Check if it makes sense for SFL.$\rightarrow$}
 
@@
 
-\noindent
-where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
-the cost of diagnosis is: C is the number of statemetns (?) that need to be
-inspected before finding the fault, right? We also need to say that we assume a
-perfect bug understanding: that is, when the developer sees the bug in the
-ranking, he can say that it is the faulty one.}
-A positive $\Delta$C means that the position of the faulty statement has decreased
-in the ranking reported computed by \combpar{k}. Hence, reducing the cost to
-find the bug.
+where C is the cost of diagnosis. \Sof{@todo: Explain this better in section 2 or 3}
+A positive $\Delta$C means that the faulty statement has risen in
+the ranking reported by \sfl{} techniques when \ds{} is used,
+producing a reduced cost of diagnosing.
+
+%% Firstly, we ran the dataset presented in Section~\ref{sec:analysis}
+%% with \sfl{} to gather the coverage statements ordered from the highest
+%% faulty statement to the lowest faulty statement. This list is the
+%% input of the \comb{} technique. For each defect, the list is evaluated
+%% in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source
+%% files. Then, Lithium minimizes each source file for each testcase of
+%% the defect considering the top-$5$ (\comb{}-$5$) and top-$10$
+%% (\comb{}-$10$) of source files separately. Some defects have more than
+%% one testcase. In the end, we update spectra $S$ based on the output of
+%% the minimization as presented in Figure~\ref{fig:ds-reduction} to
+%% obtain the faulty statements ranking after minimization. All scripts
+%% used to run these experiments and gather data are available at
+%% \url{TBA} and \url{TBA}, respectively.
+
+%% \Sof{Parei Aqui}
 
@@
 		\toprule
-		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{SFL+DS-$k$} & \multirow{2}{*}{\# Faults} \\
+		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{\comb{}-$k$} & \multirow{2}{*}{\# Faults} \\
 
@@
 	\end{tabular}
-  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
+  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \comb{}-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
   \label{table:fsws}
 \end{table*}
-
-% \begin{table*}[h]
-% 	\centering
-% 	\setlength{\tabcolsep}{4pt}
-% 	\begin{tabular}{llllll}
-% 		\toprule
-% 		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\
-% 		\midrule
-% 		\chart{}  & 20 & 76.92\% & 22 & 84.62\%  & 26\\
-% 		\jtime{}  &  &  &  &   & \\
-% 		\bottomrule
-% 	\end{tabular}
-% 	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
-% 	\label{tab:fs}
-% \end{table*}
-% \normalsize
 

### 2019-02-13 paper/ijcai/paper.tex

--- 2019-02-13 paper/ijcai/paper.tex
@@
 
-This section provides details on our \sfl{}+\ds{} combination approach
-and its heuristics.
+This section provides details on the proposed approach, \combpar{}, that combines
+\sfl{} with \cs{}; it also discusses the oracle problem.
 
-%% \Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
-%%   falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
-%%   de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
-%%   loop aninhado ao loop ``for every k'' que o lithium-slicer
-%%   implementa (algo como ``for every k and every failing test'')?  Caso
-%%   vc. faca slice contra um teste particular, vc. garante (checa saida)
-%%   que os demais testes que originalmente falhavam continuam falhando
-%%   pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
-%%   de inicio.}
-
-%% \Sof{O lithium-slicer funciona por caso de teste. Cada execução da nossa
-%% ferramenta chama o lithium tantas vezes como o número de casos de teste
-%% que falham para cada versão do projecto. Assumindo que o numero de casos de
-%% testes a falhar são 5, numa execução da nossa plataforma o lithium é executado
-%% 5x para os 5 testes diferentes. No fim, pega no resultado do slicing de cada
-%% teste e actualiza a matrix spectra para calcular o ranking. Eu confiro depois de
-%% executar a nossa ferramenta para uma versão do projecto que os
-%% testes que aparecem na pasta da versão do projecto são os mesmos quando corro
-%% o test do defects4j de novo. Uma precaução que tivemos foi ter a certeza que o
-%% oracle que estava a ser usado não sofria com a mudança de máquinas. Portanto,
-%% antes de correr as experiências eu corri o defects4j para obter as mensagens
-%% esperadas de novo para serem usadas como o oracle esperado. Estas são as verificações
-%% que faço. Posso tentar substituir as classes minimizadas nos projectos e ver se
-%% realmente a mensagem de erro continua a ser a mesma - coisa que não fiz. Relativamente,
-%% ao pseudocode eu diria que é for every $k$ and every failing test.}
-
-\subsection{The \sfl{}+\cs{} combination}
+\subsection{Combineing \sfl{} and \cs{}}
 \label{sec:comb}
@@
 
-\subsection{Results}
-\Rui{Results \& Discussion?}
+\subsection{Results and Discussion}
 
@@
 \end{table*}
-
-% \begin{table*}[h]
-% 	\centering
-% 	\setlength{\tabcolsep}{4pt}
-% 	\begin{tabular}{llllll}
-% 		\toprule
-% 		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\
-% 		\midrule
-% 		\chart{}  & 20 & 76.92\% & 22 & 84.62\%  & 26\\
-% 		\jtime{}  &  &  &  &   & \\
-% 		\bottomrule
-% 	\end{tabular}
-% 	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
-% 	\label{tab:fs}
-% \end{table*}
-% \normalsize
 

### 2019-02-13 paper/ijcai/paper.tex
some fixes

@@
 
-\subsection{Combineing \sfl{} and \cs{}}
+\subsection{Combining \sfl{} and \cs{}}
 \label{sec:comb}
@@
 
-\Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
 \Rui{This is too rought. I would not talk about lithium right away.}
@@
 	\centering
-	  \begin{tabular}{|l|ccc|cccc|c|}
+	  \begin{tabular}{l|cc|cccc|c}
 		\toprule
-		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
+		\multirow{2}{*}{Project}            & \multicolumn{2}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
 
-		            & \% $k = 5$ & \% $k = 10$  & $\Delta$ & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
+		            & \% $k = 5$ & \% $k = 10$  & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
 		\midrule
-		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\
+		 \lang{}            & 84.1\%  & 84.1\%    & 63 & 100\% & 61 & 96.8\% & 63      \\
 		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
 		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
-		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
-		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
-		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
+		\chart{}           & 84.6\%  & 92.3\% & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
+		\jtime{}           & 77.8 \%  & 100.0 \% & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
+		 \mockito{}         & 63.2\%  & 71.1\% & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
 		\bottomrule
@@
 selection bias and facilitate the comparison of our results, we decided to
-choose a benchmark that is popular in the community \Rui{cite d4j}.
+choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
 
@@
 large slices, which defeats the purpose of reducing the fault search
-space. It is worth noting that, conceptually, the \comb{} combination
+space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
 can be used with any form of dynamic slicing. We chose an
@@
 
-Spectrum-based fault localization (\sfl) is amongst the most common statistical
+Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
 fault localization technique that takes as input a test suite including at least
@@
 
-\subsection{\comb{}}
-\Rui{\comb{} ??}
+\subsection{Combination of \sfl{} and Slicing}
 

### 2019-02-13 paper/ijcai/paper.tex
fixes

@@
   the input test suite;
-  \item\label{step:susp-files} Select top $k$ most suspicious source
-  files\Rui{classes?}, according to $R$;
+  \item\label{step:susp-files} Select top $k$ most suspicious classes, according to $R$;
   \item\label{step:compute-slice} Compute slicer for every suspicious
@@
 
-Intuitively, slicing enables identification of cells\Rui{cells?} in the spectra
+Intuitively, slicing enables identification of statements in the spectra
 whose values can be set to zero, \ie{}, the components marked with $0$
@@
 A positive $\Delta$C means that the position of the faulty statement has decreased
-in the ranking reported computed by \combpar{k}. Hence, reducing the cost to
+in the ranking after applying the \combpar{k} approach. Hence, reducing the cost to
 find the bug.
@@
 \subsection{Dynamic Slicing}
-\Rui{ehmm.. what is this section all about? }
+
+This subsection aims to evaluate the performance of the \ds{} technique on slicing
+de \dfj{} projects.
 
@@
 		\toprule
-		Project             &  \combpar{k}  & \combpar{10} \\
+		Project             &  \combpar{5}  & \combpar{10} \\
 		\midrule

### 2019-02-14 paper/ijcai/paper.tex
section 3.1 comments addressed

@@
     file, obtained in Step~\ref{step:susp-files}, and every failing test;
-    \Rui{union of slices of all points ?}
+  \item\label{step:group} Assemble all the resulting slicers of each failing test; 
   \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
-    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
+    the slices of each failing test obtained in Step~\ref{step:group} and recompute ranking.
 \end{enumerate}
@@
 not part of the slice of a failing test, the combination reduces the
-value of $\N{11}$ and increases the value of $\N{01}$ \Rui{lower case N?}. Therefore,
+value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
 suspiciousness of those components decrease. Similar argument applies
@@
 
-\Rui{This is too rought. I would not talk about lithium right away.}
 Lithium takes as input a function of interest that can be designed according to the problem to be solved.

### 2019-02-14 paper/ijcai/paper.tex
more fixes

@@
 \label{sec:comb}
-
+\Sof{@todo: define slicer - set of statements}
 To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
@@
 %
+
+The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
+the idea that each statement has an effect on the test output (i.e., oracle).
 
@@
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
-		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
+		\caption{Nemenyi post-hoc analysis results \Sof{@tofix: Need to center ylabels}}
 		\label{fig:performance}

### 2019-02-15 paper/ijcai/paper.tex
another update

@@
 
-        \lang{}            & 0.77\% & 30.28\%\\
-        \cmath{}           &  & \\
+        \lang{}            & 1.42\% & 30.47\%\\
+        \cmath{}           & 9.88\% & 11.43\%\\
         \closure{}          &  & \\
 		\chart{}			& 59.30\% & 53.64\% \\
-        \jtime{}            & 17.27\% & 32.92\%\\
-        \mockito{}          & 16.99\% & 21.67\%\\
+        \jtime{}            & 17.27\% & 32.02\%\\
+        \mockito{}          & 16.54\% & 21.67\%\\
 
@@
 		\midrule
-		$<0$  & 20.00\% & 17.42\% \\
-		$=0$  & 47.10\% & 37.42\% \\
-		$>0$  & 32.90\% & 45.16\% \\
+		$<0$  & 19.53\% & 16.02\% \\
+		$=0$  & 46.88\% & 41.80\% \\
+		$>0$  & 33.59\% & 42.19\% \\
 
@@
 	\end{tabular}
-	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
+	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
 	\label{tab:diagnosis}
@@
   & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
-Mean & 387.46     & 576.74   & 522.35   \\ \midrule
-Median & 44.50      & 48.25               & 46.00                \\ \midrule
-Variance & 827.80      & 1075.90   & 1275.34    \\ \midrule
-Shapiro-Wilk & \makecell{W = 0.51 \\ p-value = 9.65 x $10^{-21}$} & \makecell{W = 0.59 \\ p-value = 5.29 x $10^{-19}$} & \makecell{W = 0.56 \\ p-value = 8.95 x $10^{-20}$}  \\ \midrule
-Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 16.87 \\ p-value = 2.2 x $10^{-4}$}} \\
+Mean & 522.47     & 684.89   & 611.04   \\ \midrule
+Median & 50.375      & 66.25               & 54.3                \\ \midrule
+Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
+Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
+Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
 \bottomrule

### 2019-02-15 paper/ijcai/paper.tex
current results status

@@
         \cmath{}           & 9.88\% & 11.43\%\\
-        \closure{}          &  & \\
+        %\closure{}          &  & \\
 		\chart{}			& 59.30\% & 53.64\% \\
@@
 	\centering
-	  \begin{tabular}{l|cc|cccc|c}
+	  \begin{tabular}{l|cccc|cccc|c}
 		\toprule
-		\multirow{2}{*}{Project}            & \multicolumn{2}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
+		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
 
-		            & \% $k = 5$ & \% $k = 10$  & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
+		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$  
+					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
 		\midrule
-		 \lang{}            & 84.1\%  & 84.1\%    & 63 & 100\% & 61 & 96.8\% & 63      \\
-		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
+		 \lang{}         &  54 & 84.4\%  & 54  & 84.4\% 
+		 				& 64 & 100\% & 62 & 96.9\% & 64      \\
+		\cmath{}           & 82 & 81.2\%  & 86 & 85.1\% 
+						& 90 & 89.1\% & 97 & 96.0\% & 101  \\   %\comments{& 177   &  -}\\
 		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
-		\chart{}           & 84.6\%  & 92.3\% & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
-		\jtime{}           & 77.8 \%  & 100.0 \% & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
-		 \mockito{}         & 63.2\%  & 71.1\% & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
+		\chart{}          & 22 & 84.6\% & 24 & 92.3\% 
+						& 20 & 76.9\% & 22 & 84.6\% & 26    \\  	
+		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \% 
+				& 22 & 81.5\% & 23 & 85.2\% & 27     \\  
+		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\% 
+		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\     
 		\bottomrule
 	\end{tabular}
-  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Sof{@todo: Add absolute numbers for SFL}\Rui{explain what $k$ is for SFL alone.}}
+  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
   \label{table:fsws}
@@
 \end{tabular}
-  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
+  \caption {Statistical tests}
   \label{table:st}

### 2019-02-15 paper/ijcai/paper.tex
table3 fixed
replacing diagnosis performance table with a chart
fixing issue

@@
 \begin{table*}[h]
+	\small
+	% \setlength{\tabcolsep}{3pt}
 	\centering
@@
 
-Table \ref{tab:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
+Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
 $\Delta C <0$ means that the faulty statement may be removed.
@@
 
-\begin{table}[h]
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{ccc}
-		\toprule
-		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
-		\midrule
-		$<0$  & 19.53\% & 16.02\% \\
-		$=0$  & 46.88\% & 41.80\% \\
-		$>0$  & 33.59\% & 42.19\% \\
+% \begin{table}[h]
+% 	\centering
+% 	\setlength{\tabcolsep}{4pt}
+% 	\begin{tabular}{ccc}
+% 		\toprule
+% 		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
+% 		\midrule
+% 		$<0$  & 19.53\% & 16.02\% \\
+% 		$=0$  & 46.88\% & 41.80\% \\
+% 		$>0$  & 33.59\% & 42.19\% \\
+%
+% 		\bottomrule
+% 	\end{tabular}
+% 	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
+% 	\label{tab:diagnosis}
+% \end{table}
 
-		\bottomrule
-	\end{tabular}
-	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
-	\label{tab:diagnosis}
-\end{table}
-\normalsize
+\begin{figure}[h]
+		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
+		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
+		\label{fig:diagnosis}
+\end{figure}
 
 \begin{table*}[h]
+	\small
 	\centering

### 2019-02-18 paper/ijcai/paper.tex
abstract

@@
 \begin{abstract}
-  Software debugging is important and challenging. This paper reports
-  on a comprehensive study to reassess the impact of combining two
-  very popular automated techniques for software fault
-  localization--Dynamic Slicing and Spectrum-based Fault
-  Localization. Our results show that \Fix{...}
+  Software debugging is difficult.
+One of its main challenges is the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy.
+We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault.
+This paper reports the results of a comprehensive study perfomed to reassess the impact of combining Dynamic Slicing with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL.
+We leverage the Mozzila's Lithium Slicer engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests.
+The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
+  Our results show that adding DS to SFL improves the diagnosis accuracy of SFL. 
 \end{abstract}
@@
 
-Software debugging is difficult. In particular, the task of locating the faulty
+Software debugging is important and challenging. In particular, the task of locating the faulty
 code (\ie{}, fault localization) is particularly challenging. For that reason,
@@
 \begin{figure}[h]
-		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
+		\centering
+		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
 		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
@@
 \begin{table*}[h]
-	\small
 	\centering

### 2019-02-18 paper/ijcai/paper.tex
note
small fix

@@
 The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
-  Our results show that adding DS to SFL improves the diagnosis accuracy of SFL. 
+  Our results show that adding DS to SFL improves its diagnosis accuracy. 
 \end{abstract}
@@
 
-The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
+\Sof{Not finished yet}The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
 the idea that each statement has an effect on the test output (i.e., oracle).

### 2019-02-18 paper/ijcai/paper.tex
statements vs components vs slice fixed

@@
 \label{sec:comb}
-\Sof{@todo: define slicer - set of statements}
+
 To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
@@
 In the following, we illustrate the workflow of the \comb{}
-approach for this scenario. First, the combined technique picks
-components $c_4$ and $c_3$, which appear at the top of the ranking,
-for further analysis. (The cutoff point is user-defined.) Second, the
-technique picks a failing test $t_2$ to slice the code.  Let us assume
+approach for this scenario. \comb{} uses a granularity of statements.
+First, the combined technique picks statements $c_4$ and $c_3$, which 
+appear at the top of the ranking, for further analysis. 
+(The cutoff point is user-defined.) Second, the
+technique picks a failing test $t_2$ to slice the code. A slice is a
+set of statements. Let us assume
 that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
-\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
+\ie, it excludes statements $c_4$ and $c_3$. Finally, the spectra and
 ranking are updated. The right-side of Figure~\ref{fig:illustration}
@@
 
-Intuitively, slicing enables identification of statements in the spectra
+Intuitively, slicing enables the identification of statements in the spectra
 whose values can be set to zero, \ie{}, the components marked with $0$

### 2019-02-18 paper/ijcai/paper.tex
section 3 all finished

@@
 This paper reports the results of a comprehensive study perfomed to reassess the impact of combining Dynamic Slicing with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL.
-We leverage the Mozzila's Lithium Slicer engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests.
+We leverage the Mozilla's Lithium engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests.
 The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
@@
 
-\begin{theorem}
+\begin{theorem}\label{the:1}
   The faulty statement may not be included in the critical slice of
@@
 
-\Sof{Not finished yet}The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
-the idea that each statement has an effect on the test output (i.e., oracle).
+The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
+operator (SSDL) of the mutation-based testing methodology. This operator 
+was designed based on the idea that each statement has an effect on the program
+output (i.e., oracle). Thus, testers are encouraged to design test sets that cause
+all statements to be executed and generate outputs that are different from the
+program under test.
 
-Lithium takes as input a function of interest that can be designed according to the problem to be solved.
+Mozilla's Lithium takes as input a function of interest that can be designed according to the problem to be solved.
 The function of interest determines if the test case output is interesting or not.
-In this study, interesting means that the test execution path is equal to the expected one.
-This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception.
+Our function simply compares the failing test output with the output obtained when re-running again the failing test after deleting the slice, as explained in Section~\ref{sec:slicing}.
+Thus, if the
+initial test output is the same as the one after removing the slice \{$c_2$,$c_5$\}, then the slice is removed.
+This means that the slice is not necessary to reveal the fault because if removed the test output is still the same.
+The output is extracted from the stacktrace obtained through the failing test execution.
+The stacktrace provides information not only about the place where the fault was revelead but also the path taken to get there.
+Thus, our approach considers not only the exception caught by the failling test but also the path that was taken to reveal the fault.
+An example is provided in the following Box:
+
+\vspace{3mm}
+\begin{myframe} \label{box:1}
+junit.framework.AssertionFailedError, \\
+at junit.framework.Assert.fail(Assert.java:55), \\
+at junit.framework.Assert.assertTrue(Assert.java:22), \\
+at junit.framework.Assert.assertFalse(Assert.java:39), \\ 
+at junit.framework.Assert.assertFalse(Assert.java:47), \\
+at junit.framework.TestCase.assertFalse(TestCase.java:219), \\ 
+at org.jfree.chart.util.junit.ShapeUtilitiesTests.\\testEqualGeneralPaths(ShapeUtilitiesTests.java:212), \\
+...
+\end{myframe}
+
+Considering some of the stacktrace information about the path taken to reveal the fault solved the issue of generic oracles (e.g., NPE or generic AssertionFailedError expections as the one presented before) mentioned in Theorem~\ref{the:1}.
+There are faults whose outputs could slightly differ from one execution to another.
+For example, exceptions including information of memory addresses.
+In this cases, it was developed a mechanism to compare the rest of the output ignoring the identifier of the memory address.
+This heuristic also handles StackOverflow oracles.
+
+%
+% This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception.
 The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails.
@@
 Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
-
-% \begin{algorithm}[h]
-% 	\caption{Function of interest (iFunc)}
-% 	\label{alg:finc}
-% 	\begin{flushleft}
-% 		\textbf{Input:} $c$ - class to be minimized\\
-% 		\hspace{2.75em} $t$ - testcase name\\
-% 		\hspace{2.75em} $expStk$ -  expected stacktrace\\
-% 		\textbf{Output:} $interest$ - $True$ if it is interesting, $False$ if not \\
-% 	\end{flushleft}
-% 	\begin{algorithmic}[1]
-% 		\Function{iFunc}{$c$, $t$, $expStk$}
-% 		\State $testStk \leftarrow$ runTest($t$)
-% 		\State $testOracle \leftarrow$ getOracleToCompare($testStk$)
-% 		\State $expOracle \leftarrow$ getOracleToCompare($expStk$)
-% 		\State \Return $testOracle$ == $expOracle$
-% 		\EndFunction
-%
-% 	\end{algorithmic}
-%
-% \end{algorithm}
 

### 2019-02-19 paper/ijcai/paper.tex
abstract,s1,s2 e s3

@@
 Software debugging is difficult.
-One of its main challenges is the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy.
+Several approaches have been proposed to the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy.
+This paper reports the outcome of a study performed to reassess the impact of combining Dynamic Slicing (DS) with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL.
 We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault.
-This paper reports the results of a comprehensive study perfomed to reassess the impact of combining Dynamic Slicing with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL.
-We leverage the Mozilla's Lithium engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests.
-The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
-  Our results show that adding DS to SFL improves its diagnosis accuracy. 
+Thus, we use Mozilla's Lithium engine to minimize the failing tests source files that comprise the highest scored faulty statements from the Defects4j dataset.
+The impact of Tandem-FL is evaluated through computing the SFL score of each fault before and after minimization.
+This study also reflects on the DS limitation of missing faulty statements.
+Our results show that adding DS to SFL improves the SFL diagnosis accuracy.\Sof{add numbers tomorrow morning after closing results}
 \end{abstract}
@@
 Slicing~\cite{Agrawal:1990:DPS:93542.93576}
-as wel as some work~\cite{Perez:2018:LQR:3304889.3304927}\Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
-some works of Wotawa}, a technique that traces back statements
-in the code that influence some point of interest, such as the evaluation
+as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927}, 
+a technique that traces back statements in the code that influence some point of interest, such as the evaluation
 of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
@@
 
-\subsection{Critical Slicing (\cs{})}
+\subsection{Dynamic Slicing (\ds{})}
 \label{sec:slicing}
 
-\Rui{intro needs to refer to Critical Slicing, somehow..}
-\Rui{Are we the first to use Critical Slicing in combination? Say so, if this
-is the case.}
 Program slicing is a program understanding technique to identify the
@@
 This section provides details on the proposed approach, \combpar{}, that combines
-\sfl{} with \cs{}; it also discusses the oracle problem.
+\sfl{} with \ds{}; it also discusses the oracle problem.
 
-\subsection{Combining \sfl{} and \cs{}}
+\subsection{Combining \sfl{} and \ds{}}
 \label{sec:comb}
 
-To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
+To illustrate the idea behind the combination of \sfl{} with \ds{}, consider a
 debugging scenario with five components $c_{1..5}$ and five
@@
 The stacktrace provides information not only about the place where the fault was revelead but also the path taken to get there.
-Thus, our approach considers not only the exception caught by the failling test but also the path that was taken to reveal the fault.
-An example is provided in the following Box:
+Thus, our approach considers not only the exception caught by the failing test but also the path that was taken to reveal the fault.
+The following provides an example:
 
@@
 For example, exceptions including information of memory addresses.
-In this cases, it was developed a mechanism to compare the rest of the output ignoring the identifier of the memory address.
+For these cases, it was developed a mechanism to compare the rest of the output ignoring the identifier of the memory address.
 This heuristic also handles StackOverflow oracles.

### 2019-02-19 paper/ijcai/paper.tex
pass abstract, S1--3

@@
 \begin{abstract}
-Software debugging is difficult.
-Several approaches have been proposed to the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy.
-This paper reports the outcome of a study performed to reassess the impact of combining Dynamic Slicing (DS) with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL.
-We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault.
-Thus, we use Mozilla's Lithium engine to minimize the failing tests source files that comprise the highest scored faulty statements from the Defects4j dataset.
-The impact of Tandem-FL is evaluated through computing the SFL score of each fault before and after minimization.
-This study also reflects on the DS limitation of missing faulty statements.
-Our results show that adding DS to SFL improves the SFL diagnosis accuracy.\Sof{add numbers tomorrow morning after closing results}
+Several approaches have been proposed to improve automated softaware fault
+diagnosis, aiming to reduce the effort and costs spent in debugging. This
+paper reports the outcome of a study
+performed to reassess\Rui{dismistify? We need to say something on why we
+decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
+spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
+suspect that several highly suspiscious components \Rui{I am using components to be
+more generic} --- often involved in failing, but seldom in passed executions ---
+may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
+the failing tests source files that comprise the highest scored faulty
+statements from the Defects4j dataset\Rui{not clear why this is in here for
+the reader: Mozilla, minimizing test cases, ... }. The impact of Tandem-FL is evaluated
+through computing the SFL score \Rui{SFL score: a reader does not know what that is}
+of each fault before and after minimization\Rui{minimization: unknown to the
+reader... He thinks that the study is on slicing}.
+This study also discusses on limitations of dynamic slicing, such as the potential
+of missing faulty statements. Our
+results show that adding combining SFL with dynamic slicing improves the diagnostic
+accuracy in \Rui{x\% on average}, hence leading to the root cause of oberved failures faster.
 \end{abstract}
@@
 
-This paper reports the results of a comprehensive study evaluating the
-impact of combining \ds{} and \sfl{} to improve software fault
-localization, a technique we coin as \comb{}. The intuition for the combination is that
-several highly ranked statements, albeit covered by failing
-executions, may be unrelated to the fault. Our empirical study involves
-\numFaults{} faults from \numPrograms{} different programs comprised
-in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
-is frequently used to evaluate fault localization research. Prior work
-reported promising results in this
+This paper reports the results of a comprehensive study evaluating the impact of
+combining \ds{} and \sfl{} to improve software fault localization, a technique
+we coin as \comb{}. The intuition for the combination is that several highly
+ranked statements, albeit covered by failing executions, may be unrelated to the
+fault. Our empirical study involves \numFaults{} faults from \numPrograms{}
+different programs comprised in the Defects4J (D4J)
+dataset~\cite{just-defects4j-issta2014}, which is frequently used to evaluate
+fault localization research. Prior work reported promising results in this
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
-but they used a non-representative set of subjects in their evaluation
-or used archaic methods to evaluate technique
+but they used a non-representative set of subjects in their evaluation or used
+archaic methods to evaluate technique
 improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
@@
 issue manifests in our experiments. The second research questions
-effectively evaluates the impact of the combination. To sum, our
+effectively evaluates the impact of the combination. Our
 results show that \Sof{@todo: sum up the results}.

### 2019-02-19 paper/ijcai/paper.tex
comment
update to this year's template
some issues fixed

@@
 \pdfpageheight=11in
-\usepackage{ijcai18}
+\usepackage{ijcai19}
 % The file ijcai18.sty is the style file for IJCAI-18 (same as ijcai08.sty).
@@
 \begin{abstract}
-Several approaches have been proposed to improve automated softaware fault
+Several approaches have been proposed to improve automated software fault
 diagnosis, aiming to reduce the effort and costs spent in debugging. This
 paper reports the outcome of a study
-performed to reassess\Rui{dismistify? We need to say something on why we
+performed to dismistify\Rui{We need to say something on why we
 decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
 spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
-suspect that several highly suspiscious components \Rui{I am using components to be
-more generic} --- often involved in failing, but seldom in passed executions ---
+suspect that several highly suspiscious components --- often involved in failing, 
+but seldom in passed executions ---
 may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
@@
 of missing faulty statements. Our
-results show that adding combining SFL with dynamic slicing improves the diagnostic
-accuracy in \Rui{x\% on average}, hence leading to the root cause of oberved failures faster.
+results show that combining SFL with dynamic slicing improves the diagnostic
+accuracy in \Rui{x\% on average}, hence leading to the root cause of observed failures faster.
 \end{abstract}
@@
 a technique that traces back statements in the code that influence some point of interest, such as the evaluation
-of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
+of a failing assertion. In contrast to \ds{} \Rui{DS, not introduced at this point
+in the intro}, \sfl{}~\cite{7390282}
 does not analyze code. Instead, it is a black-box, statistical fault

### 2019-02-19 paper/ijcai/paper.tex
ijcai

@@
 Several approaches have been proposed to improve automated software fault
-diagnosis, aiming to reduce the effort and costs spent in debugging. This
-paper reports the outcome of a study
-performed to dismistify\Rui{We need to say something on why we
-decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
-spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
-suspect that several highly suspiscious components --- often involved in failing, 
+diagnosis, aiming to reduce the effort and costs spent in debugging. 
+Dynamic Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are very popular techniques and normally seen as complementary. However, this combination has not been entirely explored yet.
+Thus, this paper reports the outcome of an empirical study
+performed to demystify the impact of combining \ds{} with \sfl{}, a technique we coin as Tandem-FL. 
+We
+suspect that several highly suspicious components --- often involved in failing, 
 but seldom in passed executions ---
-may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
-the failing tests source files that comprise the highest scored faulty
-statements from the Defects4j dataset\Rui{not clear why this is in here for
-the reader: Mozilla, minimizing test cases, ... }. The impact of Tandem-FL is evaluated
-through computing the SFL score \Rui{SFL score: a reader does not know what that is}
-of each fault before and after minimization\Rui{minimization: unknown to the
-reader... He thinks that the study is on slicing}.
+may be unrelated to the bug. 
 This study also discusses on limitations of dynamic slicing, such as the potential
@@
       \toprule
-      Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
+      Project            & Size (LOC)$^{*}$ & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
       \midrule
-      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
-      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
-      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
-      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
-      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
-      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
+      \lang{}            &   & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
+      \cmath{}           &   & 26,797 & 106     \\   %\comments{& 177   &  -}\\
+      \closure{}         &   & 27,930  & 133     \\   %\comments{& 350   &  -}\\
+      \chart{}           &   & 8,458 & 26      \\  %\comments{& 92    &  -}\\
+      \jtime{}           &   & 3,289 & 27       \\   %\comments{& 76    &  -}\\
+      \mockito{}         &   & 8,835 & 38    \\     %\comments{& 118   &  -}\\
       \bottomrule
@@
 \caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
+
 \label{tab:df4j}

### 2019-02-19 paper/ijcai/paper.tex
pass on abstract (please check)

@@
 \begin{abstract}
-Several approaches have been proposed to improve automated software fault
-diagnosis, aiming to reduce the effort and costs spent in debugging. 
-Dynamic Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are very popular techniques and normally seen as complementary. However, this combination has not been entirely explored yet.
-Thus, this paper reports the outcome of an empirical study
-performed to demystify the impact of combining \ds{} with \sfl{}, a technique we coin as Tandem-FL. 
-We
-suspect that several highly suspicious components --- often involved in failing, 
-but seldom in passed executions ---
-may be unrelated to the bug. 
-This study also discusses on limitations of dynamic slicing, such as the potential
-of missing faulty statements. Our
-results show that combining SFL with dynamic slicing improves the diagnostic
-accuracy in \Rui{x\% on average}, hence leading to the root cause of observed failures faster.
+Several approaches have been proposed in the literature to improve
+debugging costs through automated software fault diagnosis.  Dynamic
+Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
+very popular fault diagnosis techniques and normally seen as
+complementary.  This paper reports the outcome of a comprehensive
+study with the goal of demystifying the impact of combining \ds{} with
+\sfl{}.  We suspect that several highly suspicious components---often
+involved in failing, but seldom in passing executions---may be
+unrelated to the bug. With the aforementioned combination, such
+components could be identified and their suspiciousness reduced.  This
+study also discusses the impact of the dynamic slicing key
+limitation---the risk of missing faulty statements. Our results show
+that, in practice, \ds{} rarely misses faulty statements (\Fix{X}
+misses in \Fix{Y} cases) and that the \ds{}-\sfl{} combination
+improves the diagnostic accuracy in \Rui{x\% on average}. \Mar{check
+  if you agree on this...} To sum, we found that, despite tacit
+opinions of the reserach commuinity about the usefulness of \ds{} in
+automated debugging, we found the combination practical and effective,
+and encourage new \sfl{} techniques to be evaluated against that
+optimization.
+%, a technique we coin as Tandem-FL
+%% hence leading to the root cause of
+%% observed failures faster.
 \end{abstract}

### 2019-02-19 paper/ijcai/paper.tex
fixes in abstract

@@
 \begin{abstract}
-Several approaches have been proposed in the literature to improve
-debugging costs through automated software fault diagnosis.  Dynamic
-Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
-very popular fault diagnosis techniques and normally seen as
-complementary.  This paper reports the outcome of a comprehensive
-study with the goal of demystifying the impact of combining \ds{} with
-\sfl{}.  We suspect that several highly suspicious components---often
-involved in failing, but seldom in passing executions---may be
-unrelated to the bug. With the aforementioned combination, such
-components could be identified and their suspiciousness reduced.  This
-study also discusses the impact of the dynamic slicing key
-limitation---the risk of missing faulty statements. Our results show
-that, in practice, \ds{} rarely misses faulty statements (\Fix{X}
-misses in \Fix{Y} cases) and that the \ds{}-\sfl{} combination
-improves the diagnostic accuracy in \Rui{x\% on average}. \Mar{check
-  if you agree on this...} To sum, we found that, despite tacit
-opinions of the reserach commuinity about the usefulness of \ds{} in
-automated debugging, we found the combination practical and effective,
-and encourage new \sfl{} techniques to be evaluated against that
-optimization.
-%, a technique we coin as Tandem-FL
-%% hence leading to the root cause of
-%% observed failures faster.
+Several approaches have been proposed in the literature to improve debugging
+costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
+Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
+techniques and normally seen as complementary.  This paper reports the outcome
+of a study using real-world applications with the goal of demystifying the
+impact of combining \ds{} with \sfl{}.  We suspect that several highly
+suspicious components---often involved in failing, but seldom in passing
+executions---may be unrelated to the bug. With the aforementioned combination,
+such components could be identified and their suspiciousness reduced.  This
+study also discusses the impact of the dynamic slicing key limitation---the risk
+of missing faulty statements. Our results show that, in practice, \ds{} rarely
+misses faulty statements (\Fix{X} misses in \Fix{Y} cases) and that the
+\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
+in \Rui{x\% on average}. To sum, we found that, despite tacit opinions of the
+research community about the usefulness of \ds{} in automated debugging, we
+found the combination practical and effective, and encourage new \sfl{}
+techniques to be evaluated against that optimization.
 \end{abstract}

### 2019-02-19 paper/ijcai/paper.tex
more fixes

@@
 of missing faulty statements. Our results show that, in practice, \ds{} rarely
-misses faulty statements (\Fix{X} misses in \Fix{Y} cases) and that the
+misses faulty statements (22 misses in 256 cases) and that the
 \ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
@@
 to automate fault isolation. An example of a MBSD is Dynamic
-Slicing~\cite{Agrawal:1990:DPS:93542.93576}
+Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576}
 as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
 a technique that traces back statements in the code that influence some point of interest, such as the evaluation
-of a failing assertion. In contrast to \ds{} \Rui{DS, not introduced at this point
-in the intro}, \sfl{}~\cite{7390282}
+of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
 does not analyze code. Instead, it is a black-box, statistical fault
@@
 Our implementation of Critical Slicing is based on the Mozilla Lithium
-tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
-algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
+tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. It takes as input a file
 and produces as output a simplified version of that file that
@@
 		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
-		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\
+		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
+	 Total      & 203  &  & 213 & 
+	 				& 223 &  & 234 &  & 256 \\
 		\bottomrule

### 2019-02-19 paper/ijcai/paper.tex
intro

@@
 
-This paper reports the results of a comprehensive study evaluating the impact of
-combining \ds{} and \sfl{} to improve software fault localization, a technique
-we coin as \comb{}. The intuition for the combination is that several highly
-ranked statements, albeit covered by failing executions, may be unrelated to the
-fault. Our empirical study involves \numFaults{} faults from \numPrograms{}
-different programs comprised in the Defects4J (D4J)
-dataset~\cite{just-defects4j-issta2014}, which is frequently used to evaluate
-fault localization research. Prior work reported promising results in this
+This paper reports the results of a a study using real-world applications to
+evaluate the impact of combining \ds{} and \sfl{} to improve software fault
+localization. We coin the toolset materializing this approach as \comb{}.  The
+intuition for the combination is that several highly ranked statements, albeit
+covered by failing executions, may be unrelated to the fault. Our empirical
+study involves \numFaults{} faults from \numPrograms{} different programs
+comprised in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
+is frequently used to evaluate fault localization research. Prior work reported
+promising results in this
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
@@
 \end{itemize}
+
+The tool as well as a replication package will be available once double-blind
+requirements are lifted.
 

### 2019-02-19 paper/ijcai/paper.tex
more polishing intro
polishing

@@
 \begin{itemize}
-	\item A comprehensive study on the combination of \sfl{} and \ds{}
-     for bug localization of \emph{Java} faulty programs.
+	\item A study, using real-world applications and bugs, on the combination
+    of \ds{} and \sfl{} for bug localization of \emph{Java} faulty programs.
    \item A tool that implements \comb{}.
@@
 This section provides details on the proposed approach, \combpar{}, that combines
-\sfl{} with \ds{}; it also discusses the oracle problem.
+\ds{} with \sfl{}; it also discusses the oracle problem.
 
-\subsection{Combining \sfl{} and \ds{}}
+\subsection{Combining \ds{} and \sfl{}}
 \label{sec:comb}

### 2019-02-20 paper/ijcai/paper.tex
remove unnecessary comment
changing title, no acronym
abstract+results update+sec4.1

@@
 
-\title{Demystifying the Dynamic Slicing and SFL Combination}
+\title{Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault
+Localization}
 
@@
 of missing faulty statements. Our results show that, in practice, \ds{} rarely
-misses faulty statements (22 misses in 256 cases) and that the
+misses faulty statements (23 misses in 260 cases) and that the
 \ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
-in \Rui{x\% on average}. To sum, we found that, despite tacit opinions of the
+in 51\% of the faults. To sum, we found that, despite tacit opinions of the
 research community about the usefulness of \ds{} in automated debugging, we
@@
 To evaluate our approach, we compare the cost of diagnosing
-a collection of faulty versions using \sfl{} versus \comb{}.
+a collection of faults using \sfl{} versus \comb{}.
 
@@
       \toprule
-      Project            & Size (LOC)$^{*}$ & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
+     Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
       \midrule
-      \lang{}            &   & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
-      \cmath{}           &   & 26,797 & 106     \\   %\comments{& 177   &  -}\\
-      \closure{}         &   & 27,930  & 133     \\   %\comments{& 350   &  -}\\
-      \chart{}           &   & 8,458 & 26      \\  %\comments{& 92    &  -}\\
-      \jtime{}           &   & 3,289 & 27       \\   %\comments{& 76    &  -}\\
-      \mockito{}         &   & 8,835 & 38    \\     %\comments{& 118   &  -}\\
+      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
+      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
+      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
+      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
+      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
+      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
       \bottomrule
   \end{tabular}
-\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
+\caption {Characterization of \dfj{} subjects.}
 
@@
 
-\Sof{@todo: Add pie chart to show the distribution of foos}
+\begin{figure}[h]
+	\vspace{-1.5cm}
+
+		\centering
+		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
+		\vspace{-1cm}
+
+		\caption{FAULT$\_$OF$\_$OMISSION distribution in the \dfj{} dataset}
+		\label{fig:foos}
+\end{figure}
+
+Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of the faults of this dataset are FOOs.
 
@@
 
-        \lang{}            & 1.42\% & 30.47\%\\
-        \cmath{}           & 9.88\% & 11.43\%\\
+        \lang{}            & 1.40\% & 31.46\%\\
+        \cmath{}           & 10.30\% & 12.34\%\\
         %\closure{}          &  & \\
@@
 		\midrule
-		 \lang{}         &  54 & 84.4\%  & 54  & 84.4\%
-		 				& 64 & 100\% & 62 & 96.9\% & 64      \\
-		\cmath{}           & 82 & 81.2\%  & 86 & 85.1\%
-						& 90 & 89.1\% & 97 & 96.0\% & 101  \\   %\comments{& 177   &  -}\\
+		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
+		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
+		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
+						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
 		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
@@
 		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
-	 Total      & 203  &  & 213 &
-	 				& 223 &  & 234 &  & 256 \\
+	 Total      & 207  & 78.4\% & 217 & 83.0\%
+	 				& 227 & 83.8\% & 237 & 88.2\% & 260 \\
 		\bottomrule
@@
 
-\begin{table*}[h]
+\begin{table}[h]
+	\tiny
 	\centering
-	\begin{tabular}{@{}llll@{}}
+	\setlength{\tabcolsep}{3pt}
+	\begin{tabular}{@{}l|l|l|l|l@{}}
 \toprule
-  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
-Mean & 522.47     & 684.89   & 611.04   \\ \midrule
-Median & 50.375      & 66.25               & 54.3                \\ \midrule
-Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
-Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
-Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
+  & SFL-5      & SFL-10              & \combpar{5}                 & \combpar{10}                 \\ \midrule
+Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule
+Median & 49.38    & 53.00  & 69.25              & 56.93               \\ \midrule
+Variance & 1223.08  &  1148.11  & 1352.37  & 1294.87   \\ \midrule
+Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
+Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
 \bottomrule
@@
   \label{table:st}
-\end{table*}
+\end{table}
 
 \begin{figure}[h]
+	\vspace{-1.5cm}
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
-		\caption{Nemenyi post-hoc analysis results \Sof{@tofix: Need to center ylabels}}
+		\caption{Nemenyi post-hoc analysis results}
 		\label{fig:performance}

### 2019-02-20 paper/ijcai/paper.tex
another update

@@
 
-%% The main goal of our evaluation is to understand what is the impact of
-%% \ds{} on \sfl{} after minimizing the $k$ highest faulty source files
-%% which comprise the highest faulty statements.
-
-Recall from Section~\ref{sec:approach} that the \comb{}
-takes as input a value $k$ that denotes the $k$ most suspicious distinct
-classes to be considered. To evaluate the effectiveness of \comb{}, following
+To evaluate the effectiveness of \comb{}, following
 related work, we compared its
-performance with \sfl{} for each defect on each subject program from
-the dataset, for $k\in\{5,10\}$. These classes are obtained directly
-from the ranking. We refer to these variations as \combpar{k}. We
-compared \combpar{5} and \combpar{10} against \sfl{} using the
-following metrics.\Mar{Sofia, I don't see a reason for an equation to
-  only show the difference of cost. Please describe precisely the
-  metrics. In this case, I can't find what C stands for. Also,
- you need to describe precisely what top@n (or someother name) means
- in this context. Check if it makes sense for SFL.$\rightarrow$}\Rui{It might
- be good to keep it just to give it some emphasis... }
+performance with \sfl{} for each fault from
+the dataset, for $k\in\{5,10\}$, where $k$ is the number of classes comprising the highest faulty statements. These classes are obtained directly
+from the ranking which is calculated through \sfl{}.
+For each fault, spectra is updated and the fault ranking is re-calculated but only considering the $k$ highest faulty classes.
+We refer to these variations as SFL$^{k}$.
+After slicing each class of the top $k$ of the highest faulty classes for each fault, the initial spectra is updated based on the slicer output and the fault ranking is re-calculated.
+We refer to these variations as \combpar{k}.
+We
+compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using the
+following metric:
 
 \begin{equation}
-    \Delta{}C = C(\textrm{SFL}) - C(\textrm{\combpar{k}})
+    \Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})
 \end{equation}
@@
 \noindent
-where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
-the cost of diagnosis is: C is the number of statemetns (?) that need to be
-inspected before finding the fault, right? We also need to say that we assume a
-perfect bug understanding: that is, when the developer sees the bug in the
-ranking, he can say that it is the faulty one.}
+where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
 A positive $\Delta$C means that the position of the faulty statement has decreased
-in the ranking after applying the \combpar{k} approach. Hence, reducing the cost to
-find the bug.
+in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
+locating the bug.
 
-\subsection{Dynamic Slicing}
+\subsection{Dynamic Slicing}\label{sec:ds}
 
-This subsection aims to evaluate the performance of the \ds{} technique on slicing
-de \dfj{} projects.
+This subsection aims to report the performance of the \ds{} technique on slicing de faults of $5$ \dfj{} projects. Table \ref{tab:red}
+presents the reduction percentage obtained for each project after slicing the top $5$ and $10$ of classes comprising the highest faulty statements.
+Our approach was capable to reduce the \dfj{} projects in an average of 30.23\%.
 
@@
 	\end{tabular}
-	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
+	\caption {\ds{} reduction performance when considering $k=5$ and $k=10$}
 	\label{tab:red}
@@
 \normalsize
-
-Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.
 
@@
 		\toprule
-		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
+		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{\sfl{}$^{k}$}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
 
@@
 	\end{tabular}
-  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
+  \caption {Number of faults where at least one of the buggy-lines is in the \sfl{}$^{k}$ and \combpar{k} report}
   \label{table:fsws}
@@
 		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
-		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
+		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$ respectively}
 		\label{fig:diagnosis}
@@
 \toprule
-  & SFL-5      & SFL-10              & \combpar{5}                 & \combpar{10}                 \\ \midrule
+  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
 Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule

### 2019-02-20 paper/ijcai/paper.tex
first cut at the conclusion; very draft

@@
 
-\section{Conclusions and Future Work}\label{sec:conc}
+\section{Conclusions and Future Work}
+\label{sec:conc}
+%
+Several approaches have been proposed in the literature to improve debugging
+costs through automated software fault diagnosis to reduce time-to-market,
+while maintaining high quality standards. In this domain, Dynamic Slicing (DS)
+and Spectrum-based Fault Localization (SFL) are very popular fault diagnosis t
+echniques and normally seen as complementary. This paper reports the outcome of
+a study using real-world applications with the goal of demystifying the impact
+of combining DS with SFL. The results of our empirical study show that, in
+practice, DS rarely misses faulty statements (23 misses in 260 cases) and that
+the DS-SFL combination improves the diagnostic accuracy in 51\% of the faults.
+Hence, we found that, despite tacit opinions of the research community about
+the usefulness of DS in automated debugging, we found the combination practical
+and effective, and encourage new SFL techniques to be evaluated against that
+optimization.
 
+Future work is as follows: bla bla.
+
+%
 %\section*{Acknowledgments}
@@
 
-% \begin{appendices}
-% 	\section{Other data that might be interesting to report}
-% 	This section has the only purpose of presenting and discussing other data that
-% 	are not intended yet to be used in the paper. If you find something interesting
-% 	in this block of information, please report.
-%
-% 	\begin{table}[h]
-% 		\centering
-% 		\setlength{\tabcolsep}{4pt}
-% 		\begin{tabular}{ccc}
-% 			\toprule
-% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
-% 			\midrule
-% 			$<0$  & 19.2\% & 15.4\% \\
-% 			$=0$  & 23.1\% & 26.9\% \\
-% 			$>0$  & 57.7\% & 57.7\% \\
-%
-% 			\bottomrule
-% 		\end{tabular}
-% 		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-% 		\label{tab:diagchart}
-% 	\end{table}
-% 	\normalsize
-%
-% 	\begin{table}[h]
-% 		\centering
-% 		\setlength{\tabcolsep}{4pt}
-% 		\begin{tabular}{ccc}
-% 			\toprule
-% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
-% 			\midrule
-% 			$<0$  & 40.7\% & 33.3\% \\
-% 			$=0$  & 25.9\% & 18.5\% \\
-% 			$>0$  & 33.3\% & 48.1\% \\
-%
-% 			\bottomrule
-% 		\end{tabular}
-% 		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-% 		\label{tab:diagtime}
-% 	\end{table}
-% 	\normalsize
-%
-%
-% 	\begin{table}[h]
-% 		\centering
-% 		\setlength{\tabcolsep}{4pt}
-% 		\begin{tabular}{ccc}
-% 			\toprule
-% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
-% 			\midrule
-% 			$<0$  & 36.8\% & 28.9\% \\
-% 			$=0$  & 26.3\% & 28.6\% \\
-% 			$>0$  & 36.8\% & 50.0\% \\
-%
-% 			\bottomrule
-% 		\end{tabular}
-% 		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
-% 		\label{tab:diagmockito}
-% 	\end{table}
-% 	\normalsize
-%
-% 	\begin{table*}[h]
-% 		\setlength{\tabcolsep}{3pt}
-% 		\begin{tabular}{llllllllllllll}
-% 			\toprule
-% 			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
-% 		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
-% 		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
-% 			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
-% 		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
-% 		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
-% 			\bottomrule
-% 		\end{tabular}
-% 		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
-% 		\label{table:reduction}
-% 	\end{table*}
-%
-% 	\begin{table*}[h]
-% 		\small
-% 		\setlength{\tabcolsep}{3pt}
-% 		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
-% 		\toprule
-% 			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
-% 		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
-% 		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
-% 		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
-% 		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
-% 		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
-% 		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
-% 		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
-% 		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
-% 		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
-% 		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
-% 		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
-% 		\bottomrule
-% 		\end{tabular}
-% 		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
-% 		\label{table:performance}
-% 	\end{table*}
-% 	\normalsize
-
-% \end{appendices}
-
 \end{document}

### 2019-02-20 paper/ijcai/paper.tex
new values

--- 2019-02-20 paper/ijcai/paper.tex
@@
   & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
-Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule
-Median & 49.38    & 53.00  & 69.25              & 56.93               \\ \midrule
-Variance & 1223.08  &  1148.11  & 1352.37  & 1294.87   \\ \midrule
+Mean & 584.33 (580.03)  &  516.42 (502.60) & 679.67 (566.99) & 613.98 (491.47)  \\ \midrule
+Median & 49.38 (47.5)   & 53.00 (54.5)  & 69.25 (42.72)             & 56.93 (40)\\ \midrule
+Variance & 1223.08 (1236.94)  &  1148.11 (1149.09)  & 1352.37 (1229.4) & 1294.87  (1143.02) \\ \midrule
 Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule

### 2019-02-20 paper/ijcai/paper.tex
adding submission number
intro S4.4

@@
 to automate fault isolation. An example of a MBSD is Dynamic
-Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576}
-as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
-a technique that traces back statements in the code that influence some point of interest, such as the evaluation
+Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
+a technique that traces back statements in the code that influence some 
+point of interest, such as the evaluation
 of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
@@
 slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
-  static
-  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
+static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
 has been shown useful in automated software debugging where the region
@@
 Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
-simplicity/generality.\comments{ In constrast with alternative slicing
-  implementations based on dependency
-  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
-    JSlice~\cite{Wang:2004:UCB:998675.999455} and
-    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
+simplicity/generality. Critical Slicing
 prescribes a black-box language-semantics-agnostic recipe to computing
@@
 Our implementation of Critical Slicing is based on the Mozilla Lithium
-tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. It takes as input a file
+tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} 
+(Accessed on \today)}. It takes as input a file
 and produces as output a simplified version of that file that
@@
 observed with the test execution on the original program. The
-Lithium minimization process starts by determining the initial size---in number of lines---of
-chunks to delete from the input file. For that,
+Lithium minimization process starts by determining the initial size---in 
+number of lines---of chunks to delete from the input file. For that,
 it chooses the highest power of two number smaller than the file
@@
 fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
-following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
+following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$
+of $M$ system \emph{components}\footnote{A
 component can be any code artifact of arbitrary granularity
-  such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
-$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
+such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; 
+a finite set $\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
 which correspond to records of a system execution, such as test cases;
@@
   \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
-    the slices of each failing test obtained in Step~\ref{step:group} and recompute ranking.
+    the slices of each failing test obtained in Step~\ref{step:group} and 
+	recompute ranking.
 \end{enumerate}
@@
 
-Mozilla's Lithium takes as input a function of interest that can be designed according to the problem to be solved.
-The function of interest determines if the test case output is interesting or not.
-Our function simply compares the failing test output with the output obtained when re-running again the failing test after deleting the slice, as explained in Section~\ref{sec:slicing}.
-Thus, if the
-initial test output is the same as the one after removing the slice \{$c_2$,$c_5$\}, then the slice is removed.
-This means that the slice is not necessary to reveal the fault because if removed the test output is still the same.
+Mozilla's Lithium takes as input a function of interest that can be designed according
+to the problem to be solved. The function of interest determines if the test case output 
+is interesting or not. Our function simply compares the failing test output with the output 
+obtained when re-running again the failing test after deleting the slice, as explained in 
+Section~\ref{sec:slicing}. Thus, if the
+initial test output is the same as the one after removing the slice \{$c_2$,$c_5$\}, then 
+the slice is removed. This means that the slice is not necessary to reveal the fault because 
+if removed the test output is still the same.
 The output is extracted from the stacktrace obtained through the failing test execution. 
-The stacktrace provides information not only about the place where the fault was revelead but also the path taken to get there.
-Thus, our approach considers not only the exception caught by the failing test but also the path that was taken to reveal the fault.
-The following provides an example:
+The stacktrace provides information not only about the place where the fault was revelead 
+but also the path taken to get there. Thus, our approach considers not only the exception 
+caught by the failing test but also the path that was taken to reveal the fault. The following 
+provides an example:
 
@@
 
-Considering some of the stacktrace information about the path taken to reveal the fault solved the issue of generic oracles (e.g., NPE or generic AssertionFailedError expections as the one presented before) mentioned in Theorem~\ref{the:1}.
-There are faults whose outputs could slightly differ from one execution to another.
-For example, exceptions including information of memory addresses.
-For these cases, it was developed a mechanism to compare the rest of the output ignoring the identifier of the memory address.
-This heuristic also handles StackOverflow oracles.
+Considering some of the stacktrace information about the path taken to reveal the fault 
+solved the issue of generic oracles (e.g., NPE or generic AssertionFailedError expections 
+as the one presented before) mentioned in Theorem~\ref{the:1}. There are faults whose outputs 
+could slightly differ from one execution to another. For example, exceptions including information 
+of memory addresses. For these cases, it was developed a mechanism to compare the rest of the output 
+ignoring the identifier of the memory address. This heuristic also handles StackOverflow oracles.
 
@@
 
-Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of the faults of this dataset are FOOs.
+Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in the dataset, i.e., 
+faults which generally are difficult to locate. $59.7\%$ of the faults of this dataset are FOOs.
 
@@
 
-To evaluate the effectiveness of \comb{}, following
-related work, we compared its
-performance with \sfl{} for each fault from
-the dataset, for $k\in\{5,10\}$, where $k$ is the number of classes comprising the highest faulty statements. These classes are obtained directly
-from the ranking which is calculated through \sfl{}.
-For each fault, spectra is updated and the fault ranking is re-calculated but only considering the $k$ highest faulty classes.
-We refer to these variations as SFL$^{k}$.
-After slicing each class of the top $k$ of the highest faulty classes for each fault, the initial spectra is updated based on the slicer output and the fault ranking is re-calculated.
-We refer to these variations as \combpar{k}.
-We
+To evaluate the effectiveness of \comb{}, following related work, we compared its
+performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$, 
+where $k$ is the number of classes comprising the highest faulty statements. These 
+classes are obtained directly from the ranking which is calculated through \sfl{}. 
+For each fault, spectra is updated and the fault ranking is re-calculated but only 
+considering the $k$ highest faulty classes. We refer to these variations as SFL$^{k}$. 
+After slicing each class of the top $k$ of the highest faulty classes for each fault, 
+the initial spectra is updated based on the slicer output and the fault ranking is 
+re-calculated. We refer to these variations as \combpar{k}. We
 compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using the
@@
 
-This subsection aims to report the performance of the \ds{} technique on slicing de faults of $5$ \dfj{} projects. Table \ref{tab:red}
-presents the reduction percentage obtained for each project after slicing the top $5$ and $10$ of classes comprising the highest faulty statements.
-Our approach was capable to reduce the \dfj{} projects in an average of 30.23\%.
+This subsection aims to report the performance of the \ds{} technique on slicing de 
+faults of $5$ \dfj{} projects. Table \ref{tab:red}
+presents the reduction percentage obtained for each project after slicing the top 
+$5$ and $10$ of classes comprising the highest faulty statements. Our approach was 
+capable to reduce the \dfj{} projects in an average of $30.23\%$.
 
@@
 
-The following section aims to answer the research questions presented previously.
+Our approach was capable of slicing a total of $260$ faults from $5$ different 
+sujects. We are still running experiments for the \closure{} and \cmath{} projects.
+(The results of these faults will be integrated on the camera-ready if accepted).
+$33$ of the $260$ faults do not include the faulty statements in the slicer report
+after slicing.
 
@@
 
-\begin{table}[h]
-	\tiny
+\begin{table*}[h]
 	\centering
@@
   \label{table:st}
-\end{table}
+\end{table*}
 

### 2019-02-20 paper/ijcai/paper.tex
small changes

@@
 
-% \author{
-% First Author$^1$,
-% Second Author$^2$,
-% \\
-% $^1$ First Affiliation\\
-% $^2$ Second Affiliation\\
-% %
-% first@email.address,
-% second@email.address,
-% third@email.address
-% }
-
-% If your authors do not fit in the default space, you can increase it
-% by uncommenting the following (adjust the "2.5in" size to make it fit
-% properly)
-% \setlength\titlebox{2.5in}
+% Single author syntax
+\author{
+    Submission 6364
+}
+\iffalse
+\author{
+First Author$^1$
+\and
+Second Author$^2$\and
+Third Author$^{2,3}$\And
+Fourth Author$^4$
+\affiliations
+$^1$First Affiliation\\
+$^2$Second Affiliation\\
+$^3$Third Affiliation\\
+$^4$Fourth Affiliation
+\emails
+\{first, second\}@example.com,
+third@other.example.com,
+fourth@example.com
+}
+\fi
 
@@
 
-In \textbf{RQ1}, we evaluate how often \ds{} misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
-
-Table \ref{table:fsws} presents the number of faults where at least one of the faulty statements appears in the final reports of both techniques, \sfl{} and \comb{}-k.
+In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
+since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
+presents the number of faults where at least one of the faulty statements appears 
+in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
+for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
+classes of the projects. \combpar{k} finds the faulty statements faster than 
+\sfl{}$^{k}$. Using
 
@@
 
-In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.
+In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \ds{}.
 

### 2019-02-20 paper/ijcai/paper.tex
more updates
another update - S4.1

@@
 in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
-locating the bug.
+locating the bug. We also assume a perfect bug understanding, i.e., if the developer
+sees the bug in the ranking, he can say it is the faulty one.
 
@@
 Our approach was capable of slicing a total of $260$ faults from $5$ different 
-sujects. We are still running experiments for the \closure{} and \cmath{} projects.
+subjects. We are still running experiments for the \closure{} and \cmath{} projects.
 (The results of these faults will be integrated on the camera-ready if accepted).
@@
 classes of the projects. \combpar{k} finds the faulty statements faster than 
-\sfl{}$^{k}$. Using
+\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
+when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements.
 

### 2019-02-20 paper/ijcai/paper.tex
more updates in S4.1

@@
 where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
-A positive $\Delta$C means that the position of the faulty statement has decreased
+$\Delta C >0$ means that the position of the faulty statement has decreased
 in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
-locating the bug. We also assume a perfect bug understanding, i.e., if the developer
+locating the bug. $\Delta C <0$ means that the 
+faulty statement may be removed by \combpar{k}. $\Delta C=0$ means that the faulty statement 
+remained in the same position.  We also assume a perfect bug understanding, i.e., if the developer
 sees the bug in the ranking, he can say it is the faulty one.
@@
 
-\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}
+\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
 \label{sec:fault-misses}
@@
 
-\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}
+\subsubsection{RQ2: \textit{How effective is the \combpar{k} combination for bug localization?}}
 
@@
 Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
-$\Delta C <0$ means that the faulty statement may be removed.
-$\Delta C=0$ means that the faulty statement remained in the same position.
-$\Delta C >0$ means that \ds{} improved diagnosability.
 

### 2019-02-20 paper/ijcai/paper.tex
fixes in captions
equation within the text

@@
 
-		\caption{FAULT$\_$OF$\_$OMISSION distribution in the \dfj{} dataset}
+		\caption{Faults of omissions' distribution}
 		\label{fig:foos}
@@
 re-calculated. We refer to these variations as \combpar{k}. We
-compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using the
-following metric:
-
-\begin{equation}
-    \Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})
-\end{equation}
-
-\noindent
+compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using
+the commonly used metric $\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$,
 where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
@@
 	\end{tabular}
-	\caption {\ds{} reduction performance when considering $k=5$ and $k=10$}
+	\caption {\ds{} reduction for $k=5$ and $k=10$}
 	\label{tab:red}

### 2019-02-20 paper/ijcai/paper.tex
intro added results

@@
 
-Software debugging is important and challenging. In particular, the task of locating the faulty
-code (\ie{}, fault localization) is particularly challenging. For that reason,
-countless automated techniques have been proposed in the past to reduce the cost
-of fault localization~\cite{7390282}.
+Software debugging is important and challenging. In particular, the task of
+locating the faulty code (\ie{}, fault localization) is particularly
+challenging. For that reason, countless automated techniques have been proposed
+in the past to reduce the cost of fault localization~\cite{7390282}.
 
-%% Although the technique has been intensively investigated in
-%% research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
-%% exception.
-
-Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
-(\sfl{}) are two very popular techniques that leverage different principles
-to automate fault isolation. An example of a MBSD is Dynamic
-Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
-a technique that traces back statements in the code that influence some
-point of interest, such as the evaluation
-of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
-does not analyze code. Instead, it is a black-box, statistical fault
-localization method that computes suspiciousness values associated
-with program entities (e.g., methods) based on coverage information gathered
-during the execution of test cases as well as the
-output of test cases. More precisely, \sfl{} uses coverage information
-of passing and failing test cases to identify likely faulty
-statements and produces on output a list of program entities ranked in
-decreasing order of suspiciousness.
-\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
-Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
-ranks the relevant parts of the code.
+Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
+Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
+leverage different principles to automate fault isolation. An example of a MBSD
+is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
+work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
+a technique that traces back statements in the code that influence some point of
+interest, such as the evaluation of a failing assertion. In contrast to \ds{},
+\sfl{}~\cite{7390282} does not analyze code. Instead, it is a black-box,
+statistical fault localization method that computes suspiciousness values
+associated with program entities (e.g., methods) based on coverage information
+gathered during the execution of test cases as well as the output of test cases.
+More precisely, \sfl{} uses coverage information of passing and failing test
+cases to identify likely faulty statements and produces on output a list of
+program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
+are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
+Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
+the relevant parts of the code.
 
@@
 
-The goal of this paper is to reassess whether the \comb{} approach
-yields promising results under a more rigorous experimental
-methodology and a larger dataset.\comments{The D4J dataset is about
-  twice as large than the biggest test suite used in previous
-  studies.} This study covers the following research questions:
+The goal of this paper is to reassess whether the \comb{} approach yields
+promising results under a more rigorous experimental methodology and a larger
+dataset.\comments{The D4J dataset is about twice as large than the biggest test
+suite used in previous studies.} This study covers the following research
+questions:
 
@@
 effectively evaluates the impact of the combination. Our
-results show that \Sof{@todo: sum up the results}.
+results show that the combination of the two approaches improves the accuracy
+of fault localization of 51\% of the studied faults.
 

### 2019-02-20 paper/ijcai/paper.tex
intro polishing
polishing .tex

@@
     of \ds{} and \sfl{} for bug localization of \emph{Java} faulty programs.
-   \item A tool that implements \comb{}.
+   \item A tool that implements the combination of \ds{} with \sfl{}, coined
+   \comb{}.
 \end{itemize}
@@
 $\textit{ochiai}\,$=$\,\N{11}/\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}$.
-%The Ochiai formula is given by~\cite{DBLP:conf/prdc/AbreuZG06}
-%\[ochiai = \frac\]
 
@@
 
-%% \vspace{3mm}
-%% \begin{myframe} \label{box:1}
-%% \textbf{java.lang.NullPointerException}, \\
-%% at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
-%% testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
-%% ...
-%% \end{myframe}
-
 \begin{theorem}
@@
 %
-% \subsection{Function of Interest }
-% \label{sec:funcofint}
-%
-%
 
 The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
-operator (SSDL) of the mutation-based testing methodology. This operator
-was designed based on the idea that each statement has an effect on the program
-output (i.e., oracle). Thus, testers are encouraged to design test sets that cause
-all statements to be executed and generate outputs that are different from the
+operator of the mutation-based testing methodology. This operator was designed
+based on the idea that each statement has an effect on the program output (i.e.,
+oracle). Thus, testers are encouraged to design test sets that cause all
+statements to be executed and generate outputs that are different from the
 program under test.
 
-Mozilla's Lithium takes as input a function of interest that can be designed according
-to the problem to be solved. The function of interest determines if the test case output
-is interesting or not. Our function simply compares the failing test output with the output
-obtained when re-running again the failing test after deleting the slice, as explained in
-Section~\ref{sec:slicing}. Thus, if the
-initial test output is the same as the one after removing the slice \{$c_2$,$c_5$\}, then
-the slice is removed. This means that the slice is not necessary to reveal the fault because
-if removed the test output is still the same.
-The output is extracted from the stacktrace obtained through the failing test execution.
-The stacktrace provides information not only about the place where the fault was revelead
-but also the path taken to get there. Thus, our approach considers not only the exception
-caught by the failing test but also the path that was taken to reveal the fault. The following
-provides an example:
+Mozilla's Lithium takes as input a function of interest that can be designed
+according to the problem to be solved. The function of interest determines if
+the test case output is interesting or not. Our function simply compares the
+failing test output with the output obtained when re-running again the failing
+test after deleting the slice, as explained in Section~\ref{sec:slicing}. Thus,
+if the initial test output is the same as the one after removing the slice
+\{$c_2$,$c_5$\}, then the slice is removed. This means that the slice is not
+necessary to reveal the fault because if removed the test output is still the
+same. The output is extracted from the stacktrace obtained through the failing
+test execution. The stacktrace provides information not only about the place
+where the fault was revelead but also the path taken to get there. Thus, our
+approach considers not only the exception caught by the failing test but also
+the path that was taken to reveal the fault. The following provides an example:
 
@@
 
-Considering some of the stacktrace information about the path taken to reveal the fault
-solved the issue of generic oracles (e.g., NPE or generic AssertionFailedError expections
-as the one presented before) mentioned in Theorem~\ref{the:1}. There are faults whose outputs
-could slightly differ from one execution to another. For example, exceptions including information
-of memory addresses. For these cases, it was developed a mechanism to compare the rest of the output
-ignoring the identifier of the memory address. This heuristic also handles StackOverflow oracles.
-
+Considering some of the stacktrace information about the path taken to reveal
+the fault solved the issue of generic oracles (e.g., NPE or generic
+AssertionFailedError expections as the one presented before) mentioned in
+Theorem~\ref{the:1}. There are faults whose outputs could slightly differ from
+one execution to another. For example, exceptions including information of
+memory addresses. For these cases, it was developed a mechanism to compare the
+rest of the output ignoring the identifier of the memory address. This heuristic
+also handles StackOverflow oracles.
 %
-% This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception.
-The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails.
-For each chunk under evaluation, the test is executed after the chunk being deleted from the source code .
-Both test ($testStk$) and expected ($expStk$) stack traces are filtered.
-We only consider stack traces until the line where the main exception is launched.
-These operations are performed by line 3 and 4 from Algorithm 2.
-Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
-
 \section{Evaluation}
 \label{sec:eval}
-
+%
 To evaluate our approach, we compare the cost of diagnosing
 a collection of faults using \sfl{} versus \comb{}.
-
+%
 \subsection{Objects of Analysis}\label{sec:analysis}

### 2019-02-20 paper/ijcai/paper.tex
more polishing

@@
 
-We used the \dfj{} benchmark in our
-experiments~\cite{just-defects4j-issta2014}. This benchmark includes
-six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
-\lang{} is a library that provides a set of helper utilities for the
-     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
-     of self-contained mathematics and statistics components. The
-     \closure{} is a toolset for turning JavaScript files into smaller
-     scripts for faster download and execution in the
-     browser. \chart{} is a Java library for creating charts. \jtime{}
-     is a lightweight library that aims to replace the default Java
-     {\small\texttt{java.util.Date}} classes providing simpler
-     APIs. \mockito{} is a mocking testing framework.
+We used the \dfj{} benchmark in our experiments~\cite{just-defects4j-issta2014}.
+This benchmark includes six different subjects and \numFaults{} faults (Table
+\ref{tab:df4j}). \lang{} is a library that provides a set of helper utilities
+for the {\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
+self-contained mathematics and statistics components. The \closure{} is a
+toolset for turning JavaScript files into smaller scripts for faster download
+and execution in the browser. \chart{} is a Java library for creating charts.
+\jtime{} is a lightweight library that aims to replace the default Java
+{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is a
+mocking testing framework.
 
@@
 
-Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in the dataset, i.e.,
-faults which generally are difficult to locate. $59.7\%$ of the faults of this dataset are FOOs.
+Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in
+the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of
+the faults of this dataset are FOOs.
 
@@
 
-To evaluate the effectiveness of \comb{}, following related work, we compared its
-performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
-where $k$ is the number of classes comprising the highest faulty statements. These
-classes are obtained directly from the ranking which is calculated through \sfl{}.
-For each fault, spectra is updated and the fault ranking is re-calculated but only
-considering the $k$ highest faulty classes. We refer to these variations as SFL$^{k}$.
-After slicing each class of the top $k$ of the highest faulty classes for each fault,
-the initial spectra is updated based on the slicer output and the fault ranking is
-re-calculated. We refer to these variations as \combpar{k}. We
-compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using
-the commonly used metric $\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$,
-where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
-$\Delta C >0$ means that the position of the faulty statement has decreased
-in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
-locating the bug. $\Delta C <0$ means that the
-faulty statement may be removed by \combpar{k}. $\Delta C=0$ means that the faulty statement
-remained in the same position.  We also assume a perfect bug understanding, i.e., if the developer
-sees the bug in the ranking, he can say it is the faulty one.
+To evaluate the effectiveness of \comb{}, following related work, we compared
+its performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
+where $k$ is the number of classes comprising the highest faulty statements.
+These classes are obtained directly from the ranking which is calculated through
+\sfl{}. For each fault, spectra is updated and the fault ranking is
+re-calculated but only considering the $k$ highest faulty classes. We refer to
+these variations as SFL$^{k}$. After slicing each class of the top $k$ of the
+highest faulty classes for each fault, the initial spectra is updated based on
+the slicer output and the fault ranking is re-calculated. We refer to these
+variations as \combpar{k}. We compared \combpar{5} and \combpar{10} against
+\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
+C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
+diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
+that the position of the faulty statement has decreased in the ranking after
+applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
+$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
+$\Delta C=0$ means that the faulty statement remained in the same position.  We
+also assume a perfect bug understanding, i.e., if the developer sees the bug in
+the ranking, he can say it is the faulty one.
 
@@
 With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.
-
-% \begin{table}[h]
-% 	\centering
-% 	\setlength{\tabcolsep}{4pt}
-% 	\begin{tabular}{ccc}
-% 		\toprule
-% 		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
-% 		\midrule
-% 		$<0$  & 19.53\% & 16.02\% \\
-% 		$=0$  & 46.88\% & 41.80\% \\
-% 		$>0$  & 33.59\% & 42.19\% \\
-%
-% 		\bottomrule
-% 	\end{tabular}
-% 	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
-% 	\label{tab:diagnosis}
-% \end{table}
 

### 2019-02-20 paper/ijcai/paper.tex
adding info to intro

@@
 a technique that traces back statements in the code that influence some point of
-interest, such as the evaluation of a failing assertion. In contrast to \ds{},
-\sfl{}~\cite{7390282} does not analyze code. Instead, it is a black-box,
+interest, such as the evaluation of a failing assertion. On the one hand, similarly to \ds{},
+\sfl{} received tremendous attention in research over the years, but its
+applicability to support debugging remains
+questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
+On the other hand, in contrast to \ds{},
+\sfl{}~\cite{7390282} is instead a black-box,
 statistical fault localization method that computes suspiciousness values
@@
 
-%% Similarly to \ds{}, \sfl{} received
-%% tremendous attention in research over the years,
-%% but its applicability to support
-%% debugging remains
-%% questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
 %% Despite the skepticism of the research community, \sfl{} has been

### 2019-02-20 paper/ijcai/paper.tex
small fixes

--- 2019-02-20 paper/ijcai/paper.tex
@@
 
-Software debugging is important and challenging. In particular, the task of
-locating the faulty code (\ie{}, fault localization) is particularly
-challenging. For that reason, countless automated techniques have been proposed
-in the past to reduce the cost of fault localization~\cite{7390282}.
+Software debugging is important and challenging. In particular, the task of locating the faulty
+code (\ie{}, fault localization) is particularly challenging. For that reason,
+countless automated techniques have been proposed in the past to reduce the cost
+of fault localization~\cite{7390282}.
 
-Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
-Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
-leverage different principles to automate fault isolation. An example of a MBSD
-is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
-work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
-a technique that traces back statements in the code that influence some point of
-interest, such as the evaluation of a failing assertion. In contrast to \ds{},
-\sfl{}~\cite{7390282} does not analyze code. Instead, it is a black-box,
-statistical fault localization method that computes suspiciousness values
-associated with program entities (e.g., methods) based on coverage information
-gathered during the execution of test cases as well as the output of test cases.
-More precisely, \sfl{} uses coverage information of passing and failing test
-cases to identify likely faulty statements and produces on output a list of
-program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
-are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
-Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
-the relevant parts of the code.
+%% Although the technique has been intensively investigated in
+%% research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
+%% exception.
+
+Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
+(\sfl{}) are two very popular techniques that leverage different principles
+to automate fault isolation. An example of a MBSD is Dynamic
+Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
+a technique that traces back statements in the code that influence some 
+point of interest, such as the evaluation
+of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
+does not analyze code. Instead, it is a black-box, statistical fault
+localization method that computes suspiciousness values associated
+with program entities (e.g., methods) based on coverage information gathered
+during the execution of test cases as well as the
+output of test cases. More precisely, \sfl{} uses coverage information
+of passing and failing test cases to identify likely faulty
+statements and produces on output a list of program entities ranked in
+decreasing order of suspiciousness.
+\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
+Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
+ranks the relevant parts of the code.
 
@@
 
-The goal of this paper is to reassess whether the \comb{} approach yields
-promising results under a more rigorous experimental methodology and a larger
-dataset.\comments{The D4J dataset is about twice as large than the biggest test
-suite used in previous studies.} This study covers the following research
-questions:
+The goal of this paper is to reassess whether the \comb{} approach
+yields promising results under a more rigorous experimental
+methodology and a larger dataset.\comments{The D4J dataset is about
+  twice as large than the biggest test suite used in previous
+  studies.} This study covers the following research questions:
 
@@
 effectively evaluates the impact of the combination. Our
-results show that the combination of the two approaches improves the accuracy
-of fault localization of 51\% of the studied faults.
+results show that \Sof{@todo: sum up the results}.
 
@@
     of \ds{} and \sfl{} for bug localization of \emph{Java} faulty programs.
-   \item A tool that implements the combination of \ds{} with \sfl{}, coined
-   \comb{}.
+   \item A tool that implements \comb{}.
 \end{itemize}
@@
 $\textit{ochiai}\,$=$\,\N{11}/\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}$.
+%The Ochiai formula is given by~\cite{DBLP:conf/prdc/AbreuZG06}
+%\[ochiai = \frac\]
 
@@
 
+%% \vspace{3mm}
+%% \begin{myframe} \label{box:1}
+%% \textbf{java.lang.NullPointerException}, \\
+%% at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
+%% testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
+%% ...
+%% \end{myframe}
+
 \begin{theorem}
@@
 %
+% \subsection{Function of Interest }
+% \label{sec:funcofint}
+%
+%
 
 The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
-operator of the mutation-based testing methodology. This operator was designed
-based on the idea that each statement has an effect on the program output (i.e.,
-oracle). Thus, testers are encouraged to design test sets that cause all
-statements to be executed and generate outputs that are different from the
+operator (SSDL) of the mutation-based testing methodology. This operator
+was designed based on the idea that each statement has an effect on the program
+output (i.e., oracle). Thus, testers are encouraged to design test sets that cause
+all statements to be executed and generate outputs that are different from the
 program under test.
 
-Mozilla's Lithium takes as input a function of interest that can be designed
-according to the problem to be solved. The function of interest determines if
-the test case output is interesting or not. Our function simply compares the
-failing test output with the output obtained when re-running again the failing
-test after deleting the slice, as explained in Section~\ref{sec:slicing}. Thus,
-if the initial test output is the same as the one after removing the slice
-\{$c_2$,$c_5$\}, then the slice is removed. This means that the slice is not
-necessary to reveal the fault because if removed the test output is still the
-same. The output is extracted from the stacktrace obtained through the failing
-test execution. The stacktrace provides information not only about the place
-where the fault was revelead but also the path taken to get there. Thus, our
-approach considers not only the exception caught by the failing test but also
-the path that was taken to reveal the fault. The following provides an example:
+Mozilla's Lithium takes as input a function of interest that can be designed according
+to the problem to be solved. The function of interest determines if the test case output 
+is interesting or not. Our function simply compares the failing test output with the output 
+obtained when re-running again the failing test after deleting the slice, as explained in 
+Section~\ref{sec:slicing}. Thus, if the
+initial test output is the same as the one after removing the slice \{$c_2$,$c_5$\}, then 
+the slice is removed. This means that the slice is not necessary to reveal the fault because 
+if removed the test output is still the same.
+The output is extracted from the stacktrace obtained through the failing test execution. 
+The stacktrace provides information not only about the place where the fault was revelead 
+but also the path taken to get there. Thus, our approach considers not only the exception 
+caught by the failing test but also the path that was taken to reveal the fault. The following 
+provides an example:
 
@@
 
-Considering some of the stacktrace information about the path taken to reveal
-the fault solved the issue of generic oracles (e.g., NPE or generic
-AssertionFailedError expections as the one presented before) mentioned in
-Theorem~\ref{the:1}. There are faults whose outputs could slightly differ from
-one execution to another. For example, exceptions including information of
-memory addresses. For these cases, it was developed a mechanism to compare the
-rest of the output ignoring the identifier of the memory address. This heuristic
-also handles StackOverflow oracles.
+Considering some of the stacktrace information about the path taken to reveal the fault 
+solved the issue of generic oracles (e.g., NPE or generic AssertionFailedError expections 
+as the one presented before) mentioned in Theorem~\ref{the:1}. There are faults whose outputs 
+could slightly differ from one execution to another. For example, exceptions including information 
+of memory addresses. For these cases, it was developed a mechanism to compare the rest of the output 
+ignoring the identifier of the memory address. This heuristic also handles StackOverflow oracles.
+
 %
+% This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception.
+The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails.
+For each chunk under evaluation, the test is executed after the chunk being deleted from the source code .
+Both test ($testStk$) and expected ($expStk$) stack traces are filtered.
+We only consider stack traces until the line where the main exception is launched.
+These operations are performed by line 3 and 4 from Algorithm 2.
+Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
+
 \section{Evaluation}
 \label{sec:eval}
-%
+
 To evaluate our approach, we compare the cost of diagnosing
 a collection of faults using \sfl{} versus \comb{}.
-%
+
 \subsection{Objects of Analysis}\label{sec:analysis}
@@
 
-		\caption{Faults of omissions' distribution}
+		\caption{FAULT$\_$OF$\_$OMISSION distribution in the \dfj{} dataset}
 		\label{fig:foos}
@@
 re-calculated. We refer to these variations as \combpar{k}. We
-compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using
-the commonly used metric $\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$,
+compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using the
+following metric:
+
+\begin{equation}
+    \Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})
+\end{equation}
+
+\noindent
 where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
@@
 	\end{tabular}
-	\caption {\ds{} reduction for $k=5$ and $k=10$}
+	\caption {\ds{} reduction performance when considering $k=5$ and $k=10$}
 	\label{tab:red}
@@
 \normalsize
-
-\subsection{Results and Discussion}
-
-Our approach was capable of slicing a total of $260$ faults from $5$ different
-subjects. We are still running experiments for the \closure{} and \cmath{} projects.
-(The results of these faults will be integrated on the camera-ready if accepted).
-$33$ of the $260$ faults do not include the faulty statements in the slicer report
-after slicing.
-
-\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
-\label{sec:fault-misses}
-
-In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements,
-since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws}
-presents the number of faults where at least one of the faulty statements appears
-in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
-for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty
-classes of the projects. \combpar{k} finds the faulty statements faster than
-\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
-when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements.
 
@@
 \end{table*}
+
+\subsection{Results and Discussion}
+
+Our approach was capable of slicing a total of $260$ faults from $5$ different 
+subjects. We are still running experiments for the \closure{} and \cmath{} projects.
+(The results of these faults will be integrated on the camera-ready if accepted).
+$33$ of the $260$ faults do not include the faulty statements in the slicer report
+after slicing.
+
+\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
+\label{sec:fault-misses}
+
+In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
+since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
+presents the number of faults where at least one of the faulty statements appears 
+in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
+for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
+classes of the projects. \combpar{k} finds the faulty statements faster than 
+\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
+when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
+whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
+of $5.2\%$.
 

### 2019-02-20 paper/ijcai/paper.tex

--- 2019-02-20 paper/ijcai/paper.tex
@@
 
-Our approach was capable of slicing a total of $260$ faults from $5$ different
-subjects. We are still running experiments for the \closure{} and \cmath{} projects.
-(The results of these faults will be integrated on the camera-ready if accepted).
-$33$ of the $260$ faults do not include the faulty statements in the slicer report
-after slicing.
-
-\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
-\label{sec:fault-misses}
-
-In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements,
-since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws}
-presents the number of faults where at least one of the faulty statements appears
-in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
-for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty
-classes of the projects. \combpar{k} finds the faulty statements faster than
-\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
-when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements.
-
 \begin{table*}[h]
@@
 \end{table*}
+
+Our approach was capable of slicing a total of $260$ faults from $5$ different 
+subjects. We are still running experiments for the \closure{} and \cmath{} projects.
+(The results of these faults will be integrated on the camera-ready if accepted).
+$33$ of the $260$ faults do not include the faulty statements in the slicer report
+after slicing.
+
+\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
+\label{sec:fault-misses}
+
+In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
+since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
+presents the number of faults where at least one of the faulty statements appears 
+in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
+for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
+classes of the projects. \combpar{k} finds the faulty statements faster than 
+\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
+when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
+whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
+of $5.2\%$.
 
@@
   & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
-Mean & 584.33 (580.03)  &  516.42 (502.60) & 679.67 (566.99) & 613.98 (491.47)  \\ \midrule
-Median & 49.38 (47.5)   & 53.00 (54.5)  & 69.25 (42.72)             & 56.93 (40)\\ \midrule
-Variance & 1223.08 (1236.94)  &  1148.11 (1149.09)  & 1352.37 (1229.4) & 1294.87  (1143.02) \\ \midrule
-Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
-Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
+Mean & 580.0 (584.3)   &  502.6 (516.4)  & 567.0 (679.7)  & 491.5 (614.0)   \\ \midrule
+Median & 47.5 (49.4)    & 54.5 (53.0) & 42.7 (69.3)  & 40.0 (56.9)\\ \midrule
+Variance & 1237.0 (1223.1)  &  1149.1 (1148.1) & 1229.4 (1352.4) &  1143.0 (1294.9) \\ \midrule
+Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
+Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
 \bottomrule

### 2019-02-20 paper/ijcai/paper.tex
table 4

@@
 		\vspace{-1cm}
-
 		\caption{Faults of omissions' distribution}
@@
 presents the reduction percentage obtained for each project after slicing the top
-$5$ and $10$ of classes comprising the highest faulty statements. Our approach was
-capable to reduce the \dfj{} projects in an average of $30.23\%$.
+$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction 
+of 30.23\% on average in the projects considered in our study.
 
@@
 
-The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
+The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the 
+faulty statements of the \chart{}
 project. Table , reports the average rank of all faulty statements for each version of \chart{} project after
@@
 
-\begin{table*}[h]
+\begin{table}[h]
+	\tiny
 	\centering
@@
   & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
-Mean & 580.0 (584.3)   &  502.6 (516.4)  & 567.0 (679.7)  & 491.5 (614.0)   \\ \midrule
-Median & 47.5 (49.4)    & 54.5 (53.0) & 42.7 (69.3)  & 40.0 (56.9)\\ \midrule
-Variance & 1237.0 (1223.1)  &  1149.1 (1148.1) & 1229.4 (1352.4) &  1143.0 (1294.9) \\ \midrule
+Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
+Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
+Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
 Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
@@
   \label{table:st}
-\end{table*}
+\end{table}
 

### 2019-02-20 paper/ijcai/paper.tex
more updates

@@
 
+In this section, we answer the research questions proposed and discuss the results obtained.
 Our approach was capable of slicing a total of $260$ faults from $5$ different 
-subjects. We are still running experiments for the \closure{} and \cmath{} projects.
-(The results of these faults will be integrated on the camera-ready if accepted).
-$33$ of the $260$ faults do not include the faulty statements in the slicer report
-after slicing.
+projects. The remaining faults were not considered because (1) faults
+belong to the \closure{} project which requires high CPU to perform the \combpar{k} evaluation 
+or (2) faults whose test outputs were not reproducible in the machine used to run the experiments.
+\textbf{RQ1} reviews one of the main issues of \ds{} - missing faulty statements - whereas \textbf{RQ2}
+discusses how effective is the proposed approach, \combpar{k}.
 
@@
 whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
-of $5.2\%$.
+of $5.2\%$. $33$ of the $260$ faults do not include the faulty statements in the slicer report
+after slicing.
 
@@
 
-%For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%. However, top-5 has less classes to minimize than top-10.
-
 Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant.
@@
 With 99 \% of confidence, the results tell us that the distributions are not normal.
-Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman ~\cite{10.2307/2279372}.
+Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman~\cite{10.2307/2279372}.
 The null-hypothesis is that all distributions are the same.
 With 99 \% of confidence, the results show that the distributions are not all the same.
-In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis \Fix{cite}.
+In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis.
 Figure \ref{fig:performance} report the results of that analysis for all the distributions.
@@
 	\setlength{\tabcolsep}{3pt}
-	\begin{tabular}{@{}l|l|l|l|l@{}}
+	\begin{tabular}{@{}c|c|c|c|c@{}}
 \toprule
@@
 Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
-Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
+Shapiro-Wilk &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
 Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\

### 2019-02-21 paper/ijcai/paper.tex
refs + s4.4

@@
 $5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction 
-of 30.23\% on average in the projects considered in our study.
+of 30.23\% in the projects considered in our study.
 
@@
 \textbf{RQ1} reviews one of the main issues of \ds{} - missing faulty statements - whereas \textbf{RQ2}
-discusses how effective is the proposed approach, \combpar{k}.
+discusses how effective is the \combpar{k} approach against \sfl{}$^{k}$.
 
@@
 presents the number of faults where at least one of the faulty statements appears 
-in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
-for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
-classes of the projects. \combpar{k} finds the faulty statements faster than 
+in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault, we 
+only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
+classes. \combpar{k} finds the faulty statements faster than 
 \sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
 when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
-whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, an improvement
-of $5.2\%$. $33$ of the $260$ faults do not include the faulty statements in the slicer report
-after slicing.
+whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, \combpar{10} misses less
+$5.2\%$ of the faults against \sfl{}$^{10}$.
 
@@
 
-In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \ds{}.
-
-The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the 
-faulty statements of the \chart{}
-project. Table , reports the average rank of all faulty statements for each version of \chart{} project after
-applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.
-
-Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}.
-
+In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \sfl{}.
+Table~\ref{table:st}, reports the average rank of all faulty statements of all \dfj{} faults considered
+to the study after applying the both techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. $33$ of 
+the $260$ faults do not include the faulty statements in the slicer report after slicing. Thus, we report
+both values in Table~\ref{table:st}. In bold, we present the results of the $227$ faults that do not
+contain the cases where the faulty statements where removed using \combpar{k}. Inside parentheses,
+we present the rank results for all faults.
+The \combpar{k} combination yields an improvement of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
+Instead, if $K=10$ is considered the proposed approach returns an improvement of $11.1$
+on the rank mean of faulty statements. It is worth noting that Automated Program Repair techniques may directly benefit from this
+study to improve their results.
+Figure \ref{fig:diagnosis} reports the performance of the diagnosis using \combpar{5} and \combpar{10} against
+\sfl{}$^{5}$ and \sfl{}$^{10}$, respectively. Although this dataset has more than 50\% of fault of omissions,
+our simple slicing approach was capable of improving the ranking of $97$ for $k=5$ and $117$ for $K=117$ faults. 
 Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant.
-Shapiro-Wilk ~\cite{10.2307/2333709} tests the null hypothesis that results are drawn from a normal distribution.
-The test is perfomed for the three techniques under evaluation (\sfl{}, \comb{}-5, \comb{}-10).
-With 99 \% of confidence, the results tell us that the distributions are not normal.
-Given that the distributions are not normally distributed, we use the non-parametrical statistical hypothesis test Friedman~\cite{10.2307/2279372}.
-The null-hypothesis is that all distributions are the same.
-With 99 \% of confidence, the results show that the distributions are not all the same.
-In order to understand if there was a pair of distributions that are equal, we performed a Nemenyi post-hoc analysis.
-Figure \ref{fig:performance} report the results of that analysis for all the distributions.
-With 95\% of confidence, it is possible to see that \sfl{} and \comb{}-5 have similar distributions.
+Shapiro-Wilk tests the null hypothesis that results are drawn from a normal distribution.
+The test is perfomed for all techniques and its variants.
+With 99\% of confidence, the results tell us that the distributions are not normal.
+Given that $C$ is not normally distributed, we use the non-parametrical statistical hypothesis test, Friedman.
+The null-hypothesis is that the ranking results of all techniques and variants are the same.
+With 99\% of confidence, the results show that the distributions are distinct.
+In order to understand if there exist a pair of distributions that are equal, we performed a Siegel post-hoc analysis.
+Figure \ref{fig:performance} reports the results of Siegel analysis for all the distributions.
+With 99\% of confidence, it is possible to see that in general the distributions are very similar.
 
@@
 Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
-Shapiro-Wilk &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
+Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.43 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.12 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.00 x $10^{-24}$} & \makecell{$W$ = 0.47 \\ $p$ = 1.62 x $10^{-25}$}  \\ \midrule
 Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
@@
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
-		\caption{Nemenyi post-hoc analysis results}
+		\caption{Siegel post-hoc analysis results}
 		\label{fig:performance}
@@
 \Rui{needs work...}
-
-\Mar{moved from intro$\rightarrow$} It is worth noting that Automated
-Program Repair techniques should directly benefit from these
-results---either to improve their results or to be aware they should
-not invest on this integration.
 
@@
 %
+
 Several approaches have been proposed in the literature to improve debugging
@@
 %include only after review.
-
 {

### 2019-02-21 paper/ijcai/paper.tex
comments

@@
 
-In this section, we answer the research questions proposed and discuss the results obtained.
-Our approach was capable of slicing a total of $260$ faults from $5$ different 
-projects. The remaining faults were not considered because (1) faults
-belong to the \closure{} project which requires high CPU to perform the \combpar{k} evaluation 
-or (2) faults whose test outputs were not reproducible in the machine used to run the experiments.
-\textbf{RQ1} reviews one of the main issues of \ds{} - missing faulty statements - whereas \textbf{RQ2}
-discusses how effective is the \combpar{k} approach against \sfl{}$^{k}$.
+In this section, we answer the research questions proposed and discuss the
+results obtained. Our approach was capable of slicing a total of $260$ faults
+from $5$ different  projects. The remaining faults were not considered because
+(1) faults belong to the \closure{} project which requires high CPU to perform
+the \combpar{k} evaluation  or (2) faults whose test outputs were not
+reproducible in the machine used to run the experiments. \textbf{RQ1} reviews
+one of the main issues of \ds{} - missing faulty statements - whereas
+\textbf{RQ2} discusses how effective is the \combpar{k} approach against
+\sfl{}$^{k}$.
 
-\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
+\subsubsection{RQ1: \textit{How often does \ds{} misses faulty statements?}}
 \label{sec:fault-misses}
 
-In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
-since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
-presents the number of faults where at least one of the faulty statements appears 
-in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault, we 
-only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
-classes. \combpar{k} finds the faulty statements faster than 
-\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
-when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
-whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, \combpar{10} misses less
-$5.2\%$ of the faults against \sfl{}$^{10}$.
+In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
+statements,  since it is one of the main issues of dynamic slicing techniques.
+This is particularly important because when \ds{} missing a faulty statement
+means that it will not be in the diagnostic report and therefore has a negative
+impact in the fault localization accuracy. Table \ref{table:fsws}  presents the
+number of faults where at least one of the faulty statements appears  in the
+final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
+we  only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
+of the highest faulty  classes. \combpar{k} finds the faulty statements faster
+than  \sfl{}$^{k}$. \Rui{Starting from here, I don't see the connection with
+the rq... the rq has nothing to do with the combination. We need to somehow
+motivate why we are discussing these numbers here.}
+Using \combpar{10} we are able to find more $20$ faulty
+statements than when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$
+of the faulty statements whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty
+statements. Thus, \combpar{10} misses less $5.2\%$ of the faults against
+\sfl{}$^{10}$.
 
@@
 
-In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \sfl{}.
-Table~\ref{table:st}, reports the average rank of all faulty statements of all \dfj{} faults considered
-to the study after applying the both techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. $33$ of 
-the $260$ faults do not include the faulty statements in the slicer report after slicing. Thus, we report
-both values in Table~\ref{table:st}. In bold, we present the results of the $227$ faults that do not
-contain the cases where the faulty statements where removed using \combpar{k}. Inside parentheses,
-we present the rank results for all faults.
-The \combpar{k} combination yields an improvement of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
-Instead, if $K=10$ is considered the proposed approach returns an improvement of $11.1$
-on the rank mean of faulty statements. It is worth noting that Automated Program Repair techniques may directly benefit from this
-study to improve their results.
-Figure \ref{fig:diagnosis} reports the performance of the diagnosis using \combpar{5} and \combpar{10} against
-\sfl{}$^{5}$ and \sfl{}$^{10}$, respectively. Although this dataset has more than 50\% of fault of omissions,
-our simple slicing approach was capable of improving the ranking of $97$ for $k=5$ and $117$ for $K=117$ faults. 
-Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant.
-Shapiro-Wilk tests the null hypothesis that results are drawn from a normal distribution.
-The test is perfomed for all techniques and its variants.
-With 99\% of confidence, the results tell us that the distributions are not normal.
-Given that $C$ is not normally distributed, we use the non-parametrical statistical hypothesis test, Friedman.
-The null-hypothesis is that the ranking results of all techniques and variants are the same.
-With 99\% of confidence, the results show that the distributions are distinct.
-In order to understand if there exist a pair of distributions that are equal, we performed a Siegel post-hoc analysis.
-Figure \ref{fig:performance} reports the results of Siegel analysis for all the distributions.
-With 99\% of confidence, it is possible to see that in general the distributions are very similar.
+In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
+to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
+statements of the \dfj{} faults considered to the study after applying the both
+techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
+$33$ of the $260$ \Rui{Ehmm... is this in sycn with previous section?}
+faulty versions do not include the faulty statements in the slicer report after slicing.
+Thus, we report both values in Table~\ref{table:st}. In bold, we present the
+results of the $227$ faults that do not contain the cases where the faulty
+statements where removed using \combpar{k}. Inside parentheses, we present the
+rank results for all faults. The \combpar{k} combination yields an improvement
+of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
+Instead, if $K=10$ is considered the proposed approach returns an improvement of
+$11.1$ on the rank mean of faulty statements.
+\Rui{APR doesn't belong here, maybe the last thing to discuss in this section,
+but not here in the middle}
+It is worth noting that Automated
+Program Repair techniques may directly benefit from this study to improve their
+results. Figure \ref{fig:diagnosis} reports the performance of the diagnosis
+using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
+respectively. Although this dataset has more than 50\% of fault of omissions,
+our simple slicing approach was capable of improving the ranking of $97$ for
+$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
+to determine if the observed results are statistically significant. Shapiro-Wilk
+tests the null hypothesis that results are drawn from a normal distribution. The
+test is perfomed for all techniques and its variants. With 99\% of confidence,
+the results tell us that the distributions are not normal. Given that $C$ is not
+normally distributed, we use the non-parametrical statistical hypothesis test,
+Friedman. The null-hypothesis is that the ranking results of all techniques and
+variants are the same. With 99\% of confidence, the results show that the
+distributions are distinct. To understand if there exist a pair of
+distributions that are equal \Rui{equal? isn't this test the effect size?}, we performed a Siegel post-hoc analysis. Figure
+\ref{fig:performance} reports the results of Siegel analysis for all the
+distributions. With 99\% of confidence, it is possible to see that in general
+the distributions are very similar. \Rui{so??}
+
+\Rui{Weakness: there has to be discussion on whether there is potential/promising
+results somewhere.}
 

### 2019-02-21 paper/ijcai/paper.tex
polishing and shortening abstract

@@
 \begin{abstract}
-Several approaches have been proposed in the literature to improve debugging
-costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
-Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
-techniques and normally seen as complementary.  This paper reports the outcome
-of a study using real-world applications with the goal of demystifying the
-impact of combining \ds{} with \sfl{}.  We suspect that several highly
-suspicious components---often involved in failing, but seldom in passing
-executions---may be unrelated to the bug. With the aforementioned combination,
-such components could be identified and their suspiciousness reduced.  This
-study also discusses the impact of the dynamic slicing key limitation---the risk
-of missing faulty statements. Our results show that, in practice, \ds{} rarely
-misses faulty statements (23 misses in 260 cases) and that the
-\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
-in 51\% of the faults. To sum, we found that, despite tacit opinions of the
-research community about the usefulness of \ds{} in automated debugging, we
-found the combination practical and effective, and encourage new \sfl{}
-techniques to be evaluated against that optimization.
+Several approaches have been proposed in the literature to reduce
+debugging costs through automated software fault diagnosis.  Dynamic
+Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
+popular fault diagnosis techniques and normally seen as complementary.
+This paper reports on a comprehensive study\comments{--using
+  \numFaults{} documented software faults from a credible dataset--}
+to evaluate the effects of combining \ds{} with \sfl{}. We suspect
+that several highly suspicious components---often involved in failing,
+but seldom in passing test runs---may be unrelated to the bug. With
+the aforementioned combination, such components could be located and
+their suspiciousness reduced.  This study also discusses the practical
+impact of the \ds{} key limitation---the risk of missing faulty
+statements. Results indicate that \ds{} misses faulty statements in
+only 9\%\comments{(23 misses)} of the 260 cases\Mar{we are using
+  \numFaults{} in the paper. please, revise and use macros.} and that
+the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
+the diagnostic accuracy by \Fix{Z} in 51\% of the cases. To sum, we
+found that the \ds{}-\sfl{} combination was practical and effective
+and encourage new \sfl{} techniques to be evaluated against that
+optimization.
 \end{abstract}
@@
 \section{Introduction}
+
+\Mar{move this elsewhere...}
+\Fix{
+with the
+goal of demystifying the impact of combining \ds{} with \sfl{}.
+
+Despite tacit negative opinions of the research
+community about the usefulness of \ds{} in automated debugging,}
 
@@
 In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
-statements,  since it is one of the main issues of dynamic slicing techniques.
-This is particularly important because when \ds{} missing a faulty statement
+statements,  since it is one of the main issues of dynamic slicing techniques. This 
+is particularly important because when \ds{} misses a faulty statement
 means that it will not be in the diagnostic report and therefore has a negative
-impact in the fault localization accuracy. Table \ref{table:fsws}  presents the
+impact in the fault localization accuracy. Table~\ref{table:fsws}  presents the
 number of faults where at least one of the faulty statements appears  in the
@@
 we  only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
-of the highest faulty  classes. \combpar{k} finds the faulty statements faster
-than  \sfl{}$^{k}$. \Rui{Starting from here, I don't see the connection with
-the rq... the rq has nothing to do with the combination. We need to somehow
-motivate why we are discussing these numbers here.}
+of the highest faulty  classes.
+
+As observed in~\ref{table:fsws}, \combpar{k} 
+finds the faulty statements faster than \sfl{}$^{k}$.
+
+We observe that $33$ of the $260$ faulty versions do not include the 
+faulty statements in the slicer report after slicing.
+
 Using \combpar{10} we are able to find more $20$ faulty
@@
 techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
-$33$ of the $260$ \Rui{Ehmm... is this in sycn with previous section?}
+$33$ of the $260$ 
 faulty versions do not include the faulty statements in the slicer report after slicing.
@@
 $11.1$ on the rank mean of faulty statements.
-\Rui{APR doesn't belong here, maybe the last thing to discuss in this section,
-but not here in the middle}
-It is worth noting that Automated
-Program Repair techniques may directly benefit from this study to improve their
-results. Figure \ref{fig:diagnosis} reports the performance of the diagnosis
+ Figure \ref{fig:diagnosis} reports the performance of the diagnosis
 using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
@@
 variants are the same. With 99\% of confidence, the results show that the
-distributions are distinct. To understand if there exist a pair of
-distributions that are equal \Rui{equal? isn't this test the effect size?}, we performed a Siegel post-hoc analysis. Figure
+distributions are distinct. To understand if there is any relationship
+between the distributions, 
+we performed a Siegel post-hoc analysis. Figure
 \ref{fig:performance} reports the results of Siegel analysis for all the
@@
 the distributions are very similar. \Rui{so??}
+
+It is worth noting that Automated
+Program Repair techniques may directly benefit from this study to improve their
+results.
 
@@
 \begin{figure}[h]
-	\vspace{-1.5cm}
+	\vspace{-1.2cm}
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}

### 2019-02-21 paper/ijcai/paper.tex
pass on intro

--- 2019-02-21 paper/ijcai/paper.tex
@@
 the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
-the diagnostic accuracy by \Fix{Z} in 51\% of the cases. To sum, we
-found that the \ds{}-\sfl{} combination was practical and effective
+the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
+we found that the \ds{}-\sfl{} combination was practical and effective
 and encourage new \sfl{} techniques to be evaluated against that
@@
 
-\Mar{move this elsewhere...}
-\Fix{
-with the
-goal of demystifying the impact of combining \ds{} with \sfl{}.
+%% provide context (debugging + fault localization)
+Software debugging is important and challenging. The task of locating
+the faulty code (\ie{}, fault localization) is particularly
+challenging. As such, countless automated techniques have been
+proposed in the past to reduce the cost of fault
+localization~\cite{7390282}. Model-based software diagnosis
+(MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault
+Localization (\sfl{})~\cite{DBLP:journals/stvr/HarroldRSWY00} are two
+popular techniques that leverage different principles to automate
+fault isolation~\cite{DBLP:conf/sac/AbreuGZG08}.  At a high-level,
+MBSD
+techniques~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130}
+attempt to eliminate non-suspicious components whereas \sfl{}
+techniques attempt to rank suspicious components with the goal of
+reducing fault diagnosis cost.
 
-Despite tacit negative opinions of the research
-community about the usefulness of \ds{} in automated debugging,}
+%% detail context (DS + SFL)
+Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} is an
+instance of MBSD that has attracted huge attention in research over
+the last decades~\cite{Silva:2012:VPS:2187671.2187674}. The technique
+traces back the statements in the code that influence a given point of
+interest, such as the evaluation of a failing assertion.  Similarly to
+\ds{}, \sfl{}~\cite{DBLP:journals/stvr/HarroldRSWY00} received
+tremendous attention in research over the years~\cite{7390282}.  It
+computes suspiciousness values associated with program components
+(e.g., statements) based on coverage information gathered during the
+execution of test cases.  More precisely, \sfl{} uses coverage
+information of passing and failing test cases to identify likely
+faulty statements and produces on output a list of program components
+ranked in decreasing order of suspiciousness.
 
-Software debugging is important and challenging. In particular, the task of
-locating the faulty code (\ie{}, fault localization) is particularly
-challenging. For that reason, countless automated techniques have been proposed
-in the past to reduce the cost of fault localization~\cite{7390282}.
+%% \ds{} and \sfl{} are complementary~\cite{DBLP:conf/sac/AbreuGZG08} and
+%% could be combined.
 
-Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
-Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
-leverage different principles to automate fault isolation. An example of a MBSD
-is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
-work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
-a technique that traces back statements in the code that influence some point of
-interest, such as the evaluation of a failing assertion. On the one hand, similarly to \ds{},
-\sfl{} received tremendous attention in research over the years, but its
-applicability to support debugging remains
-questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
-On the other hand, in contrast to \ds{},
-\sfl{}~\cite{7390282} is instead a black-box,
-statistical fault localization method that computes suspiciousness values
-associated with program entities (e.g., methods) based on coverage information
-gathered during the execution of test cases as well as the output of test cases.
-More precisely, \sfl{} uses coverage information of passing and failing test
-cases to identify likely faulty statements and produces on output a list of
-program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
-are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
-Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
-the relevant parts of the code.
+Intuitively, \ds{} identifies irrelevant parts of the code (\ie{},
+parts that do not contribute to the fault) whereas \sfl{} ranks the
+relevant parts of the code. It is conceivable, therefore, to combine
+these two techniques based on the intuition that highly ranked
+statements (as per \sfl{}), albeit covered by failing executions,
+could be in fact unrelated to the fault (as per \ds{}). In fact, prior
+work reported promising preliminary results on this
+combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
+Unfortunately, they used a small set of subjects in their evaluation
+or archaic---often optimistic---methods to evaluate fault localization
+improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
+
+Given the importance of fault localization, this paper revisits the
+problem of assessing the effectiveness of combining \ds{} and \sfl{},
+addressing the issues from prior work. The study we conducted involves
+\numFaults{}\Mar{check} faults from \numPrograms{}\Mar{check}
+different programs from the Defects4J (D4J)
+dataset~\cite{just-defects4j-issta2014}, which is frequently used to
+evaluate fault localization research. The study covers the following
+research questions:
+
+%% The goal of this paper is to reassess whether the \comb{} approach yields
+%% promising results under a more rigorous experimental methodology and a larger
+%% dataset.\comments{The D4J dataset is about twice as large than the biggest test
+%% suite used in previous studies.}
+
+\newcommand{\rqone}{How often does DS miss faulty statements?}
+\newcommand{\rqthree}{How effective is the \comb{} approach?}
+
+\begin{itemize}[leftmargin=*]
+\item[]{\footnotesize[(un)soundness]}~\textit{\rqone{}}
+\item[]{\footnotesize[effectiveness]}~\textit{\rqthree{}}
+\end{itemize}
+
+The first question addresses the problem that affects all dynamic
+slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}--that of
+missing faulty statements. Naturally, the consequence of that problem
+for debugging is that developers would never be able to locate
+faults. Different slicers can miss faulty statements for different
+reasons. In this paper, we used Critical
+Slicing~\cite{DeMillo:1996:CSS:229000.226310}, which, in principle,
+could miss statements because of imprecise oracles that guide the
+slicing process.\comments{ We evaluated how often that issue manifests
+  in our experiments.} The second research question evaluates the
+impact of the combination. To sum, our results show that the
+combination of the two approaches improves the accuracy of fault
+localization on average by \avgImprov\ in 51\% of the studied faults.
+
+The contributions of this work are: 1)~an empirical study, using
+real-world applications and bugs, on the combination of \ds{} and
+\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
+tool that implements the combination of \ds{} with \sfl{}, coined
+\comb{}.  The tool as well as a replication package will be available
+once double-blind requirements are lifted.
+
+%% -----------------
+%% This paper reports the results of a comprehensive study to assess the
+%% impact of combining two complementary techniques to improve software
+%% fault localization.
+
+%% It is worth noting that
+
+%%  We
+%% developed a tool, coined as \comb{}, materializing the
+%% combination.
+
+%% the research community manifests
+%% explicit~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}
+%% or tacit negative opinions about the usefulness of \ds{} and \sfl{} in
+%% automated debugging.
+%% -----------------
+
+%Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576}------and \sfl{}.
+%%% explain what each technique does (at a high level)
 
@@
 %% the rank is trimmed to the first $k$ components.
-
-This paper reports the results of a a study using real-world applications to
-evaluate the impact of combining \ds{} and \sfl{} to improve software fault
-localization. We coin the toolset materializing this approach as \comb{}.  The
-intuition for the combination is that several highly ranked statements, albeit
-covered by failing executions, may be unrelated to the fault. Our empirical
-study involves \numFaults{} faults from \numPrograms{} different programs
-comprised in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
-is frequently used to evaluate fault localization research. Prior work reported
-promising results in this
-combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
-but they used a non-representative set of subjects in their evaluation or used
-archaic methods to evaluate technique
-improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
-
-The goal of this paper is to reassess whether the \comb{} approach yields
-promising results under a more rigorous experimental methodology and a larger
-dataset.\comments{The D4J dataset is about twice as large than the biggest test
-suite used in previous studies.} This study covers the following research
-questions:
-
-\newcommand{\rqone}{How often does DS miss faulty statements?}
-\newcommand{\rqthree}{How effective is the \comb{} approach?}
-
-\begin{itemize}[leftmargin=*]
-\item[]{\footnotesize[(un)soundness]}~\textit{\rqone{}}
-\item[]{\footnotesize[effectiveness]}~\textit{\rqthree{}}
-\end{itemize}
-
-The first question addresses the important problem of missing faulty
-statements. Naturally, the consequence of that problem for debugging
-is that developers would never be able to locate faults. Different
-slicers can miss faulty statements for different reasons. In this
-paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
-which, in principle, could miss statements because of imprecise
-oracles that guide the slicing process. We evaluated how often that
-issue manifests in our experiments. The second research questions
-effectively evaluates the impact of the combination. Our
-results show that the combination of the two approaches improves the accuracy
-of fault localization of 51\% of the studied faults.
-
-The contributions of this work are the following ones:
-\begin{itemize}
-	\item A study, using real-world applications and bugs, on the combination
-    of \ds{} and \sfl{} for bug localization of \emph{Java} faulty programs.
-   \item A tool that implements the combination of \ds{} with \sfl{}, coined
-   \comb{}.
-\end{itemize}
-
-The tool as well as a replication package will be available once double-blind
-requirements are lifted.
 

### 2019-02-21 paper/ijcai/paper.tex
another table 4 update

@@
   & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
-Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
-Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
-Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
-Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.43 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.12 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.00 x $10^{-24}$} & \makecell{$W$ = 0.47 \\ $p$ = 1.62 x $10^{-25}$}  \\ \midrule
-Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
+Mean & \textbf{590.7} (584.3)   &  \textbf{512.7} (516.4)  & \textbf{573.4} (679.7)  & \textbf{506.6} (614.0)   \\ \midrule
+Median & \textbf{46.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
+Variance & \textbf{1257.0} (1223.1)  &  \textbf{1171.5} (1148.1) & \textbf{1239.1} (1352.4) &  \textbf{1167.0} (1294.9) \\ \midrule
+Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
+Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
 \bottomrule

### 2019-02-21 paper/ijcai/paper.tex
pass on background

@@
 Our implementation of Critical Slicing is based on the Mozilla Lithium
-tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium}
-(Accessed on \today)}. It takes as input a file
+tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
 and produces as output a simplified version of that file that
@@
 iterations. Proofs of the algorithm complexity can be found
-elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
+elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed \today)}. Our implementation is publicly
 available at \textit{$<$anonymized for double-blind review$>$}.
+
+\begin{theorem}\label{the:1}
+  The faulty statement may not be included in the critical slice of
+  failing test cases.
+\end{theorem}
+
+If test oracles are too general, it is possible, conceptually, that
+the critical slicing algorithm produces slices without the faulty
+code. Suppose that a test fails with a Null-Pointer Exception (NPE)
+and the criterion used to slice the code in that case (\ie{}, the
+oracle) is the presence of NPE in the output, regardless of the
+location that raises that exception. It is therefore possible that the
+slice obtained at some iteration of the aforementioned algorithm
+raises NPE, but it does so in a different part of the code. If that
+happens, the critical slicing algorithm would consider that as an
+acceptable simplification--as it satisfied the criterion--and would
+continue. As the algorithm does not backtrack, it would be impossible,
+to obtain a slice containing the faulty component from that point
+on.\hfill{\tiny$\blacksquare$}
+
+It is worth noting that this is not a problem that afflicts only CS;
+\emph{all} purely dynamic slicing techniques manifest this
+problem~\cite{Lin:2018:BDE:3238147.3238163}. To mitigate the issue in
+CS, it is necessary to make oracles more specific. For that, our
+approach was to use as the slicing criterion the stack trace
+associated with the test failure. That decision increases the chances
+that the sliced program will follow a path to the error similar to
+that followed by the original program. \Mar{Sofia, if you think it is
+  necessary, explain if you needed to abstract something in the
+  stacktrace. I did not understand that memory location thing.}
+
+% \subsection{Implementation}
+% \label{sec:impl}
+
+% \Mar{Sofia, I think this was way too low-level for intro and decided
+%   to move here. please check how to fit.}
+% \Fix{
+% A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
+\morpho{} retrieves as an output the input for \lithium{}.
+\lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statmeents that resulted from the minimization.
+\morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}.
+}
+
+% Two different tools were developed to support this research: \morpho{} and \lithium{}.
+\morpho{} was designed to calculate the suspiciousness of all statements of a project before, and after the top-k minimization performed by \lithium{} whereas \lithium{} is responsible for reducing the search domain of each \texttt{Java} class of the project for the after-\sfl{} analysis.
+\morpho{} uses the spectrum matrix (Figure \ref{fig:spectrum-example}), and the pair \emph{name\#location} for each statement to calculate the respective ranking.
+All rankings are ordered from highest to lowest ranked.
+This information is retrieved along with each test case stack trace in a \texttt{.json} file which serves as an output to \lithium{}.
+\lithium{} starts by generating the inputs (Algorithm \ref{alg:ls}, line $2$) for the top-k classes of each failing test based, mainly, on the output of \emph{morpho} ~---~ ranked list of statements and the test cases stacktraces.
+Then, the tool iterates each class from the top-k classes ($c$) of each test $t$.
+In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{JavaParser is available at http://javaparser.org/ (accessed November 2018).} library.
+This step was added to \lithium{} because it turns \texttt{MozillaLithium} faster since the empty lines are ignored.
+Then, \texttt{MozillaLithium} performs the class minimization using a function of interest (Algorithm \ref{alg:finc}) which compares the output of the test with the expected one which is given as an input.
+Finally, the location of all relevant statements (Algorithm \ref{alg:ls}, line 9) is saved in a \texttt{.json} which is used for the before-\sfl{} analysis.
+\morpho{} uses the output from \lithium{} to create a copy of the older spectrum matrix and updates it according to the explanation provided on Figure \ref{fig:ds-reduction} where the statements that are not in the slice of the test suffer a suspiciouness reduction.
+In the end, \morpho{} performs the \sfl{} analysis for both matrixes and calculates the probability of the first line being faulty, the probability of the last line being faulty, and the mean and median of the position of the faulty line in the ranking.
+These are the metrics used to evaluate how considerable is the improvement obtained when combining \ds{} with \sfl{}.
+
+% \begin{algorithm}[h]
+% 	\caption{Class Minimization Algorithm}
+% 	\label{alg:ls}
+% 	\begin{flushleft}
+% 		\textbf{Input:} $proj$ - project name \\
+% 		\hspace{2.75em} $bug$ - bug number\\
+% 		\hspace{2.75em} $k$ - number of top ranked classes\\
+% 		\hspace{2.75em} $stk$ - expected stacktrace\\
+% 	 \textbf{Output:} Top-k classes minimization for each test \\
+% 	\end{flushleft}
+% 	\begin{algorithmic}[1]
+% 		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
+% 			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
+% 			\ForAll {$t \in testsInfo$}
+% 				\State $classes \leftarrow$ getClasses($proj$, $bug$)
+% 				\ForAll {$c \in classes$}
+% 					\State $unc \leftarrow$ removeComments($c$)
+% 					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
+% 				\EndFor
+% 				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
+% 			\EndFor
+% 			\State \Return $slicer$
+% 		\EndProcedure
+% 	\end{algorithmic}
+%
+% \end{algorithm}
+%
+% \begin{figure*}[t]
+% 	\centering
+% 	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
+% 	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
+% \end{figure*}
+%
+
+%---------------------------------------------------------
+%% \subsubsection{\label{sec:oracleheuristics}Oracle Heuristics.}~
+
+%% The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
+%% operator of the mutation-based testing methodology. This operator was designed
+%% based on the idea that each statement has an effect on the program output (i.e.,
+%% oracle). Thus, testers are encouraged to design test sets that cause all
+%% statements to be executed and generate outputs that are different from the
+%% program under test.
+
+%% Mozilla's Lithium takes as input a function of interest that can be designed
+%% according to the problem to be solved. The function of interest determines if
+%% the test case output is interesting or not. Our function simply compares the
+%% failing test output with the output obtained when re-running again the failing
+%% test after deleting the slice, as explained in Section~\ref{sec:slicing}. Thus,
+%% if the initial test output is the same as the one after removing the slice
+%% \{$c_2$,$c_5$\}, then the slice is removed. This means that the slice is not
+%% necessary to reveal the fault because if removed the test output is still the
+%% same. The output is extracted from the stacktrace obtained through the failing
+%% test execution. The stacktrace provides information not only about the place
+%% where the fault was revelead but also the path taken to get there. Thus, our
+%% approach considers not only the exception caught by the failing test but also
+%% the path that was taken to reveal the fault. The following provides an example:
+
+%% \vspace{3mm}
+%% \begin{myframe} \label{box:1}
+%% junit.framework.AssertionFailedError, \\
+%% at junit.framework.Assert.fail(Assert.java:55), \\
+%% at junit.framework.Assert.assertTrue(Assert.java:22), \\
+%% at junit.framework.Assert.assertFalse(Assert.java:39), \\
+%% at junit.framework.Assert.assertFalse(Assert.java:47), \\
+%% at junit.framework.TestCase.assertFalse(TestCase.java:219), \\
+%% at org.jfree.chart.util.junit.ShapeUtilitiesTests.\\testEqualGeneralPaths(ShapeUtilitiesTests.java:212), \\
+%% ...
+%% \end{myframe}
+
+%% Considering some of the stacktrace information about the path taken to reveal
+%% the fault solved the issue of generic oracles (e.g., NPE or generic
+%% AssertionFailedError expections as the one presented before) mentioned in
+%% Theorem~\ref{the:1}. There are faults whose outputs could slightly differ from
+%% one execution to another. For example, exceptions including information of
+%% memory addresses. For these cases, it was developed a mechanism to compare the
+%% rest of the output ignoring the identifier of the memory address. This heuristic
+%% also handles StackOverflow oracles.
+%---------------------------------------------------------
 
@@
 
-\begin{wrapfigure}[8]{2}{0.3\textwidth}
+\begin{wrapfigure}[8]{1}{0.25\textwidth}
   \hspace{-2ex}
@@
   \scriptsize
+  \setlength{\tabcolsep}{3.5pt}  
   \begin{tabular}{c|cccc|c}
@@
 
-\begin{theorem}\label{the:1}
-  The faulty statement may not be included in the critical slice of
-  failing test cases.
-\end{theorem}
-
-Conceptually, if the oracles implemented in faulty tests are too
-general, the critical slicing algorithm could produce slices without
-the faulty code. For example, consider the scenario of an unexpected
-Null-Pointer Exception (NPE) thrown in the code. If the oracle checks
-for the presence of NPE regardless of where it occurs, it is possible,
-in principle, that the final slice does not include the faulty code
-but still raises NPE (in a different part of the code). The critical
-slicing algorithm would consider that as an acceptable simplification
-and would continue. Section~\ref{sec:oracleheuristics} shows how we
-mitigate this fundamental limitation of Critical Slicing and
-Section~\ref{sec:fault-misses} shows how problematic is that issue in
-practice.
-
 \begin{theorem}
@@
 below the faulty components, the ranking of the faulty components is
-unaffected.
+unaffected.\hfill{\tiny$\blacksquare$}
 
-\subsection{Oracle Heuristics}
-\label{sec:oracleheuristics}
-
-% \subsection{Implementation}
-% \label{sec:impl}
-
-% \Mar{Sofia, I think this was way too low-level for intro and decided
-%   to move here. please check how to fit.}
-% \Fix{
-% A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}.
-\morpho{} retrieves as an output the input for \lithium{}.
-\lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization.
-\morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}.
-}
-
-% Two different tools were developed to support this research: \morpho{} and \lithium{}.
-\morpho{} was designed to calculate the suspiciousness of all statements of a project before, and after the top-k minimization performed by \lithium{} whereas \lithium{} is responsible for reducing the search domain of each \texttt{Java} class of the project for the after-\sfl{} analysis.
-\morpho{} uses the spectrum matrix (Figure \ref{fig:spectrum-example}), and the pair \emph{name\#location} for each statement to calculate the respective ranking.
-All rankings are ordered from highest to lowest ranked.
-This information is retrieved along with each test case stack trace in a \texttt{.json} file which serves as an output to \lithium{}.
-\lithium{} starts by generating the inputs (Algorithm \ref{alg:ls}, line $2$) for the top-k classes of each failing test based, mainly, on the output of \emph{morpho} ~---~ ranked list of statements and the test cases stacktraces.
-Then, the tool iterates each class from the top-k classes ($c$) of each test $t$.
-In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{JavaParser is available at http://javaparser.org/ (accessed November 2018).} library.
-This step was added to \lithium{} because it turns \texttt{MozillaLithium} faster since the empty lines are ignored.
-Then, \texttt{MozillaLithium} performs the class minimization using a function of interest (Algorithm \ref{alg:finc}) which compares the output of the test with the expected one which is given as an input.
-Finally, the location of all relevant statements (Algorithm \ref{alg:ls}, line 9) is saved in a \texttt{.json} which is used for the before-\sfl{} analysis.
-\morpho{} uses the output from \lithium{} to create a copy of the older spectrum matrix and updates it according to the explanation provided on Figure \ref{fig:ds-reduction} where the statements that are not in the slice of the test suffer a suspiciouness reduction.
-In the end, \morpho{} performs the \sfl{} analysis for both matrixes and calculates the probability of the first line being faulty, the probability of the last line being faulty, and the mean and median of the position of the faulty line in the ranking.
-These are the metrics used to evaluate how considerable is the improvement obtained when combining \ds{} with \sfl{}.
-
-% \begin{algorithm}[h]
-% 	\caption{Class Minimization Algorithm}
-% 	\label{alg:ls}
-% 	\begin{flushleft}
-% 		\textbf{Input:} $proj$ - project name \\
-% 		\hspace{2.75em} $bug$ - bug number\\
-% 		\hspace{2.75em} $k$ - number of top ranked classes\\
-% 		\hspace{2.75em} $stk$ - expected stacktrace\\
-% 	 \textbf{Output:} Top-k classes minimization for each test \\
-% 	\end{flushleft}
-% 	\begin{algorithmic}[1]
-% 		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
-% 			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
-% 			\ForAll {$t \in testsInfo$}
-% 				\State $classes \leftarrow$ getClasses($proj$, $bug$)
-% 				\ForAll {$c \in classes$}
-% 					\State $unc \leftarrow$ removeComments($c$)
-% 					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
-% 				\EndFor
-% 				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
-% 			\EndFor
-% 			\State \Return $slicer$
-% 		\EndProcedure
-% 	\end{algorithmic}
-%
-% \end{algorithm}
-%
-% \begin{figure*}[t]
-% 	\centering
-% 	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
-% 	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
-% \end{figure*}
-%
-
-The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
-operator of the mutation-based testing methodology. This operator was designed
-based on the idea that each statement has an effect on the program output (i.e.,
-oracle). Thus, testers are encouraged to design test sets that cause all
-statements to be executed and generate outputs that are different from the
-program under test.
-
-Mozilla's Lithium takes as input a function of interest that can be designed
-according to the problem to be solved. The function of interest determines if
-the test case output is interesting or not. Our function simply compares the
-failing test output with the output obtained when re-running again the failing
-test after deleting the slice, as explained in Section~\ref{sec:slicing}. Thus,
-if the initial test output is the same as the one after removing the slice
-\{$c_2$,$c_5$\}, then the slice is removed. This means that the slice is not
-necessary to reveal the fault because if removed the test output is still the
-same. The output is extracted from the stacktrace obtained through the failing
-test execution. The stacktrace provides information not only about the place
-where the fault was revelead but also the path taken to get there. Thus, our
-approach considers not only the exception caught by the failing test but also
-the path that was taken to reveal the fault. The following provides an example:
-
-\vspace{3mm}
-\begin{myframe} \label{box:1}
-junit.framework.AssertionFailedError, \\
-at junit.framework.Assert.fail(Assert.java:55), \\
-at junit.framework.Assert.assertTrue(Assert.java:22), \\
-at junit.framework.Assert.assertFalse(Assert.java:39), \\
-at junit.framework.Assert.assertFalse(Assert.java:47), \\
-at junit.framework.TestCase.assertFalse(TestCase.java:219), \\
-at org.jfree.chart.util.junit.ShapeUtilitiesTests.\\testEqualGeneralPaths(ShapeUtilitiesTests.java:212), \\
-...
-\end{myframe}
-
-Considering some of the stacktrace information about the path taken to reveal
-the fault solved the issue of generic oracles (e.g., NPE or generic
-AssertionFailedError expections as the one presented before) mentioned in
-Theorem~\ref{the:1}. There are faults whose outputs could slightly differ from
-one execution to another. For example, exceptions including information of
-memory addresses. For these cases, it was developed a mechanism to compare the
-rest of the output ignoring the identifier of the memory address. This heuristic
-also handles StackOverflow oracles.
 %

### 2019-02-22 paper/ijcai/paper.tex
rw comment

@@
 \section{Related Work}
-\Rui{needs work...}
+\Rui{Introductory sentences should say something like: model-based software
+debugging, from the DX community, has been shown to be similar to slicing
+Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
+interesting techniques having been pursued because of scalability. We have
+achieved it with a type of program slicing --- critical slicing. Next, we
+visit the previous works on program slicing and SFL, without the idea of
+being exhaustive, but merely discussing the works that we deem relevant for
+this paper.}
+
+\Rui{revisit sentences; check if recent papers are cited.}
 
@@
 methodology.
-
+%
 \section{Conclusions and Future Work}

### 2019-02-22 paper/ijcai/paper.tex
adjust margins
more fixes

@@
 statements. Results indicate that \ds{} misses faulty statements in
-only 9\%\comments{(23 misses)} of the 260 cases\Mar{we are using
-  \numFaults{} in the paper. please, revise and use macros.} and that
+ 12.7\%\comments{(33 misses)} of the \numFaults{} cases and that
 the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
@@
 addressing the issues from prior work. The study we conducted involves
-\numFaults{}\Mar{check} faults from \numPrograms{}\Mar{check}
+\numFaults{} faults from \numPrograms{}
 different programs from the Defects4J (D4J)
@@
 We used the \dfj{} benchmark in our experiments~\cite{just-defects4j-issta2014}.
-This benchmark includes six different subjects and \numFaults{} faults (Table
+Originally, this benchmark includes six different subjects and 395 faults (Table
 \ref{tab:df4j}). \lang{} is a library that provides a set of helper utilities
@@
 \begin{figure}[h]
-	\vspace{-1.5cm}
+  \vspace{-0.5cm}
 
@@
 		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
-		\vspace{-1cm}
+		\vspace{-0.75cm}
 		\caption{Faults of omissions' distribution}
@@
 
+We observed that $33$ of the $260$ faulty versions do not include the
+faulty statements in the slicer report after slicing.
 As observed in~\ref{table:fsws}, \combpar{k}
 finds the faulty statements faster than \sfl{}$^{k}$.
-
-We observe that $33$ of the $260$ faulty versions do not include the
-faulty statements in the slicer report after slicing.
 

### 2019-02-22 paper/ijcai/paper.tex
organizing and polishing text (moving to eval)

@@
 dataset~\cite{just-defects4j-issta2014}, which is frequently used to
-evaluate fault localization research. The study covers the following
-research questions:
-
-%% The goal of this paper is to reassess whether the \comb{} approach yields
-%% promising results under a more rigorous experimental methodology and a larger
-%% dataset.\comments{The D4J dataset is about twice as large than the biggest test
-%% suite used in previous studies.}
-
-\newcommand{\rqone}{How often does DS miss faulty statements?}
-\newcommand{\rqthree}{How effective is the \comb{} approach?}
-
-\begin{itemize}[leftmargin=*]
-\item[]{\footnotesize[(un)soundness]}~\textit{\rqone{}}
-\item[]{\footnotesize[effectiveness]}~\textit{\rqthree{}}
-\end{itemize}
-
-The first question addresses the problem that affects all dynamic
-slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}--that of
-missing faulty statements. Naturally, the consequence of that problem
-for debugging is that developers would never be able to locate
-faults. Different slicers can miss faulty statements for different
-reasons. In this paper, we used Critical
-Slicing~\cite{DeMillo:1996:CSS:229000.226310}, which, in principle,
-could miss statements because of imprecise oracles that guide the
-slicing process.\comments{ We evaluated how often that issue manifests
-  in our experiments.} The second research question evaluates the
-impact of the combination. To sum, our results show that the
-combination of the two approaches improves the accuracy of fault
-localization on average by \avgImprov\ in 51\% of the studied faults.
-
-The contributions of this work are: 1)~an empirical study, using
-real-world applications and bugs, on the combination of \ds{} and
-\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
-tool that implements the combination of \ds{} with \sfl{}, coined
-\comb{}.  The tool as well as a replication package will be available
-once double-blind requirements are lifted.
+evaluate fault localization research. The contributions of this work
+are: 1)~an empirical study, using real-world applications and bugs, on
+the combination of \ds{} and \sfl{} for bug localization of
+\emph{Java} faulty programs and 2)~a tool that implements the
+combination of \ds{} with \sfl{}, coined \comb{}.  The tool as well as
+a replication package will be available once double-blind requirements
+are lifted.
 
@@
 
-\section{Background}
-\label{sec:background}
+%\section{Background}
+%This section summarizes the ground concepts of our approach.
 
-This section summarizes the ground concepts of our approach.
-
-\subsection{Dynamic Slicing (\ds{})}
+\section{Dynamic Slicing (\ds{})}
+%\label{sec:background}
 \label{sec:slicing}
@@
 
-\subsection{Spectrum-based Fault Localization (\sfl)}
+\section{Spectrum-based Fault Localization (\sfl)}
 \label{sec:sfl}
@@
 components likely to be in
-fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
+fault~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
 following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$
@@
 \label{sec:approach}
-
-This section provides details on the proposed approach, \combpar{}, that combines
-\ds{} with \sfl{}; it also discusses the oracle problem.
-
-\subsection{Combining \ds{} and \sfl{}}
 \label{sec:comb}
 
-To illustrate the idea behind the combination of \sfl{} with \ds{}, consider a
-debugging scenario with five components $c_{1..5}$ and five
-transactions $t_{1..5}$, two of which are failing. Consider,
-additionally, that the component $c_2$ is faulty.
-Figure~\ref{fig:illustration} shows, at the left-hand side of the
-arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
-ranking, produced with the Ochiai predictor. Each line in the ranking
-shows, respectively, the rank/position, the component label, and the
-Ochiai score (in parentheses).
+This section describes \combpar{}, a technique where \ds{} and \sfl{}
+work in tandem to solve the fault localization problem. To illustrate
+the idea behind \combpar{}, consider a debugging scenario with five
+components $c_{1..5}$ and five transactions $t_{1..5}$, two of which
+are failing. Consider, additionally, that the component $c_2$ is
+faulty.  Figure~\ref{fig:illustration} shows, at the left-hand side of
+the arrow ($\Rightarrow$), an hypothetical spectra and its
+corresponding ranking, produced with the Ochiai predictor. Each line
+in the ranking shows, respectively, the rank/position, the component
+label, and the Ochiai score (in parentheses).
 
@@
 
-In the following, we illustrate the workflow of the \comb{}
-approach for this scenario. \comb{} uses a granularity of statements.
-First, the combined technique picks statements $c_4$ and $c_3$, which
-appear at the top of the ranking, for further analysis.
-(The cutoff point is user-defined.) Second, the
-technique picks a failing test $t_2$ to slice the code. A slice is a
-set of statements. Let us assume
-that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
-\ie, it excludes statements $c_4$ and $c_3$. Finally, the spectra and
-ranking are updated. The right-side of Figure~\ref{fig:illustration}
-shows the modified spectra and ranking after slicing test $t_2$
-against $c_4$ and $c_3$. It is worth noting that the technique slices
-the code for every failing tests. More precisely, the workflow of the
-\comb{} approach consists of four steps:
+We illustrate the workflow of the \comb{} approach for this scenario
+in the following. Let us analyze components at the granularity of
+statements.  First, \comb{} picks the first two statements at the top
+of the ranking, $c_4$ and $c_3$, for further analysis.  (The cutoff
+point is user-defined.) Second, the technique picks a failing test to
+slice the code, say $t_2$. A slice is a set of statements. Let us
+assume that the slice obtained for the transaction $t_2$ is $\{c_2,
+c_5\}$, \ie, it excludes statements $c_4$ and $c_3$ that were
+previously covered by the test. Finally, the spectra and ranking are
+updated. The right-side of Figure~\ref{fig:illustration} shows the
+modified spectra and ranking after slicing the code against $t_2$. It
+is worth noting that the technique slices the code for every failing
+tests. Intuitively, slicing enables the identification of statements
+in the spectra whose values can be set to zero, \ie{}, the components
+marked with $0$ are irrelevant to determine the test output.
+
+Let us now observe the effect of this spectra modification on the
+ranking. Analyzing the Ochiai formula, one observes that, for the
+components $j$, which are not part of the slice of a failing test, the
+combination reduces the value of $\N{11}$ and increases the value of
+$\N{01}$. Therefore, suspiciousness of those components
+decrease. Similar argument applies to other fault predictors. In the
+running example from Figure~\ref{fig:illustration}, the components
+$c_3$ and $c_4$, which are not in the slice of $t_2$, have their
+suspiciousness reduced, enabling the faulty component $c_2$ to rise
+from the third to the first position in the ranking.
+
+\vspace{1ex}
+To sum, the workflow of \comb{} consists of four steps:
 \begin{enumerate}
@@
   \item\label{step:group} Assemble all the resulting slicers of each failing test;
-  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
-    the slices of each failing test obtained in Step~\ref{step:group} and
-	recompute ranking.
+  \item Adjust spectra $S$, from step~\ref{step:spectra}, with
+    the slices of each failing test, from
+    step~\ref{step:group}, and then
+	recompute the ranking.
 \end{enumerate}
-
-Intuitively, slicing enables the identification of statements in the spectra
-whose values can be set to zero, \ie{}, the components marked with $0$
-are irrelevant to determine the test output. Let us now observe the
-effect of this spectra modification on the ranking. Analyzing the
-Ochiai formula, one observes that, for the components $j$ which are
-not part of the slice of a failing test, the combination reduces the
-value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
-suspiciousness of those components decrease. Similar argument applies
-to other fault predictors. In the running example,
-Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
-not in the slice of $t_2$, have their suspiciousness reduced, enabling
-the faulty component $c_2$ to rise from the third to the first
-position in the ranking.
 
@@
 \label{sec:eval}
+
+We studied the following research questions:
+
+%% The goal of this paper is to reassess whether the \comb{} approach yields
+%% promising results under a more rigorous experimental methodology and a larger
+%% dataset.\comments{The D4J dataset is about twice as large than the biggest test
+%% suite used in previous studies.}
+
+\newcommand{\rqone}{How effective is DS in eliminating code?}
+\newcommand{\rqtwo}{How often does DS miss faulty statements?}
+\newcommand{\rqthree}{How effective is \comb{} for bug localization?}
+
+\begin{itemize}[leftmargin=0em]
+\item[]{\textbf{RQ1.}}~\textit{\rqone{}}
+\item[]{\textbf{RQ2.}}~\textit{\rqtwo{}}
+\item[]{\textbf{RQ2.}}~\textit{\rqthree{}}
+\end{itemize}
+
+The first question \Fix{...elaborate...}
+The second question addresses the problem that affects all dynamic
+slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of
+missing faulty statements (see
+Section~\ref{sec:slicing}). Understanding that issue is important; the
+consequence for debugging is that developers would never be able to
+locate faults. The third research question evaluates the impact of the
+combination. To sum, our results show that the combination of the two
+approaches improves the accuracy of fault localization on average by
+\avgImprov\ in 51\% of the studied faults.
+
+%%  shows that CS can
+%% miss faulty statements because of imprecise oracles that guide the
+%% slicing process. 
+%% Different slicers can miss faulty statements for different
+%% reasons. In this paper, we used Critical
+%% Slicing~\cite{DeMillo:1996:CSS:229000.226310}, which, in principle,
+
 %

### 2019-02-22 paper/ijcai/paper.tex
more updates

--- 2019-02-22 paper/ijcai/paper.tex
@@
 statements. Results indicate that \ds{} misses faulty statements in
- 12.7\%\comments{(33 misses)} of the \numFaults{} cases and that
+ 9\%\comments{(23 misses)} of the \numFaults{} cases and that
 the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
@@
 		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
-	 Total      & 207  & 78.4\% & 217 & 83.0\%
-	 				& 227 & 83.8\% & 237 & 88.2\% & 260 \\
+	 Total      & 207  & 79.6\% & 217 & 83.5\%
+	 				& 227 & 87.3\% & 237 & 91.2\% & 260 \\
 		\bottomrule
 	\end{tabular}
-  \caption {Number of faults where at least one of the buggy-lines is in the \sfl{}$^{k}$ and \combpar{k} report}
+  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
   \label{table:fsws}
@@
 
-We observed that $33$ of the $260$ faulty versions do not include the
-faulty statements in the slicer report after slicing.
-As observed in~\ref{table:fsws}, \combpar{k}
-finds the faulty statements faster than \sfl{}$^{k}$.
+In~\ref{table:fsws}, we observe that
+
+\combpar{k}
+finds the faulty statements faster than \sfl{}$^{k}$. For both $k$ scenarios ($k=5$ or $k=10$), \combpar{k} performs better, i.e., it misses less faulty statements than \sfl{}$^{k}$.
+
+\combpar{k}The best scena $23$ of the $260$ ($8.8\%$) faults do not include the
+faulty statements in the slicer report after slicing the $10$ highest faulty classes.
 

### 2019-02-22 paper/ijcai/paper.tex
restruturação

@@
 \item[]{\textbf{RQ2.}}~\textit{\rqtwo{}}
-\item[]{\textbf{RQ2.}}~\textit{\rqthree{}}
+\item[]{\textbf{RQ3.}}~\textit{\rqthree{}}
 \end{itemize}
@@
 the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of
-the faults of this dataset are FOOs.
+the faults of this dataset are FOOs. \Sof{@todo: Explain better what are FOOs}
 
@@
 the ranking, he can say it is the faulty one.
-
-\subsection{Dynamic Slicing}\label{sec:ds}
-
-This subsection aims to report the performance of the \ds{} technique on slicing de
-faults of $5$ \dfj{} projects. Table \ref{tab:red}
-presents the reduction percentage obtained for each project after slicing the top
-$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction
-of 30.23\% in the projects considered in our study.
-
-\begin{table}[h]
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lcc}
-		\toprule
-		Project             &  \combpar{5}  & \combpar{10} \\
-		\midrule
-
-        \lang{}            & 1.40\% & 31.46\%\\
-        \cmath{}           & 10.30\% & 12.34\%\\
-        %\closure{}          &  & \\
-		\chart{}			& 59.30\% & 53.64\% \\
-        \jtime{}            & 17.27\% & 32.02\%\\
-        \mockito{}          & 16.54\% & 21.67\%\\
-
-		\bottomrule
-	\end{tabular}
-	\caption {\ds{} reduction for $k=5$ and $k=10$}
-	\label{tab:red}
-\end{table}
-\normalsize
 
@@
 the \combpar{k} evaluation  or (2) faults whose test outputs were not
-reproducible in the machine used to run the experiments. \textbf{RQ1} reviews
-one of the main issues of \ds{} - missing faulty statements - whereas
-\textbf{RQ2} discusses how effective is the \combpar{k} approach against
+reproducible in the machine used to run the experiments. \textbf{RQ1} evaluates how effective is \ds{} on reducing the test cases, \textbf{RQ2} reviews
+one of the main issues of \ds{} - missing faulty statements - and
+\textbf{RQ3} discusses how effective is the \combpar{k} approach against
 \sfl{}$^{k}$.
 
-\subsubsection{RQ1: \textit{How often does \ds{} misses faulty statements?}}
-\label{sec:fault-misses}
+\subsubsection{RQ1: \textit{\rqone}}
+\label{rq:1}
+
+This subsection aims to report the performance of the \ds{} technique on slicing de
+faults of $5$ \dfj{} projects. Table \ref{tab:red}
+presents the reduction percentage obtained for each project after slicing the top
+$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction
+of $30.23\%$ in the projects considered in our study.
+
+\begin{table}[H]
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lcc}
+		\toprule
+		Project             &  \combpar{5}  & \combpar{10} \\
+		\midrule
+
+        \lang{}            & 1.40\% & 31.46\%\\
+        \cmath{}           & 10.30\% & 12.34\%\\
+        %\closure{}          &  & \\
+		\chart{}			& 59.30\% & 53.64\% \\
+        \jtime{}            & 17.27\% & 32.02\%\\
+        \mockito{}          & 16.54\% & 21.67\%\\
+
+		\bottomrule
+	\end{tabular}
+	\caption {\ds{} reduction for $k=5$ and $k=10$}
+	\label{tab:red}
+\end{table}
+\normalsize
+
+\subsubsection{RQ2: \textit{\rqtwo}}
+\label{rq:2}
 
@@
 
-\subsubsection{RQ2: \textit{How effective is the \combpar{k} combination for bug localization?}}
+\subsubsection{RQ3: \textit{\rqthree}}
 

### 2019-02-22 paper/ijcai/paper.tex
RQ2 finished

@@
 \begin{table}[h]
+
   \centering
@@
 
-In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
+In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
 statements, since it is one of the main issues of dynamic slicing techniques. This
@@
 
-In~\ref{table:fsws}, we observe that
-
-\combpar{k}
-finds the faulty statements faster than \sfl{}$^{k}$. For both $k$ scenarios ($k=5$ or $k=10$), \combpar{k} performs better, i.e., it misses less faulty statements than \sfl{}$^{k}$.
-
-\combpar{k}The best scena $23$ of the $260$ ($8.8\%$) faults do not include the
-faulty statements in the slicer report after slicing the $10$ highest faulty classes.
-
-Using \combpar{10} we are able to find more $20$ faulty
-statements than when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$
-of the faulty statements whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty
-statements. Thus, \combpar{10} misses less $5.2\%$ of the faults against
-\sfl{}$^{10}$.
+In Table~\ref{table:fsws}, we observe that for both scenarios ($k=5$ and $k=10$), \combpar{k}
+finds the faulty statements faster than \sfl{}$^{k}$. 
+\sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., 
+\combpar{5} misses less $20$ ($7.7\%$) faults than \sfl{}$^{5}$.
+\sfl{}$^{10}$ finds $217$ ($83.5\%$) faults where as \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10} misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$.
+There is also a significant difference within each technique.
+Generally, the majority of faulty statements are found on the $5$ highest ranked faulty classes.
+There are few cases where the faulty statements are only find if the approach considers the first $10$ highest ranked faulty classes.
+\combpar{10} is the variant of our approach
+that performs better \textbf{missing only 23 out of 260 (8.8\%) cases}.
 
@@
 to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
-statements of the \dfj{} faults considered to the study after applying the both
-techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
+statements of the \dfj{} faults considered to the study after applying both
+techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.
+
+Figure
 $33$ of the $260$
-faulty versions do not include the faulty statements in the slicer report after slicing.
+faulty versions represent cases where we find 
 Thus, we report both values in Table~\ref{table:st}. In bold, we present the

### 2019-02-22 paper/ijcai/paper.tex
RQ3 - missing final discussion of APR

@@
 Generally, the majority of faulty statements are found on the $5$ highest ranked faulty classes.
-There are few cases where the faulty statements are only find if the approach considers the first $10$ highest ranked faulty classes.
-\combpar{10} is the variant of our approach
+There are few cases where the faulty statements are only find if the approach considers the first $10$ highest ranked faulty classes \combpar{10} is the variant of our approach
 that performs better \textbf{missing only 23 out of 260 (8.8\%) cases}.
@@
 
-In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
-to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
+In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} with \sfl{}
+to improve fault localization. For each fault, we calculated the cost of diagnosis 
+$\Delta{}C$ between \sfl{}$^{k}$ and \combpar{k} for both variants $k = 5$ and $k=10$.
+
+Figure \ref{fig:diagnosis} reports the cost of diagnosis of using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$,
+respectively. For $k=5$, we observe that in $30$ ($11.5\%$) of the faults
+the position of faulty statements decreases
+in the ranking, $97$($37.3\%$) of the faults the position of faulty statements increases in the rankinh whereas $133$ ($51.2\%$) of the faults the position of faulty stamenets remains the same.
+For $k=10$, we observe an increasing of $20$ cases where the position of faulty statements increases in the ranking $117$ ($45.0\%$).
+The number of cases whose faulty statements position remained the same are $110$ ($42.3\%$) and that suffered a decrease in the ranking is $33$ ($12.7\%$).
+
+Table~\ref{table:st}, reports the average rank of all faulty
 statements of the \dfj{} faults considered to the study after applying both
-techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.
+techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. $33$ of the $260$
+faulty versions are cases whose faulty statements decreased in the ranking list due to being a fault of omission case or due to limitations regarding the test design which \ds{} could not handle.
+Thus, we report both values in Table~\ref{table:st}.
+In bold, we present the
+results of the $227$ faults that do not contain the cases that are result of the limitations mentioned before. Inside parentheses, we present the
+rank results for all faults. The \combpar{k} combination yields an improvement
+of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
+Instead, if $k=10$ is considered the proposed approach returns an improvement of
+$6.1$ on the rank mean of all faulty statements.
+This $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none. Yet,
+if we only consider the faults ($116$) where there was improvement in at least 
+one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for 
+$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is very significant.
 
-Figure
-$33$ of the $260$
-faulty versions represent cases where we find 
-Thus, we report both values in Table~\ref{table:st}. In bold, we present the
-results of the $227$ faults that do not contain the cases where the faulty
-statements where removed using \combpar{k}. Inside parentheses, we present the
-rank results for all faults. The \combpar{k} combination yields an improvement
-of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
-Instead, if $K=10$ is considered the proposed approach returns an improvement of
-$11.1$ on the rank mean of faulty statements.
- Figure \ref{fig:diagnosis} reports the performance of the diagnosis
-using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
-respectively. Although this dataset has more than 50\% of fault of omissions,
-our simple slicing approach was capable of improving the ranking of $97$ for
-$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
+Although this dataset has more than $50\%$ of fault of omissions,
+our simple slicing approach was capable of improving the ranking of $95$ faults for
+$k=5$ and $115$ faults for $k=10$. Table \ref{table:st} presents the statistics
 to determine if the observed results are statistically significant. Shapiro-Wilk
 tests the null hypothesis that results are drawn from a normal distribution. The
-test is perfomed for all techniques and its variants. With 99\% of confidence,
+test is perfomed for all techniques and its variants. With $99\%$ of confidence,
 the results tell us that the distributions are not normal. Given that $C$ is not
@@
 Friedman. The null-hypothesis is that the ranking results of all techniques and
-variants are the same. With 99\% of confidence, the results show that the
-distributions are distinct. To understand if there is any relationship
-between the distributions,
+variants are the same. With $99\%$ of confidence, the results show that the
+distributions are distinct. To understand which techniques perform differently - i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
 we performed a Siegel post-hoc analysis. Figure
-\ref{fig:performance} reports the results of Siegel analysis for all the
-distributions. With 99\% of confidence, it is possible to see that in general
-the distributions are very similar. \Rui{so??}
+\ref{fig:performance} reports the results of Siegel analysis for all pairs of techniques.
+Each square represents the significance between the correspondent techniques, i.e., if it is significant it means that the techniques perform differently.
+With $95\%$ of confidence, it is possible to confirm that the performance of all techniques is different expect when comparing \combpar{5} with \combpar{10}.
 
@@
 		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
-		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$ respectively}
+		\caption{Cost of diagnosis of using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$, respectively}
 		\label{fig:diagnosis}

### 2019-02-22 paper/ijcai/paper.tex
another pass on initial section; finally going to eval

@@
 Unfortunately, they used a small set of subjects in their evaluation
-or archaic---often optimistic---methods to evaluate fault localization
+or over optimistic methods to evaluate fault localization
 improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
@@
 problem of assessing the effectiveness of combining \ds{} and \sfl{},
-addressing the issues from prior work. The study we conducted involves
-\numFaults{} faults from \numPrograms{}
-different programs from the Defects4J (D4J)
+addressing the key issues of prior work. We conducted a comprehensive
+study involving \numFaults{} faults from \numPrograms{} different
+programs from the Defects4J (D4J)
 dataset~\cite{just-defects4j-issta2014}, which is frequently used to
-evaluate fault localization research. The contributions of this work
-are: 1)~an empirical study, using real-world applications and bugs, on
-the combination of \ds{} and \sfl{} for bug localization of
-\emph{Java} faulty programs and 2)~a tool that implements the
-combination of \ds{} with \sfl{}, coined \comb{}.  The tool as well as
-a replication package will be available once double-blind requirements
-are lifted.
+evaluate fault localization research. Results show that \ds{} misses
+faulty statements in 9\%\comments{(23 misses)} of the \numFaults{}
+faults analyzed. Furthermore, we found that the combination of the two
+approaches improves fault localization in 51\% of the cases with an
+average improvement of \avgImprov. To sum, results indicate that the
+risk of applying the technique is relatively low for the positive
+impact it may bring and the tool implementing the technique works
+out-of-the-box, \ie{}, it puts no requirements on the running
+environment, subject programs it can be used, and requires no special
+setup.
+
+The contributions of this work are: 1)~an empirical study, using
+real-world applications and bugs, on the combination of \ds{} and
+\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
+tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination. The
+tool as well as a replication package will be available once
+double-blind requirements are lifted.
 
@@
 
-\begin{figure}[t!]
-
-  \centering
-  \begin{subfigure}{0.5\textwidth}
-    {\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
-      \begin{tabular}{c|ccccc|c}
-        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
-        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
-        $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
-        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
-        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
-        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
-        \hline
-      \end{tabular}
-      \quad
-      $\Rightarrow$
-      \quad
-      \begin{tabular}{c|ccccc|c}
-        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
-        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
-        $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
-        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
-        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
-        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
-        \hline
-      \end{tabular}
-    }
-    \caption{Spectra update.}
-    \label{fig:ds-reduction}
-  \end{subfigure}
-
-  \vspace{2ex}
-
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \begin{tabular}{cccccc}
-      1 & $c_4$ (0.59) & & 1 & $c_2$ (0.35) \\
-      2 & $c_3$ (0.55) & & 2.5 & $c_1$ (0.32)\\
-      3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
-      4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
-      4.5 & $c_5$ (0.32) & & 5 & $c_4$ (0.00)\\
-    \end{tabular}
-    \caption{Ranking update.}
-  \end{subfigure}
-
-  \caption{Modifications on spectra and ranking as result of slicing
-    code against test $t_2$. Double arrow ($\Rightarrow$) indicates
-    before and after.}
-  \label{fig:illustration}
-  \vspace{-2ex}
-\end{figure}
-
 We illustrate the workflow of the \comb{} approach for this scenario
@@
 
+\begin{figure}[t!]
+
+  \centering
+  \begin{subfigure}{0.5\textwidth}
+    {\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
+      \begin{tabular}{c|ccccc|c}
+        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
+        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
+        $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
+        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
+        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
+        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
+        \hline
+      \end{tabular}
+      \quad
+      $\Rightarrow$
+      \quad
+      \begin{tabular}{c|ccccc|c}
+        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
+        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
+        $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
+        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
+        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
+        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
+        \hline
+      \end{tabular}
+    }
+    \caption{Spectra update.}
+    \label{fig:ds-reduction}
+  \end{subfigure}
+
+  \vspace{2ex}
+
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \begin{tabular}{cccccc}
+      1 & $c_4$ (0.59) & & 1 & $c_2$ (0.35) \\
+      2 & $c_3$ (0.55) & & 2.5 & $c_1$ (0.32)\\
+      3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
+      4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
+      4.5 & $c_5$ (0.32) & & 5 & $c_4$ (0.00)\\
+    \end{tabular}
+    \caption{Ranking update.}
+  \end{subfigure}
+
+  \caption{Modifications on spectra and ranking as result of slicing
+    code against test $t_2$. Double arrow ($\Rightarrow$) indicates
+    before and after.}
+  \label{fig:illustration}
+  \vspace{-2ex}
+\end{figure}
+
 %
@@
 
-The first question \Fix{...elaborate...}
-The second question addresses the problem that affects all dynamic
-slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of
-missing faulty statements (see
-Section~\ref{sec:slicing}). Understanding that issue is important; the
-consequence for debugging is that developers would never be able to
-locate faults. The third research question evaluates the impact of the
-combination. To sum, our results show that the combination of the two
-approaches improves the accuracy of fault localization on average by
-\avgImprov\ in 51\% of the studied faults.
+The first question evaluates the ability of dynamic slicing reducing
+application code. Improvements on fault localization depends on that
+ability. The second question addresses the problem that affects all
+dynamic slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that
+of missing faulty statements (see
+Section~\ref{sec:slicing}). Developers would not be able to
+successfully debug code if that issue is manifested. The third
+research question evaluates the impact of the combination as
+substantiated by \comb.
 
@@
 
+\Fix{
+The main lesson of this work is that
+fault localization research should consider compare new techniques
+against this combination.}
+
 Several approaches have been proposed in the literature to improve debugging

### 2019-02-22 paper/ijcai/paper.tex
up to 5.2 (excluding)

@@
     \begin{tabular}{cccccc}
-      1 & $c_4$ (0.59) & & 1 & $c_2$ (0.35) \\
-      2 & $c_3$ (0.55) & & 2.5 & $c_1$ (0.32)\\
+      {\cellcolor{Gray}1} & {\cellcolor{Gray}$c_4$ (0.59)} & & 1 & $c_2$ (0.35) \\
+      {\cellcolor{Gray}2} & {\cellcolor{Gray}$c_3$ (0.55)} & & 2.5 & $c_1$ (0.32)\\
       3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
-      4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
-      4.5 & $c_5$ (0.32) & & 5 & $c_4$ (0.00)\\
+      4.5 & $c_1$ (0.32) & & {\cellcolor{Gray}4} & {\cellcolor{Gray}$c_3$ (0.29)}\\
+      4.5 & $c_5$ (0.32) & & {\cellcolor{Gray}5} & {\cellcolor{Gray}$c_4$ (0.00)}\\
     \end{tabular}
@@
 
-The first question evaluates the ability of dynamic slicing reducing
-application code. Improvements on fault localization depends on that
-ability. The second question addresses the problem that affects all
-dynamic slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that
-of missing faulty statements (see
-Section~\ref{sec:slicing}). Developers would not be able to
-successfully debug code if that issue is manifested. The third
-research question evaluates the impact of the combination as
-substantiated by \comb.
+The first question evaluates the ability of dynamic slicing to reduce
+the size of application code. Improvements on fault localization
+depend on that ability. The second question addresses the problem that
+affects all dynamic slicing
+techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of missing
+faulty statements (see Theorem~\ref{the:1}). Developers would
+not be able to successfully debug code for the cases that issue is
+manifested. The third research question evaluates the impact of the
+combination, as substantiated by \comb, to fault localization.
 
@@
 %
-To evaluate our approach, we compare the cost of diagnosing
-a collection of faults using \sfl{} versus \comb{}.
 %
@@
 
-We used the \dfj{} benchmark in our experiments~\cite{just-defects4j-issta2014}.
-Originally, this benchmark includes six different subjects and 395 faults (Table
-\ref{tab:df4j}). \lang{} is a library that provides a set of helper utilities
-for the {\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
-self-contained mathematics and statistics components. The \closure{} is a
-toolset for turning JavaScript files into smaller scripts for faster download
-and execution in the browser. \chart{} is a Java library for creating charts.
-\jtime{} is a lightweight library that aims to replace the default Java
-{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is a
-mocking testing framework.
+We used subject programs from the \dfj{}
+benchmark~\cite{just-defects4j-issta2014} in our evaluation.
+Table~\ref{tab:df4j} shows size, number of tests, and number of
+faults, for each considered program.
 
-\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
 \begin{table}[h]
-
+  \small  
   \centering
@@
     \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
-      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
+    %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
     \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
@@
   \caption {Characterization of \dfj{} subjects.}
-
   \label{tab:df4j}
@@
 
-\begin{figure}[h]
-  \vspace{-0.5cm}
+\lang{} is a
+library that provides a set of helper utilities for the
+{\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
+self-contained mathematics and statistics components.\comments{ The
+  \closure{} is a toolset for turning JavaScript files into smaller
+  scripts for faster download and execution in the browser.} \chart{}
+is a Java library for creating charts.  \jtime{} is a lightweight
+library that aims to replace the default Java
+{\small\texttt{java.util.Date}} classes providing simpler
+APIs. \mockito{} is a mocking testing framework.
 
-		\centering
-		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
-		\vspace{-0.75cm}
-		\caption{Faults of omissions' distribution}
-		\label{fig:foos}
-\end{figure}
+%% Originally, this benchmark includes six different subjects and 395
+%% faults (Table \ref{tab:df4j}).
 
-Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in
-the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of
-the faults of this dataset are FOOs. \Sof{@todo: Explain better what are FOOs}
+%%%%%%%%%%%%%%%%%%%%% I commented because there are just two cases;
+%%%%%%%%%%%%%%%%%%%%% not much information added (that could not be
+%%%%%%%%%%%%%%%%%%%%% said in text). -Marcelo
+%% \begin{figure}[h]
+%%   \vspace{-0.5cm}
+%% 		\centering
+%% 		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
+%% 		\vspace{-0.75cm}
+%% 		\caption{Faults of omissions' distribution}
+%% 		\label{fig:foos}
+%% \end{figure}
+
+As to quantify complexity of fault localization on this dataset, we
+additionally counted the number of cases of ``fault of omission'', a
+popular metric in fault localization research for that
+purpose~\Fix{cite}. A fault of omission occurs when
+\Fix{...explain...}. Intuitivelly, the ability of techniques to
+produce good diagnosis in those cases reduce as \Fix{...explain...}. A
+total of $59.7\%$ of the cases in this dataset manifest fault of
+omission, which is a good indication of difficulty.
+
+%in producing
+%high-qualitiy diagnosis.
 
 \subsection{Experimental Methodology}\label{sec:methodology}
+
+\Fix{
+To evaluate our approach, we compare the cost of diagnosing
+a collection of faults using \sfl{} versus \comb{}.
+}
 
@@
 \begin{table}[H]
+  \small
 	\centering

### 2019-02-22 paper/ijcai/paper.tex
pass on 5.2

@@
 
-\subsection{Experimental Methodology}\label{sec:methodology}
+%\subsection{Experimental Methodology}
+%\label{sec:methodology}
 
-\Fix{
-To evaluate our approach, we compare the cost of diagnosing
-a collection of faults using \sfl{} versus \comb{}.
-}
+\subsection{Techniques}
+One important independent variable for this study is the scope of
+dynamic slicing. Slicing the entire code would be unacceptably
+expensive as Critical Slicing needs to re-compile the affected file at
+every iteration, \ie{}, after deleting statements and before checking
+the oracle (see Section~\ref{sec:slicing}). We control the scope of
+slicing through the variable $k$, which denotes the number of distinct
+files that dynamic slicing will minimize. In this study, we used 5 and
+10 as the values of $k$. The $k$ files for minimization are selected
+from the \sfl{} ranking as follows. First, we build a rank of files by
+determining, for each ranked statement, the file that declares
+it. Then, we select the top $k$ distinct files from such file ranking.
 
-To evaluate the effectiveness of \comb{}, following related work, we compared
-its performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
-where $k$ is the number of classes comprising the highest faulty statements.
-These classes are obtained directly from the ranking which is calculated through
-\sfl{}. For each fault, spectra is updated and the fault ranking is
-re-calculated but only considering the $k$ highest faulty classes. We refer to
-these variations as SFL$^{k}$. After slicing each class of the top $k$ of the
-highest faulty classes for each fault, the initial spectra is updated based on
-the slicer output and the fault ranking is re-calculated. We refer to these
-variations as \combpar{k}. We compared \combpar{5} and \combpar{10} against
-\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
-C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
-diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
-that the position of the faulty statement has decreased in the ranking after
-applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
-$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
-$\Delta C=0$ means that the faulty statement remained in the same position.  We
-also assume a perfect bug understanding, i.e., if the developer sees the bug in
-the ranking, he can say it is the faulty one.
+The techniques we evaluate in this study are \combpar{k} and
+SFL$^{k}$, which is the comparison baseline. \combpar{k} is as defined
+in Section~\ref{sec:approach} (see Step 2 of the workflow) whereas
+SFL$^{k}$ is as SFL, but it produces a ranking including exclusively
+the statements from the best-$k$ ranked files.
 
-\subsection{Results and Discussion}
+%% To evaluate the effectiveness of \comb{}, following related work, we compared
+%% its performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
+%% where $k$ is the number of classes comprising the highest faulty statements.
+%% These classes are obtained directly from the ranking which is calculated through
+%% \sfl{}.
+
+%% For each fault, spectra is updated and the fault ranking is
+%% re-calculated but only considering the $k$ highest faulty classes. We refer to
+%% these variations as SFL$^{k}$. After slicing each class of the top $k$ of the
+%% highest faulty classes for each fault, the initial spectra is updated based on
+%% the slicer output and the fault ranking is re-calculated. We refer to these
+%% variations as \combpar{k}.
+
+\subsection{Results}
+
+\Mar{--------------------------- estou aqui}
+
+This section addresses the research questions we posed.
+
+%% proposed and discuss the
+%% results obtained. Our approach was capable of slicing a total of $260$ faults
+%% from $5$ different  projects.
+%% \textbf{RQ1} evaluates how effective is \ds{} on reducing the test cases, \textbf{RQ2} reviews
+%% one of the main issues of \ds{} - missing faulty statements - and
+%% \textbf{RQ3} discusses how effective is the \combpar{k} approach against
+%% \sfl{}$^{k}$.
 
@@
 \end{table*}
-
-In this section, we answer the research questions proposed and discuss the
-results obtained. Our approach was capable of slicing a total of $260$ faults
-from $5$ different  projects. The remaining faults were not considered because
-(1) faults belong to the \closure{} project which requires high CPU to perform
-the \combpar{k} evaluation  or (2) faults whose test outputs were not
-reproducible in the machine used to run the experiments. \textbf{RQ1} evaluates how effective is \ds{} on reducing the test cases, \textbf{RQ2} reviews
-one of the main issues of \ds{} - missing faulty statements - and
-\textbf{RQ3} discusses how effective is the \combpar{k} approach against
-\sfl{}$^{k}$.
 
@@
 \subsubsection{RQ3: \textit{\rqthree}}
+
+\Mar{metric only used here...revise}
+\Fix{
+We compared \combpar{5} and \combpar{10} against
+\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
+C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
+diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
+that the position of the faulty statement has decreased in the ranking after
+applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
+$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
+$\Delta C=0$ means that the faulty statement remained in the same position.  We
+also assume a perfect bug understanding, i.e., if the developer sees the bug in
+the ranking, he can say it is the faulty one.
+}
 
@@
 \subsection{Threats to validity}
+
+\Mar{incorporate this here. we were presenting this too early (initial
+  par. of results). not very appealing ;)}
+\Fix{
+The remaining faults were not considered because
+(1) faults belong to the \closure{} project which requires high CPU to perform
+the \combpar{k} evaluation  or (2) faults whose test outputs were not
+reproducible in the machine used to run the experiments.
+}
+
 %

### 2019-02-22 paper/ijcai/paper.tex
pass on RQ1

@@
 \label{sec:slicing}
-
+\Sof{Falar de model-based diagnosis}\Rui{important to connect to the AI
+community --- we are submitting this to ijcai.}
 Program slicing is a program understanding technique to identify the
@@
     \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
-    \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
+    \cmath{}           & 306,276  & 26,797 & 104     \\   %\comments{& 177   &  -}\\
     %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
@@
 it. Then, we select the top $k$ distinct files from such file ranking.
+\Rui{we should say that k follows from typical SFL metrics (top k)}
 
@@
 
-\Mar{--------------------------- estou aqui}
-
-This section addresses the research questions we posed.
+This section answers the research questions.
 
@@
 
-\subsubsection{RQ1: \textit{\rqone}}
-\label{rq:1}
-
-This subsection aims to report the performance of the \ds{} technique on slicing de
-faults of $5$ \dfj{} projects. Table \ref{tab:red}
-presents the reduction percentage obtained for each project after slicing the top
-$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction
-of $30.23\%$ in the projects considered in our study.
+%% This subsection aims to report the performance of the \ds{} technique
+%% on slicing de faults of $5$ \dfj{} projects.
+
+\subsubsection{\label{rq:1}RQ1: \textit{\rqone}}
+
+A necessary but insufficient condition for improvement of fault
+localization with \comb{} is that dynamic slicing eliminates a high
+amount of code in the best ranked files. Table \ref{tab:red} shows, as
+percentages, the average reduction on the sum of top file sizes
+obtained with dynamic slicing for different values of
+$k$.\Mar{$\leftarrow$sofia, please check.} Overall, results indicate
+that dynamic slicing substantially reduces the size of highly-ranked
+files. \Mar{sofia, it would be more convincing if you (additionally)
+  show reduction wrt to the the parts of the file that are covered.}
+
+%% obtained for each project after slicing the top $5$ and
+%% $10$ of classes comprising the highest faulty statements. We observed
+%% a reduction of $30.23\%$ in the projects considered in our study.
 
@@
 	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lcc}
+	\begin{tabular}{lrr}
 		\toprule
-		Project             &  \combpar{5}  & \combpar{10} \\
+		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
 		\midrule
 
-        \lang{}            & 1.40\% & 31.46\%\\
-        \cmath{}           & 10.30\% & 12.34\%\\
+        \lang{}            & 1.40 & 31.46\\
+        \cmath{}           & 10.30 & 12.34\\
         %\closure{}          &  & \\
-		\chart{}			& 59.30\% & 53.64\% \\
-        \jtime{}            & 17.27\% & 32.02\%\\
-        \mockito{}          & 16.54\% & 21.67\%\\
+		\chart{}			& 59.30 & 53.64 \\
+        \jtime{}            & 17.27 & 32.02\\
+        \mockito{}          & 16.54 & 21.67\\
 
@@
 	\end{tabular}
-	\caption {\ds{} reduction for $k=5$ and $k=10$}
+	\caption {\ds{} reduction, as percentages. Higher is better.}
 	\label{tab:red}
@@
 \label{rq:2}
+
+\Mar{-------------------- estou aqui}
 
@@
 one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for
-$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is very significant.
+$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is significant.
 
@@
 the results tell us that the distributions are not normal. Given that $C$ is not
-normally distributed, we use the non-parametrical statistical hypothesis test,
+normally distributed, we use the non-parametrical statistical hypothesis test
 Friedman. The null-hypothesis is that the ranking results of all techniques and

### 2019-02-23 paper/ijcai/paper.tex
small fixes

--- 2019-02-22 paper/ijcai/paper.tex
@@
 \label{sec:slicing}
-
+\Sof{Falar de model-based diagnosis}
 Program slicing is a program understanding technique to identify the
@@
 one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for 
-$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is very significant.
+$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is significant.
 

### 2019-02-23 paper/ijcai/paper.tex
comment

@@
 \label{sec:slicing}
-\Sof{Falar de model-based diagnosis}
+\Sof{Falar de model-based diagnosis}\Rui{important to connect to the AI
+community --- we are submitting this to ijcai.}
 Program slicing is a program understanding technique to identify the

### 2019-02-23 paper/ijcai/paper.tex
another comment
pass on RQ2

--- 2019-02-22 paper/ijcai/paper.tex
@@
 
-\Mar{-------------------- estou aqui}
-
-In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
-statements, since it is one of the main issues of dynamic slicing techniques. This
-is particularly important because when \ds{} misses a faulty statement
-means that it will not be in the diagnostic report and therefore has a negative
-impact in the fault localization accuracy. Table~\ref{table:fsws} presents the
-number of faults where at least one of the faulty statements appears in the
-final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
-we only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
-of the highest faulty classes.
-
-In Table~\ref{table:fsws}, we observe that for both scenarios ($k=5$ and $k=10$), \combpar{k}
-finds the faulty statements faster than \sfl{}$^{k}$.
-\sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e.,
-\combpar{5} misses less $20$ ($7.7\%$) faults than \sfl{}$^{5}$.
-\sfl{}$^{10}$ finds $217$ ($83.5\%$) faults where as \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10} misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$.
-There is also a significant difference within each technique.
-Generally, the majority of faulty statements are found on the $5$ highest ranked faulty classes.
-There are few cases where the faulty statements are only find if the approach considers the first $10$ highest ranked faulty classes \combpar{10} is the variant of our approach
-that performs better \textbf{missing only 23 out of 260 (8.8\%) cases}.
+%% For automated debugging that
+%% means that it will not be in the diagnostic report and therefore has a negative
+%% impact in the fault localization accuracy.
+
+%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
+%% statements, since it is one of the main issues of dynamic slicing techniques. This
+%% is particularly important because when \ds{} misses a faulty statement
+
+%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
+
+A fundamental issue of purely dynamic slicing techniques, critical
+slicing in particular, is the risk of discarding faulty statements
+(see Section~\ref{sec:slicing}). This research question evaluates the
+practical impact of this conceptual issue. Table~\ref{table:fsws}
+presents the number of faults where at least one of the faulty
+statements appears in the final reports.\Mar{$\leftarrow$this seems a
+  sensible choice that needs reasonable (to-the-point)
+  justification. is there a rationale for this?  if not, was this
+  choice used in other study? if yes, just say it was used and cite.}
+More precisely, we look for faulty statements in the top 5 and 10 most
+suspicious classes (as per the file ranking).
+
+\Mar{CRITICAL: Sofia, I am really confused here. Is there a reason for
+  why you chose not to show the proportion of cases where **DS** (not
+  SFL(k) or \combpar{k}) includes the faulty statement? Wouldn't it be
+  sufficient and simpler/clearer answering this question in terms of
+  DS for k=5,10? (Note that the question is about DS.) On a similar
+  note, considering this metric, I don't understand how SFL(k) can
+  produce different result compared to \combpar{k}. I thought the
+  difference in this case would only be the position in the
+  ranking. This is counter-intuitive and needs a good explanation.}
+Table~\ref{table:fsws} compares \sfl{}$^{k}$ and \combpar{k} with
+respect to the metric number of cases where a faulty statement appears
+in the ranking. Results show that \combpar{k} finds the faulty
+statements \Fix{faster}\Mar{faster? chose another word.} than
+\sfl{}$^{k}$.\Mar{I will revise the rest of this par. when I
+  understand what is going on here...}  \sfl{}$^{5}$ finds $207$
+($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults
+for $k=5$, i.e., \combpar{5} misses $20$ ($7.7\%$) less faults
+compared to \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults
+whereas \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e.,
+\combpar{10} misses less $20$ ($7.7\%$) faults than
+\sfl{}$^{10}$. There is also a significant difference within each
+technique. Generally, the majority of faulty statements are found on
+the $5$ highest ranked faulty classes. There are few cases where the
+faulty statements are only found if the approach considers the first
+$10$ highest ranked faulty classes \combpar{10} is the variant of our
+approach that performs better \textbf{missing only 23 out of 260
+  (8.8\%) cases}.
 
 \subsubsection{RQ3: \textit{\rqthree}}
+
+\Mar{---------------------- I am here}
 

### 2019-02-23 paper/ijcai/paper.tex
initial pass on RQ3

@@
 
-\begin{table*}[h]
+\begin{table*}[t!]
 	\small
@@
 
+In \textbf{RQ3}, we evaluate the effective impact of combining \ds{}
+with \sfl{} to improve fault localization.
+
+The first experiment we ran to assess impact consisted of measuring
+the \emph{difference of diagnosis cost}. This metric has been
+previously used in other studies~\Fix{cite cite}. More specifically,
+we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
+C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
+obtained by computing the mean position in the ranking of all buggy
+statements. $\Delta C >0$ means that the position of the faulty
+statement has decreased with \combpar{k}, \ie{}, the combination had a
+positive impact. $\Delta C <0$ means that \combpar{k} performs worse
+compared to its baseline. That could happen if dynamic slicing misses
+the faulty statement---the statements not included in the slice will
+have their suspiciousness scores reduced and ranks potentially
+reduced. $\Delta C=0$ means that the faulty statement remained in the
+same position.  It is worth noting that we assume a perfect bug
+understanding, i.e., if the developer sees the bug in the ranking, he
+is able to precisely determine if it is the faulty one.
+
+\Mar{I see there are different results/metrics/tables. We need to
+  organize this better, with sub-questions or stating different
+  other experiments to answer the main question.}
+
 \Mar{---------------------- I am here}
-
-\Mar{metric only used here...revise}
-\Fix{
-We compared \combpar{5} and \combpar{10} against
-\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
-C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
-diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
-that the position of the faulty statement has decreased in the ranking after
-applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
-$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
-$\Delta C=0$ means that the faulty statement remained in the same position.  We
-also assume a perfect bug understanding, i.e., if the developer sees the bug in
-the ranking, he can say it is the faulty one.
-}
-
-In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} with \sfl{}
-to improve fault localization. For each fault, we calculated the cost of diagnosis
-$\Delta{}C$ between \sfl{}$^{k}$ and \combpar{k} for both variants $k = 5$ and $k=10$.
 

### 2019-02-23 paper/ijcai/paper.tex
new table
pass on RQ2

@@
 
+%% This subsection aims to report the performance of the \ds{} technique
+%% on slicing de faults of $5$ \dfj{} projects.
+
+\subsubsection{\label{rq:1}RQ1: \textit{\rqone}}
+
+A necessary but insufficient condition for improvement of fault
+localization with \comb{} is that dynamic slicing eliminates a high
+amount of code in the best ranked files. Table \ref{tab:red} shows, as
+percentages, the average reduction on the sum of top file sizes
+obtained with dynamic slicing for different values of
+$k$.\Mar{$\leftarrow$sofia, please check.} Overall, results indicate
+that dynamic slicing substantially reduces the size of highly-ranked
+files. \Mar{sofia, it would be more convincing if you (additionally)
+  show reduction wrt to the the parts of the file that are covered.}
+
+%% obtained for each project after slicing the top $5$ and
+%% $10$ of classes comprising the highest faulty statements. We observed
+%% a reduction of $30.23\%$ in the projects considered in our study.
+
+\begin{table}[H]
+  \small
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrr}
+		\toprule
+		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
+		\midrule
+
+        \lang{}            & 1.40 & 31.46\\
+        \cmath{}           & 10.30 & 12.34\\
+        %\closure{}          &  & \\
+		\chart{}			& 59.30 & 53.64 \\
+        \jtime{}            & 17.27 & 32.02\\
+        \mockito{}          & 16.54 & 21.67\\
+
+		\bottomrule
+	\end{tabular}
+	\caption {\ds{} reduction in file size (percentages). Higher is better.}
+	\label{tab:red}
+\end{table}
+\normalsize
+
+\subsubsection{RQ2: \textit{\rqtwo}}
+\label{rq:2}
+
+\begin{table}[H]
+  \small
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrr}
+		\toprule
+		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
+		\midrule
+
+        \lang{}            & 100 & 96.9\\
+        \cmath{}           & 89.4 & 95.2\\
+        %\closure{}          &  & \\
+		\chart{}			& 76.9 & 84.6 \\
+        \jtime{}            & 81.5 & 85.2\\
+        \mockito{}          & 71.1 & 78.9\\
+
+		\bottomrule
+	\end{tabular}
+	\caption {\ds{} performance on capturing faulty statements, as percentages.}
+	\label{tab:red}
+\end{table}
+\normalsize
+
+%% For automated debugging that
+%% means that it will not be in the diagnostic report and therefore has a negative
+%% impact in the fault localization accuracy.
+
+%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
+%% statements, since it is one of the main issues of dynamic slicing techniques. This
+%% is particularly important because when \ds{} misses a faulty statement
+
+%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
+
+A fundamental issue of purely dynamic slicing techniques is the risk
+of discarding faulty statements (see Section~\ref{sec:slicing}). This
+research question evaluates the practical impact of this conceptual
+issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
+dynamic slicing captures at least one of the faulty statements among
+the sliced files for different values of $k$. These numbers indicat
+that \Fix{...elaborate...}
+
+\begin{table}[H]
+  \small
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrr}
+		\toprule
+		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
+		\midrule
+
+        \lang{}            & - & -\\
+        \cmath{}           & - & -\\
+        %\closure{}          &  & \\
+		\chart{}			& - & - \\
+        \jtime{}            & - & -\\
+        \mockito{}          & - & -\\
+
+		\bottomrule
+	\end{tabular}
+	\caption {Percentages of cases \ds{} captures faults. Higher is better.}
+	\label{tab:ds-cases-captured}
+\end{table}
+\normalsize
+
+%% Table~\ref{table:fsws} presents the number of faults where at
+%% least one of the faulty statements appears in the final
+%% reports.\Mar{$\leftarrow$this seems a sensible choice that needs
+%%   reasonable (to-the-point) justification. is there a rationale for
+%%   this?  if not, was this choice used in other study? if yes, just say
+%%   it was used and cite.}  More precisely, we look for faulty
+%% statements in the top 5 and 10 most suspicious classes (as per the
+%% file ranking).
+%% \Mar{CRITICAL: Sofia, I am really confused here. Is there a reason for
+%%   why you chose not to show the proportion of cases where **DS** (not
+%%   SFL(k) or \combpar{k}) includes the faulty statement? Wouldn't it be
+%%   sufficient and simpler/clearer answering this question in terms of
+%%   DS for k=5,10? (Note that the question is about DS.) On a similar
+%%   note, considering this metric, I don't understand how SFL(k) can
+%%   produce different result compared to \combpar{k}. I thought the
+%%   difference in this case would only be the position in the
+%%   ranking. This is counter-intuitive and needs a good explanation.}
+
+To analyze the impact of dynamic slicing in context, we also compared
+\combpar{k} and \sfl{}$^{k}$ considering the same metric, \ie{}, the
+number of cases the fault is captured by the technique. Note that the
+reason \sfl{}$^{k}$ misses the fault is different compared to
+\combpar{k}. It captures the fault if the fault is included within the
+top $k$ files; it misses otherwise. Table~\ref{table:fsws} shows
+results, indicating that \combpar{k} performs better than \sfl{}$^{k}$
+on this metric.\Mar{my opinion is that we should not compare these two
+techniques here: 1) it is not the goal of this RQ and 2) this is not
+the best metric.} \sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas
+\combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., \combpar{5}
+misses $20$ ($7.7\%$) less faults compared to
+\sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults whereas
+\combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10}
+misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$. There is also a
+significant difference within each technique. Generally, the majority
+of faulty statements are found on the $5$ highest ranked faulty
+classes. There are few cases where the faulty statements are only
+found if the approach considers the first $10$ highest ranked faulty
+classes \combpar{10} is the variant of our approach that performs
+better \textbf{missing only 23 out of 260 (8.8\%) cases}.
+
 \begin{table*}[t!]
@@
 
-%% This subsection aims to report the performance of the \ds{} technique
-%% on slicing de faults of $5$ \dfj{} projects.
-
-\subsubsection{\label{rq:1}RQ1: \textit{\rqone}}
-
-A necessary but insufficient condition for improvement of fault
-localization with \comb{} is that dynamic slicing eliminates a high
-amount of code in the best ranked files. Table \ref{tab:red} shows, as
-percentages, the average reduction on the sum of top file sizes
-obtained with dynamic slicing for different values of
-$k$.\Mar{$\leftarrow$sofia, please check.} Overall, results indicate
-that dynamic slicing substantially reduces the size of highly-ranked
-files. \Mar{sofia, it would be more convincing if you (additionally)
-  show reduction wrt to the the parts of the file that are covered.}
-
-%% obtained for each project after slicing the top $5$ and
-%% $10$ of classes comprising the highest faulty statements. We observed
-%% a reduction of $30.23\%$ in the projects considered in our study.
-
-\begin{table}[H]
-  \small
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lrr}
-		\toprule
-		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
-		\midrule
-
-        \lang{}            & 1.40 & 31.46\\
-        \cmath{}           & 10.30 & 12.34\\
-        %\closure{}          &  & \\
-		\chart{}			& 59.30 & 53.64 \\
-        \jtime{}            & 17.27 & 32.02\\
-        \mockito{}          & 16.54 & 21.67\\
-
-		\bottomrule
-	\end{tabular}
-	\caption {\ds{} reduction, as percentages. Higher is better.}
-	\label{tab:red}
-\end{table}
-\normalsize
-
-\subsubsection{RQ2: \textit{\rqtwo}}
-\label{rq:2}
-
-%% For automated debugging that
-%% means that it will not be in the diagnostic report and therefore has a negative
-%% impact in the fault localization accuracy.
-
-%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
-%% statements, since it is one of the main issues of dynamic slicing techniques. This
-%% is particularly important because when \ds{} misses a faulty statement
-
-%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
-
-A fundamental issue of purely dynamic slicing techniques, critical
-slicing in particular, is the risk of discarding faulty statements
-(see Section~\ref{sec:slicing}). This research question evaluates the
-practical impact of this conceptual issue. Table~\ref{table:fsws}
-presents the number of faults where at least one of the faulty
-statements appears in the final reports.\Mar{$\leftarrow$this seems a
-  sensible choice that needs reasonable (to-the-point)
-  justification. is there a rationale for this?  if not, was this
-  choice used in other study? if yes, just say it was used and cite.}
-More precisely, we look for faulty statements in the top 5 and 10 most
-suspicious classes (as per the file ranking).
-
-\Mar{CRITICAL: Sofia, I am really confused here. Is there a reason for
-  why you chose not to show the proportion of cases where **DS** (not
-  SFL(k) or \combpar{k}) includes the faulty statement? Wouldn't it be
-  sufficient and simpler/clearer answering this question in terms of
-  DS for k=5,10? (Note that the question is about DS.) On a similar
-  note, considering this metric, I don't understand how SFL(k) can
-  produce different result compared to \combpar{k}. I thought the
-  difference in this case would only be the position in the
-  ranking. This is counter-intuitive and needs a good explanation.}
-Table~\ref{table:fsws} compares \sfl{}$^{k}$ and \combpar{k} with
-respect to the metric number of cases where a faulty statement appears
-in the ranking. Results show that \combpar{k} finds the faulty
-statements \Fix{faster}\Mar{faster? chose another word.} than
-\sfl{}$^{k}$.\Mar{I will revise the rest of this par. when I
-  understand what is going on here...}  \sfl{}$^{5}$ finds $207$
-($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults
-for $k=5$, i.e., \combpar{5} misses $20$ ($7.7\%$) less faults
-compared to \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults
-whereas \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e.,
-\combpar{10} misses less $20$ ($7.7\%$) faults than
-\sfl{}$^{10}$. There is also a significant difference within each
-technique. Generally, the majority of faulty statements are found on
-the $5$ highest ranked faulty classes. There are few cases where the
-faulty statements are only found if the approach considers the first
-$10$ highest ranked faulty classes \combpar{10} is the variant of our
-approach that performs better \textbf{missing only 23 out of 260
-  (8.8\%) cases}.
-
 \subsubsection{RQ3: \textit{\rqthree}}
@@
 variants are the same. With $99\%$ of confidence, the results show that the
-distributions are distinct. To understand which techniques perform differently - i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
+distributions are distinct. To understand which techniques perform differently 
+- i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
 we performed a Siegel post-hoc analysis. Figure

### 2019-02-23 paper/ijcai/paper.tex
pass on RQ2
minor tweaks on RQ2

@@
 
+%% For automated debugging that
+%% means that it will not be in the diagnostic report and therefore has a negative
+%% impact in the fault localization accuracy.
+
+%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
+%% statements, since it is one of the main issues of dynamic slicing techniques. This
+%% is particularly important because when \ds{} misses a faulty statement
+
+%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
+
+A fundamental issue of purely dynamic slicing techniques is the risk
+of discarding faulty statements (see Section~\ref{sec:slicing}). This
+research question evaluates the practical impact of this conceptual
+issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
+dynamic slicing captures at least one of the faulty statements among
+the sliced files for different values of $k$. These numbers indicat
+that \Fix{...elaborate...}
+
 \begin{table}[H]
@@
 	\end{tabular}
-	\caption {\ds{} performance on capturing faulty statements, as percentages.}
+	\caption {\ds{} performance on capturing faulty statements, as
+     percentages. Higher is better.}
 	\label{tab:red}
-\end{table}
-\normalsize
-
-%% For automated debugging that
-%% means that it will not be in the diagnostic report and therefore has a negative
-%% impact in the fault localization accuracy.
-
-%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
-%% statements, since it is one of the main issues of dynamic slicing techniques. This
-%% is particularly important because when \ds{} misses a faulty statement
-
-%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
-
-A fundamental issue of purely dynamic slicing techniques is the risk
-of discarding faulty statements (see Section~\ref{sec:slicing}). This
-research question evaluates the practical impact of this conceptual
-issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
-dynamic slicing captures at least one of the faulty statements among
-the sliced files for different values of $k$. These numbers indicat
-that \Fix{...elaborate...}
-
-\begin{table}[H]
-  \small
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lrr}
-		\toprule
-		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
-		\midrule
-
-        \lang{}            & - & -\\
-        \cmath{}           & - & -\\
-        %\closure{}          &  & \\
-		\chart{}			& - & - \\
-        \jtime{}            & - & -\\
-        \mockito{}          & - & -\\
-
-		\bottomrule
-	\end{tabular}
-	\caption {Percentages of cases \ds{} captures faults. Higher is better.}
    \label{tab:ds-cases-captured}   
@@
 
+%% \Mar{my
+%%   opinion is that we should not compare these two techniques here: 1)
+%%   it is not the goal of this RQ and 2) this is not the best metric.}
+
 To analyze the impact of dynamic slicing in context, we also compared
-\combpar{k} and \sfl{}$^{k}$ considering the same metric, \ie{}, the
-number of cases the fault is captured by the technique. Note that the
-reason \sfl{}$^{k}$ misses the fault is different compared to
-\combpar{k}. It captures the fault if the fault is included within the
-top $k$ files; it misses otherwise. Table~\ref{table:fsws} shows
-results, indicating that \combpar{k} performs better than \sfl{}$^{k}$
-on this metric.\Mar{my opinion is that we should not compare these two
-techniques here: 1) it is not the goal of this RQ and 2) this is not
-the best metric.} \sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas
-\combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., \combpar{5}
-misses $20$ ($7.7\%$) less faults compared to
-\sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults whereas
-\combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10}
-misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$. There is also a
-significant difference within each technique. Generally, the majority
-of faulty statements are found on the $5$ highest ranked faulty
-classes. There are few cases where the faulty statements are only
-found if the approach considers the first $10$ highest ranked faulty
-classes \combpar{10} is the variant of our approach that performs
-better \textbf{missing only 23 out of 260 (8.8\%) cases}.
+\combpar{k} and \sfl{}$^{k}$ considering the number of cases where the
+fault is captured by the technique. Note that the reason \sfl{}$^{k}$
+misses the fault is different compared to \combpar{k}. \sfl{}$^{k}$
+captures the fault if the fault is included within the top $k$ files;
+it misses the fault otherwise. Table~\ref{table:fsws} shows results,
+indicating that \combpar{k}, on average, captures more faults compared
+to \sfl{}$^{k}$. In only two cases \sfl{}$^{k}$ outperformed
+\combpar{k}. These results show that the majority of faulty statements
+are found on the $5$ highest ranked faulty classes and that
+\combpar{10} is the variant of our approach that performs better
+missing only 23 out of the \numFaults\ ($\sim$8.8\%) faults.
+
+%% \sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas
+%% \combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., \combpar{5}
+%% misses $20$ ($7.7\%$) less faults compared to
+%% \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults whereas
+%% \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10}
+%% misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$.
+
+%% repeated...
+%%  (2) there are few
+%% cases where the faulty statements are only found if the approach
+%% considers the first $10$ highest ranked faulty classes
 

### 2019-02-23 paper/ijcai/paper.tex
refactoring of table 4
polishing tabel
section 2

@@
 \section{Dynamic Slicing (\ds{})}
-%\label{sec:background}
 \label{sec:slicing}
-\Sof{Falar de model-based diagnosis}\Rui{important to connect to the AI
-community --- we are submitting this to ijcai.}
-Program slicing is a program understanding technique to identify the
-relevant parts of the program with respect to given points of
-interest. Dynamic
-slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
+
+% Program slicing is a program understanding technique to identify the
+% relevant parts of the program with respect to given points of
+% interest.
+\Sof{MBSD connection review please}
+Dynamic slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
 static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
+is an instance of Model-based software diagnosis that
 has been shown useful in automated software debugging where the region
@@
 that the sliced program will follow a path to the error similar to
-that followed by the original program. \Mar{Sofia, if you think it is
-  necessary, explain if you needed to abstract something in the
-  stacktrace. I did not understand that memory location thing.}
+that followed by the original program. \Sof{Added oracle generalization example}
+There are faults whose outputs 
+may slightly differ from one execution to another. For example, 
+exceptions including memory addresses identifiers, which change on 
+each execution. For these cases, it was developed a mechanism to compare the
+rest of the output ignoring the identifier of the memory address.
 
@@
 
+% \begin{table*}[t!]
+% 	\small
+% 	% \setlength{\tabcolsep}{3pt}
+% 	\centering
+% 	  \begin{tabular}{l|cccc|cccc|c}
+% 		\toprule
+% 		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{\sfl{}$^{k}$}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
+%
+% 		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
+% 					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
+% 		\midrule
+% 		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
+% 		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
+% 		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
+% 						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
+% 		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
+% 		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
+% 						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
+% 		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
+% 				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
+% 		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
+% 		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
+% 	 Total      & 207  & 79.6\% & 217 & 83.5\%
+% 	 				& 227 & 87.3\% & 237 & 91.2\% & 260 \\
+% 		\bottomrule
+% 	\end{tabular}
+%   \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
+%   \label{table:fsws}
+% \end{table*}
+
 \begin{table*}[t!]
@@
 	\centering
-	  \begin{tabular}{l|cccc|cccc|c}
+	  \begin{tabular}{l|cc|cc|c}
 		\toprule
-		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{\sfl{}$^{k}$}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\
-
-		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
-					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
+		 Project        &   \sfl{}$^{5}$   & \combpar{5}
+		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
 		\midrule
-		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
-		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
-		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
-						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
-		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
-		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
-						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
-		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
-				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
-		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
-		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
-	 Total      & 207  & 79.6\% & 217 & 83.5\%
-	 				& 227 & 87.3\% & 237 & 91.2\% & 260 \\
+		 \lang{}         &   84.6   & 100 & 84.6 & 96.9 & 65      \\
+		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 & 104  \\   
+		\chart{}           & 84.6 & 76.9 & 92.3 & 84.6 & 26  \\
+		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2 & 27  \\   
+		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9 & 38  \\   \midrule
+		Total         & 79.6 & 87.3 & 83.5 & 91.2 & 260  \\  
 		\bottomrule

### 2019-02-23 paper/ijcai/paper.tex
pass on statistical tests

@@
 
-        \lang{}            & 100 & 96.9\\
+        \lang{}            & 100.0 & 96.9\\
         \cmath{}           & 89.4 & 95.2\\
@@
 
-\begin{table*}[t!]
+\begin{table}[h!]
 	\small
-	% \setlength{\tabcolsep}{3pt}
+	\setlength{\tabcolsep}{3pt}
 	\centering
-	  \begin{tabular}{l|cc|cc|c}
+	  \begin{tabular}{l|rr|rr}
 		 \toprule
-		 Project        &   \sfl{}$^{5}$   & \combpar{5}
-		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
+       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
+		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
 		\midrule
-		 \lang{}         &   84.6   & 100 & 84.6 & 96.9 & 65      \\
-		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 & 104  \\   
-		\chart{}           & 84.6 & 76.9 & 92.3 & 84.6 & 26  \\
-		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2 & 27  \\   
-		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9 & 38  \\   \midrule
-		Total         & 79.6 & 87.3 & 83.5 & 91.2 & 260  \\  
+		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
+		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\   
+		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
+		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\   
+		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
+		Total         & 79.6 & 87.3 & 83.5 & 91.2\\  
 		\bottomrule
@@
   \label{table:fsws}
-\end{table*}
+\end{table}
 
@@
 
-The first experiment we ran to assess impact consisted of measuring
-the \emph{difference of diagnosis cost}. This metric has been
-previously used in other studies~\Fix{cite cite}. More specifically,
-we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
-C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
-obtained by computing the mean position in the ranking of all buggy
-statements. $\Delta C >0$ means that the position of the faulty
-statement has decreased with \combpar{k}, \ie{}, the combination had a
-positive impact. $\Delta C <0$ means that \combpar{k} performs worse
-compared to its baseline. That could happen if dynamic slicing misses
-the faulty statement---the statements not included in the slice will
-have their suspiciousness scores reduced and ranks potentially
-reduced. $\Delta C=0$ means that the faulty statement remained in the
-same position.  It is worth noting that we assume a perfect bug
-understanding, i.e., if the developer sees the bug in the ranking, he
-is able to precisely determine if it is the faulty one.
-
-\Mar{I see there are different results/metrics/tables. We need to
-  organize this better, with sub-questions or stating different
-  other experiments to answer the main question.}
+The first experiment we ran to assess impact consists of measuring the
+\emph{difference of diagnosis cost}. This metric has been previously
+used in other studies~\Fix{cite cite}. More specifically, we computed
+$\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where
+$C$ denotes the diagnosis cost and is obtained by computing the mean
+position in the ranking of all buggy statements. $\Delta C >0$ means
+that the position of the faulty statement has decreased with
+\combpar{k}, \ie{}, the combination had a positive impact. $\Delta C
+<0$ means that \combpar{k} performs worse compared to its
+baseline. That could happen if dynamic slicing misses the faulty
+statement---the statements not included in the slice will have their
+suspiciousness scores reduced and ranks potentially reduced. $\Delta
+C=0$ means that the faulty statement remained in the same position.
+It is worth noting that we assume a perfect bug understanding, i.e.,
+if the developer sees the bug in the ranking, he is able to precisely
+determine if it is the faulty one.
+
+Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
+relative to \sfl{}$^{k}$ using histograms over $\Delta{}C$ for
+different values of $k$. Note that (1) the number of cases where
+\sfl{}$^{k}$ outperforms \combpar{k} is very small compared and (2)
+the number of cases \combpar{k} outperforms \sfl{}$^{k}$ is
+significant and, as we increase the value of $k$, it increases (from
+97 to 117 faults).
+
+%% For $k=5$, we observe that in $30$ ($11.5\%$) of the faults the
+%% position of faulty statements decreases in the ranking, $97$($37.3\%$)
+%% of the faults the position of faulty statements increases in the
+%% rankinh whereas $133$ ($51.2\%$) of the faults the position of faulty
+%% stamenets remains the same. For $k=10$, we observe an increasing of
+%% $20$ cases where the position of faulty statements increases in the
+%% ranking $117$ ($45.0\%$).  The number of cases whose faulty statements
+%% position remained the same are $110$ ($42.3\%$) and that suffered a
+%% decrease in the ranking is $33$ ($12.7\%$).
+
+\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
+		\caption{Histograms of $\Delta{}C$.}
+		\label{fig:diagnosis}
+\end{figure}
 
 \Mar{---------------------- I am here}
-
-Figure \ref{fig:diagnosis} reports the cost of diagnosis of using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$,
-respectively. For $k=5$, we observe that in $30$ ($11.5\%$) of the faults
-the position of faulty statements decreases
-in the ranking, $97$($37.3\%$) of the faults the position of faulty statements increases in the rankinh whereas $133$ ($51.2\%$) of the faults the position of faulty stamenets remains the same.
-For $k=10$, we observe an increasing of $20$ cases where the position of faulty statements increases in the ranking $117$ ($45.0\%$).
-The number of cases whose faulty statements position remained the same are $110$ ($42.3\%$) and that suffered a decrease in the ranking is $33$ ($12.7\%$).
 
@@
 one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for
-$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which is significant.
-
-Although this dataset has more than $50\%$ of fault of omissions,
-our simple slicing approach was capable of improving the ranking of $95$ faults for
-$k=5$ and $115$ faults for $k=10$. Table \ref{table:st} presents the statistics
-to determine if the observed results are statistically significant. Shapiro-Wilk
-tests the null hypothesis that results are drawn from a normal distribution. The
-test is perfomed for all techniques and its variants. With $99\%$ of confidence,
-the results tell us that the distributions are not normal. Given that $C$ is not
-normally distributed, we use the non-parametrical statistical hypothesis test
-Friedman. The null-hypothesis is that the ranking results of all techniques and
-variants are the same. With $99\%$ of confidence, the results show that the
-distributions are distinct. To understand which techniques perform differently 
-- i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
-we performed a Siegel post-hoc analysis. Figure
-\ref{fig:performance} reports the results of Siegel analysis for all pairs of techniques.
-Each square represents the significance between the correspondent techniques, i.e., if it is significant it means that the techniques perform differently.
-With $95\%$ of confidence, it is possible to confirm that the performance of all techniques is different expect when comparing \combpar{5} with \combpar{10}.
-
-It is worth noting that Automated
-Program Repair techniques may directly benefit from this study to improve their
-results.
-
-\Rui{Weakness: there has to be discussion on whether there is potential/promising
-results somewhere.}
-
-\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
-		\caption{Cost of diagnosis of using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$, respectively}
-		\label{fig:diagnosis}
-\end{figure}
-
-\begin{table}[h]
+$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained
+in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which
+is significant.
+
+\begin{table}[h!]
 	\tiny
@@
 \end{table}
+
+Although this dataset has more than $50\%$ of fault of omissions, our
+simple slicing approach was capable of improving the ranking of $95$
+faults for $k=5$ and $115$ faults for $k=10$. Table \ref{table:st}
+presents the statistics to determine if the observed results are
+statistically significant. Shapiro-Wilk tests the null hypothesis that
+results are drawn from a normal distribution. The test is perfomed for
+all techniques and its variants. With $99\%$ of confidence, the
+results tell us that the distributions are not normal. Given that $C$
+is not normally distributed, we use Friedman test, a non-parametric
+statistical test of hypothesis. The null-hypothesis is that the
+ranking results of all techniques and variants are the same. With
+$99\%$ confidence, the results show that the distributions are
+distinct.
+
+To understand which techniques perform differently, \ie{} to answer
+the question \textit{Does \combpar{k} perform differently than
+  \sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
+\ref{fig:performance} reports the results of Siegel analysis for all
+pairs of techniques. Each square\Mar{gray intensity?} represents the
+significance\Mar{of what?} between the corresponding techniques, i.e.,
+if it is significant it means that the techniques perform
+differently. We can determine with $95\%$ confidence that the
+performance of each pair of techniques is different.
+
+\Rui{Weakness: there has to be discussion on whether there is potential/promising
+results somewhere.}
 

### 2019-02-23 paper/ijcai/paper.tex
temp

--- 2019-02-23 paper/ijcai/paper.tex
@@
 \label{sec:slicing}
+
+Model-based software diagnosis has been
+
+model-based software debugging, from the DX community, has been shown to be similar to slicing Mayer and Stumptner, 2008; Wotawa and Nica; etc.
+Having said that, not many inter- esting techniques having been pursued because of scalability.
+We have achieved it with a type of program slicing — critical slicing.
 

### 2019-02-23 paper/ijcai/paper.tex

--- 2019-02-23 paper/ijcai/paper.tex
@@
 
-        \lang{}            & 100.0 & 96.9\\
+        \lang{}            & 100 & 96.9\\
         \cmath{}           & 89.4 & 95.2\\
@@
 
-\begin{table}[h!]
+\begin{table*}[t!]
 	\small
-	\setlength{\tabcolsep}{3pt}
+	% \setlength{\tabcolsep}{3pt}
 	\centering
-	  \begin{tabular}{l|rr|rr}
+	  \begin{tabular}{l|cc|cc|c}
 		\toprule
-       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
-		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
+		 Project        &   \sfl{}$^{5}$   & \combpar{5}
+		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
 		\midrule
-		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
-		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\   
-		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
-		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\   
-		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
-		Total         & 79.6 & 87.3 & 83.5 & 91.2\\  
+		 \lang{}         &   84.6   & 100 & 84.6 & 96.9 & 65      \\
+		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 & 104  \\   
+		\chart{}           & 84.6 & 76.9 & 92.3 & 84.6 & 26  \\
+		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2 & 27  \\   
+		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9 & 38  \\   \midrule
+		Total         & 79.6 & 87.3 & 83.5 & 91.2 & 260  \\  
 		\bottomrule

### 2019-02-23 paper/ijcai/paper.tex
changes in S2

--- 2019-02-23 paper/ijcai/paper.tex
@@
 
-% Program slicing is a program understanding technique to identify the
-% relevant parts of the program with respect to given points of
-% interest.
-\Sof{MBSD connection review please}
+Model-based diagnosis is a well-known approach that has been proposed by the
+DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
+of model-based diagnosis to localize software faults have demonstrated that it
+can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,Mayer:2008:EMM:1642931.1642950}.
+
 Dynamic slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
@@
 that the sliced program will follow a path to the error similar to
-that followed by the original program. \Sof{Added oracle generalization example}
+that followed by the original program.
 There are faults whose outputs

### 2019-02-23 paper/ijcai/paper.tex
another pass on RQ3

@@
 
-\Mar{---------------------- I am here}
-
+If we focus at the $116$\Mar{117?} faults where there was improvement
+in at least one of the variants, the mean improvement in the ranking
+was 41.1 statements for $k=5$ and 18.7 statements for $k=10$. We
+observed an impressive maximum ranking improvement of $3170.5$\Mar{why
+  the .5 if this is the maximum case?} statements for $k=5$ and $209$
+statements for $k=10$. Such difference is justified by the fact that
+entire files are discarded in \combpar{5}, whose statements are
+included in the ranking of \combpar{10}. Consequently, the
+improvements obtained by the technique will not be as high if slicing
+on these additional files is unable to aggressively and safely discard
+statements. This also shows that slicing files, in addition to slicing
+statements from those files, is very beneficial for fault localization
+performance.
+
+\Mar{show distribution...}
+
+In the following, we present statistical analysis to demonstrate that
+the distributions of $C$ for each technique are different.
 Table~\ref{table:st}, reports the average rank of all faulty
@@
 $6.1$ on the rank mean of all faulty statements.
-This $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none. Yet,
-if we only consider the faults ($116$) where there was improvement in at least
-one of the variants ($k=5$ or $k=10$) the \textbf{ranking increases in a mean of 41.1} for
-$k=5$ and \textbf{18.7} for $k=10$. The maximum improvement obtained
-in the \sfl{} rank was  $3170.5$ for $k=5$ and $209$ for $k=10$, which
-is significant.
+These $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none.
 

### 2019-02-23 paper/ijcai/paper.tex
explaining k
changes

--- 2019-02-23 paper/ijcai/paper.tex
@@
  9\%\comments{(23 misses)} of the \numFaults{} cases and that
-the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
-the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
+the \ds{}-\sfl{} combination, coined as Tandem-SL, improves
+the diagnostic accuracy of the diagnostic report in \avgImprov\ on average
+for 51\% of the cases. To sum,
 we found that the \ds{}-\sfl{} combination was practical and effective
@@
 slicing through the variable $k$, which denotes the number of distinct
-files that dynamic slicing will minimize. In this study, we used 5 and
-10 as the values of $k$. The $k$ files for minimization are selected
+files that dynamic slicing will minimize. In this study, we used $5$ and
+$10$ as the values of $k$, following the same values as in previous fault
+localiztion studies~\cite{ang-perez-van-deursen-rui-2017}.
+The $k$ files for minimization are selected
 from the \sfl{} ranking as follows. First, we build a rank of files by
@@
 it. Then, we select the top $k$ distinct files from such file ranking.
-\Rui{we should say that k follows from typical SFL metrics (top k)}
 

### 2019-02-24 paper/ijcai/paper.tex
abstract+intro update

--- 2019-02-23 paper/ijcai/paper.tex
@@
 statements. Results indicate that \ds{} misses faulty statements in
- 9\%\comments{(23 misses)} of the \numFaults{} cases and that
+ $9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
 the \ds{}-\sfl{} combination, coined as Tandem-SL, improves 
-the diagnostic accuracy of the diagnostic report in \avgImprov\ on average
-for 51\% of the cases. To sum,
+the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average)\Sof{Calculei
+mal a média antes. A melhoria média para o top-5 é 9.6\% e a máxima
+melhoria que a técnica atingiu foi de 96.7\%. Eu reportei aqui no abstract para o
+top-10 porque a \% de melhoria é maior. Se vocês acharem que é mais vantajoso
+reportar os valores do top-10, avisem. Podemos reportar ambas. Atenção, só considero
+os casos em que pelo menos uma das variantes obteve melhoria}. To sum,
 we found that the \ds{}-\sfl{} combination was practical and effective
@@
 evaluate fault localization research. Results show that \ds{} misses
-faulty statements in 9\%\comments{(23 misses)} of the \numFaults{}
+faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
 faults analyzed. Furthermore, we found that the combination of the two
-approaches improves fault localization in 51\% of the cases with an
-average improvement of \avgImprov. To sum, results indicate that the
+approaches may improve fault localization up to $73.7\%$ (\avgImprov\ on average).
+ To sum, results indicate that the
 risk of applying the technique is relatively low for the positive
-impact it may bring and the tool implementing the technique works
+impact it may bring; and, the tool implementing the technique works
 out-of-the-box, \ie{}, it puts no requirements on the running
@@
 
-Model-based diagnosis is a well-known approach that has been proposed by the
-DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
-of model-based diagnosis to localize software faults have demonstrated that it
-can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,Mayer:2008:EMM:1642931.1642950}.
-
+Model-based software diagnosis has been
+
+model-based software debugging, from the DX community, has been shown to be similar to slicing Mayer and Stumptner, 2008; Wotawa and Nica; etc.
+Having said that, not many inter- esting techniques having been pursued because of scalability.
+We have achieved it with a type of program slicing — critical slicing.
+
+% Program slicing is a program understanding technique to identify the
+% relevant parts of the program with respect to given points of
+% interest.
+\Sof{MBSD connection review please}
 Dynamic slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
@@
 that the sliced program will follow a path to the error similar to
-that followed by the original program.
+that followed by the original program. \Sof{Added oracle generalization example}
 There are faults whose outputs 
@@
 slicing through the variable $k$, which denotes the number of distinct
-files that dynamic slicing will minimize. In this study, we used $5$ and
-$10$ as the values of $k$, following the same values as in previous fault
-localiztion studies~\cite{ang-perez-van-deursen-rui-2017}.
-The $k$ files for minimization are selected
+files that dynamic slicing will minimize. In this study, we used 5 and
+10 as the values of $k$. The $k$ files for minimization are selected
 from the \sfl{} ranking as follows. First, we build a rank of files by
@@
 
-\begin{table}[h!]
+\begin{table*}[t!]
 	\small
-	\setlength{\tabcolsep}{3pt}
+	% \setlength{\tabcolsep}{3pt}
 	\centering
-	  \begin{tabular}{l|rr|rr}
+	  \begin{tabular}{l|cc|cc|c}
 		\toprule
-       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
-		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
+		 Project        &   \sfl{}$^{5}$   & \combpar{5}
+		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
 		\midrule
-		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
-		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
-		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
-		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
-		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
-		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
+		 \lang{}         &   84.6   & 100 & 84.6 & 96.9 & 65      \\
+		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 & 104  \\   
+		\chart{}           & 84.6 & 76.9 & 92.3 & 84.6 & 26  \\
+		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2 & 27  \\   
+		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9 & 38  \\   \midrule
+		Total         & 79.6 & 87.3 & 83.5 & 91.2 & 260  \\  
 		\bottomrule

### 2019-02-24 paper/ijcai/paper.tex

--- 2019-02-23 paper/ijcai/paper.tex
@@
 statements. Results indicate that \ds{} misses faulty statements in
- 9\%\comments{(23 misses)} of the \numFaults{} cases and that
+$9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
 the \ds{}-\sfl{} combination, coined as Tandem-SL, improves 
-the diagnostic accuracy of the diagnostic report in \avgImprov\ on average
-for 51\% of the cases. To sum,
+the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average)\Sof{Calculei
+mal a média antes. A melhoria média para o top-5 é 9.6\% e a máxima
+melhoria que a técnica atingiu foi de 96.7\%. Eu reportei aqui no abstract para o
+top-10 porque a \% de melhoria é maior. Se vocês acharem que é mais vantajoso
+reportar os valores do top-10, avisem. Podemos reportar ambas. Atenção, só considero
+os casos em que pelo menos uma das variantes obteve melhoria}. To sum,
 we found that the \ds{}-\sfl{} combination was practical and effective
@@
 
-\begin{table}[h!]
+\begin{table*}[t!]
 	\small
-	\setlength{\tabcolsep}{3pt}
+	% \setlength{\tabcolsep}{3pt}
 	\centering
-	  \begin{tabular}{l|rr|rr}
+	  \begin{tabular}{l|cc|cc|c}
 		\toprule
-       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
-		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
+		 Project        &   \sfl{}$^{5}$   & \combpar{5}
+		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
 		\midrule

### 2019-02-24 paper/ijcai/paper.tex
more fixes

@@
 of model-based diagnosis to localize software faults have demonstrated that it
-can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,Mayer:2008:EMM:1642931.1642950}.
+can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
+\Sof{A primeira citação estava repetida. @Rui, por favor, verifica se a segunda é a que eu introduzi
+mayer2008prioritising ou se é outra ou então se estava repetida por engano.}
 
@@
 Table~\ref{tab:df4j} shows size, number of tests, and number of
-faults, for each considered program.
+faults, for each considered program. $2$ subjects from Math
+were not considered because we were not able to reproduce them
+in the machine used for the experiments.
 
@@
 popular metric in fault localization research for that
-purpose~\Fix{cite}. A fault of omission occurs when
-\Fix{...explain...}. Intuitivelly, the ability of techniques to
+purpose~\Fix{cite}\Sof{Not sure what to cite here}. A fault of omission occurs when
+the program is buggy because some code is missing, i.e., a bug that is 
+corrected by adding code. Intuitivelly, 
+the ability of techniques to
 produce good diagnosis in those cases reduce as \Fix{...explain...}. A
@@
 
-\Mar{incorporate this here. we were presenting this too early (initial
-  par. of results). not very appealing ;)}
-\Fix{
-The remaining faults were not considered because
-(1) faults belong to the \closure{} project which requires high CPU to perform
-the \combpar{k} evaluation  or (2) faults whose test outputs were not
-reproducible in the machine used to run the experiments.
-}
-
 %
@@
 choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
+It is importance to notice that our study does not evaluate the fault of the \closure{} 
+project since it requires high CPU to perform the \combpar{k} evaluation.
 

### 2019-02-24 paper/ijcai/paper.tex
redo

@@
 the program is buggy because some code is missing, i.e., a bug that is 
-corrected by adding code. Intuitivelly, 
-the ability of techniques to
-produce good diagnosis in those cases reduce as \Fix{...explain...}. A
-total of $59.7\%$ of the cases in this dataset manifest fault of
-omission, which is a good indication of difficulty.
+corrected by adding code. Intuitivelly, the ability of techniques to
+produce good diagnosis in those cases is poor since fault of omission
+are non-executable statements which means that the execution information
+cannot help locate the fault directly. A total of $59.7\%$ of the cases 
+in this dataset manifest fault of omission, which is a good indication of 
+difficulty\Sof{note to self: Improve the good indication of difficulty}.
 
@@
 amount of code in the best ranked files. Table \ref{tab:red} shows, as
-percentages, the average reduction on the sum of top file sizes
+percentages, the reduction of the top file sizes
 obtained with dynamic slicing for different values of
-$k$.\Mar{$\leftarrow$sofia, please check.} Overall, results indicate
+$k$. Overall, results indicate
 that dynamic slicing substantially reduces the size of highly-ranked
@@
 
-\begin{table*}[t!]
+\begin{table}[h!]
 	\small
-	% \setlength{\tabcolsep}{3pt}
+	\setlength{\tabcolsep}{3pt}
 	\centering
-	  \begin{tabular}{l|cc|cc|c}
+\begin{tabular}{l|rr|rr}
 		 \toprule
-		 Project        &   \sfl{}$^{5}$   & \combpar{5}
-		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
+       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
+		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
 		\midrule

### 2019-02-24 paper/ijcai/paper.tex
typo

@@
 $10$ as the values of $k$, following the same values as in previous fault
-localiztion studies~\cite{ang-perez-van-deursen-rui-2017}.
+localization studies~\cite{ang-perez-van-deursen-rui-2017}.
 The $k$ files for minimization are selected

### 2019-02-24 paper/ijcai/paper.tex
adding boxplots and cleaning
last updates

@@
 that dynamic slicing substantially reduces the size of highly-ranked
-files. \Mar{sofia, it would be more convincing if you (additionally)
-  show reduction wrt to the the parts of the file that are covered.}
+files.
+
+%\Mar{sofia, it would be more convincing if you (additionally)
+%  show reduction wrt to the the parts of the file that are covered.}
 
@@
 dynamic slicing captures at least one of the faulty statements among
-the sliced files for different values of $k$. These numbers indicat
-that \Fix{...elaborate...}
+the sliced files for different values of $k$. These numbers indicate
+that in general \ds{} finds at least one faulty statement in the top
+$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
+is slightly improved for $91.2\%$ if we consider 
+the top $10$ of the highest-ranked faulty classes.
+\Sof{Percebo o objectivo da tabela 3 mas não seria melhor arranjar 
+maneira de não precisar de repetir? Estes resultados estão na tabela 4}
 
@@
         \jtime{}            & 81.5 & 85.2\\
-        \mockito{}          & 71.1 & 78.9\\
+        \mockito{}          & 71.1 & 78.9\\\midrule
+        Total          & 87.3 & 91.2\\
 
@@
 
+\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.42\textwidth]{figures/boxplot_>0.pdf}
+		\caption{Boxplot of $\Delta{}C$. \Sof{Considering only the best cases}}
+		\label{fig:boxplot}
+\end{figure}
+
+\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
+		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
+		\label{fig:boxplot}
+\end{figure}
+
 If we focus at the $116$\Mar{117?} faults where there was improvement

### 2019-02-24 paper/ijcai/paper.tex
fix citation
minor fixes

@@
 the \ds{}-\sfl{} combination, coined as Tandem-SL, improves
-the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average)\Sof{Calculei
-mal a média antes. A melhoria média para o top-5 é 9.6\% e a máxima
-melhoria que a técnica atingiu foi de 96.7\%. Eu reportei aqui no abstract para o
-top-10 porque a \% de melhoria é maior. Se vocês acharem que é mais vantajoso
-reportar os valores do top-10, avisem. Podemos reportar ambas. Atenção, só considero
-os casos em que pelo menos uma das variantes obteve melhoria}. To sum,
+the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average). To sum,
 we found that the \ds{}-\sfl{} combination was practical and effective
@@
 can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
-\Sof{A primeira citação estava repetida. @Rui, por favor, verifica se a segunda é a que eu introduzi
-mayer2008prioritising ou se é outra ou então se estava repetida por engano.}
 
@@
 popular metric in fault localization research for that
-purpose~\Fix{cite}\Sof{Not sure what to cite here}. A fault of omission occurs when
+purpose~\cite{Pearson:2017:EIF:3097368.3097441,just-defects4j-issta2014}. 
+A fault of omission occurs when
 the program is buggy because some code is missing, i.e., a bug that is
 corrected by adding code. Intuitivelly, the ability of techniques to
-produce good diagnosis in those cases is poor since fault of omission
+produce accurate diagnostic reports in those cases is poor since fault of omission
 are non-executable statements which means that the execution information
@@
 		\centering
-		\includegraphics[width=0.42\textwidth]{figures/boxplot_>0.pdf}
-		\caption{Boxplot of $\Delta{}C$. \Sof{Considering only the best cases}}
+		\includegraphics[width=0.47\textwidth]{figures/double-boxplot.pdf}
+		\caption{Boxplot of $\Delta{}C$.}
 		\label{fig:boxplot}
 \end{figure}
-
-\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
-		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
-		\label{fig:boxplot}
-\end{figure}
+%
+% \begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
+% 		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
+% 		\label{fig:boxplot}
+% \end{figure}
 

### 2019-02-24 paper/ijcai/paper.tex
boxplot update

@@
 in this dataset manifest fault of omission, which is a good indication of
-difficulty\Sof{note to self: Improve the good indication of difficulty}.
+difficulty\Sof{icse17 check}.
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
   \small
@@
 the top $10$ of the highest-ranked faulty classes.
-\Sof{Percebo o objectivo da tabela 3 mas não seria melhor arranjar
-maneira de não precisar de repetir? Estes resultados estão na tabela 4}
-
-\begin{table}[H]
+
+\begin{table}[h]
   \small
@@
 significant and, as we increase the value of $k$, it increases (from
-97 to 117 faults).
+$97$ to $117$ faults).
 
@@
 		\centering
-		\includegraphics[width=0.47\textwidth]{figures/double-boxplot.pdf}
+		\includegraphics[width=0.49\textwidth]{figures/boxplot.pdf}
 		\caption{Boxplot of $\Delta{}C$.}

### 2019-02-24 paper/ijcai/paper.tex
cleanup
more fixes

@@
 popular metric in fault localization research for that
-purpose~\cite{Pearson:2017:EIF:3097368.3097441,just-defects4j-issta2014}. 
-A fault of omission occurs when
+purpose~\cite{Pearson:2017:EIF:3097368.3097441}. 
+A fault of omission (\foo) occurs when
 the program is buggy because some code is missing, i.e., a bug that is
-corrected by adding code. Intuitivelly, the ability of techniques to
-produce accurate diagnostic reports in those cases is poor since fault of omission
-are non-executable statements which means that the execution information
-cannot help locate the fault directly. A total of $59.7\%$ of the cases
-in this dataset manifest fault of omission, which is a good indication of
-difficulty\Sof{icse17 check}.
-
+corrected by adding code. Intuitively, the ability of techniques to
+produce accurate diagnostic reports in those cases might be poor since 
+fault of omission bugs are very difficult to locate. This dataset has a
+total of $59.7\%$ of \foo s which may contribute negatively to our
+results since \sfl{} strives to rank these cases.
 %in producing
@@
 
-\subsection{Results}
-
-This section answers the research questions.
+\subsection{Results and Discussion}
+
+This section discusses and answers the research questions.
 
@@
 
+\begin{table}[H]
+  \small
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrr}
+		\toprule
+		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
+		\midrule
+
+        \lang{}            & 1.40 & 31.46\\
+        \cmath{}           & 10.30 & 12.34\\
+        %\closure{}          &  & \\
+		\chart{}			& 59.30 & 53.64 \\
+        \jtime{}            & 17.27 & 32.02\\
+        \mockito{}          & 16.54 & 21.67\\
+
+		\bottomrule
+	\end{tabular}
+	\caption {\ds{} reduction in file size (percentages). Higher is better.}
+	\label{tab:red}
+\end{table}
+\normalsize
+
+\subsubsection{RQ2: \textit{\rqtwo}}
+\label{rq:2}
+
+%% For automated debugging that
+%% means that it will not be in the diagnostic report and therefore has a negative
+%% impact in the fault localization accuracy.
+
+%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
+%% statements, since it is one of the main issues of dynamic slicing techniques. This
+%% is particularly important because when \ds{} misses a faulty statement
+
+%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
+
+A fundamental issue of purely dynamic slicing techniques is the risk
+of discarding faulty statements (see Section~\ref{sec:slicing}). This
+research question evaluates the practical impact of this conceptual
+issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
+dynamic slicing captures at least one of the faulty statements among
+the sliced files for different values of $k$. These numbers indicate
+that in general \ds{} finds at least one faulty statement in the top
+$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
+is slightly improved to $91.2\%$ if we consider
+the top $10$ of the highest-ranked faulty classes.
+
 \begin{table}[h]
@@
 
-        \lang{}            & 1.40 & 31.46\\
-        \cmath{}           & 10.30 & 12.34\\
-        %\closure{}          &  & \\
-		\chart{}			& 59.30 & 53.64 \\
-        \jtime{}            & 17.27 & 32.02\\
-        \mockito{}          & 16.54 & 21.67\\
-
-		\bottomrule
-	\end{tabular}
-	\caption {\ds{} reduction in file size (percentages). Higher is better.}
-	\label{tab:red}
-\end{table}
-\normalsize
-
-\subsubsection{RQ2: \textit{\rqtwo}}
-\label{rq:2}
-
-%% For automated debugging that
-%% means that it will not be in the diagnostic report and therefore has a negative
-%% impact in the fault localization accuracy.
-
-%% In \textbf{RQ2}, our concern is to evaluate how often \ds{} misses faulty
-%% statements, since it is one of the main issues of dynamic slicing techniques. This
-%% is particularly important because when \ds{} misses a faulty statement
-
-%% of both techniques, \sfl{}$^{k}$ and \combpar{k}
-
-A fundamental issue of purely dynamic slicing techniques is the risk
-of discarding faulty statements (see Section~\ref{sec:slicing}). This
-research question evaluates the practical impact of this conceptual
-issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
-dynamic slicing captures at least one of the faulty statements among
-the sliced files for different values of $k$. These numbers indicate
-that in general \ds{} finds at least one faulty statement in the top
-$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
-is slightly improved for $91.2\%$ if we consider
-the top $10$ of the highest-ranked faulty classes.
-
-\begin{table}[h]
-  \small
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{lrr}
-		\toprule
-		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
-		\midrule
-
         \lang{}            & 100.0 & 96.9\\
@@
      percentages. Higher is better.}
-	\label{tab:red}
    \label{tab:ds-cases-captured}
+\vspace{-0.2cm}
+
 \end{table}
-\normalsize
+%\normalsize
 
@@
 \combpar{10} is the variant of our approach that performs better
-missing only 23 out of the \numFaults\ ($\sim$8.8\%) faults.
+missing only $23$ out of the \numFaults\ ($\sim$8.8\%) faults.
 
@@
 \begin{table}[h!]
+	\vspace{-0.2cm}
+
 	\small
@@
   \label{table:fsws}
+\vspace{-0.4cm}
 \end{table}
@@
 In \textbf{RQ3}, we evaluate the effective impact of combining \ds{}
-with \sfl{} to improve fault localization.
-
-The first experiment we ran to assess impact consists of measuring the
+with \sfl{} to improve fault localization. The first experiment we ran to assess impact consists of measuring the
 \emph{difference of diagnosis cost}. This metric has been previously
-used in other studies~\Fix{cite cite}. More specifically, we computed
+used in other studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}. More specifically, we computed
 $\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where
@@
 significant and, as we increase the value of $k$, it increases (from
-$97$ to $117$ faults).
+$97$ to $117$ faults). The faults where the cost of diagnosis is
+negative are cases that (1) the faulty statements decreased in the ranking 
+list due to being a fault of omission, (2) the test has design limitations
+which \ds~is not capable of handling, or (3) the buggy-class in not in
+the top $k$ of the highest-ranked faulty classes under analysis.
 
@@
 \begin{figure}[h]
+	\vspace{-0.3cm}
 		\centering
-		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
-		\caption{Histograms of $\Delta{}C$.}
+		\includegraphics[width=0.415\textwidth]{figures/performance.pdf}
+		\vspace{-0.4cm}
+		\caption{Cost of Diagnosis ($\Delta{}C$) per variant}
 		\label{fig:diagnosis}
@@
 
+Figure~\ref{fig:boxplot} shows the $\Delta{}C$ distribution for each
+variant in two different cases. On the left, we do not consider the
+test engineering problems and faults of omission ($227$ faults). The two negative 
+outliers present the cases where the buggy-class was not in the top
+$k$. On the right, we only consider the cases where at least one 
+of the variants resulted in an increase of $\Delta{}C$ ($116$ faults), i.e., the 
+cases where \ds{} improves \sfl. Although, we observe
+a considerable amount of cases where $\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
 \begin{figure}[h]
+		\vspace{-0.2cm}
 		\centering
 		\includegraphics[width=0.49\textwidth]{figures/boxplot.pdf}
-		\caption{Boxplot of $\Delta{}C$.}
+		\vspace{-0.6cm}
+
+		\caption{Distribution of $\Delta{}C$ per variant when not considering 
+		test engineering problems and fault of omissions (left) and only considering
+		the cases where \combpar{k} achieved improvement under one of the variants}
 		\label{fig:boxplot}
+		\vspace{-0.2cm}
+
 \end{figure}
-%
-% \begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
-% 		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
-% 		\label{fig:boxplot}
-% \end{figure}
-
-If we focus at the $116$\Mar{117?} faults where there was improvement
-in at least one of the variants, the mean improvement in the ranking
-was 41.1 statements for $k=5$ and 18.7 statements for $k=10$. We
-observed an impressive maximum ranking improvement of $3170.5$\Mar{why
-  the .5 if this is the maximum case?} statements for $k=5$ and $209$
-statements for $k=10$. Such difference is justified by the fact that
+
+If we consider only the faults which can benefit from our approach, we can observe that there is a considerable
+amount of cases where the approach is actually successful. For
+$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ on average) statements
+on the ranking and an impressive maximum ranking improvement
+of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
+achieves a mean improvement of $19$ ($13.35\%$ on average) statements
+on the ranking and a maximum ranking improvement
+of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
 entire files are discarded in \combpar{5}, whose statements are
@@
 performance.
-
-\Mar{show distribution...}
-
 In the following, we present statistical analysis to demonstrate that
@@
 statements of the \dfj{} faults considered to the study after applying both
-techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. $33$ of the $260$
-faulty versions are cases whose faulty statements decreased in the ranking list due to being a fault of omission case or due to limitations regarding the test design which \ds{} could not handle.
-Thus, we report both values in Table~\ref{table:st}.
-In bold, we present the
-results of the $227$ faults that do not contain the cases that are result of the limitations mentioned before. Inside parentheses, we present the
+techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. 
+In bold, we present the results of the $227$ faults that do not contain the 
+cases that are result of the limitations mentioned before (test design and fault of omission). Inside parentheses, we present the
 rank results for all faults. The \combpar{k} combination yields an improvement
 of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
-Instead, if $k=10$ is considered the proposed approach returns an improvement of
+Instead, if $k=10$ is considered, the proposed approach returns an improvement of
 $6.1$ on the rank mean of all faulty statements.
-These $227$ faults contain cases where the faulty class was not in the choosen set of classes $k$ and a high amount of cases where the improvement was none.
+These $227$ faults contain cases where the faulty class was not in the choosen 
+set of classes $k$ and a high amount of cases where the improvement was none.
 
@@
 \end{tabular}
-  \caption {Statistical tests}
+  \caption {Statistical tests for $C$}
   \label{table:st}
@@
 \ref{fig:performance} reports the results of Siegel analysis for all
-pairs of techniques. Each square\Mar{gray intensity?} represents the
-significance\Mar{of what?} between the corresponding techniques, i.e.,
+pairs of techniques. Each square represents the
+statistical significance of the diagnostic accuracy amongst the different techniques, i.e.,
 if it is significant it means that the techniques perform

### 2019-02-24 paper/ijcai/paper.tex
more updates

@@
 
-If we consider only the faults which can benefit from our approach, we can observe that there is a considerable
+In the following, we present statistical analysis to demonstrate that
+the distributions of $C$ for each technique are different.
+Table~\ref{table:st}, reports the average rank of all faulty
+statements of the \dfj{} faults considered to the study after applying both
+techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. 
+In bold, we present the results of the $227$ faults that do not comprise the 
+cases that are result of the limitations mentioned before (test design and fault of omission). These results show that \ds{} improves \sfl{} in a mean
+of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements, when considering $k=10$. Inside parentheses, we present the
+rank results for all faults which do not report promissing results. However, If we only consider the faults which can benefit from our approach, we can observe that there is a considerable
 amount of cases where the approach is actually successful. For
@@
 performance.
-In the following, we present statistical analysis to demonstrate that
-the distributions of $C$ for each technique are different.
-Table~\ref{table:st}, reports the average rank of all faulty
-statements of the \dfj{} faults considered to the study after applying both
-techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. 
-In bold, we present the results of the $227$ faults that do not contain the 
-cases that are result of the limitations mentioned before (test design and fault of omission). Inside parentheses, we present the
-rank results for all faults. The \combpar{k} combination yields an improvement
-of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
-Instead, if $k=10$ is considered, the proposed approach returns an improvement of
-$6.1$ on the rank mean of all faulty statements.
-These $227$ faults contain cases where the faulty class was not in the choosen 
-set of classes $k$ and a high amount of cases where the improvement was none.
 
@@
 
-\Rui{Weakness: there has to be discussion on whether there is potential/promising
-results somewhere.}
-
 \begin{figure}[h]
@@
 \subsection{Threats to validity}
-
 %
@@
 
-\Fix{
-The main lesson of this work is that
-fault localization research should consider compare new techniques
-against this combination.}
-
 Several approaches have been proposed in the literature to improve debugging
 costs through automated software fault diagnosis to reduce time-to-market,
-while maintaining high quality standards. In this domain, Dynamic Slicing (DS)
-and Spectrum-based Fault Localization (SFL) are very popular fault diagnosis t
-echniques and normally seen as complementary. This paper reports the outcome of
+while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
+and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
 a study using real-world applications with the goal of demystifying the impact
-of combining DS with SFL. The results of our empirical study show that, in
-practice, DS rarely misses faulty statements (23 misses in 260 cases) and that
-the DS-SFL combination improves the diagnostic accuracy in 51\% of the faults.
+of combining \ds~with \sfl. The results of our empirical study show that, in
+practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
+the \ds-\sfl~combination, coined as \combpar{k}, 
+improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
 Hence, we found that, despite tacit opinions of the research community about
-the usefulness of DS in automated debugging, we found the combination practical
-and effective, and encourage new SFL techniques to be evaluated against that
+the usefulness of \ds~in automated debugging, we found the combination practical
+and effective, and encourage new \sfl~techniques to be evaluated against that
 optimization.
 
-Future work is as follows: bla bla.
+Future work is as follows:
 

### 2019-02-24 paper/ijcai/paper.tex
fixing citation

@@
 one failing test and reports on output a ranked list of components likely to be
-in fault ~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
+in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
 

### 2019-02-24 paper/ijcai/paper.tex
conclusion

--- 2019-02-24 paper/ijcai/paper.tex
@@
 differently. We can determine with $95\%$ confidence that the
-performance of each pair of techniques is different.
+performance of each pair of techniques is different. As the results
+are statiscally significant, we can confirm that \ds{} improves \sfl{}.
 
 \begin{figure}[h]
-	\vspace{-1.2cm}
+	\vspace{-1cm}
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
@@
 while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
-and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
+and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. \ds{} is This paper reports the outcome of
 a study using real-world applications with the goal of demystifying the impact
@@
 
-Future work is as follows:
+Future work is as follows: improve our oracle heuristics to handle more exceptions;
+conduct experiments in more \dfj{} faults or other datasets; find techniques to
+handle the cases which harm the cost of diagnosis, such as, faults of omission,
+test design problems and the cases which the buggy-class is not in the top-$k$ of 
+highest-rank faulty classes.
 

### 2019-02-24 paper/ijcai/paper.tex
another udpate

@@
 		test engineering problems and fault of omissions (left) and only considering
-		the cases where \combpar{k} achieved improvement under one of the variants}
+		the cases where \combpar{k} achieved improvement under one of the variants (right)}
 		\label{fig:boxplot}
@@
 In bold, we present the results of the $227$ faults that do not comprise the
-cases that are result of the limitations mentioned before (test design and fault of omission). These results show that \ds{} improves \sfl{} in a mean
-of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements, when considering $k=10$. Inside parentheses, we present the
-rank results for all faults which do not report promissing results. However, If we only consider the faults which can benefit from our approach, we can observe that there is a considerable
+cases that are result of the limitations mentioned before (test design and fault 
+of omission). These results show that \ds{} improves \sfl{} in a mean
+of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements, 
+when considering $k=10$. Inside parentheses, we present the
+rank results for all faults which do not report promissing results. However, 
+if we only consider the faults which can benefit from our approach, we can observe that there is a considerable
 amount of cases where the approach is actually successful. For
@@
 \begin{figure}[h]
-	\vspace{-1cm}
+	\vspace{-1.8cm}
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
@@
 		\label{fig:performance}
+		\vspace{-0.3cm}
 \end{figure}
@@
 \section{Related Work}
-\Rui{Introductory sentences should say something like: model-based software
-debugging, from the DX community, has been shown to be similar to slicing
-Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
-interesting techniques having been pursued because of scalability. We have
-achieved it with a type of program slicing --- critical slicing. Next, we
-visit the previous works on program slicing and SFL, without the idea of
-being exhaustive, but merely discussing the works that we deem relevant for
-this paper.}
-
-\Rui{revisit sentences; check if recent papers are cited.}
-
-\subsection{Program Slicing}
-
-Program Slicing is an old technique with several applications in PL
-and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
-implemented in different ways. Dynamic Slicing has found its main
-application in fault
-localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
-context, failing tests exist. Research in this area has mainly focused
-on slicing code
-efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
-and avoiding data and control omission
-errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
-cases where tests fail because some part of the code was not executed
-when it should. Dynamic fault localization techniques cannot hope to
-soundly report bugs in those cases. The issue is that incorporating
-static information to capture those cases can result in unacceptably
-large slices, which defeats the purpose of reducing the fault search
-space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
-can be used with any form of dynamic slicing. We chose an
-implementation of Critical
-Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.
-
-\subsection{SFL}
-
-Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
-popular automated fault localization techniques within the Software Engineering
-community. They correlate information about program fragments that have been
-exercised in multiple program execution traces (also called \textit{program
-spectra}) with information about successful and failing executions. By doing
-that, statistics-based approaches yield a list of suspect program fragments
-sorted by their likelihood to be at fault. Since this technique is efficient in
-practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
-
-Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
-fault localization technique that takes as input a test suite including at least
-one failing test and reports on output a ranked list of components likely to be
-in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
-
-\subsection{Combination of \sfl{} and Slicing}
-
-Prior work has investigated the combination of dynamic slicing and
-spectrum-based fault
-localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
-the methodology used in these papers vary, the overall message is that
-the combination is valuable. Note that slicing alone does not provide
-the guarantee of improvement to \sfl{} as statements discarded with
-slicing could have been ranked lower compared to faulty
-statements. This paper differs from prior work in that it uses a much
-larger dataset of programs and faults and a more rigorous experimental
-methodology.
-%
+
+Model-based diagnosis is a well-known approach that has been proposed by the
+DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
+of model-based diagnosis to localize software faults have demonstrated that it
+can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
+
+% \Rui{Introductory sentences should say something like: model-based software
+% debugging, from the DX community, has been shown to be similar to slicing
+% Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
+% interesting techniques having been pursued because of scalability. We have
+% achieved it with a type of program slicing --- critical slicing. Next, we
+% visit the previous works on program slicing and SFL, without the idea of
+% being exhaustive, but merely discussing the works that we deem relevant for
+% this paper.}
+%
+% \Rui{revisit sentences; check if recent papers are cited.}
+
+% \subsection{Program Slicing}
+%
+% Program Slicing is an old technique with several applications in PL
+% and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
+% implemented in different ways. Dynamic Slicing has found its main
+% application in fault
+% localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
+% context, failing tests exist. Research in this area has mainly focused
+% on slicing code
+% efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
+% and avoiding data and control omission
+% errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
+% cases where tests fail because some part of the code was not executed
+% when it should. Dynamic fault localization techniques cannot hope to
+% soundly report bugs in those cases. The issue is that incorporating
+% static information to capture those cases can result in unacceptably
+% large slices, which defeats the purpose of reducing the fault search
+% space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
+% can be used with any form of dynamic slicing. We chose an
+% implementation of Critical
+% Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.
+%
+%
+% \subsection{SFL}
+%
+% Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
+% popular automated fault localization techniques within the Software Engineering
+% community. They correlate information about program fragments that have been
+% exercised in multiple program execution traces (also called \textit{program
+% spectra}) with information about successful and failing executions. By doing
+% that, statistics-based approaches yield a list of suspect program fragments
+% sorted by their likelihood to be at fault. Since this technique is efficient in
+% practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
+%
+% Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
+% fault localization technique that takes as input a test suite including at least
+% one failing test and reports on output a ranked list of components likely to be
+% in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
+%
+% \subsection{Combination of \sfl{} and Slicing}
+%
+% Prior work has investigated the combination of dynamic slicing and
+% spectrum-based fault
+% localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
+% the methodology used in these papers vary, the overall message is that
+% the combination is valuable. Note that slicing alone does not provide
+% the guarantee of improvement to \sfl{} as statements discarded with
+% slicing could have been ranked lower compared to faulty
+% statements. This paper differs from prior work in that it uses a much
+% larger dataset of programs and faults and a more rigorous experimental
+% methodology.
+% %
 \section{Conclusions and Future Work}
@@
 while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
-and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. \ds{} is This paper reports the outcome of
+and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
 a study using real-world applications with the goal of demystifying the impact

### 2019-02-24 paper/ijcai/paper.tex
rw

@@
 can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
-
-% \Rui{Introductory sentences should say something like: model-based software
-% debugging, from the DX community, has been shown to be similar to slicing
-% Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
-% interesting techniques having been pursued because of scalability. We have
-% achieved it with a type of program slicing --- critical slicing. Next, we
-% visit the previous works on program slicing and SFL, without the idea of
-% being exhaustive, but merely discussing the works that we deem relevant for
-% this paper.}
-%
-% \Rui{revisit sentences; check if recent papers are cited.}
-
-% \subsection{Program Slicing}
-%
-% Program Slicing is an old technique with several applications in PL
-% and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
-% implemented in different ways. Dynamic Slicing has found its main
-% application in fault
-% localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
-% context, failing tests exist. Research in this area has mainly focused
-% on slicing code
-% efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
-% and avoiding data and control omission
-% errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
-% cases where tests fail because some part of the code was not executed
-% when it should. Dynamic fault localization techniques cannot hope to
-% soundly report bugs in those cases. The issue is that incorporating
-% static information to capture those cases can result in unacceptably
-% large slices, which defeats the purpose of reducing the fault search
-% space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
-% can be used with any form of dynamic slicing. We chose an
-% implementation of Critical
-% Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.
-%
+Not many interesting techniques have been pursued due to scalability limitations.
+We have tackled this using an old program slicing technique --- critical slicing~\cite{DeMillo:1996:CSS:229000.226310}.
+
+Dynamic Slicing has found its main
+application in fault
+localization~\cite{Agrawal:1990:DPS:93542.93576} on the minimization of failing tests. Research in this area has mainly focused
+on slicing code
+efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
+and avoiding data and control omission
+errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Dynamic fault localization techniques cannot hope to
+soundly report bugs in those cases. The issue is that incorporating
+static information to capture those cases can result in unacceptably
+large slices, which defeats the purpose of reducing the fault search
+space. 
 %
@@
 %
-% Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
-% popular automated fault localization techniques within the Software Engineering
-% community. They correlate information about program fragments that have been
-% exercised in multiple program execution traces (also called \textit{program
-% spectra}) with information about successful and failing executions. By doing
-% that, statistics-based approaches yield a list of suspect program fragments
-% sorted by their likelihood to be at fault. Since this technique is efficient in
-% practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
+Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
+popular automated fault localization techniques within the Software Engineering
+community. They correlate information about program fragments that have been
+exercised in multiple program execution traces (also called \textit{program
+spectra}) with information about successful and failing executions. By doing
+that, statistics-based approaches yield a list of suspect program fragments
+sorted by their likelihood to be at fault. Since this technique is efficient in
+practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
 %
@@
 optimization.
-
 Future work is as follows: improve our oracle heuristics to handle more exceptions;

### 2019-02-25 paper/ijcai/paper.tex
discussion + rw

@@
 	\vspace{-0.2cm}
-
 	\small
@@
 
-Although this dataset has more than $50\%$ of fault of omissions, our
-simple slicing approach was capable of improving the ranking of $95$
-faults for $k=5$ and $115$ faults for $k=10$. Table \ref{table:st}
+Table \ref{table:st}
 presents the statistics to determine if the observed results are
@@
 $99\%$ confidence, the results show that the distributions are
-distinct.
-
-To understand which techniques perform differently, \ie{} to answer
+distinct. To understand which techniques perform differently, \ie{} to answer
 the question \textit{Does \combpar{k} perform differently than
@@
 differently. We can determine with $95\%$ confidence that the
-performance of each pair of techniques is different. As the results
-are statiscally significant, we can confirm that \ds{} improves \sfl{}.
+performance of each pair of techniques is different.
 
@@
 
+As the results are statistically significant, it is possible to state that \combpar{k} has a positive effect on the localization of some types of bugs.
+There is indeed a problem on using slicing on fault of omission bugs that needs further research.
+Although, this dataset has more than $50\%$ of fault of omissions, our
+simple slicing approach was capable of improving the ranking of $95$ faults for $k=5$ and $115$ faults for $k=10$. These are promissing results from what Automated
+Program Repair techniques may directly benefit to improve the accuracy of their own techniques.
+
 \subsection{Threats to validity}
 %
-A potential threat to external validity related to the set of programs used in
+A potential threat to \textit{external validity} related to the set of programs used in
 our study. When choosing the projects for our study, our aim was to opt for
@@
 It is importance to notice that our study does not evaluate the fault of the \closure{}
-project since it requires high CPU to perform the \combpar{k} evaluation.
-
-A potential threat to construct validity relates to the choice of oracle generation
+project since it requires high CPU to perform the \combpar{k} evaluation. A potential threat to \textit{construct validity} relates to the choice of oracle generation
 for the Lithium toolset. However, we argue that our choice is able to capture whether
 a program is failing because of the same reason.
-
-The main threat to internal validity lies in the complexity of several of the tools
+The main threat to \textit{internal validity} lies in the complexity of several of the tools
 used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
@@
 Model-based diagnosis is a well-known approach that has been proposed by the
-DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
+DX community, a sub-field of AI~\cite{REITER198757,wotawa2002relationship,DEKLEER200325}. Applications
 of model-based diagnosis to localize software faults have demonstrated that it
-can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.
+can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,nica2013use}.
 Not many interesting techniques have been pursued due to scalability limitations.
-We have tackled this using an old program slicing technique --- critical slicing~\cite{DeMillo:1996:CSS:229000.226310}.
+We have tackled this using the program slicing technique --- critical slicing~\cite{DeMillo:1996:CSS:229000.226310} --- for its simplicity and generality.
 
@@
 application in fault
-localization~\cite{Agrawal:1990:DPS:93542.93576} on the minimization of failing tests. Research in this area has mainly focused
+localization~\cite{Agrawal:1990:DPS:93542.93576}, e.g.,  on the minimization of failing tests through the identification of code components that do not contribute to the fault revelation.
+Research in this area has mainly focused
 on slicing code
 efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
-and avoiding data and control omission
-errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Dynamic fault localization techniques cannot hope to
-soundly report bugs in those cases. The issue is that incorporating
-static information to capture those cases can result in unacceptably
-large slices, which defeats the purpose of reducing the fault search
-space. 
+and locate and contour faults of omission~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. 
 %
@@
 Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
-popular automated fault localization techniques within the Software Engineering
-community. They correlate information about program fragments that have been
-exercised in multiple program execution traces (also called \textit{program
-spectra}) with information about successful and failing executions. By doing
-that, statistics-based approaches yield a list of suspect program fragments
-sorted by their likelihood to be at fault. Since this technique is efficient in
-practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
-%
-% Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
-% fault localization technique that takes as input a test suite including at least
-% one failing test and reports on output a ranked list of components likely to be
-% in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
-%
-% \subsection{Combination of \sfl{} and Slicing}
-%
-% Prior work has investigated the combination of dynamic slicing and
-% spectrum-based fault
-% localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
-% the methodology used in these papers vary, the overall message is that
-% the combination is valuable. Note that slicing alone does not provide
-% the guarantee of improvement to \sfl{} as statements discarded with
-% slicing could have been ranked lower compared to faulty
-% statements. This paper differs from prior work in that it uses a much
-% larger dataset of programs and faults and a more rigorous experimental
-% methodology.
+popular automated fault localization techniques. Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
+fault localization technique used to rank faulty components ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
+This technique uses tests coverage information to rank program's components.
+We suspect that several highly suspicious components—often involved in failing, but seldom in passing test runs—may be unrelated to the bug.
+Prior work has investigated the \ds{}-\sfl{} combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
+Overall,
+these studies reported promissing results but based their conclusions on a very small group of faults and using different techniques.
+Although, \ds{} does not ensure the improvement of \sfl{} since it can remove faulty statements from the failing test, we believe it has a great potential to help reducing test cases and improve \sfl{} accuracy.
+In this study, a larger set of faults is evaluated and a more rigorous experimental methodology.
+
 % %

### 2019-02-25 paper/ijcai/paper.tex
pass over rw

@@
 
-Model-based diagnosis is a well-known approach that has been proposed by the
-DX community, a sub-field of AI~\cite{REITER198757,wotawa2002relationship,DEKLEER200325}. Applications
-of model-based diagnosis to localize software faults have demonstrated that it
-can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,nica2013use}.
-Not many interesting techniques have been pursued due to scalability limitations.
-We have tackled this using the program slicing technique --- critical slicing~\cite{DeMillo:1996:CSS:229000.226310} --- for its simplicity and generality.
-
-Dynamic Slicing has found its main
-application in fault
-localization~\cite{Agrawal:1990:DPS:93542.93576}, e.g.,  on the minimization of failing tests through the identification of code components that do not contribute to the fault revelation.
-Research in this area has mainly focused
-on slicing code
-efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
-and locate and contour faults of omission~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. 
-%
-% \subsection{SFL}
-%
+Model-based diagnosis is a well-known approach that has been proposed by the DX
+community, a sub-field of
+AI~\cite{REITER198757,wotawa2002relationship,DEKLEER200325}. Applications of
+model-based diagnosis to localize software faults have demonstrated that it can
+be framed as dynamic
+slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,nica2013use}.
+Not many interesting techniques have been pursued due to scalability
+limitations. We have tackled this using the program slicing technique ---
+critical slicing~\cite{DeMillo:1996:CSS:229000.226310} --- for its simplicity
+and generality.
+
+Dynamic Slicing has found its main application in fault
+localization~\cite{Agrawal:1990:DPS:93542.93576}, e.g.,  on the minimization of
+failing tests through the identification of code components that do not
+contribute to the fault revelation. Research in this area has mainly focused on
+slicing code
+efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455} and
+locate and contour faults of
+omission~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}.
+
 Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
-popular automated fault localization techniques. Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
-fault localization technique used to rank faulty components ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
+popular automated fault localization techniques. Spectrum-based fault
+localization (\sfl{}) is amongst the most common statistical fault localization
+technique used to rank faulty components
+~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
 This technique uses tests coverage information to rank program's components.
-We suspect that several highly suspicious components—often involved in failing, but seldom in passing test runs—may be unrelated to the bug.
-Prior work has investigated the \ds{}-\sfl{} combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
-Overall,
-these studies reported promissing results but based their conclusions on a very small group of faults and using different techniques.
-Although, \ds{} does not ensure the improvement of \sfl{} since it can remove faulty statements from the failing test, we believe it has a great potential to help reducing test cases and improve \sfl{} accuracy.
-In this study, a larger set of faults is evaluated and a more rigorous experimental methodology.
+\Rui{this sentence does not belong to rw (We suspect...)-->} We
+suspect that several highly suspicious components—often involved in failing, but
+seldom in passing test runs—may be unrelated to the bug.
+
+Prior work has investigated the \ds{}-\sfl{}
+combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
+Overall, these studies reported promissing results but based their conclusions
+on a very small group of (mostly artificial) faults and using different
+techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
+Although, \ds{} does not ensure the improvement of \sfl{} since it
+can remove faulty statements from the failing test, we believe it has a great
+potential to help reducing test cases and improve \sfl{} accuracy. In this
+study, a larger set of faults is evaluated and a more rigorous experimental
+methodology.
 

### 2019-02-25 paper/ijcai/paper.tex
minor issues
pass on abstract (reconsider last sentence later)

@@
   \numFaults{} documented software faults from a credible dataset--}
-to evaluate the effects of combining \ds{} with \sfl{}. We suspect
-that several highly suspicious components---often involved in failing,
-but seldom in passing test runs---may be unrelated to the bug. With
-the aforementioned combination, such components could be located and
-their suspiciousness reduced.  This study also discusses the practical
-impact of the \ds{} key limitation---the risk of missing faulty
-statements. Results indicate that \ds{} misses faulty statements in
-$9\%$\comments{($23$ misses)} of the $\numFaults{}$ cases and that
-the \ds{}-\sfl{} combination, coined as Tandem-SL, improves
-the diagnostic accuracy up to $73.7\%$ (\avgImprov\ on average). To sum,
-we found that the \ds{}-\sfl{} combination was practical and effective
-and encourage new \sfl{} techniques to be evaluated against that
-optimization.
+to reassess the effects of combining \ds{} with \sfl{}.  With this
+combination, components that are often involved in failing but seldom
+in passing test runs could be located and their suspiciousness
+reduced. Results show that the \ds{}-\sfl{} combination, coined as
+Tandem-SL, improves the diagnostic accuracy up to $73.7\%$
+(\avgImprov\ on average). Furthermore, results indicate that the risk
+of missing faulty statements, which \ds{}'s key limitation, is not
+high---~\ds{} misses faulty statements in $9\%$\comments{($23$
+  misses)} of the $\numFaults{}$ cases. To sum, we found that the
+\ds{}-\sfl{} combination was practical and effective and encourage new
+\sfl{} techniques to be evaluated against that optimization.
 \end{abstract}
@@
 		\vspace{-0.4cm}
-		\caption{Cost of Diagnosis ($\Delta{}C$) per variant}
+		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
 		\label{fig:diagnosis}
@@
 is not normally distributed, we use Friedman test, a non-parametric
-statistical test of hypothesis. The null-hypothesis is that the
+statistical test of hypothesis. The null hypothesis is that the
 ranking results of all techniques and variants are the same. With

### 2019-02-25 paper/ijcai/paper.tex
quick pass up to (excluding) 5.2

@@
 programs from the Defects4J (D4J)
-dataset~\cite{just-defects4j-issta2014}, which is frequently used to
+benchmark~\cite{just-defects4j-issta2014}, which is frequently used to
 evaluate fault localization research. Results show that \ds{} misses
@@
 faults analyzed. Furthermore, we found that the combination of the two
-approaches may improve fault localization up to $73.7\%$ (\avgImprov\ on average).
- To sum, results indicate that the
+approaches may improve fault localization up to $73.7\%$
+(\avgImprov\ on average).\Mar{do we have supporting data to say that
+  the improvement is bigger when we care the most? for the cases SFL
+  performs worse? if yes, can we show average for that?} To sum, results indicate that the
 risk of applying the technique is relatively low for the positive
@@
 Model-based diagnosis is a well-known approach that has been proposed by the
-DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
+DX community\Mar{I don't know what is DX. suggest to expand the
+  acronym and/or cite.}\Mar{say shortly (in general terms) what is the
+  goal. what is that good for.}, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
 of model-based diagnosis to localize software faults have demonstrated that it
@@
 Table~\ref{tab:df4j} shows size, number of tests, and number of
-faults, for each considered program. $2$ subjects from Math
-were not considered because we were not able to reproduce them
-in the machine used for the experiments.
+faults, for each considered program. Two faults from \cmath{} were not
+considered because we were unable to reproduce them in our
+environment.
+
+\lang{} is a library providing utility functions for the
+     {\small\texttt{java.lang}} API. \cmath{} is a library of
+     self-contained mathematics and statistics components.\comments{
+       The \closure{} is a toolset for turning JavaScript files into
+       smaller scripts for faster download and execution in the
+       browser.} \chart{} is a Java library for creating charts.
+     \jtime{} is a library for manipulating date and time\comments{,
+       providing a simpler API compared to
+       {\small\texttt{java.util.Date}}}. \mockito{} is a mocking
+     testing framework.
 
@@
 
-\lang{} is a
-library that provides a set of helper utilities for the
-{\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
-self-contained mathematics and statistics components.\comments{ The
-  \closure{} is a toolset for turning JavaScript files into smaller
-  scripts for faster download and execution in the browser.} \chart{}
-is a Java library for creating charts.  \jtime{} is a lightweight
-library that aims to replace the default Java
-{\small\texttt{java.util.Date}} classes providing simpler
-APIs. \mockito{} is a mocking testing framework.
-
 %% Originally, this benchmark includes six different subjects and 395
@@
 
-As to quantify complexity of fault localization on this dataset, we
-additionally counted the number of cases of ``fault of omission'', a
-popular metric in fault localization research for that
-purpose~\cite{Pearson:2017:EIF:3097368.3097441}.
-A fault of omission (\foo) occurs when
-the program is buggy because some code is missing, i.e., a bug that is
-corrected by adding code. Intuitively, the ability of techniques to
-produce accurate diagnostic reports in those cases might be poor since
-fault of omission bugs are very difficult to locate. This dataset has a
-total of $59.7\%$ of \foo s which may contribute negatively to our
-results since \sfl{} strives to rank these cases.
-%in producing
-%high-qualitiy diagnosis.
-
-%\subsection{Experimental Methodology}
-%\label{sec:methodology}
+As to quantify complexity of fault localization on this benchmark, we
+counted the number of cases of ``fault of omission'', a popular metric
+in fault localization research for that
+purpose~\cite{Pearson:2017:EIF:3097368.3097441}.  A fault of omission
+(\foo) occurs when the program is buggy because some code is missing,
+i.e., a fix to the bug iss created by adding code as opposed to
+modifying or changing code. Intuitively, the ability of techniques to
+produce accurate diagnostic reports in those cases might be poor as
+techniques can only extract information about existing statements,
+which are not problematic. This dataset has a total of $59.7\%$ of
+\foo s, making it challenging for techniques to perform
+well. \Mar{Sofia, does it make sense to show a histogram of (initial)
+  rankings of pure SFL to complement this argument? Say, frequency of
+  cases SFL reports on <top-10 statements in the ranking, then
+  frequency within top-10> and <top-20, etc.}
 
 \subsection{Techniques}
+\Mar{---------------------- estou aqui}
+
 One important independent variable for this study is the scope of

### 2019-02-25 paper/ijcai/paper.tex
minor comment

@@
 		test engineering problems and fault of omissions (left) and only considering
-		the cases where \combpar{k} achieved improvement under one of the variants (right)}
+		the cases where \combpar{k} achieved improvement under one of
+      the variants (right)\Mar{por favor, aumente o tamanho dos labels
+      (nao consigo enxergar na impressao).}}
 		\label{fig:boxplot}

### 2019-02-25 paper/ijcai/paper.tex
DX

@@
 Model-based diagnosis is a well-known approach that has been proposed by the
-DX community\Mar{I don't know what is DX. suggest to expand the
-  acronym and/or cite.}\Mar{say shortly (in general terms) what is the
-  goal. what is that good for.}, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
+DX community, a sub-field of AI that develops algorithms and techniques to
+determine the root-cause of observed failures.~\cite{REITER198757,DEKLEER200325}. Applications
 of model-based diagnosis to localize software faults have demonstrated that it
@@
 
-Prior work has investigated the \ds{}-\sfl{}
+coPrior work has investigated the \ds{}-\sfl{}
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.

### 2019-02-25 paper/ijcai/paper.tex
another fix

@@
 approaches may improve fault localization up to $73.7\%$
-(\avgImprov\ on average).\Mar{do we have supporting data to say that
-  the improvement is bigger when we care the most? for the cases SFL
-  performs worse? if yes, can we show average for that?} To sum, results indicate that the
+(\avgImprov\ on average). To sum, results indicate that the
 risk of applying the technique is relatively low for the positive
@@
 setup.
+% \Mar{do we have supporting data to say that
+%   the improvement is bigger when we care the most? for the cases SFL
+%   performs worse? if yes, can we show average for that?}
 
@@
 \foo s, making it challenging for techniques to perform
-well. \Mar{Sofia, does it make sense to show a histogram of (initial)
-  rankings of pure SFL to complement this argument? Say, frequency of
-  cases SFL reports on <top-10 statements in the ranking, then
-  frequency within top-10> and <top-20, etc.}
+well.
+
+% \Mar{Sofia, does it make sense to show a histogram of (initial)
+%   rankings of pure SFL to complement this argument? Say, frequency of
+%   cases SFL reports on <top-10 statements in the ranking, then
+%   frequency within top-10> and <top-20, etc.}
 
@@
 		the cases where \combpar{k} achieved improvement under one of
-      the variants (right)\Mar{por favor, aumente o tamanho dos labels
-      (nao consigo enxergar na impressao).}}
+      the variants (right)}
 		\label{fig:boxplot}

### 2019-02-25 paper/ijcai/paper.tex
small fixes

@@
 (\avgImprov\ on average). Furthermore, results indicate that the risk
-of missing faulty statements, which \ds{}'s key limitation, is not
+of missing faulty statements, which is a \ds{}'s key limitation, is not
 high---~\ds{} misses faulty statements in $9\%$\comments{($23$
@@
 SFL$^{k}$, which is the comparison baseline. \combpar{k} is as defined
-in Section~\ref{sec:approach} (see Step 2 of the workflow) whereas
+in Section~\ref{sec:approach} (see Step $2$ of the workflow) whereas
 SFL$^{k}$ is as SFL, but it produces a ranking including exclusively
@@
 
-\begin{table}[h!]
+\begin{table}[h]
 	\vspace{-0.2cm}
@@
 In \textbf{RQ3}, we evaluate the effective impact of combining \ds{}
-with \sfl{} to improve fault localization. The first experiment we ran to assess impact consists of measuring the
-\emph{difference of diagnosis cost}. This metric has been previously
-used in other studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}. More specifically, we computed
+with \sfl{} to improve fault localization. The first experiment we ran 
+to assess impact consists of measuring the \emph{difference of diagnosis 
+cost}. This metric has been previously used in other studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}. 
+More specifically, we computed
 $\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where
@@
 cases where \ds{} improves \sfl. Although, we observe
-a considerable amount of cases where $\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
+a considerable amount of cases where $\Delta{}C$ is negative or zero in 
+Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount 
+of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
+
 \begin{figure}[h]
@@
 		\vspace{-0.2cm}
-
 \end{figure}
@@
 rank results for all faults which do not report promissing results. However,
-if we only consider the faults which can benefit from our approach, we can observe that there is a considerable
+if we only consider the faults which can benefit from our approach, 
+we can observe that there is a considerable
 amount of cases where the approach is actually successful. For
-$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ on average) statements
-on the ranking and an impressive maximum ranking improvement
+$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ 
+on average) statements on the ranking and an impressive maximum ranking improvement
 of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
@@
 
-\begin{table}[h!]
+\begin{table}[h]
 	\tiny
@@
 pairs of techniques. Each square represents the
-statistical significance of the diagnostic accuracy amongst the different techniques, i.e.,
-if it is significant it means that the techniques perform
+statistical significance of the diagnostic accuracy amongst the different 
+techniques, i.e., if it is significant it means that the techniques perform
 differently. We can determine with $95\%$ confidence that the
@@
 
-As the results are statistically significant, it is possible to state that \combpar{k} has a positive effect on the localization of some types of bugs.
-There is indeed a problem on using slicing on fault of omission bugs that needs further research.
+As the results are statistically significant, it is possible to state that \combpar{k} 
+has a positive effect on the localization of some types of bugs. There is indeed a 
+problem on using slicing on fault of omission bugs that needs further research. 
 Although, this dataset has more than $50\%$ of fault of omissions, our
-simple slicing approach was capable of improving the ranking of $95$ faults for $k=5$ and $115$ faults for $k=10$. These are promissing results from what Automated
-Program Repair techniques may directly benefit to improve the accuracy of their own techniques.
+simple slicing approach was capable of improving the ranking of $95$ faults for $k=5$ 
+and $115$ faults for $k=10$. These are promissing results from what Automated
+Program Repair techniques may directly benefit to improve the accuracy of their own 
+techniques.
 
@@
 It is importance to notice that our study does not evaluate the fault of the \closure{}
-project since it requires high CPU to perform the \combpar{k} evaluation. A potential threat to \textit{construct validity} relates to the choice of oracle generation
+project since it requires high CPU to perform the \combpar{k} evaluation. A potential
+threat to \textit{construct validity} relates to the choice of oracle generation
 for the Lithium toolset. However, we argue that our choice is able to capture whether
@@
 while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
-and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
+and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis 
+techniques and normally seen as complementary. This paper reports the outcome of
 a study using real-world applications with the goal of demystifying the impact

### 2019-02-25 paper/ijcai/paper.tex
pass on techniques (5.2)

@@
 \subsection{Techniques}
-\Mar{---------------------- estou aqui}
-
 One important independent variable for this study is the scope of
-dynamic slicing. Slicing the entire code would be unacceptably
-expensive as Critical Slicing needs to re-compile the affected file at
-every iteration, \ie{}, after deleting statements and before checking
-the oracle (see Section~\ref{sec:slicing}). We control the scope of
-slicing through the variable $k$, which denotes the number of distinct
-files that dynamic slicing will minimize. In this study, we used $5$ and
-$10$ as the values of $k$, following the same values as in previous fault
-localization studies~\cite{ang-perez-van-deursen-rui-2017}.
-The $k$ files for minimization are selected
-from the \sfl{} ranking as follows. First, we build a rank of files by
-determining, for each ranked statement, the file that declares
-it. Then, we select the top $k$ distinct files from such file ranking.
+analysis for the techniques. Analyzing long rankings would be
+unacceptably expensive not only for
+humans~\cite{Parnin:2011:ADT:2001420.2001445} but also for
+machines. For example, Critical Slicing needs to re-compile the
+affected file at every iteration, \ie{}, after deleting statements and
+before checking the oracle (see Section~\ref{sec:slicing}).
+%% how we do it
+We control the scope of analysis through the variable $k$, denoting
+the number of most-suspicious files that will be analyzed. These files
+are selected from the \sfl{} ranking as follows. First, we build a
+ranking of files by determining, for each ranked statement, the file
+that declares it. Then, we select the top-$k$ distinct files from such
+file ranking.
 
@@
 in Section~\ref{sec:approach} (see Step $2$ of the workflow) whereas
-SFL$^{k}$ is as SFL, but it produces a ranking including exclusively
-the statements from the best-$k$ ranked files.
+SFL$^{k}$ is as SFL, but it produces a ranking only including the
+statements from the top-$k$ ranked files. In this study, we used $5$
+and $10$ as the values of $k$, following the same choice as in
+previous fault localization
+studies~\cite{ang-perez-van-deursen-rui-2017}.
 
@@
 \toprule
-  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
-Mean  & \textbf{590.7} (584.3)   &  \textbf{512.7} (516.4)  & \textbf{573.4} (679.7)  & \textbf{506.6} (614.0)   \\ \midrule
-Median & \textbf{46.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
-Variance & \textbf{1257.0} (1223.1)  &  \textbf{1171.5} (1148.1) & \textbf{1239.1} (1352.4) &  \textbf{1167.0} (1294.9) \\ \midrule
-Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
+  & SFL$^{5}$  & \combpar{5}       & SFL$^{10}$                 & \combpar{10}              \\ \midrule
+Mean  & \textbf{590.7} (584.3) & \textbf{573.4} (679.7)   &  \textbf{512.7} (516.4)    & \textbf{506.6} (614.0)   \\ \midrule
+Median & \textbf{46.5} (49.4) & \textbf{42.7} (69.3)      & \textbf{54.5} (53.0) & \textbf{40.0} (56.9)\\ \midrule
+Variance & \textbf{1257.0} (1223.1) & \textbf{1239.1} (1352.4)  &  \textbf{1171.5} (1148.1) &  \textbf{1167.0} (1294.9) \\ \midrule
+Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} &  \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
 Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
@@
 This technique uses tests coverage information to rank program's components.
-\Rui{this sentence does not belong to rw (We suspect...)-->} We
-suspect that several highly suspicious components—often involved in failing, but
-seldom in passing test runs—may be unrelated to the bug.
-
-coPrior work has investigated the \ds{}-\sfl{}
+
+Prior work has investigated the \ds{}-\sfl{}
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
@@
 on a very small group of (mostly artificial) faults and using different
-techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
-Although, \ds{} does not ensure the improvement of \sfl{} since it
-can remove faulty statements from the failing test, we believe it has a great
-potential to help reducing test cases and improve \sfl{} accuracy. In this
+techniques. In this
 study, a larger set of faults is evaluated and a more rigorous experimental
 methodology.
+In contrast with other studies on this combination,
+our approach is the first using Critical Slicing to minimize test cases
+and leveraging \sfl{} rank to choose and minimize the top-$k$ of
+highest-ranked faulty classes.
 
@@
 \end{document}
+
+%%  LocalWords:  SFL

### 2019-02-25 paper/ijcai/paper.tex
updating table 5

--- 2019-02-25 paper/ijcai/paper.tex
@@
 This technique uses tests coverage information to rank program's components.
+
 \Rui{this sentence does not belong to rw (We suspect...)-->} We
@@
 
-coPrior work has investigated the \ds{}-\sfl{}
+Prior work has investigated the \ds{}-\sfl{}
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
@@
 on a very small group of (mostly artificial) faults and using different
-techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
+techniques.
+
+\Rui{not related work. more of motivation (avoid words such as believe)-->}
 Although, \ds{} does not ensure the improvement of \sfl{} since it

### 2019-02-25 paper/ijcai/paper.tex
rw

@@
 
-\Rui{this sentence does not belong to rw (We suspect...)-->} We
-suspect that several highly suspicious components—often involved in failing, but
-seldom in passing test runs—may be unrelated to the bug.
-
 Prior work has investigated the \ds{}-\sfl{}
@@
 on a very small group of (mostly artificial) faults and using different
-techniques.
-
-\Rui{not related work. more of motivation (avoid words such as believe)-->}
-Although, \ds{} does not ensure the improvement of \sfl{} since it
-can remove faulty statements from the failing test, we believe it has a great
-potential to help reducing test cases and improve \sfl{} accuracy. In this
+techniques. In this
 study, a larger set of faults is evaluated and a more rigorous experimental
 methodology.
+In contrast with other studies on this combination,
+our approach is the first using Critical Slicing to minimize test cases
+and leveraging \sfl{} rank to choose and minimize the top-$k$ of
+highest-ranked faulty classes.
 

### 2019-02-25 paper/ijcai/paper.tex
pass on RQ3 (halfway through)

--- 2019-02-25 paper/ijcai/paper.tex
@@
 
+%% a popular metric in fault
+%% localization research for that
+%% purpose.  A fault of omission
+%% (\foo) occurs when the program is buggy because some code is missing,
+%% i.e., a fix to the bug is created by adding code as opposed to
+%% modifying or changing code.
+
 As to quantify complexity of fault localization on this benchmark, we
-counted the number of cases of ``fault of omission'', a popular metric
-in fault localization research for that
-purpose~\cite{Pearson:2017:EIF:3097368.3097441}.  A fault of omission
-(\foo) occurs when the program is buggy because some code is missing,
-i.e., a fix to the bug iss created by adding code as opposed to
-modifying or changing code. Intuitively, the ability of techniques to
-produce accurate diagnostic reports in those cases might be poor as
-techniques can only extract information about existing statements,
-which are not problematic. This dataset has a total of $59.7\%$ of
-\foo s, making it challenging for techniques to perform
-well.
+measured the frequency of ``faults of omission'' (\foo), which is a
+fault whose fix is materialized only with the addition of new
+code~\cite{Pearson:2017:EIF:3097368.3097441}. Intuitively, the ability
+of techniques to produce accurate diagnostic reports in those cases
+might be poor as existing statements are not problematic. We found
+that this dataset has a total of $59.7\%$ of \foo s, making it
+challenging for techniques to perform well.
 
@@
 localization with \comb{} is that dynamic slicing eliminates a high
-amount of code in the best ranked files. Table \ref{tab:red} shows, as
-percentages, the reduction of the top file sizes
-obtained with dynamic slicing for different values of
-$k$. Overall, results indicate
+amount of code from the best ranked files. Table \ref{tab:red} shows,
+as percentages, the size reduction of the top files obtained with
+dynamic slicing for different values of $k$. Overall, results indicate
 that dynamic slicing substantially reduces the size of highly-ranked
-files.
+files. \Mar{+ coverage?}
 
@@
 the sliced files for different values of $k$. These numbers indicate
-that in general \ds{} finds at least one faulty statement in the top
-$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
-is slightly improved to $91.2\%$ if we consider
+that in $87.3\%$ of the cases, on average, dynamic slicing finds at
+least one faulty statement in the top $5$ of the highest-ranked faulty
+classes. This number is slightly improved to $91.2\%$ if we consider
 the top $10$ of the highest-ranked faulty classes.
@@
 	\end{tabular}
-	\caption {\ds{} performance on capturing faulty statements, as
+	\caption {Dynamic Slicing performance on capturing faulty statements, as
      percentages. Higher is better.}
@@
 \combpar{k} and \sfl{}$^{k}$ considering the number of cases where the
-fault is captured by the technique. Note that the reason \sfl{}$^{k}$
-misses the fault is different compared to \combpar{k}. \sfl{}$^{k}$
-captures the fault if the fault is included within the top $k$ files;
-it misses the fault otherwise. Table~\ref{table:fsws} shows results,
-indicating that \combpar{k}, on average, captures more faults compared
-to \sfl{}$^{k}$. In only two cases \sfl{}$^{k}$ outperformed
-\combpar{k}. These results show that the majority of faulty statements
-are found on the $5$ highest ranked faulty classes and that
-\combpar{10} is the variant of our approach that performs better
-missing only $23$ out of the \numFaults\ ($\sim$8.8\%) faults.
+fault is captured by the technique within a certain bound $k$. Note
+that the reason \sfl{}$^{k}$ misses the fault is different compared to
+\combpar{k}. \sfl{}$^{k}$ captures the fault if it is included within
+the top $k$ files; it misses the fault
+otherwise. Table~\ref{table:fsws} shows results, indicating that
+\combpar{k}, typically, captures more faults compared to
+\sfl{}$^{k}$. In only two cases, highlighted in gray color,
+\sfl{}$^{k}$ outperformed \combpar{k}. These results show that the
+majority of faulty statements are found on the $5$ highest ranked
+faulty classes and that \combpar{10} is the variant of our approach
+that performs better missing only $23$ out of the
+\numFaults\ ($\sim$8.8\%) faults.
 
@@
 	\end{tabular}
-  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
+  \caption {Number of faults where at least one of the faulty
+    statements appears at the report of the technique. Higher is better.}
   \label{table:fsws}
@@
 
-In \textbf{RQ3}, we evaluate the effective impact of combining \ds{}
-with \sfl{} to improve fault localization. The first experiment we ran 
-to assess impact consists of measuring the \emph{difference of diagnosis 
-cost}. This metric has been previously used in other studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}. 
-More specifically, we computed
-$\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where
-$C$ denotes the diagnosis cost and is obtained by computing the mean
-position in the ranking of all buggy statements. $\Delta C >0$ means
-that the position of the faulty statement has decreased with
-\combpar{k}, \ie{}, the combination had a positive impact. $\Delta C
-<0$ means that \combpar{k} performs worse compared to its
-baseline. That could happen if dynamic slicing misses the faulty
-statement---the statements not included in the slice will have their
-suspiciousness scores reduced and ranks potentially reduced. $\Delta
-C=0$ means that the faulty statement remained in the same position.
-It is worth noting that we assume a perfect bug understanding, i.e.,
-if the developer sees the bug in the ranking, he is able to precisely
+In \textbf{RQ3}, we evaluate the impact of combining \ds{} with \sfl{}
+to improve fault localization. The first experiment we ran consists of
+measuring the \emph{difference of diagnosis cost} between the two
+fault localization techniques. This metric has been previously used in
+other
+studies~\cite{7390282,ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Perez:2018:LQR:3304889.3304927}.
+More specifically, we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
+C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
+obtained by computing the mean position in the ranking of all buggy
+statements. $\Delta C >0$ means that \combpar{k} outperformed the
+baseline, \ie{} the mean position of the faulty statements is smaller
+in \combpar{k} compared to that of the baseline. $\Delta C <0$ means
+that \combpar{k} performs worse compared to its baseline. That could
+happen if dynamic slicing misses the faulty statement. $\Delta C=0$
+means that the faulty statement remained in the same position.  It is
+worth noting that we assume perfect bug
+understanding~\cite{Parnin:2011:ADT:2001420.2001445}, i.e., if the
+developer sees the bug in the ranking, he is able to precisely
 determine if it is the faulty one.
@@
 Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
-relative to \sfl{}$^{k}$ using histograms over $\Delta{}C$ for
-different values of $k$. Note that (1) the number of cases where
-\sfl{}$^{k}$ outperforms \combpar{k} is very small compared and (2)
-the number of cases \combpar{k} outperforms \sfl{}$^{k}$ is
-significant and, as we increase the value of $k$, it increases (from
-$97$ to $117$ faults). The faults where the cost of diagnosis is
-negative are cases that (1) the faulty statements decreased in the ranking
-list due to being a fault of omission, (2) the test has design limitations
-which \ds~is not capable of handling, or (3) the buggy-class in not in
-the top $k$ of the highest-ranked faulty classes under analysis.
+relative to \sfl{}$^{k}$. The figure shows a histogram over
+$\Delta{}C$ for different values of $k$. Note that (1) the number of
+cases where the baseline outperforms \combpar{k} is small (\eg{}, $33$
+of the \numFaults\ faults for $k=10$) and that (2) the number of cases
+\combpar{k} outperforms the baseline is significative (\eg{}, $117$ of
+the \numFaults\ faults for $k=10$). One of the following reasons
+justifies the baseline outperforming \combpar{k}:\Mar{following
+  sentence is confusing IMO. suggest to clarify or remove. aren't
+  points two and three equivalent? as for one, isn't foo an issue both
+  for \combpar{k} and \sfl{}$^{k}$?} (1) a fault of omission, (2) the
+test has design limitations which \ds~is not capable of handling, or
+(3) the buggy-class in not in the top $k$ of the highest-ranked faulty
+classes under analysis.
 
@@
 \end{figure}
+
+\Mar{-------------------------- estou aqui}
 

### 2019-02-25 paper/ijcai/paper.tex
pass on RQ3 (not done)

@@
 
-\Mar{-------------------------- estou aqui}
-
-Figure~\ref{fig:boxplot} shows the $\Delta{}C$ distribution for each
-variant in two different cases. On the left, we do not consider the
-test engineering problems and faults of omission ($227$ faults). The two negative
-outliers present the cases where the buggy-class was not in the top
-$k$. On the right, we only consider the cases where at least one
-of the variants resulted in an increase of $\Delta{}C$ ($116$ faults), i.e., the
-cases where \ds{} improves \sfl. Although, we observe
-a considerable amount of cases where $\Delta{}C$ is negative or zero in 
-Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount 
-of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
+Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$. On
+the left-hand-side, the figure shows the distributions of $\Delta{}C$
+for different values of $k$, considering all faults except those where
+test engineering problems and faults of omission are manifested ($227$
+faults). The two negative outliers present the cases where the
+buggy-class was not in the top $k$. On the right, we only consider the
+cases where at least one of the variants resulted in an increase of
+$\Delta{}C$ ($116$ faults), i.e., the cases where \ds{} improves
+\sfl. Although, we observe a considerable amount of cases where
+$\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also
+see that there is a considerable amount of faults which could benefit
+a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
 
@@
 
-		\caption{Distribution of $\Delta{}C$ per variant when not considering
-		test engineering problems and fault of omissions (left) and only considering
-		the cases where \combpar{k} achieved improvement under one of
-      the variants (right)}
+		\caption{Distributions of $\Delta{}C$. On the left, distribution
+        considering all faults but those manifesting faults of
+        omission and engineering problems (227 faults). On the right,
+        distribution considering all cases where \combpar{k}
+        outperformed the baseline (116 faults).}
 		\label{fig:boxplot}
@@
      \toprule
-  & SFL$^{5}$  & \combpar{5}       & SFL$^{10}$                 & \combpar{10}              \\ \midrule
+  & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
+  & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
 Mean  & \textbf{590.7} (584.3) & \textbf{573.4} (679.7)   &  \textbf{512.7} (516.4)    & \textbf{506.6} (614.0)   \\ \midrule

### 2019-02-25 paper/ijcai/paper.tex
another pass

@@
 
+%% k=10
+\newcommand{\numOutPerformed}{$33$}%
+\newcommand{\numEquallyPerformed}{$110$}%
+
 Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
@@
 $\Delta{}C$ for different values of $k$. Note that (1) the number of
-cases where the baseline outperforms \combpar{k} is small (\eg{}, $33$
-of the \numFaults\ faults for $k=10$) and that (2) the number of cases
-\combpar{k} outperforms the baseline is significative (\eg{}, $117$ of
-the \numFaults\ faults for $k=10$). One of the following reasons
-justifies the baseline outperforming \combpar{k}:\Mar{following
-  sentence is confusing IMO. suggest to clarify or remove. aren't
-  points two and three equivalent? as for one, isn't foo an issue both
-  for \combpar{k} and \sfl{}$^{k}$?} (1) a fault of omission, (2) the
-test has design limitations which \ds~is not capable of handling, or
-(3) the buggy-class in not in the top $k$ of the highest-ranked faulty
-classes under analysis.
+cases where the baseline outperforms \combpar{k} is small (\eg{},
+\numOutPerformed\ of the \numFaults\ faults for $k=10$) and that (2)
+the number of cases \combpar{k} outperforms the baseline is
+significative (\eg{}, $117$ of the \numFaults\ faults for $k=10$). One
+of the following reasons justifies the baseline outperforming
+\combpar{k}:\Mar{following sentence is confusing IMO. suggest to
+  clarify or remove. aren't points two and three equivalent? as for
+  one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
+a fault of omission, (2) the test has design limitations which \ds~is
+not capable of handling, or (3) the buggy-class in not in the top $k$
+of the highest-ranked faulty classes under analysis.
 
@@
 
-Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$. On
-the left-hand-side, the figure shows the distributions of $\Delta{}C$
-for different values of $k$, considering all faults except those where
-test engineering problems and faults of omission are manifested ($227$
-faults). The two negative outliers present the cases where the
-buggy-class was not in the top $k$. On the right, we only consider the
-cases where at least one of the variants resulted in an increase of
-$\Delta{}C$ ($116$ faults), i.e., the cases where \ds{} improves
-\sfl. Although, we observe a considerable amount of cases where
-$\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also
-see that there is a considerable amount of faults which could benefit
-a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
+Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ for
+different sets of faults as to better understand the performance of
+\combpar{k}. On the left-hand-side, we show distributions of
+$\Delta{}C$, for different values of $k$, considering all cases where
+the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
+\numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
+(see Figure~\ref{fig:diagnosis}). The boxplots on the right-hand-side
+of the figure considers all the cases where the predicate
+$\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
+the cases of faults where the techniques perform equally.\Mar{sofia,
+  are you sure there are no zeros in this dataset? The min. in this
+  distibution (as per the base of the plot) seems to be 0.} To sum,
+although we observed a relatively small number cases where $\Delta{}C$
+is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
+is zero (\numEquallyPerformed), we observed that there is a
+considerable amount of cases where the use of \combpar{k} would be
+very beneficial.
 
@@
 
-In the following, we present statistical analysis to demonstrate that
-the distributions of $C$ for each technique are different.
-Table~\ref{table:st}, reports the average rank of all faulty
-statements of the \dfj{} faults considered to the study after applying both
-techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.
-In bold, we present the results of the $227$ faults that do not comprise the
-cases that are result of the limitations mentioned before (test design and fault
-of omission). These results show that \ds{} improves \sfl{} in a mean
-of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements,
-when considering $k=10$. Inside parentheses, we present the
-rank results for all faults which do not report promissing results. However,
-if we only consider the faults which can benefit from our approach, 
-we can observe that there is a considerable
-amount of cases where the approach is actually successful. For
-$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ 
-on average) statements on the ranking and an impressive maximum ranking improvement
-of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
-achieves a mean improvement of $19$ ($13.35\%$ on average) statements
-on the ranking and a maximum ranking improvement
-of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
-entire files are discarded in \combpar{5}, whose statements are
-included in the ranking of \combpar{10}. Consequently, the
-improvements obtained by the technique will not be as high if slicing
-on these additional files is unable to aggressively and safely discard
-statements. This also shows that slicing files, in addition to slicing
-statements from those files, is very beneficial for fault localization
-performance.
+In the following, we present statistical analysis of the techniques.
+Table~\ref{table:st} reports descriptive statistics about the
+distributions of $C$ for the techniques under different values of $k$.
+In bold, we present the results of the $227$ faults that do not
+comprise the cases that are result of the limitations mentioned before
+(test design and fault of omission). The number in parentheses are
+relative to the dataset including all data faults; note that results
+for this dataset are \emph{not} encouraging.
+
+These results show that \ds{}
+improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
+the average ranking of all faulty statements, when considering
+$k=10$. 
+However, if we only consider
+the faults which can benefit from our approach, we can observe that
+there is a considerable amount of cases where the approach is actually
+successful. For $k=5$, our approach achieves a mean improvement of
+$41.1$ ($9.57\%$ on average) statements on the ranking and an
+impressive maximum ranking improvement of $3171$ ($96.7\%$ on average)
+statements. Whereas for $k=10$, \combpar{k} achieves a mean
+improvement of $19$ ($13.35\%$ on average) statements on the ranking
+and a maximum ranking improvement of $209$ ($73.7\%$ on average)
+statements. Such difference is justified by the fact that entire files
+are discarded in \combpar{5}, whose statements are included in the
+ranking of \combpar{10}. Consequently, the improvements obtained by
+the technique will not be as high if slicing on these additional files
+is unable to aggressively and safely discard statements. This also
+shows that slicing files, in addition to slicing statements from those
+files, is very beneficial for fault localization performance.
 

### 2019-02-25 paper/ijcai/paper.tex
abstract + intro

@@
 \begin{abstract}
-Several approaches have been proposed in the literature to reduce
-debugging costs through automated software fault diagnosis.  Dynamic
-Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
-popular fault diagnosis techniques and normally seen as complementary.
-This paper reports on a comprehensive study\comments{--using
-  \numFaults{} documented software faults from a credible dataset--}
-to reassess the effects of combining \ds{} with \sfl{}.  With this
-combination, components that are often involved in failing but seldom
-in passing test runs could be located and their suspiciousness
-reduced. Results show that the \ds{}-\sfl{} combination, coined as
-Tandem-SL, improves the diagnostic accuracy up to $73.7\%$
-(\avgImprov\ on average). Furthermore, results indicate that the risk
-of missing faulty statements, which is a \ds{}'s key limitation, is not
-high---~\ds{} misses faulty statements in $9\%$\comments{($23$
-  misses)} of the $\numFaults{}$ cases. To sum, we found that the
-\ds{}-\sfl{} combination was practical and effective and encourage new
-\sfl{} techniques to be evaluated against that optimization.
+Several approaches have been proposed to reduce debugging costs through
+automated software fault diagnosis.  Dynamic Slicing (\ds{}) and Spectrum-based
+Fault Localization (\sfl{}) are popular fault diagnosis techniques and normally
+seen as complementary. This paper reports on a comprehensive
+study\comments{--using \numFaults{} documented software faults from a credible
+dataset--} to reassess the effects of combining \ds{} with \sfl{}.  With this
+combination, components that are often involved in failing but seldom in passing
+test runs could be located and their suspiciousness reduced. Results show that
+the \ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic
+accuracy up to $73.7\%$ (\avgImprov\ on average). Furthermore, results indicate
+that the risk of missing faulty statements, which is a \ds{}'s key limitation,
+is not high~---~\ds{} misses faulty statements in $9\%$\comments{($23$ misses)}
+of the $\numFaults{}$ cases. To sum, we found that the \ds{}-\sfl{} combination
+was practical and effective and encourage new \sfl{} techniques to be evaluated
+against that optimization.
 \end{abstract}
@@
 
-The contributions of this work are: 1)~an empirical study, using
+The contributions of this work are:
+\begin{itemize}
+ \item[1)]~an empirical study, using
 real-world applications and bugs, on the combination of \ds{} and
-\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
-tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination. The
+\sfl{} for bug localization of \emph{Java} faulty programs and
+\item[2)]~a
+tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination.
+\end{itemize}
+The
 tool as well as a replication package will be available once

### 2019-02-25 paper/ijcai/paper.tex
polishing

@@
 test runs could be located and their suspiciousness reduced. Results show that
-the \ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic
+the \ds{}-\sfl{} combination, coined as \comb, improves the diagnostic
 accuracy up to $73.7\%$ (\avgImprov\ on average). Furthermore, results indicate
@@
 is not high~---~\ds{} misses faulty statements in $9\%$\comments{($23$ misses)}
-of the $\numFaults{}$ cases. To sum, we found that the \ds{}-\sfl{} combination
+of the $\numFaults{}$ cases. To sum up, we found that the \ds{}-\sfl{} combination
 was practical and effective and encourage new \sfl{} techniques to be evaluated

### 2019-02-25 paper/ijcai/paper.tex
polishing

@@
 study involving \numFaults{} faults from \numPrograms{} different
-programs from the Defects4J (D4J)
+programs from the Defects4J 
 benchmark~\cite{just-defects4j-issta2014}, which is frequently used to

### 2019-02-25 paper/ijcai/paper.tex
polishing

@@
 faults analyzed. Furthermore, we found that the combination of the two
-approaches may improve fault localization up to $73.7\%$
-(\avgImprov\ on average). To sum, results indicate that the
+approaches improves fault localization up to $73.7\%$
+(\avgImprov\ on average). To sum up, results indicate that the
 risk of applying the technique is relatively low for the positive

### 2019-02-25 paper/ijcai/paper.tex
more polishing

@@
 static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
-is an instance of Model-based software diagnosis that
+is an instance of model-based software diagnosis that
 has been shown useful in automated software debugging where the region
@@
 \vspace{1ex}
-To sum, the workflow of \comb{} consists of four steps:
+Briefly, the workflow of \comb{} consists of four steps:
 \begin{enumerate}
@@
 faulty classes and that \combpar{10} is the variant of our approach
-that performs better missing only $23$ out of the
+that performs better, missing only $23$ out of the
 \numFaults\ ($\sim$8.8\%) faults.

### 2019-02-25 paper/ijcai/paper.tex
important notes

@@
 different sets of faults as to better understand the performance of
-\combpar{k}. On the left-hand-side, we show distributions of
+\combpar{k}. 
+\Sof{This is not correct}
+On the left-hand-side, we show distributions of
 $\Delta{}C$, for different values of $k$, considering all cases where
@@
 $\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
-the cases of faults where the techniques perform equally.\Mar{sofia,
+the cases of faults where the techniques perform equally.\Sof{Needs to be reverted}
+\Mar{sofia,
   are you sure there are no zeros in this dataset? The min. in this
-  distibution (as per the base of the plot) seems to be 0.} To sum,
+  distibution (as per the base of the plot) seems to be 0.}\Sof{Yes, check hangouts} To sum,
 although we observed a relatively small number cases where $\Delta{}C$

### 2019-02-25 paper/ijcai/paper.tex
cleaning variants

@@
 majority of faulty statements are found on the $5$ highest ranked
-faulty classes and that \combpar{10} is the variant of our approach
+faulty classes and that \combpar{10} is the technique
 that performs better, missing only $23$ out of the
@@
 results are drawn from a normal distribution. The test is perfomed for
-all techniques and its variants. With $99\%$ of confidence, the
+all techniques and both $k$s. With $99\%$ of confidence, the
 results tell us that the distributions are not normal. Given that $C$
@@
 statistical test of hypothesis. The null hypothesis is that the
-ranking results of all techniques and variants are the same. With
+ranking results of all techniques for each $k$ are the same. With
 $99\%$ confidence, the results show that the distributions are

### 2019-02-26 paper/ijcai/paper.tex
another pass on RQ3

--- 2019-02-25 paper/ijcai/paper.tex
@@
 that dynamic slicing substantially reduces the size of highly-ranked
-files. \Mar{+ coverage?}
+files.
+
+%\Mar{+ coverage?}
 
@@
 
+%% k=10
+\newcommand{\numOutPerformed}{$33$}%
+\newcommand{\numEquallyPerformed}{$110$}%
+
 In \textbf{RQ3}, we evaluate the impact of combining \ds{} with \sfl{}
@@
 obtained by computing the mean position in the ranking of all buggy
-statements. $\Delta C >0$ means that \combpar{k} outperformed the
-baseline, \ie{} the mean position of the faulty statements is smaller
-in \combpar{k} compared to that of the baseline. $\Delta C <0$ means
-that \combpar{k} performs worse compared to its baseline. That could
-happen if dynamic slicing misses the faulty statement. $\Delta C=0$
-means that the faulty statement remained in the same position.  It is
-worth noting that we assume perfect bug
+statements. $\Delta C <0$ means that \combpar{k} performs worse
+compared to its baseline. That could happen if dynamic slicing misses
+the faulty statement. $\Delta C=0$ means that the faulty statement
+remained in the same position. $\Delta C >0$ means that \combpar{k}
+outperformed the baseline, \ie{} the mean position of the faulty
+statements is smaller in \combpar{k} compared to that of the
+baseline. It is worth noting that we assume perfect bug
 understanding~\cite{Parnin:2011:ADT:2001420.2001445}, i.e., if the
 developer sees the bug in the ranking, he is able to precisely
-determine if it is the faulty one.
-
-%% k=10
-\newcommand{\numOutPerformed}{$33$}%
-\newcommand{\numEquallyPerformed}{$110$}%
-
-Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
-relative to \sfl{}$^{k}$. The figure shows a histogram over
-$\Delta{}C$ for different values of $k$. Note that (1) the number of
-cases where the baseline outperforms \combpar{k} is small (\eg{},
-\numOutPerformed\ of the \numFaults\ faults for $k=10$) and that (2)
-the number of cases \combpar{k} outperforms the baseline is
-significative (\eg{}, $117$ of the \numFaults\ faults for $k=10$). One
-of the following reasons justifies the baseline outperforming
-\combpar{k}:\Mar{following sentence is confusing IMO. suggest to
-  clarify or remove. aren't points two and three equivalent? as for
-  one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
-a fault of omission, (2) the test has design limitations which \ds~is
-not capable of handling, or (3) the buggy-class in not in the top $k$
-of the highest-ranked faulty classes under analysis.
+determine if it is the faulty one.  Figure \ref{fig:diagnosis}
+summarizes the performance of \combpar{k} relative to
+\sfl{}$^{k}$. The figure shows a histogram over $\Delta{}C$ for
+different values of $k$. Note that (1) the number of cases where the
+baseline outperforms \combpar{k} is small (\eg{}, \numOutPerformed\ of
+the \numFaults\ faults for $k=10$) and that (2) the number of cases
+\combpar{k} outperforms the baseline is significative (\eg{}, $117$ of
+the \numFaults\ faults for $k=10$).
+
+%% One
+%% of the following reasons justifies the baseline outperforming
+%% \combpar{k}:\Mar{following sentence is confusing IMO. suggest to
+%%   clarify or remove. aren't points two and three equivalent? as for
+%%   one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
+%% a fault of omission, (2) the test has design limitations which \ds~is
+%% not capable of handling, or (3) the buggy-class in not in the top $k$
+%% of the highest-ranked faulty classes under analysis.
 
@@
 
-Table \ref{table:st}
-presents the statistics to determine if the observed results are
-statistically significant. Shapiro-Wilk tests the null hypothesis that
-results are drawn from a normal distribution. The test is perfomed for
-all techniques and its variants. With $99\%$ of confidence, the
-results tell us that the distributions are not normal. Given that $C$
-is not normally distributed, we use Friedman test, a non-parametric
-statistical test of hypothesis. The null hypothesis is that the
-ranking results of all techniques and variants are the same. With
-$99\%$ confidence, the results show that the distributions are
-distinct. To understand which techniques perform differently, \ie{} to answer
-the question \textit{Does \combpar{k} perform differently than
-\sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
-\ref{fig:performance} reports the results of Siegel analysis for all
-pairs of techniques. Each square represents the
-statistical significance of the diagnostic accuracy amongst the different
-techniques, i.e., if it is significant it means that the techniques perform
-differently. We can determine with $95\%$ confidence that the
+Table \ref{table:st} presents the statistics to determine if the
+observed results are statistically significant. Shapiro-Wilk tests the
+null hypothesis that results are drawn from a normal distribution. The
+test is perfomed for all techniques and its variants. With $99\%$ of
+confidence, the results tell us that the distributions are not
+normal. Given that $C$ is not normally distributed, we use Friedman, a
+non-parametric statistical test of hypothesis. The null hypothesis is
+that the ranking results of all techniques and variants are the
+same. With $99\%$ confidence, the results show that the distributions
+are distinct. To understand which techniques perform differently,
+\ie{}, to answer the question \textit{Does \combpar{k} perform
+  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
+analysis. Figure \ref{fig:performance} reports results. Each square
+shows the statistical significance of the difference in diagnostic
+accuracy amongst the different techniques--the lighter color and
+smaller value of $p$ indicates higher significance. Based on these
+results, it is possible to determine with $95\%$ confidence that the
 performance of each pair of techniques is different.
@@
 
-As the results are statistically significant, it is possible to state that \combpar{k}
-has a positive effect on the localization of some types of bugs. There is indeed a
-problem on using slicing on fault of omission bugs that needs further research.
-Although, this dataset has more than $50\%$ of fault of omissions, our
-simple slicing approach was capable of improving the ranking of $95$ faults for $k=5$
-and $115$ faults for $k=10$. These are promissing results from what Automated
-Program Repair techniques may directly benefit to improve the accuracy of their own
-techniques.
+As the results are statistically significant, it is possible to state
+that \combpar{k} has a positive effect on the localization of some
+types of bugs. There is indeed a problem on using slicing on fault of
+omission bugs that needs further research.  Although, this dataset has
+more than $50\%$ of fault of omissions, our simple slicing approach
+was capable of improving the ranking of $95$ faults for $k=5$ and
+$115$ faults for $k=10$. \Mar{Sofia, acho mais apropriado colocar isto
+  em conclusions}These are promissing results from what Automated
+Program Repair techniques may directly benefit to improve the accuracy
+of their own techniques.
 

### 2019-02-26 paper/ijcai/paper.tex

@@
 null hypothesis that results are drawn from a normal distribution. The
-test is perfomed for all techniques and its variants. With $99\%$ of
+test is perfomed for all techniques and values of $k$. With $99\%$
 confidence, the results tell us that the distributions are not
-normal. Given that $C$ is not normally distributed, we use Friedman, a
+normal. Given that $C$ is not normally distributed, we used Friedman, a
 non-parametric statistical test of hypothesis. The null hypothesis is
-that the ranking results of all techniques and variants are the
+that the rankings obtained with all techniques and variants are the
 same. With $99\%$ confidence, the results show that the distributions

### 2019-02-26 paper/ijcai/paper.tex
comments
pass on threats to validity

@@
 
+\Mar{Sofia, vc. precisa revisar com mais cuidado os dois proximos paragrafos...}
+
 Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ for
@@
 
-\Mar{-------------------------- estou aqui}
-
 In the following, we present statistical analysis of the techniques.
@@
 %
-A potential threat to \textit{external validity} related to the set of programs used in
+A potential threat to \textit{external validity} relates to the set of programs used in
 our study. When choosing the projects for our study, our aim was to opt for
@@
 choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
-It is importance to notice that our study does not evaluate the fault of the \closure{}
-project since it requires high CPU to perform the \combpar{k} evaluation. A potential
-threat to \textit{construct validity} relates to the choice of oracle generation
-for the Lithium toolset. However, we argue that our choice is able to capture whether
-a program is failing because of the same reason.
+Our study did not evaluate the faults from the \closure{}
+project because of the high CPU cost of running \combpar{k} on it. A potential
+threat to \textit{construct validity} relates to the choice of oracle
+we used for the Lithium slicer. We found empirically that our choice was able to capture 
+the faults for the cases we analyzed.
 The main threat to \textit{internal validity} lies in the complexity of several of the tools
 used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
-and the implementation of \comb{}.
+and the implementation of \comb{}. To mitigate this threat, we
+carefully inspected our code and looked for discrepancies and
+incoherences in our results.
+
 %

### 2019-02-26 paper/ijcai/paper.tex
pass on conclusion

@@
 
-Several approaches have been proposed in the literature to improve debugging
-costs through automated software fault diagnosis to reduce time-to-market,
-while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
+Several approaches have been proposed in the literature to reduce debugging
+costs through automated software fault diagnosis with the goal of
+improving productivity in software developement. In this domain, Dynamic Slicing (\ds)
 and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis
@@
 improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
-Hence, we found that, despite tacit opinions of the research community about
-the usefulness of \ds~in automated debugging, we found the combination practical
-and effective, and encourage new \sfl~techniques to be evaluated against that
-optimization.
-Future work is as follows: improve our oracle heuristics to handle more exceptions;
-conduct experiments in more \dfj{} faults or other datasets; find techniques to
-handle the cases which harm the cost of diagnosis, such as, faults of omission,
-test design problems and the cases which the buggy-class is not in the top-$k$ of
-highest-rank faulty classes.
+
+Despite tacit opinions of the research community about the usefulness
+of \ds~in automated debugging, we found te \ds{}-\sfl{} combination
+practical (as per the relatively low number of misses) and effective
+(as per the improvements of $\Delta(C)$ on the relevant cases), and
+encourage new \sfl~techniques to be evaluated against that
+optimization.  Future work includes 1)~improving our oracle heuristics
+to handle more exceptions, 2)~conducting experiments in more \dfj{}
+faults and other datasets, and 3)~handling cases of faults of
+omission.
+
+The dataset and tools (Lithium slicer and \comb{}) will be made
+available once double-blind requirements are lifted.
+
+%% the
+%% cases which harm the cost of diagnosis, such as, faults of omission,
+%% test design problems and the cases which the buggy-class is not in the
+%% top-$k$ of highest-rank faulty classes.
 

### 2019-02-26 paper/ijcai/paper.tex
boxplot

@@
 it chooses the highest power of two number smaller than the file
-size. For example, if the file has 1,000 lines, Lithium sets the
-initial chunk size to 512 lines. Then, the tool starts a local search looking
+size. For example, if the file has $1,000$ lines, Lithium sets the
+initial chunk size to $512$ lines. Then, the tool starts a local search looking
 for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
@@
 that followed by the original program.
-There are faults whose outputs
+In addition, there are faults whose outputs
 may slightly differ from one execution to another. For example,
-exceptions including memory addresses identifiers, which change on
+exceptions including memory address identifiers, which change on
 each execution. For these cases, it was developed a mechanism to compare the
@@
 \combpar{k} outperforms the baseline is significative (\eg{}, $117$ of
-the \numFaults\ faults for $k=10$).
-
-%% One
-%% of the following reasons justifies the baseline outperforming
-%% \combpar{k}:\Mar{following sentence is confusing IMO. suggest to
-%%   clarify or remove. aren't points two and three equivalent? as for
-%%   one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
-%% a fault of omission, (2) the test has design limitations which \ds~is
-%% not capable of handling, or (3) the buggy-class in not in the top $k$
-%% of the highest-ranked faulty classes under analysis.
+the \numFaults\ faults for $k=10$). One
+of the following reasons justifies the baseline outperforming
+\combpar{k}: (1)
+a fault of omission or (2) the test has design limitations which \ds~is
+not capable of handling (mentioned in Section~\ref{sec:slicing}).
 
@@
 \begin{figure}[h]
-	\vspace{-0.3cm}
 		\centering
@@
 
-\Mar{Sofia, vc. precisa revisar com mais cuidado os dois proximos paragrafos...}
-
-Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ for
-different sets of faults as to better understand the performance of
-\combpar{k}. 
-\Sof{This is not correct}
-On the left-hand-side, we show distributions of
-$\Delta{}C$, for different values of $k$, considering all cases where
-the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
-\numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
-(see Figure~\ref{fig:diagnosis}). The boxplots on the right-hand-side
-of the figure considers all the cases where the predicate
-$\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
-the cases of faults where the techniques perform equally.\Sof{Needs to be reverted}
-\Mar{sofia,
-  are you sure there are no zeros in this dataset? The min. in this
-  distibution (as per the base of the plot) seems to be 0.}\Sof{Yes, check hangouts} To sum,
-although we observed a relatively small number cases where $\Delta{}C$
+% \Mar{Sofia, vc. precisa revisar com mais cuidado os dois proximos paragrafos...}
+
+Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
+cases where the predicate $\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
+the cases of faults where the techniques perform equally for at least one $k$. 
+To sum, although we observed a relatively small number of cases where $\Delta{}C$
 is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
-is zero (\numEquallyPerformed), we observed that there is a
+is zero (\numEquallyPerformed), we conclude that there is a
 considerable amount of cases where the use of \combpar{k} would be
 very beneficial.
+% On the left-hand-side, we show distributions of
+% $\Delta{}C$, for different values of $k$, considering all cases where
+% the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
+% \numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
+% (see Figure~\ref{fig:diagnosis}).
+
+% The boxplots on the right-hand-side
+% of the figure considers all the cases where the predicate
+% $\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
+% the cases of faults where the techniques perform equally.\Sof{Needs to be reverted}
+% \Mar{sofia,
+%   are you sure there are no zeros in this dataset? The min. in this
+%   distibution (as per the base of the plot) seems to be 0.}\Sof{Yes, check hangouts}
 
@@
 		\centering
-		\includegraphics[width=0.49\textwidth]{figures/boxplot.pdf}
-		\vspace{-0.6cm}
-
-		\caption{Distributions of $\Delta{}C$. On the left, distribution
-        considering all faults but those manifesting faults of
-        omission and engineering problems (227 faults). On the right,
-        distribution considering all cases where \combpar{k}
-        outperformed the baseline (116 faults).}
+		\includegraphics[width=0.45\textwidth]{figures/boxplot.pdf}
+		\vspace{-0.4cm}
+
+		\caption{Distributions of $\Delta{}C$ considering all cases where \combpar{k}
+        outperformed the baseline}
 		\label{fig:boxplot}
@@
 (test design and fault of omission). The number in parentheses are
-relative to the dataset including all data faults; note that results
+relative to the dataset including all data faults; \Sof{improve}note that results
 for this dataset are \emph{not} encouraging.
@@
   & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
-Mean  & \textbf{590.7} (584.3) & \textbf{573.4} (679.7)   &  \textbf{512.7} (516.4)    & \textbf{506.6} (614.0)   \\ \midrule
-Median & \textbf{46.5} (49.4) & \textbf{42.7} (69.3)      & \textbf{54.5} (53.0) & \textbf{40.0} (56.9)\\ \midrule
-Variance & \textbf{1257.0} (1223.1) & \textbf{1239.1} (1352.4)  &  \textbf{1171.5} (1148.1) &  \textbf{1167.0} (1294.9) \\ \midrule
-Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} &  \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
-Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
+Mean  & \textbf{779.3} (584.3) & \textbf{738.2} (679.7)   &  \textbf{630.6} (516.4)    & \textbf{611.9} (614.0)   \\ \midrule
+Median & \textbf{187.7} (49.4) & \textbf{167.2} (69.3)      & \textbf{167.2} (53.0) & \textbf{107.5} (56.9)\\ \midrule
+Variance & \textbf{1218.3} (1223.1) & \textbf{1186.3} (1352.4)  &  \textbf{1058.4} (1148.1) &  \textbf{1048.6} (1294.9) \\ \midrule
+Shapiro-Wilk &\makecell{$W$ = 0.67 \\ $p$ = 9.64 x $10^{-15}$} & \makecell{$W$ = 0.66 \\ $p$ = 5.59 x $10^{-15}$} & \makecell{$W$ = 0.63 \\ $p$ = 1.09 x $10^{-15}$} &  \makecell{$W$ = 0.63 \\ $p$ = 8.95 x $10^{-16}$}  \\ \midrule
+Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 175.18 \\ p-value = 9.71 x $10^{-38}$}} \\
 \bottomrule
@@
 \begin{figure}[h]
-	\vspace{-1.8cm}
+	\vspace{-1cm}
 		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
@@
 was capable of improving the ranking of $95$ faults for $k=5$ and
-$115$ faults for $k=10$. \Mar{Sofia, acho mais apropriado colocar isto
-  em conclusions}These are promissing results from what Automated
-Program Repair techniques may directly benefit to improve the accuracy
+$115$ faults for $k=10$. These may be promissing results from what Automated
+Program Repair (APR) techniques may directly benefit to improve the accuracy
 of their own techniques.

### 2019-02-26 paper/ijcai/paper.tex
another pass on RQ3

@@
 		\centering
-		\includegraphics[width=0.415\textwidth]{figures/performance.pdf}
+		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
 		\vspace{-0.4cm}
@@
 Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
-cases where the predicate $\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
-the cases of faults where the techniques perform equally for at least one $k$. 
+cases where the predicate $\Delta{}C>0$ holds, \ie{}, it focuses only
+on the cases \combpar{k} outperformed the baseline technique.
 To sum, although we observed a relatively small number of cases where $\Delta{}C$
-is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
-is zero (\numEquallyPerformed), we conclude that there is a
-considerable amount of cases where the use of \combpar{k} would be
-very beneficial.
+is negative (\numOutPerformed) and a high number of cases where $\Delta{}C$
+is zero (\numEquallyPerformed), there is a
+considerable amount of cases where $\Delta{}C$ is positive and for
+those cases \combpar{k} seems very beneficial.
 % On the left-hand-side, we show distributions of
@@
 distributions of $C$ for the techniques under different values of $k$.
-In bold, we present the results of the $227$ faults that do not
-comprise the cases that are result of the limitations mentioned before
-(test design and fault of omission). The number in parentheses are
-relative to the dataset including all data faults; \Sof{improve}note that results
-for this dataset are \emph{not} encouraging.
-
-These results show that \ds{}
-improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
-the average ranking of all faulty statements, when considering
-$k=10$.
-However, if we only consider
-the faults which can benefit from our approach, we can observe that
-there is a considerable amount of cases where the approach is actually
-successful. For $k=5$, our approach achieves a mean improvement of
-$41.1$ ($9.57\%$ on average) statements on the ranking and an
-impressive maximum ranking improvement of $3171$ ($96.7\%$ on average)
-statements. Whereas for $k=10$, \combpar{k} achieves a mean
+In bold, we present the results for the $227$ faults corresponding to
+the cases where $\Delta(C)\geq{}0$. The number in parentheses are
+relative to the dataset including all faults.
+
+%% These results show that \ds{}
+%% improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
+%% the average ranking of all faulty statements, when considering
+%% $k=10$.
+
+We observe the following when considering the faults which can benefit
+from \comb\ (numbers in bold). For $k=5$, \comb\ achieves a mean
+improvement of $41.1$ ($9.57\%$ on average) statements on the ranking
+and an impressive maximum ranking improvement of $3171$ ($96.7\%$ on
+average) statements. For $k=10$, \combpar{k} achieves a mean
 improvement of $19$ ($13.35\%$ on average) statements on the ranking

### 2019-02-26 paper/ijcai/paper.tex
pass on conclusions

@@
 
-Several approaches have been proposed in the literature to reduce debugging
-costs through automated software fault diagnosis with the goal of
-improving productivity in software developement. In this domain, Dynamic Slicing (\ds)
-and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis
-techniques and normally seen as complementary. This paper reports the outcome of
-a study using real-world applications with the goal of demystifying the impact
-of combining \ds~with \sfl. The results of our empirical study show that, in
-practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
-the \ds-\sfl~combination, coined as \combpar{k},
-improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
+Several approaches have been proposed in the literature to reduce
+software debugging costs through automated fault diagnosis with the
+goal of improving productivity in software development. In this
+domain, Dynamic Slicing (\ds) and Spectrum-based Fault Localization
+(\sfl) are very popular techniques and normally seen as complementary.
+
+This paper reports the outcome of a comprehensive study using
+real-world applications with the goal of demystifying the impact of
+combining \ds~with \sfl. The results of our empirical study show that,
+in practice, \ds\ misses faulty statements infrequently $9\%$ ($23$
+misses in $260$ cases) and that the \ds-\sfl~combination, coined as
+\combpar{k}, improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$
+on average).
 

### 2019-02-26 paper/ijcai/paper.tex
eating up some space
paper
spell checking

@@
    \label{tab:ds-cases-captured}
-\vspace{-0.2cm}
 
@@
 null hypothesis that results are drawn from a normal distribution. The
-test is perfomed for all techniques and values of $k$. With $99\%$
+test is performed for all techniques and values of $k$. With $99\%$
 confidence, the results tell us that the distributions are not
@@
 	\vspace{-1cm}
-		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
+		\includegraphics[width=0.48\textwidth]{figures/heatmap_nemenyi_result.pdf}
 		\caption{Siegel post-hoc analysis results}
@@
 was capable of improving the ranking of $95$ faults for $k=5$ and
-$115$ faults for $k=10$. These may be promissing results from what Automated
+$115$ faults for $k=10$. These may be promising results from what Automated
 Program Repair (APR) techniques may directly benefit to improve the accuracy
@@
 carefully inspected our code and looked for discrepancies and
-incoherences in our results.
+incoherence in our results.
 
@@
 combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
-Overall, these studies reported promissing results but based their conclusions
+Overall, these studies reported promising results but based their conclusions
 on a very small group of (mostly artificial) faults and using different
@@
 Despite tacit opinions of the research community about the usefulness
-of \ds~in automated debugging, we found te \ds{}-\sfl{} combination
+of \ds~in automated debugging, we found the \ds{}-\sfl{} combination
 practical (as per the relatively low number of misses) and effective
@@
 
-%%  LocalWords:  SFL
+%%  LocalWords:  SFL dataset suspiciousness MBSD DS DX anonymized NPE
+%%  LocalWords:  ij pq Ochiai ochiai significative Siegel hoc amongst
+%%  LocalWords:  toolset scalability

### 2019-04-15 rebuttal.md
first rebuttal.md commit

# Paper\# 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization}

###Review \#210912
**Summary:** This paper deals with combining dynamic slicing with spectrum-based fault localization with the purpose of improving the overall debugging quality, i.e., providing a better ranking that allows programmers to more quickly find faults responsible for detected failures. The paper tackles an interesting challenge, i.e., automated debugging, that is still active. The paper is well written and structured. The ideas behind the approach are well explained and the paper also includes an empirical evaluation that is based on well-known example programs that are often used for evaluating debugging approaches.

**Weakness (1):** The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements. This is definitely a weakness of this paper.

However, there is an empirical evaluation that is novel capturing important research questions.

**Weakness (2):** Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable. In this particular case, I would argue that the combination of slicing and spectrum-based fault localization should lead to improvements because of the fact that we can rule out some components that do not influence the computation of wrong values. The study itself is fine but there are some issues the authors should discuss. From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same. I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5? I would assume that taking care of more statements should improve debugging performance.

In addition, there is no discussion of drawbacks behind the approach. Spectrum-based fault localization is successful because it does not require a lot of tools and can be more or less easily adapted for other programming languages. This is not the case for slicing. For slicing we require to know not only that a test case is failing but also to identify all output variables that deliver wrong values. In case of exceptions (as discussed a little bit in the paper) we may also use different slicing approaches to improve the results. There is some work on dynamic slicing in case of exceptions. Moreover, slicing needs more time for analysis and running time might become an issue.

In summary, the paper provides a novel evaluation of a not so novel debugging approach. The paper is well written but there is still room for improvement. The main issues are regarding missing discussions about limitations and drawback, and the empirical evaluation, which may need more detailed explanations.

###Review \#252039

> This paper proposes a novel approach to automated debugging: dynamic slicing + software fault localization. The paper is empirical in nature and shows good degree of scholarship: it is actually rare to see such comprehensive empirical study published at a conference. The results from study are promising and the reader is convinced that the combination of the two approaches yields better fault isolation compared to each approach separately.

> It would be interesting to compare/combine the proposed algorithm with machine learning. Of course, such a study would not fit a 6 pp conference paper. Here is a link that is relevant to the study:

> Baah, George K., Alexander Gray, and Mary Jean Harrold. "On-line anomaly detection of deployed software: a statistical machine learning approach." Proceedings of the 3rd international workshop on Software quality assurance. ACM, 2006.

> An area for improvement is the formality of the whole paper.

> Some minor issues:

> 1. Theorem 1 -> Claim 1

> 2. Applications of MBD to localize software faults have demonstrated that it ... -> which it?

> 3. Threats to validity -> Threats to Validity

###Review \#263473

The paper titled "Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization" provides an account of a comprehensive amount of experiments using a combination of dynamic slicing and Ochiai ranking based spectrum-based fault localization on Java benchmarks available in the Defects4J project.

The idea of proposing a baseline approach combining dynamic slicing with spectrum-based fault localisation makes sense, as many authors seem to have discovered and explored it to some extent in numerous publications, many of which are cited by the authors. The fact that recent surveys on fault localisation have not had such a benchmark on record confirms the need.

However it seems that the goal is rather ambitious because many people have tried the combination and the authors of the current paper are left with the tedious task of sifting though all previous results to make sure the new baseline is a comprehensive summary of previous results. The authors say in the Related Work section on page 6 that many authors have previously investigated the combination of DS and SBFL, but their approaches were evaluated on rather small set of benchmarks. The main contribution of the current paper is running DS-SBFL on a larger set of benchmarks.

Thus the contribution of the paper is a an extensive experiment of how well the combination of Ochiai ranking performs with respect to the combination of dynamic slicing together with Ochiai ranking.

The work is important and the authors have been very careful with applying a methodological approach. However, it seems that such refactoring contributions seem to better fit into the journal setting where the reviewers can actually take a look at the proposed implementation and the authors are not so constrained with space.

Some suggestions for future work:

* An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms. That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai? It feels that calling the observation a theorem is a bit  ambitious. Perhaps such property is something to characterize the ranking algorithms by?

* A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm. It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.

* Perhaps the approach should be called DS-SBFL instead of Tandem-FL?  The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).

* Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.

* Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.

###Review \#263474

The topic of the paper is software debugging. In particular, a methodology for locating the faulty code is experimentally evaluated. The considered methodology combines two well know techniques: (a) Dynamic  (DS) which reduce the code by removing the parts which not contribute to the fault; (b) Spectrum-based Fault Localization (SFL) which computes suspiciousness values associated with program components based on coverage information. The two techniques are suitable combined (DS is exploited to enhance the results of SFL). As correctly reported in the paper the idea of combining the two techniques is not new and it has already checked for effectiveness. The claim of the author(s) is that the more extended experimental setting provided in the this paper and the more rigorous methodological approach allow to reassess the results of the previous investigation in favor of the combination.

The paper is well structured and it is well written. I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable. My only concern is whether the investigated issue fits the main topics of the conference (no comment of author(s) helps in this sense). For sure this kind of paper would be more appropriate in conferences on software engineering, validation and testing. In those venues I had proposed acceptance. In this context I’m a little bit puzzled.

### 2019-04-15 rebuttal.md
Update rebuttal.md

@@
 
-###Review \#210912
-**Summary:** This paper deals with combining dynamic slicing with spectrum-based fault localization with the purpose of improving the overall debugging quality, i.e., providing a better ranking that allows programmers to more quickly find faults responsible for detected failures.
+##Review \#210912##
+
+> **Summary:** This paper deals with combining dynamic slicing with spectrum-based fault localization with the purpose of improving the overall debugging quality, i.e., providing a better ranking that allows programmers to more quickly find faults responsible for detected failures.
 The paper tackles an interesting challenge, i.e., automated debugging, that is still active.
@@
 The ideas behind the approach are well explained and the paper also includes an empirical evaluation that is based on well-known example programs that are often used for evaluating debugging approaches.
-
-**Weakness (1):** The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
+> **Weakness (1):** The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
 This is definitely a weakness of this paper.
-
-However, there is an empirical evaluation that is novel capturing important research questions.
-
-**Weakness (2):** Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.
+> However, there is an empirical evaluation that is novel capturing important research questions. 
+> **Weakness (2):** Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.
 In this particular case, I would argue that the combination of slicing and spectrum-based fault localization should lead to improvements because of the fact that we can rule out some components that do not influence the computation of wrong values.
@@
 I would assume that taking care of more statements should improve debugging performance.
-
-In addition, there is no discussion of drawbacks behind the approach.
+> In addition, there is no discussion of drawbacks behind the approach.
 Spectrum-based fault localization is successful because it does not require a lot of tools and can be more or less easily adapted for other programming languages.
@@
 Moreover, slicing needs more time for analysis and running time might become an issue.
-
-In summary, the paper provides a novel evaluation of a not so novel debugging approach.
+> In summary, the paper provides a novel evaluation of a not so novel debugging approach.
 The paper is well written but there is still room for improvement.
@@
 
-###Review \#252039
+##Review \#252039
 
@@
 The results from study are promising and the reader is convinced that the combination of the two approaches yields better fault isolation compared to each approach separately.
-
 > It would be interesting to compare/combine the proposed algorithm with machine learning. Of course, such a study would not fit a 6 pp conference paper. Here is a link that is relevant to the study:
-
 > Baah, George K., Alexander Gray, and Mary Jean Harrold.
@@
 ACM, 2006.
-
 > An area for improvement is the formality of the whole paper.
-
 > Some minor issues:
-
 > 1. Theorem 1 -> Claim 1
-
 > 2. Applications of MBD to localize software faults have demonstrated that it ... -> which it?
-
 > 3. Threats to validity -> Threats to Validity
 
-###Review \#263473
+##Review \#263473##
 
@@
 
-###Review \#263474
+##Review \#263474##
 

### 2019-04-15 rebuttal.md
Update rebuttal.md

@@
-# Paper\# 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization}
+# Paper 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization}
 
-##Review \#210912##
+### Review 210912:
 
@@
 The ideas behind the approach are well explained and the paper also includes an empirical evaluation that is based on well-known example programs that are often used for evaluating debugging approaches.
+>
 > **Weakness (1):** The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
@@
 > However, there is an empirical evaluation that is novel capturing important research questions. 
+>
 > **Weakness (2):** Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.
@@
 
-##Review \#252039
+### Review 252039:
 
@@
 
-##Review \#263473##
+### Review 263473:
 
-The paper titled "Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization" provides an account of a comprehensive amount of experiments using a combination of dynamic slicing and Ochiai ranking based spectrum-based fault localization on Java benchmarks available in the Defects4J project.
-
-The idea of proposing a baseline approach combining dynamic slicing with spectrum-based fault localisation makes sense, as many authors seem to have discovered and explored it to some extent in numerous publications, many of which are cited by the authors.
+> The paper titled "Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization" provides an account of a comprehensive amount of experiments using a combination of dynamic slicing and Ochiai ranking based spectrum-based fault localization on Java benchmarks available in the Defects4J project.
+> The idea of proposing a baseline approach combining dynamic slicing with spectrum-based fault localisation makes sense, as many authors seem to have discovered and explored it to some extent in numerous publications, many of which are cited by the authors.
 The fact that recent surveys on fault localisation have not had such a benchmark on record confirms the need.
-
-However it seems that the goal is rather ambitious because many people have tried the combination and the authors of the current paper are left with the tedious task of sifting though all previous results to make sure the new baseline is a comprehensive summary of previous results.
+> However it seems that the goal is rather ambitious because many people have tried the combination and the authors of the current paper are left with the tedious task of sifting though all previous results to make sure the new baseline is a comprehensive summary of previous results.
 The authors say in the Related Work section on page 6 that many authors have previously investigated the combination of DS and SBFL, but their approaches were evaluated on rather small set of benchmarks.
 The main contribution of the current paper is running DS-SBFL on a larger set of benchmarks.
-
-Thus the contribution of the paper is a an extensive experiment of how well the combination of Ochiai ranking performs with respect to the combination of dynamic slicing together with Ochiai ranking.
-
-The work is important and the authors have been very careful with applying a methodological approach.
+> Thus the contribution of the paper is a an extensive experiment of how well the combination of Ochiai ranking performs with respect to the combination of dynamic slicing together with Ochiai ranking.
+> The work is important and the authors have been very careful with applying a methodological approach.
 However, it seems that such refactoring contributions seem to better fit into the journal setting where the reviewers can actually take a look at the proposed implementation and the authors are not so constrained with space.
-
-Some suggestions for future work:
-
-* An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
+> Some suggestions for future work:
+> * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
 That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
@@
 Perhaps such property is something to characterize the ranking algorithms by?
+> * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
+It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
+> * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
+The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
+> * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
+> * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.
 
-* A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
-It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
+## Review 263474:
 
-* Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
-The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
-
-* Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
-
-* Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.
-
-##Review \#263474##
-
-The topic of the paper is software debugging.
+> The topic of the paper is software debugging.
 In particular, a methodology for locating the faulty code is experimentally evaluated.
@@
 
-The paper is well structured and it is well written.
+> The paper is well structured and it is well written.
 I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable.

### 2019-04-16 rebuttal.md
Update rebuttal.md

@@
-# Paper 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization}
+# Paper 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization
 
@@
 
-> **Summary:** This paper deals with combining dynamic slicing with spectrum-based fault localization with the purpose of improving the overall debugging quality, i.e., providing a better ranking that allows programmers to more quickly find faults responsible for detected failures.
-The paper tackles an interesting challenge, i.e., automated debugging, that is still active.
-The paper is well written and structured.
-The ideas behind the approach are well explained and the paper also includes an empirical evaluation that is based on well-known example programs that are often used for evaluating debugging approaches.
->
 > **Weakness (1):** The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
@@
 > **Weakness (2):** Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable. 
-In this particular case, I would argue that the combination of slicing and spectrum-based fault localization should lead to improvements because of the fact that we can rule out some components that do not influence the computation of wrong values.
+>
+>In this particular case, I would argue that the combination of slicing and spectrum-based fault localization should lead to improvements because of the fact that we can rule out some components that do not influence the computation of wrong values.
 The study itself is fine but there are some issues the authors should discuss.
-From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same.
-I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5?
+> **issue(1):** From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same. 
+> **issue(2):** I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5?
 I would assume that taking care of more statements should improve debugging performance.
@@
 Moreover, slicing needs more time for analysis and running time might become an issue.
-> In summary, the paper provides a novel evaluation of a not so novel debugging approach.
-The paper is well written but there is still room for improvement.
-The main issues are regarding missing discussions about limitations and drawback, and the empirical evaluation, which may need more detailed explanations.
+> **Conclusion:** The main issues are regarding missing discussions about limitations and drawback, and the empirical evaluation, which may need more detailed explanations.
 
@@
 
-> This paper proposes a novel approach to automated debugging: dynamic slicing + software fault localization.
-The paper is empirical in nature and shows good degree of scholarship: it is actually rare to see such comprehensive empirical study published at a conference.
-The results from study are promising and the reader is convinced that the combination of the two approaches yields better fault isolation compared to each approach separately.
-> It would be interesting to compare/combine the proposed algorithm with machine learning. Of course, such a study would not fit a 6 pp conference paper. Here is a link that is relevant to the study:
-> Baah, George K., Alexander Gray, and Mary Jean Harrold.
-"On-line anomaly detection of deployed software: a statistical machine learning approach." Proceedings of the 3rd international workshop on Software quality assurance.
-ACM, 2006.
-> An area for improvement is the formality of the whole paper.
-> Some minor issues:
-> 1. Theorem 1 -> Claim 1
-> 2. Applications of MBD to localize software faults have demonstrated that it ... -> which it?
-> 3. Threats to validity -> Threats to Validity
+No problems found on this review.
 
@@
 
-> The paper titled "Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization" provides an account of a comprehensive amount of experiments using a combination of dynamic slicing and Ochiai ranking based spectrum-based fault localization on Java benchmarks available in the Defects4J project.
+> **Summary:** The paper titled "Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization" provides an account of a comprehensive amount of experiments using a combination of dynamic slicing and Ochiai ranking based spectrum-based fault localization on Java benchmarks available in the Defects4J project.
 > The idea of proposing a baseline approach combining dynamic slicing with spectrum-based fault localisation makes sense, as many authors seem to have discovered and explored it to some extent in numerous publications, many of which are cited by the authors.
@@
 In this context I’m a little bit puzzled.
+
+# Improvements
+
+* An area for improvement is the formality of the whole paper.
+
+# Minor Issues
+
+# Future Work
+
+* It would be interesting to compare/combine the proposed algorithm with machine learning. Of course, such a study would not fit a 6 pp conference paper. Here is a link that is relevant to the study:
+
+> Baah, George K., Alexander Gray, and Mary Jean Harrold.
+"On-line anomaly detection of deployed software: a statistical machine learning approach." Proceedings of the 3rd international workshop on Software quality assurance.
+ACM, 2006.

### 2019-04-16 rebuttal.md
rebuttal organization

@@
 
-> **Weakness (1):** The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
+**issue 1:** Not sure if this point needs comments.
+> The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
 This is definitely a weakness of this paper.
-> However, there is an empirical evaluation that is novel capturing important research questions. 
->
-> **Weakness (2):** Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable. 
->
->In this particular case, I would argue that the combination of slicing and spectrum-based fault localization should lead to improvements because of the fact that we can rule out some components that do not influence the computation of wrong values.
-The study itself is fine but there are some issues the authors should discuss.
-> **issue(1):** From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same. 
-> **issue(2):** I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5?
-I would assume that taking care of more statements should improve debugging performance.
+However, there is an empirical evaluation that is novel capturing important research questions.
+
+**issue 2:** 
+> Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.
+
+**issue 3:** 
+I think the reviewer is confused because we present the results of DS two times in different tables.
+> From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same.
+
+**issue 4:** 
+Explain why it can be worse.
+> I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5? I would assume that taking care of more statements should improve debugging performance.
+
+**issue 5:** 
 > In addition, there is no discussion of drawbacks behind the approach.
@@
 There is some work on dynamic slicing in case of exceptions.
-Moreover, slicing needs more time for analysis and running time might become an issue.
-> **Conclusion:** The main issues are regarding missing discussions about limitations and drawback, and the empirical evaluation, which may need more detailed explanations.
+
+**issue 6:** 
+> Moreover, slicing needs more time for analysis and running time might become an issue.
 
@@
 
-> **Summary:** The paper titled "Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization" provides an account of a comprehensive amount of experiments using a combination of dynamic slicing and Ochiai ranking based spectrum-based fault localization on Java benchmarks available in the Defects4J project.
-> The idea of proposing a baseline approach combining dynamic slicing with spectrum-based fault localisation makes sense, as many authors seem to have discovered and explored it to some extent in numerous publications, many of which are cited by the authors.
-The fact that recent surveys on fault localisation have not had such a benchmark on record confirms the need.
-> However it seems that the goal is rather ambitious because many people have tried the combination and the authors of the current paper are left with the tedious task of sifting though all previous results to make sure the new baseline is a comprehensive summary of previous results.
-The authors say in the Related Work section on page 6 that many authors have previously investigated the combination of DS and SBFL, but their approaches were evaluated on rather small set of benchmarks.
-The main contribution of the current paper is running DS-SBFL on a larger set of benchmarks.
-> Thus the contribution of the paper is a an extensive experiment of how well the combination of Ochiai ranking performs with respect to the combination of dynamic slicing together with Ochiai ranking.
+**issue 7:** 
+Should we try to address this review?
 > The work is important and the authors have been very careful with applying a methodological approach.
 However, it seems that such refactoring contributions seem to better fit into the journal setting where the reviewers can actually take a look at the proposed implementation and the authors are not so constrained with space.
-> Some suggestions for future work:
-> * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
-That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
-It feels that calling the observation a theorem is a bit  ambitious.
-Perhaps such property is something to characterize the ranking algorithms by?
-> * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
-It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
-> * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
-The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
-> * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
-> * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.
 
@@
 
-> The topic of the paper is software debugging.
-In particular, a methodology for locating the faulty code is experimentally evaluated.
-The considered methodology combines two well know techniques: (a) Dynamic  (DS) which reduce the code by removing the parts which not contribute to the fault; (b) Spectrum-based Fault Localization (SFL) which computes suspiciousness values associated with program components based on coverage information.
-The two techniques are suitable combined (DS is exploited to enhance the results of SFL).
-As correctly reported in the paper the idea of combining the two techniques is not new and it has already checked for effectiveness.
-The claim of the author(s) is that the more extended experimental setting provided in the this paper and the more rigorous methodological approach allow to reassess the results of the previous investigation in favor of the combination.
-
-> The paper is well structured and it is well written.
-I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable.
-My only concern is whether the investigated issue fits the main topics of the conference (no comment of author(s) helps in this sense).
+**issue 8:** 
+Focus on model-based diagnosis!
+> I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable.
+My only concern is whether the **investigated issue fits the main topics of the conference** (no comment of author(s) helps in this sense).
 For sure this kind of paper would be more appropriate in conferences on software engineering, validation and testing.
@@
 
-# Improvements
+### Improvements
 
@@
 
-# Minor Issues
+### Minor Issues
 
-# Future Work
+* Theorem 1 -> Claim 1
+
+* Applications of MBD to localize software faults have demonstrated that it ... -> which it?
+
+* Threats to validity -> Threats to Validity
+
+### Future Work
 
@@
 ACM, 2006.
+
+* An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
+That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
+It feels that calling the observation a theorem is a bit  ambitious.
+Perhaps such property is something to characterize the ranking algorithms by?
+* A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
+It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
+* Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
+The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
+* Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
+* Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.

### 2019-04-16 rebuttal.md
polishing

@@
 
+**note:** this seems to be a point we should address in the rebuttal using Rui's paper (*Evaluating and improving fault localization*).
 * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
 That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
-It feels that calling the observation a theorem is a bit  ambitious.
-Perhaps such property is something to characterize the ranking algorithms by?
+
+* It feels that calling the observation a theorem is a bit  ambitious. Perhaps such property is something to characterize the ranking algorithms by?
+
 * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
-It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
+
 * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
 The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
+
 * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
+
 * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.

### 2019-04-16 rebuttal.md
final org
more polishing

@@
 
-**issue 2:** 
+**issue 2:** Not in the paper. Should be mentioned in the paper (Threats to Validity).
 > Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.
@@
 
-**issue 6:** 
+**issue 6:** This issue is addressed in threats to validity...
 > Moreover, slicing needs more time for analysis and running time might become an issue.
@@
 
-**note:** this seems to be a point we should address in the rebuttal using Rui's paper (*Evaluating and improving fault localization*).
+**note:** Should the next point be addressed in the rebuttal using Rui's paper (*Evaluating and improving fault localization*) ?
 * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.

### 2019-04-18 rebuttal.md
minor fixes
Review #252039 and Review #263474 addressed

@@
 
+**ANSWER:**
+
 ### Review 252039:
 
-No problems found on this review.
+**ANSWER:**
+
+We kindly thank the reviewer for the feedback on our work.
+We will make sure that the paper's formality will be improved.
+Minor issues will also be addressed.
+We will definitely explore the statistical machine learning approach in future work.
 
@@
 
+> * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
+That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
+It feels that calling the observation a theorem is a bit  ambitious.
+Perhaps such property is something to characterize the ranking algorithms by?
+> * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
+It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
+> * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
+The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
+> * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
+> * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.
+
+**ANSWER:**
+
 ## Review 263474:
@@
 **issue 8:** 
-Focus on model-based diagnosis!
 > I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable.
@@
 In this context I’m a little bit puzzled.
+
+**ANSWER:**
+
+We kindly thank the reviewer for the comments on our work.
+As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing which is the technique proposed to improve software fault localization.
+Model-based diagnosis is a well-known approach that has been proposed by the diagnosis community.
+This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults.
+We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that IJCAI can be the home to this paper since we are applying AI to improve SBFL.
 

### 2019-04-18 rebuttal.md
Polishing

@@
 This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults.
-We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that IJCAI can be the home to this paper since we are applying AI to improve SBFL.
+We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.
+
+## Other points
 

### 2019-04-18 rebuttal.md
Polishing

@@
 
-**ANSWER:**
+**Rebuttal:**
 
@@
 
-**ANSWER:**
+**Rebuttal:**
 
-We kindly thank the reviewer for the feedback on our work.
-We will make sure that the paper's formality will be improved.
-Minor issues will also be addressed.
-We will definitely explore the statistical machine learning approach in future work.
+We kindly thank the reviewer for its insights and comments on our work.
+
+We will make sure that the paper's formality will be improved and that minor issues will also be addressed. We will definitely explore the statistical machine learning approach in future work.
 
@@
 
-**issue 7:** 
-Should we try to address this review?
-> The work is important and the authors have been very careful with applying a methodological approach.
-However, it seems that such refactoring contributions seem to better fit into the journal setting where the reviewers can actually take a look at the proposed implementation and the authors are not so constrained with space.
-
+**Issues:** 
 > * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
@@
 
-**ANSWER:**
+**Rebuttal:**
+
+We thank the reviewer for the feedback provided on our work.
+
+Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true.
+To answer your question, the present work needs to be extended.
+We plan to investigate the veracity of claim 2 using other ranking algorithms, such as, Tarantula, Op2, Barinel and etc.
+This, however remains for future work.
+
+< Still have to justify why have we not compared with other slicing approaches >
+
+< Not sure what to say about the name, do we agree?>
+
+We agree that our theorems are rather observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed on the paper.
 
@@
 
-**ANSWER:**
+**Rebuttal:**
 
 We kindly thank the reviewer for the comments on our work.
+
 As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing which is the technique proposed to improve software fault localization.

### 2019-04-18 rebuttal.md
Polishing

@@
 
-**issue 1:** Not sure if this point needs comments.
+needs to be addressed?
 > The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
@@
 **Rebuttal:**
+
+We kindly thank the reviewer for the comments and questions raised on our work.
+
+In fact, we did not address the limitation regarding programs and generalization. We will add this discussion to Threats to Validity.
+
+Regarding the point about slicing running time needs, we indirectly touch on that in Threats to Validity when it is mentioned that the faults from the Closure compiler project were not evaluated because of the high CPU cost of the technique.
+Yet, we will clarify it.
 

### 2019-04-18 rebuttal.md
Polishing

@@
 In fact, we did not address the limitation regarding programs and generalization. We will add this discussion to Threats to Validity.
+
+The results k=10 suffer a decrease because the slicer is evaluating 10 full classes instead of only 5.
+For each k, we evaluate if at least one of the buggy-lines of the k classes is on the slicer report.
+When the 10 classes (k=10) are evaluated, there might be some of the buggy-lines that were not taken into account for k=5 that are being evaluated now and are not found in the report.
+
+< not sure yet how to answer issue 5>
 

### 2019-04-18 rebuttal.md
Review 263474 finished

@@
 
-needs to be addressed?
+** issue 1:**
 > The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
@@
 There is some work on dynamic slicing in case of exceptions.
-
-**issue 6:** This issue is addressed in threats to validity...
-> Moreover, slicing needs more time for analysis and running time might become an issue.
+Moreover, slicing needs more time for analysis and running time might become an issue.
 
@@
 It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
-> * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
-The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
 > * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
@@
 
-**issue 8:** 
-> I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable.
-My only concern is whether the **investigated issue fits the main topics of the conference** (no comment of author(s) helps in this sense).
-For sure this kind of paper would be more appropriate in conferences on software engineering, validation and testing.
-In those venues I had proposed acceptance.
-In this context I’m a little bit puzzled.
-
 **Rebuttal:**
@@
 
-As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing which is the technique proposed to improve software fault localization.
+As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing by Wolfgang Mayer and Markus Stumptner in previous research which is the technique we propose to improve software fault localization.
 Model-based diagnosis is a well-known approach that has been proposed by the diagnosis community.
@@
 We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.
-
-## Other points
-
-### Improvements
-
-* An area for improvement is the formality of the whole paper.
-
-### Minor Issues
-
-* Theorem 1 -> Claim 1
-
-* Applications of MBD to localize software faults have demonstrated that it ... -> which it?
-
-* Threats to validity -> Threats to Validity
-
-### Future Work
-
-* It would be interesting to compare/combine the proposed algorithm with machine learning. Of course, such a study would not fit a 6 pp conference paper. Here is a link that is relevant to the study:
-
-> Baah, George K., Alexander Gray, and Mary Jean Harrold.
-"On-line anomaly detection of deployed software: a statistical machine learning approach." Proceedings of the 3rd international workshop on Software quality assurance.
-ACM, 2006.
-
-**note:** Should the next point be addressed in the rebuttal using Rui's paper (*Evaluating and improving fault localization*) ?
-* An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
-That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
-
-* It feels that calling the observation a theorem is a bit  ambitious. Perhaps such property is something to characterize the ranking algorithms by?
-
-* A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
-
-* Perhaps the approach should be called DS-SBFL instead of Tandem-FL?
-The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
-
-* Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
-
-* Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.

### 2019-04-18 rebuttal.md
Review 263473 and Review 252039 finished

@@
 
-We will make sure that the paper's formality will be improved and that minor issues will also be addressed. We will definitely explore the statistical machine learning approach in future work.
+We will make sure that the paper's formality will be improved and that the minor issues will be addressed.
+We will definitely explore the statistical machine learning approach in future work.
+Thank you for the hint!
 
@@
 
-**Issues:** 
-> * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms.
-That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai?
-It feels that calling the observation a theorem is a bit  ambitious.
-Perhaps such property is something to characterize the ranking algorithms by?
-> * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm.
-It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
-> * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
-> * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.
-
 **Rebuttal:**
 
-We thank the reviewer for the feedback provided on our work.
+We kindly thank the reviewer for the feedback provided on our work.
+
+We agree that our "theorems" are rather claims/observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed on the paper.
 
 Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true.
-To answer your question, the present work needs to be extended.
+For now we decided to only focus on the ranking algorithm that provided the best results in previous research - ochiai.
+To answer the reviewer question precisely, the present work needs to be extended.
 We plan to investigate the veracity of claim 2 using other ranking algorithms, such as, Tarantula, Op2, Barinel and etc.
@@
 
-< Still have to justify why have we not compared with other slicing approaches >
-
-< Not sure what to say about the name, do we agree?>
-
-We agree that our theorems are rather observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed on the paper.
+Our focus in the paper was to show that dynamic slicing may considerable improve SBFL (we found an improvement of 73.7%).
+We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity and scalability.
+Our idea was that if we were able to show that CS works, then later we could leverage more accurate slicing techniques to improve our results.
+It is also important to notice that the numbers of tools implementing this type of techniques is very small.
+However, we will explore this in more detail in the future.
 
@@
 
-As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing by Wolfgang Mayer and Markus Stumptner in previous research which is the technique we propose to improve software fault localization.
-Model-based diagnosis is a well-known approach that has been proposed by the diagnosis community.
+As we mention in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner in previous research have demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization.
+MBDS is a well-known approach that has been proposed by the diagnosis community.
 This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults.

### 2019-04-18 rebuttal.md
Missing only 1 issue

@@
 ### Review 210912:
-
-** issue 1:**
-> The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements.
-This is definitely a weakness of this paper.
-However, there is an empirical evaluation that is novel capturing important research questions.
-
-**issue 2:** Not in the paper. Should be mentioned in the paper (Threats to Validity).
-> Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.
-
-**issue 3:** 
-I think the reviewer is confused because we present the results of DS two times in different tables.
-> From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same.
 
@@
 
-**issue 5:** 
-> In addition, there is no discussion of drawbacks behind the approach.
-Spectrum-based fault localization is successful because it does not require a lot of tools and can be more or less easily adapted for other programming languages.
-This is not the case for slicing.
-For slicing we require to know not only that a test case is failing but also to identify all output variables that deliver wrong values.
-In case of exceptions (as discussed a little bit in the paper) we may also use different slicing approaches to improve the results.
-There is some work on dynamic slicing in case of exceptions.
-Moreover, slicing needs more time for analysis and running time might become an issue.
-
 **Rebuttal:**
@@
 
-In fact, we did not address the limitation regarding programs and generalization. We will add this discussion to Threats to Validity.
+As the title states, we intend to demystify the combination of Dynamic Slicing with Spectrum-based Fault Localization.
+Previous research have already shown impact and importance of both techniques - combined and separated.
+However, from the studies available about combining these two techniques, it was not yet clear if DS could help SBFL on obtaining more accurate results and how great would that improvement be.
+Thus, we find that our research questions and results might be important to guide researchers on performing research based on the combination of both techniques.
 
-The results k=10 suffer a decrease because the slicer is evaluating 10 full classes instead of only 5.
+We have not address the limitation regarding programs and generalization. Thus, we will fix and add this discussion to Threats to Validity.
+
+In table 3, we present the results for dynamic slicing alone whereas in table 4 we present the results of SFL vs.
+Tandem-FL for each k.
+Dynamic slicing in table 3 is the same as Tandem-FL in table 4.
+Thus, the values are the same.
+We only presented the same results in different views.
+On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's.
+Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k.
+We understand that this might create some confusion.
+Thus, we will try to improve it.
+
+_The results k=10 suffer a decrease because the slicer is evaluating 10 full classes instead of only 5.
 For each k, we evaluate if at least one of the buggy-lines of the k classes is on the slicer report.
-When the 10 classes (k=10) are evaluated, there might be some of the buggy-lines that were not taken into account for k=5 that are being evaluated now and are not found in the report.
+When the 10 classes (k=10) of fault are evaluated, there might be some of the buggy-lines that were not taken into account for k=5 that are being evaluated now and are not found in the report._ (!!
+not finished yet)
 
-< not sure yet how to answer issue 5>
-
-Regarding the point about slicing running time needs, we indirectly touch on that in Threats to Validity when it is mentioned that the faults from the Closure compiler project were not evaluated because of the high CPU cost of the technique.
-Yet, we will clarify it.
+These techniques have a few pratical limitations.
+We can only ensure that the proposed technique will work with defects4j programs because we generalized our function of interess according with the type of failling tests messages that exist on the dataset.
+Thus, some messages with very specific characteristics may not provide valide results.
+However, we intend to make clear what type of observed faults the tools is able to evaluate and turn the tool open-source after publishing it.
+Analysis and running time it is an issue, specially, in programs where the codebases are larger such as the Closure Compiler.
+Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.
 

### 2019-04-18 rebuttal.md
spellchecker

@@
 ### Review 210912:
-
-**issue 4:** 
-Explain why it can be worse.
-> I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5? I would assume that taking care of more statements should improve debugging performance.
 
@@
 As the title states, we intend to demystify the combination of Dynamic Slicing with Spectrum-based Fault Localization.
-Previous research have already shown impact and importance of both techniques - combined and separated.
+Previous research has already shown the impact and importance of both techniques - combined and separated.
 However, from the studies available about combining these two techniques, it was not yet clear if DS could help SBFL on obtaining more accurate results and how great would that improvement be.
@@
 
-We have not address the limitation regarding programs and generalization. Thus, we will fix and add this discussion to Threats to Validity.
+We have not addressed the limitation regarding programs and generalization. Thus, we will fix and add this discussion to Threats to Validity.
 
@@
 
-_The results k=10 suffer a decrease because the slicer is evaluating 10 full classes instead of only 5.
-For each k, we evaluate if at least one of the buggy-lines of the k classes is on the slicer report.
-When the 10 classes (k=10) of fault are evaluated, there might be some of the buggy-lines that were not taken into account for k=5 that are being evaluated now and are not found in the report._ (!!
-not finished yet)
+In commons-lang, the performance of capturing faulty statements of k=10 should be equal to k=5 or higher.
+The 100% cases for k=5 include two faults of omission (limitation mentioned in RQ3) which were not filtered when the report was retrieved.
+We apologize for that, the mistake has been fixed.
 
-These techniques have a few pratical limitations.
-We can only ensure that the proposed technique will work with defects4j programs because we generalized our function of interess according with the type of failling tests messages that exist on the dataset.
-Thus, some messages with very specific characteristics may not provide valide results.
-However, we intend to make clear what type of observed faults the tools is able to evaluate and turn the tool open-source after publishing it.
-Analysis and running time it is an issue, specially, in programs where the codebases are larger such as the Closure Compiler.
+These techniques have a few practical limitations.
+We can only ensure that the proposed technique will work with defects4j programs because we generalized our function of interest according to the type of failing tests messages that exist on the dataset.
+Thus, some messages with very specific characteristics may not provide valid results.
+However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing it.
+Analysis and running time it is an issue, especially, in programs where the codebases are larger such as the Closure Compiler.
 Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.
-
 ### Review 252039:
@@
 
-We agree that our "theorems" are rather claims/observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed on the paper.
+We agree that our "theorems" are rather claims/observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed in the paper.
 
 Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true.
-For now we decided to only focus on the ranking algorithm that provided the best results in previous research - ochiai.
+For now, we decided to only focus on the ranking algorithm that provided the best results in previous research - Ochiai.
 To answer the reviewer question precisely, the present work needs to be extended.
-We plan to investigate the veracity of claim 2 using other ranking algorithms, such as, Tarantula, Op2, Barinel and etc.
-This, however remains for future work.
+We plan to investigate the veracity of claim 2 using other ranking algorithms, such as Tarantula, Op2, Barinel and etc.
+This, however, remains for future work.
 
-Our focus in the paper was to show that dynamic slicing may considerable improve SBFL (we found an improvement of 73.7%).
-We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity and scalability.
+Our focus in the paper was to show that dynamic slicing may considerably improve SBFL (we found an improvement of 73.7%).
+We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity, and scalability.
 Our idea was that if we were able to show that CS works, then later we could leverage more accurate slicing techniques to improve our results.
-It is also important to notice that the numbers of tools implementing this type of techniques is very small.
+It is also important to notice that the numbers of tools implementing this type of technique is very small.
 However, we will explore this in more detail in the future.
@@
 
-As we mention in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner in previous research have demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization.
+As we mentioned in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner has demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization.
 MBDS is a well-known approach that has been proposed by the diagnosis community.
-This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults.
-We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.
+This community develops algorithms and techniques that leverage AI to determine the root cause of observed faults.
+We agree that this paper will be a good suit in software engineering, validation, and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.

### 2019-04-18 rebuttal.md
pass

@@
 Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.
+
 ### Review 252039:
@@
 
-We will make sure that the paper's formality will be improved and that the minor issues will be addressed.
-We will definitely explore the statistical machine learning approach in future work.
-Thank you for the hint!
+We will ascertain that the paper's formality will be improved as well as the minor issues will be addressed. Exploring the statistical machine learning approach remains as future work.
 
@@
 
-We agree that our "theorems" are rather claims/observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed in the paper.
+We agree that the "theorems" are rather claims/observations or properties of the ranking algorithm. Following the suggestion of one of reviewers, we will rename them as "claims".
 
-Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true.
+Regarding the question whether claim 2 is also valid for other ranking algorithms, there is a possibility this might not be true.
 For now, we decided to only focus on the ranking algorithm that provided the best results in previous research - Ochiai.
-To answer the reviewer question precisely, the present work needs to be extended.
-We plan to investigate the veracity of claim 2 using other ranking algorithms, such as Tarantula, Op2, Barinel and etc.
+To answer the reviewer question accurately, the present work needs to be extended.
+We plan to investigate the veracity of claim 2 using other ranking algorithms, such as Tarantula, Op2, Barinel.
 This, however, remains for future work.
 
-Our focus in the paper was to show that dynamic slicing may considerably improve SBFL (we found an improvement of 73.7%).
+The focus of the paper is to show that dynamic slicing considerably improves SBFL (we found an improvement of 73.7%).
 We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity, and scalability.
-Our idea was that if we were able to show that CS works, then later we could leverage more accurate slicing techniques to improve our results.
-It is also important to notice that the numbers of tools implementing this type of technique is very small.
-However, we will explore this in more detail in the future.
+We argue that if we are able to show that CS works, then the results could be further improved by using more accurate slicing techniques.
+It is also important to notice that the numbers of tools implementing slicing is rather limited.
 
@@
 As we mentioned in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner has demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization.
-MBDS is a well-known approach that has been proposed by the diagnosis community.
-This community develops algorithms and techniques that leverage AI to determine the root cause of observed faults.
-We agree that this paper will be a good suit in software engineering, validation, and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.
+MBDS is a well-known approach that has been proposed by the diagnosis community, an AI sub-community.
+We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience, since we are applying an AI-based technique to improve SBFL.

### 2019-04-18 rebuttal.md
another pass

@@
 
-As the title states, we intend to demystify the combination of Dynamic Slicing with Spectrum-based Fault Localization.
-Previous research has already shown the impact and importance of both techniques - combined and separated.
-However, from the studies available about combining these two techniques, it was not yet clear if DS could help SBFL on obtaining more accurate results and how great would that improvement be.
-Thus, we find that our research questions and results might be important to guide researchers on performing research based on the combination of both techniques.
+This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL.
+There are previous works which show the value of combining both techniques.
+However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults.
+The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.
 
-We have not addressed the limitation regarding programs and generalization. Thus, we will fix and add this discussion to Threats to Validity.
+We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable.
+We will improve our discussion in the Threats to Validity section regarding this issue.
 
-In table 3, we present the results for dynamic slicing alone whereas in table 4 we present the results of SFL vs.
+In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs.
 Tandem-FL for each k.
@@
 Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k.
-We understand that this might create some confusion.
-Thus, we will try to improve it.
+We understand that this might create some confusion, and will be clarified.
 
@@
 
-As we mentioned in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner has demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization.
-MBDS is a well-known approach that has been proposed by the diagnosis community, an AI sub-community.
+As we mentioned in section 2, a previous studies have demonstrated that Model-based software diagnosis can be framed as dynamic slicing.
+This is a well-known approach that has been proposed by the diagnosis community, an AI sub-community.
 We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience, since we are applying an AI-based technique to improve SBFL.

### 2019-04-18 rebuttal.md
another pass

@@
 These techniques have a few practical limitations.
-We can only ensure that the proposed technique will work with defects4j programs because we generalized our function of interest according to the type of failing tests messages that exist on the dataset.
+We can only ensure that the proposed technique will work with Defects4j programs because we generalized our function of interest according to the type of failing tests messages that exist on the dataset.
 Thus, some messages with very specific characteristics may not provide valid results.

### 2019-04-18 rebuttal.md
another pass

@@
 
+[very problematic/confusing]
 In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs.
@@
 
+[Problematic Text: this leads to a reject! No apologies.]
 In commons-lang, the performance of capturing faulty statements of k=10 should be equal to k=5 or higher.

### 2019-04-19 rebuttal.md
another pass
polishing

--- 2019-04-18 rebuttal.md
@@
 
+Table 3 and 4 are the different present different views to answer RQ2.
+
 In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs.
@@
 
-In commons-lang, the performance of capturing faulty statements of k=10 should be equal to k=5 or higher.
-The 100% cases for k=5 include two faults of omission (limitation mentioned in RQ3) which were not filtered when the report was retrieved.
-We apologize for that, the mistake has been fixed.
+We double-checked the empirical results and the decrease observed in table 3 and 4 for commons-lang is a typo.
+The percentage of faults for k=5 is also 96.9%.
+We have double-checked all other values, they stand correct.
+This will be fixed.
 

### 2019-04-19 rebuttal.md
polishing

@@
 
-Table 3 and 4 are the different present different views to answer RQ2.
-
-In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs.
-Tandem-FL for each k.
-Dynamic slicing in table 3 is the same as Tandem-FL in table 4.
-Thus, the values are the same.
-We only presented the same results in different views.
-On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's.
-Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k.
-We understand that this might create some confusion, and will be clarified.
+Table 3 and 4 are present different views to answer RQ2. [missing 2nd part of DS vs Tandem-FL and DS being a set]
 

### 2019-04-19 rebuttal.md
polishing
another pass

@@
 
-We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable.
+We agree with the reviewer that the conclusions we can draw from our empirical study is limited to the used programs and therefore the generalization is always questionable.
 We will improve our discussion in the Threats to Validity section regarding this issue.
 
-Table 3 and 4 are present different views to answer RQ2. [missing 2nd part of DS vs Tandem-FL and DS being a set]
+Table 3 and 4 present different views to answer RQ2, and should be clarified.
+As dynamic slicing produces a set, hence not being possible to select the top-k components, what is reported in Table 3 is Tandem-FL.
+Our decision to call it dynamic slicing alone was unfortunate and leads to confusion.
+Perhaps the best is to only include current table 4.
 
-We double-checked the empirical results and the decrease observed in table 3 and 4 for commons-lang is a typo.
+After double-checking the empirical results, the decrease in table 3 and 4 for commons-lang is due to a typo.
 The percentage of faults for k=5 is also 96.9%.
-We have double-checked all other values, they stand correct.
+Further, we double-checked all other values, they stand correct.
 This will be fixed.
 
-These techniques have a few practical limitations.
-We can only ensure that the proposed technique will work with Defects4j programs because we generalized our function of interest according to the type of failing tests messages that exist on the dataset.
-Thus, some messages with very specific characteristics may not provide valid results.
-However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing it.
-Analysis and running time it is an issue, especially, in programs where the codebases are larger such as the Closure Compiler.
+It is a fact that the implementation of our approach does not come without practical limitations.
+We can only ensure that the current implementation works with Defects4j programs only because we generalized our function of interest according to the type of failing messages that exist on the dataset.
+Thus, some messages with specific characteristics may not provide valid results in other datasets.
+However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing the paper.
+Analysis and running time may be an issue, especially, in programs where the codebases are rather large.
 Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

### 2019-04-19 rebuttal.md
another pass

@@
 
-We agree with the reviewer that the conclusions we can draw from our empirical study is limited to the used programs and therefore the generalization is always questionable.
+We agree with the reviewer that the conclusions we can draw from our empirical study are limited to the used programs and therefore the generalization is always questionable.
 We will improve our discussion in the Threats to Validity section regarding this issue.
 
-Table 3 and 4 present different views to answer RQ2, and should be clarified.
+Table 3 and 4 show different views we thought were adequate to answer RQ2, but we realize that they should be further clarified.
 As dynamic slicing produces a set, hence not being possible to select the top-k components, what is reported in Table 3 is Tandem-FL.
@@
 Further, we double-checked all other values, they stand correct.
-This will be fixed.
+This will be clarified.
 

### 2019-04-19 rebuttal.md
another pass

@@
 
-We will ascertain that the paper's formality will be improved as well as the minor issues will be addressed. Exploring the statistical machine learning approach remains as future work.
+We will ascertain that the paper's formality will be improved as well as the minor issues will be addressed. Exploring the statistical machine learning approach remains as future work, though.
 
@@
 
-As we mentioned in section 2, a previous studies have demonstrated that Model-based software diagnosis can be framed as dynamic slicing.
-This is a well-known approach that has been proposed by the diagnosis community, an AI sub-community.
-We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience, since we are applying an AI-based technique to improve SBFL.
+As we mentioned in section 2, previous studies have demonstrated that Model-based software diagnosis (MBSD) can be framed as dynamic slicing.
+MBSD is a well-known approach that has been proposed by the diagnosis community, an AI sub-community.
+We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience.

### 2019-04-19 rebuttal.md
another pass
Update rebuttal.md
updating review one. please check.

@@
 
-We kindly thank the reviewer for the comments and questions raised on our work.
+Thank you for the constructive review.
 
-This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL.
-There are previous works which show the value of combining both techniques.
-However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults.
-The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.
+This paper is not intended to propose a new approach, but, instead, to reassess the impact of an existing approach that combines dynamic slicing and Spectrum-based Fault Localization.
+Previous works show the effect of combining both techniques.
+However, results were inconclusive---they used rather small programs (because of limitations on their infrastructure), small number of faults, and evaluation metrics that can inflate diagnosis performance.
+The central contribution of our paper is to demonstrate that combining both techniques work for real and large programs.
 
-We agree with the reviewer that the conclusions we can draw from our empirical study are limited to the used programs and therefore the generalization is always questionable.
+We agree with the reviewer that the conclusions we can draw from our empirical study are limited to the used programs and therefore generalization is always questionable.
 We will improve our discussion in the Threats to Validity section regarding this issue.
 
-Table 3 and 4 show different views we thought were adequate to answer RQ2, but we realize that they should be further clarified.
-As dynamic slicing produces a set, hence not being possible to select the top-k components, what is reported in Table 3 is Tandem-FL.
+Tables 3 and 4 show different views we thought were adequate to answer RQ2, but we realize that they should be further clarified.
+Dynamic slicing produces a set of components (e.g., statements).
+As such, it is not possible to rank results and select the top-k components.
+For that reason, Table 3 reports the results of Tandem-FL.
 Our decision to call it dynamic slicing alone was unfortunate and leads to confusion.
@@
 
-After double-checking the empirical results, the decrease in table 3 and 4 for commons-lang is due to a typo.
+After double-checking the empirical results, we found that the decrease in value pointes on tables 3 and 4 for commons-lang is due to a typo.
 The percentage of faults for k=5 is also 96.9%.
-Further, we double-checked all other values, they stand correct.
+We double-checked all other values, and confirm that are correct.
 This will be clarified.
@@
 We can only ensure that the current implementation works with Defects4j programs only because we generalized our function of interest according to the type of failing messages that exist on the dataset.
-Thus, some messages with specific characteristics may not provide valid results in other datasets.
+This generalization does not cover all cases.
+Although this can be customized, as it is, lithium-slicer may not produce valid results in other datasets.
 However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing the paper.
-Analysis and running time may be an issue, especially, in programs where the codebases are rather large.
+Analysis and running time may be an issue, especially for programs where the codebases are rather large.
 Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

### 2019-04-19 rebuttal.md
Update rebuttal.md
shrink

@@
 
-Thank you for the constructive review.
+Thanks for the constructive review.
 
-This paper is not intended to propose a new approach, but, instead, to reassess the impact of an existing approach that combines dynamic slicing and Spectrum-based Fault Localization.
-Previous works show the effect of combining both techniques.
-However, results were inconclusive---they used rather small programs (because of limitations on their infrastructure), small number of faults, and evaluation metrics that can inflate diagnosis performance.
-The central contribution of our paper is to demonstrate that combining both techniques work for real and large programs.
+This paper is not intended to propose a new approach, but to reassess the impact of combining dynamic slicing and Spectrum-based Fault Localization.
+Previous works reported inconclusive results---they used rather small programs/faults (limitations on their infrastructure) and evaluation metrics that can inflate diagnosis performance.
+Our central contribution is to demonstrate that combining both techniques works for real/large programs.
 
-We agree with the reviewer that the conclusions we can draw from our empirical study are limited to the used programs and therefore generalization is always questionable.
+We agree that the conclusions drawn from our empirical study are limited to the programs used, hence questionable generalization.
 We will improve our discussion in the Threats to Validity section regarding this issue.
 
-Tables 3 and 4 show different views we thought were adequate to answer RQ2, but we realize that they should be further clarified.
+Tables 3-4 show views we thought were adequate to answer RQ2, but we realize that they should be clarified.
 Dynamic slicing produces a set of components (e.g., statements).
@@
 Our decision to call it dynamic slicing alone was unfortunate and leads to confusion.
-Perhaps the best is to only include current table 4.
+Perhaps the best is to only include table 4.
 
@@
 
-It is a fact that the implementation of our approach does not come without practical limitations.
-We can only ensure that the current implementation works with Defects4j programs only because we generalized our function of interest according to the type of failing messages that exist on the dataset.
+It is a fact that the implementation of our approach does not come without limitations.
+We only ensure that the current implementation works with Defects4j programs because we generalized the function of interest given the failing observed.
 This generalization does not cover all cases.
@@
 The focus of the paper is to show that dynamic slicing considerably improves SBFL (we found an improvement of 73.7%).
-We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity, and scalability.
+We decided to start with a very simple approach (critical slicing) for its generality, simplicity, and scalability.
 We argue that if we are able to show that CS works, then the results could be further improved by using more accurate slicing techniques.

### 2019-05-12 paper/ijcai/rebuttal.md
ijcai final rebuttal

--- 2019-04-19 rebuttal.md
@@
 This paper is not intended to propose a new approach, but to reassess the impact of combining dynamic slicing and Spectrum-based Fault Localization.
-Previous works reported inconclusive results---they used rather small programs/faults (limitations on their infrastructure) and evaluation metrics that can inflate diagnosis performance.
+Previous works reported inconclusive results---they used rather small programs (infrastructure limitations) and evaluation metrics that can inflate diagnosis performance.
 Our central contribution is to demonstrate that combining both techniques works for real/large programs.
-
-We agree that the conclusions drawn from our empirical study are limited to the programs used, hence questionable generalization.
-We will improve our discussion in the Threats to Validity section regarding this issue.
+We agree that the conclusions drawn from our empirical study are limited to the programs used, hence questionable generalization. We will improve our discussion in the Threats to Validity section.
 
 Tables 3-4 show views we thought were adequate to answer RQ2, but we realize that they should be clarified.
-Dynamic slicing produces a set of components (e.g., statements).
+Dynamic slicing produces a set of components.
 As such, it is not possible to rank results and select the top-k components.
@@
 
-After double-checking the empirical results, we found that the decrease in value pointes on tables 3 and 4 for commons-lang is due to a typo.
+After double-checking the empirical results, we found that the decrease in tables 3-4 for commons-lang is due to a typo.
 The percentage of faults for k=5 is also 96.9%.
-We double-checked all other values, and confirm that are correct.
+All other values were confirmed and are correct.
 This will be clarified.
 
-It is a fact that the implementation of our approach does not come without limitations.
-We only ensure that the current implementation works with Defects4j programs because we generalized the function of interest given the failing observed.
-This generalization does not cover all cases.
+The implementation of our approach does not come without limitations.
+We only ensure that the current implementation works with Defects4j programs because we generalized the function of interest given the failing observed, which does not cover all cases.
 Although this can be customized, as it is, lithium-slicer may not produce valid results in other datasets.
-However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing the paper.
-Analysis and running time may be an issue, especially for programs where the codebases are rather large.
-Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.
+We intend to clarify what type of observed faults the tool is able to evaluate and turn it open-source after publication.
+Analysis and running time may be an issue, especially for programs where the codebases are rather large which can be softened through the application of parallel programming to dynamic slicing.
 

### 2019-05-12 paper/ijcai/paper.tex
minor fixes
todo list of fixes for camera ready added

@@
 
-% Single author syntax
+% É esta a ordem? Se não for alterem.
 \author{
-    Submission 6364
+Sofia Reis$^1$
+\and
+Rui Abreu$^1$\and
+Marcelo D'Amorim$^2$\affiliations
+$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
+\emails
+sofia.o.reis@tecnico.ulisboa.pt,
+rui@computer.org\\
+$^2$Federal University of Pernambuco, Brazil\\
+\emails
+damorim@cin.ufpe.br
 }
-\iffalse
-\author{
-First Author$^1$
-\and
-Second Author$^2$\and
-Third Author$^{2,3}$\And
-Fourth Author$^4$
-\affiliations
-$^1$First Affiliation\\
-$^2$Second Affiliation\\
-$^3$Third Affiliation\\
-$^4$Fourth Affiliation
-\emails
-\{first, second\}@example.com,
-third@other.example.com,
-fourth@example.com
-}
-\fi
 
@@
 \begin{table}[h]
-	\vspace{-0.2cm}
 	\small
@@
   \label{table:fsws}
-\vspace{-0.4cm}
 \end{table}
@@
 
-\subsection{Threats to validity}
+\subsection{Threats to Validity}
 %
@@
 
-%
-%\section*{Acknowledgments}
-%include only after review.
+\section*{Acknowledgments}
+
 {

### 2019-05-12 paper/ijcai/paper.tex
added link to the tool + theorem1 -> claim 1 fixed

@@
 \usepackage{ijcai19}
-% The file ijcai18.sty is the style file for IJCAI-18 (same as ijcai08.sty).
 
@@
 
-\hypersetup{draft}
+%\hypersetup{draft}
 \begin{document}
@@
 iterations. Proofs of the algorithm complexity can be found
-elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed \today)}. Our implementation is publicly
-available at \textit{$<$anonymized for double-blind review$>$}.
-
-\begin{theorem}\label{the:1}
+elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
+(Accessed \today)}. Our implementation is publicly available at 
+\url{https://github.com/damorim/lithium-slicer}.
+
+\begin{namedthm}{Claim}\label{claim:1}
   The faulty statement may not be included in the critical slice of
   failing test cases.
-\end{theorem}
+\end{namedthm}
 
@@
 
-\begin{theorem}
+\begin{namedthm}{Claim}\label{claim:2}
   The rank of faulty statements cannot decrease if the slice includes
   the faulty statements.
-\end{theorem}
+\end{namedthm}
 
@@
 techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of missing
-faulty statements (see Theorem~\ref{the:1}). Developers would
+faulty statements (see Claim~\ref{claim:1}). Developers would
 not be able to successfully debug code for the cases that issue is

### 2019-05-14 paper/ijcai/paper.tex
acks
small fixes

@@
 Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
-cases where the predicate $\Delta{}C>0$ holds, \ie{}, it focuses only
-on the cases \combpar{k} outperformed the baseline technique.
+cases where the predicate $\Delta{}C>=0$ holds, \ie{}, it focuses only
+on the cases where \combpar{k} outperformed the baseline technique in at least one $k$.
 To sum, although we observed a relatively small number of cases where $\Delta{}C$
@@
 shows the statistical significance of the difference in diagnostic
-accuracy amongst the different techniques--the lighter color and
-smaller value of $p$ indicates higher significance. Based on these
-results, it is possible to determine with $95\%$ confidence that the
-performance of each pair of techniques is different.
+accuracy amongst the different techniques--the lighter color means no
+statistical significance and smaller values of $p$ indicates higher significance. 
+Based on these results, it is possible to determine with $95\%$ confidence that the
+performance of each pair of techniques is different (except for \combpar{5} 
+versus \combpar{10}, where there is no significance).
 
@@
 
+This material is based upon work supported by Fundação para a Ciência e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017.
+
 {

### 2019-05-17 paper/pldi/R/stacked-density.r
folders structure

@@ -1,34 +1,0 @@
-library("ggplot2")
-
-names <- c("commons-lang", "jfreechart", "jodatime", "mockito")
-
-suffixes <- c("-onefailingtest-filtering", "-allfailingtest-filtering", "-allfailingtest", "-onefailingtest")
-
-for (name in names) {
-    for (suffix in suffixes) {
-        # loading file
-        filename <- paste(name, suffix, sep="")
-        mydata <- read.table(paste(filename, ".dat", sep=""), header=TRUE)
-            
-        # rendering plot
-        p <- ggplot(mydata, aes(n, topn, group=slicing))+
-        geom_step()+
-        geom_point(aes(colour=slicing))+
-        annotate("text",x=min(mydata$n)+30,y=min(mydata$topn)+2,hjust=.2,label=name)+
-        scale_x_continuous(breaks = seq(min(mydata$n), max(mydata$n), 20), limits = c(min(mydata$n), max(mydata$n))) +
-        # scale_y_continuous(breaks = seq(0, 100, 20), limits = c(0, 100)) +
-        theme(legend.position=c(.9,.15)) +
-        theme(axis.text.x = element_text(size=9))  +
-        theme(axis.text.y = element_text(size=9))  
-        
-        
-        p <- p + geom_vline(xintercept=10, color="red")
-
-        # saving plot to file
-        update_geom_defaults("point", list(size=1))
-        theme_set(theme_grey(base_size=6))
-        pdf(paste(filename, ".pdf", sep=""), width=3, height=2)
-        print(p)
-        graphics.off()
-    }
-}

### 2019-05-17 paper/pldi/figures/example1.java

@@ -1,12 +1,0 @@
-|   | input a;  /* input for a is 7 */
-|   | x = 0;
-| | | j = 5;
-| |   a = a - 10; /* should a = a + 10; */
-| |   if (a > j) {
-        x = x + 1;
-      }
-|     else {
-|       z = 0;
-|     }
-| | | x = x + j;
-| | | print x;   /* x is 5, but should be 6 */

### 2019-05-30 paper/IJCAI19/paper.tex
folders structure
small fixes

--- 2019-05-14 paper/ijcai/paper.tex
@@
 
-% É esta a ordem? Se não for alterem.
 \author{
@@
 seen as complementary. This paper reports on a comprehensive
-study\comments{--using \numFaults{} documented software faults from a credible
-dataset--} to reassess the effects of combining \ds{} with \sfl{}.  With this
+study to reassess the effects of combining \ds{} with \sfl{}.  With this
 combination, components that are often involved in failing but seldom in passing
@@
 	\end{tabular}
-	\caption {Dynamic Slicing performance on capturing faulty statements, as
+	\caption {\combpar{k} performance on capturing faulty statements, as
      percentages. Higher is better.}
@@
 
-The dataset and tools (Lithium slicer and \comb{}) will be made
-available once double-blind requirements are lifted.
-
 %% the
@@
 
-This material is based upon work supported by Fundação para a Ciência e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017.
+This material is based upon work supported by Fundação para a Ciência 
+e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017. The work
+reported in this article was supported by national funds through Fundação
+para a Ciência e a Tecnologia (FCT) with reference UID/CEC/50021/2019.
 

### 2019-05-30 paper/IJCAI19/paper.tex
refs and acks

@@
 This material is based upon work supported by Fundação para a Ciência 
-e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017. The work
-reported in this article was supported by national funds through Fundação
-para a Ciência e a Tecnologia (FCT) with reference UID/CEC/50021/2019.
+e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017, and by national funds also through FCT with reference UID/CEC/50021/2019.
 

### 2019-06-01 paper/IJCAI19/paper.tex
acks
cr ready

@@
 \begin{itemize}
- \item[1)]~an empirical study, using
-real-world applications and bugs, on the combination of \ds{} and
-\sfl{} for bug localization of \emph{Java} faulty programs and
-\item[2)]~a
-tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination.
+ \item[1)]An empirical study, using
+real-world applications and bugs, on the combination of \ds{}-\sfl{} for bug localization of \emph{Java} faulty programs.
+\item[2)]A
+tool\footnote{Tool and dataset available at/through \url{https://github.com/damorim/lithium-slicer} (Accessed \today)}, dubbed \comb{}, implementing the \ds{}-\sfl{} combination. 
 \end{itemize}
-The
-tool as well as a replication package will be available once
-double-blind requirements are lifted.
 
@@
 elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
-(Accessed \today)}. Our implementation is publicly available at 
-\url{https://github.com/damorim/lithium-slicer}.
+(Accessed \today)}.
 
@@
 considered because we were unable to reproduce them in our
-environment.
-
-\lang{} is a library providing utility functions for the
+environment. \lang{} is a library providing utility functions for the
      {\small\texttt{java.lang}} API. \cmath{} is a library of
@@
 
-        \lang{}            & 100.0 & 96.9\\
+        \lang{}            & 96.9 & 96.9\\
         \cmath{}           & 89.4 & 95.2\\
@@
 		\midrule
-		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
+		 \lang{}         &   84.6   & 96.9 & 84.6 & 96.9  \\
 		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
@@
 		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
-		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
+		Total         & 79.6 & 86.5 & 83.5 & 90.4\\
 		\bottomrule
@@
 		\centering
-		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
+		\includegraphics[width=0.45\textwidth]{figures/performance.png}
 		\vspace{-0.4cm}
@@
 		\centering
-		\includegraphics[width=0.45\textwidth]{figures/boxplot.pdf}
+		\includegraphics[width=0.45\textwidth]{figures/boxplot.png}
 		\vspace{-0.4cm}
@@
 relative to the dataset including all faults.
-
-%% These results show that \ds{}
-%% improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
-%% the average ranking of all faulty statements, when considering
-%% $k=10$.
-
 We observe the following when considering the faults which can benefit
@@
 \begin{figure}[h]
-	\vspace{-1cm}
-		\includegraphics[width=0.48\textwidth]{figures/heatmap_nemenyi_result.pdf}
+	\vspace{-2cm}
+		\includegraphics[width=0.48\textwidth]{figures/heatmap_seg_result.png}
 		\caption{Siegel post-hoc analysis results}

### 2019-06-18 paper/IJCAI19/paper.tex
ijcai editor mandatory reviews

@@
 \usepackage{latexsym}
+\urlstyle{rm}
 
@@
 Rui Abreu$^1$\and
-Marcelo D'Amorim$^2$\affiliations
+Marcelo d'Amorim$^2$\affiliations
 $^1$IST, University of Lisbon \& INESC-ID, Portugal\\
+$^2$Federal University of Pernambuco, Brazil\\
 \emails
 sofia.o.reis@tecnico.ulisboa.pt,
-rui@computer.org\\
-$^2$Federal University of Pernambuco, Brazil\\
-\emails
-damorim@cin.ufpe.br
+rui@computer.org; damorim@cin.ufpe.br\\
 }
 
-%\hypersetup{draft}
 \begin{document}
@@
 by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
-iterations. Proofs of the algorithm complexity can be found
-elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
-(Accessed \today)}.
+iterations. % Proofs of the algorithm complexity can be found
+% elsewhere\footnote{Lithium complexity available at \mbox{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md}
+% (Accessed \today)}.
 
@@
 following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$
-of $M$ system \emph{components}\footnote{A
-component can be any code artifact of arbitrary granularity
+of $M$ system \emph{components}\footnote{A component can be any code artifact of arbitrary granularity
 such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.};
@@
 
-\begin{figure}[t!]
-
+\begin{figure}[tb]
   \centering
@@
 
-\begin{table}[h]
+\begin{table}[tb]
   \small
@@
 
-\subsubsection{\label{rq:1}RQ1: \textit{\rqone}}
+\subsubsection{\label{rq:1}RQ1: \rqone}
 
@@
 
-\subsubsection{RQ2: \textit{\rqtwo}}
+\subsubsection{RQ2: \rqtwo}
 \label{rq:2}
@@
 
-\begin{table}[h]
+\begin{table}[tb]
 	\small
@@
 
-\subsubsection{RQ3: \textit{\rqthree}}
+\subsubsection{RQ3: \rqthree}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[tb]
 		\centering
-		\includegraphics[width=0.45\textwidth]{figures/performance.png}
+		\includegraphics[width=0.42\textwidth]{figures/performance.png}
 		\vspace{-0.4cm}
@@
 
-\begin{figure}[h]
+\begin{figure}[tb]
 		\vspace{-0.2cm}
 		\centering
-		\includegraphics[width=0.45\textwidth]{figures/boxplot.png}
+		\includegraphics[width=0.42\textwidth]{figures/boxplot.png}
 		\vspace{-0.4cm}
-
 		\caption{Distributions of $\Delta{}C$ considering all cases where \combpar{k}
@@
 
-\begin{table}[h]
-	\tiny
+\begin{table}[tb]
+    \begin{adjustwidth}{-.5in}{-.5in}
+
+	\scriptsize
 	\centering
@@
   \label{table:st}
+  \end{adjustwidth}
 \end{table}
@@
 
-\begin{figure}[h]
+\begin{figure}[tb]
 	\vspace{-2cm}
-		\includegraphics[width=0.48\textwidth]{figures/heatmap_seg_result.png}
+		\includegraphics[width=0.5\textwidth]{figures/heatmap_seg_result.png}
 		\caption{Siegel post-hoc analysis results}
 		\label{fig:performance}
-		\vspace{-0.3cm}
+		\vspace{-0.2cm}
 \end{figure}
@@
 This material is based upon work supported by Fundação para a Ciência 
-e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017, and by national funds also through FCT with reference UID/CEC/50021/2019.
+e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017, and by 
+national funds also through FCT with reference UID/CEC/50021/2019.
+This research was partially funded by INES 2.0, FACEPE grants PRONEX 
+APQ 0388-1.03/14 and APQ-0399-1.03/17, and CNPq grant 465614/2014-0.
 
 {
-  \small
-  \balance
   \bibliographystyle{named}

### 2019-06-18 paper/IJCAI19/paper.tex
closes #5#

@@
 \and
-Rui Abreu$^1$\and
+Rui Abreu$^1$ \textnormal{and}
 Marcelo d'Amorim$^2$\affiliations

### 2019-07-04 paper/IJCAI19/paper.tex
fixes of the last editorial feedback

--- 2019-06-18 paper/IJCAI19/paper.tex
@@
 \author{
-Sofia Reis$^1$
+Sofia Reis$^{1,2}$
 \and
-Rui Abreu$^1$\and
-Marcelo d'Amorim$^2$\affiliations
-$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
-$^2$Federal University of Pernambuco, Brazil\\
+Rui Abreu$^{1,2}$ \textnormal{and}
+Marcelo d'Amorim$^3$\affiliations
+$^1$IST, University of Lisbon, Portugal\\
+$^2$INESC-ID, Portugal\\
+$^3$Federal University of Pernambuco, Brazil\\
 \emails
@@
 
-\begin{wrapfigure}[8]{1}{0.25\textwidth}
+\begin{figure}[tb]
   \hspace{-2ex}
@@
   \label{fig:spectrum-example}
-\end{wrapfigure}
+\end{figure}
 
@@
 	\label{tab:red}
+	    \vspace{-2ex}
 \end{table}
+
 \normalsize
-
 \subsubsection{RQ2: \rqtwo}
@@
 		\label{fig:boxplot}
-		\vspace{-0.2cm}
+		\vspace{-0.3cm}
 \end{figure}
@@
   \end{adjustwidth}
+  \vspace{-2ex}
 \end{table}
@@
 \begin{figure}[tb]
-	\vspace{-2cm}
+	\vspace{-2.3cm}
 		\includegraphics[width=0.5\textwidth]{figures/heatmap_seg_result.png}
+		\vspace{-0.6cm}
 		\caption{Siegel post-hoc analysis results}
 		\label{fig:performance}
-		\vspace{-0.2cm}
+		\vspace{-0.4cm}
 \end{figure}

### 2019-07-04 app/generate_expected_msg.py
no need to add test case error messages to the data json file anymore

@@ -74,7 +74,7 @@ def generate_seed(project, bugnumber):
             bug_number = bug.replace(".json", "")
 
             # getting the expected message
-            expected_dir = 'expected/'+project_name+'/'
+            expected_dir = 'oracle/'+project_name+'/'
             if not os.path.exists(expected_dir):
                 os.makedirs(expected_dir)
             

### 2019-07-04 app/generate_inputs.py

@@ -5,7 +5,7 @@ from utils import json_to_dict, get_testname_expected_msg, call_cmd
 main = argparse.ArgumentParser()
 main.add_argument("--output", type=str, nargs=1, help="The output path to save the seed file")
 main.add_argument("--project", type=str, nargs=1, help="Project name")
-main.add_argument("--bugnumber", type=str, nargs=1, default="0", help="Number that represent a Bug in Project") # 0 corresponde to all
+main.add_argument("--bugnumber", type=str, nargs=1, default="0", help="Number that represent a Bug in Project") # 0 means all bugs
 main.add_argument("--files_per_bug", type=str, nargs=1, default="10", help="Max quantity of files per bug")
 
 args = main.parse_args()
@@ -92,15 +92,19 @@ def generate_seed(project, bugnumber, output):
                 classes = ",".join(classes) # converts [classA, classB] to classA,classB
             else:
                 classes = classes[0] # get only line
-
-            expected_dir = 'expected/'+project_name+'/'
+            
+            expected_dir = 'oracle/'+project_name+'/'
             expected_msg_path = expected_dir+bug_number
             
-            for test in data['failing']:
-                testcase = test['test']
-                seed_file.write(
-                        "{} {} {} {} {}\n".format(project, bug_number, testcase, classes, expected_msg_path)
-                    )
-
+            i = 0; f = 0; c = 0;
+            with open(expected_msg_path) as f:
+                failing = f.readlines()
+                for l in failing:
+                    if '---' in l:
+                        testcase = l.strip().split(' ')[1]
+                        seed_file.write(
+                                "{} {} {} {} {}\n".format(project, bug_number, testcase, classes, expected_msg_path)
+                            )
+                    
 generate_seed(project_name, bugs, output)
 

### 2019-07-04 app/get-expected-msg.sh

@@ -1,25 +1,0 @@
-#!/bin/bash
-
-# check if defects4j is installed
-command -v defects4j >/dev/null 2>&1 || { echo >&2 "defects4j not found.  Aborting."; exit 1; }
-
-if [ -z "$1" ];then
-    echo "The project name is empty. [Chart, Lang, Time, Mockito, Closure, Math]"
-    exit 1;
-elif [ -z "$2" ];then
-    echo "The bug number is empty. Use 0 to run all bugs, use a number (e.g. 5) to minimize the bug 5 or use a list of numbers (e.g. 1,3,5,10)"
-    exit 1;
-fi
-
-PROJECT=$1 # project name
-BUGS=$2 # bugs
-BASEPATH=$(pwd)
-
-for BUG in $(seq 1 $BUGS); do
-    gen_inputs=$(python3 generate_expected_msg.py --project "$PROJECT" --bugnumber "$BUG")
-    if [[ $gen_inputs == *"FAILED"* ]]; then
-        exit 1;
-    fi
-    echo "Bug $BUG - $PROJECT. Process finished."
-done
-

### 2019-07-04 app/runner.sh

@@ -9,6 +9,9 @@ if [ -z "$1" ];then
 elif [ -z "$2" ];then
     echo "The bug number is empty. Use 0 to run all bugs, use a number (e.g. 5) to minimize the bug 5 or use a list of numbers (e.g. 1,3,5,10)"
     exit 1;
+elif [ -z "$3" ];then
+    echo "The top-number is empty. Use an integer."
+    exit 1;
 fi
 
 PROJECT=$1 # project name
@@ -17,6 +20,17 @@ TOP=$3 # k from top-k
 BASEPATH=$(pwd)
 
 INPUTS="inputs-${PROJECT}_${BUG}_${TOP}" # data filename
+
+ORACLE_PATH="oracle/${PROJECT}/${BUG}"
+if [ ! -f "$ORACLE_PATH" ]; then
+	gen_expected_msg=$(python3 generate_expected_msg.py --project "$PROJECT" --bugnumber "$BUG")
+	if [[ $gen_expected_msg == *"FAILED"* ]]; then
+	    exit 1;
+	fi
+	echo "Test ${PROJECT}_${BUG} oracle extracted."
+else
+	echo "Test ${PROJECT}_${BUG} oracle was already extracted."
+fi
 
 # generates a document that contains the inputs to run the minimizer
 gen_inputs=$(python3 generate_inputs.py --project "$PROJECT" --output "$INPUTS" --bugnumber "$BUG" --files_per_bug "$TOP")

### 2019-07-04 app/utils.py

@@ -48,6 +48,7 @@ def get_relative_path(project, class_name, bug_number):
     class_name = class_name[index:]
 
     return class_name
+    
 
 def remove_comments(string):
     """ remove the comments in java file """
@@ -219,6 +220,7 @@ def get_to_compare(stacktrace, test):
             if re.search(r'.*Test(.*).java',stacktrace[i]):
                 break 
     return lines, buggy_line
+
 
 @timeout(timeout_seconds) # 60s at most (compile and run test)
 def call_cmd(cmd_line):
